### 2010-08-21 ms.tex
Initial commit.  Paper skeleton.

%\documentclass[apj,onecolumn]{emulateapj}
\documentclass[12pt,preprint]{aastex}

\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage[section] {placeins}
\bibliographystyle{apj}
\citestyle{apj}

%%%%%%%% Begin custom definitions %%%%%%%%%%%%%

\input macros.tex

%%%%%%%% End custom definitions %%%%%%%%%%

\begin{document}

\shorttitle{TRANSITION TO POPULATION II}
\shortauthors{WISE ET AL.}

\title{How Short Lived is the Population III Epoch?}

\author{John H. Wise\altaffilmark{1,2}, 
  Tom Abel\altaffilmark{3}, 
  Michael L. Norman\altaffilmark{4}}

\altaffiltext{1}{Department of Astrophysical Sciences, Princeton
  University, Peyton Hall, Ivy Lane, Princeton, NJ 08544}
\altaffiltext{2}{Hubble Fellow}
\altaffiltext{3}{Kavli Institute for Particle Astrophysics and
  Cosmology, Stanford University, Menlo Park, CA 94025}
\altaffiltext{4}{Center for Astrophysics and Space Sciences,
  University of California at San Diego, La Jolla, CA 92093}
\email{jwise@astro.princeton.edu}

\begin{abstract}

\end{abstract}

\keywords{cosmology --- methods: numerical --- hydrodynamics ---
  radiative transfer --- star formation}

\section{Motivation}

\acknowledgments

J.H.W. is supported by the Hubble Fellowship etc.  The majority of the
analysis and plots were done with \texttt{yt} \citep{yt}.

\clearpage
%\input biblio.tex
\bibliography{ms}

\end{document}

### 2010-08-24 ms.tex
First draft of introduction.  Wrote abstract without results.

@@
-%\documentclass[apj,onecolumn]{emulateapj}
-\documentclass[12pt,preprint]{aastex}
+\documentclass[apjl]{emulateapj}
+%\documentclass[12pt,preprint]{aastex}
 
@@
 \author{John H. Wise\altaffilmark{1,2}, 
-  Tom Abel\altaffilmark{3}, 
-  Michael L. Norman\altaffilmark{4}}
+  Michael L. Norman\altaffilmark{3},
+  Tom Abel\altaffilmark{4}}
 
@@
 \altaffiltext{2}{Hubble Fellow}
-\altaffiltext{3}{Kavli Institute for Particle Astrophysics and
+\altaffiltext{3}{Center for Astrophysics and Space Sciences,
+  University of California at San Diego, La Jolla, CA 92093}
+\altaffiltext{4}{Kavli Institute for Particle Astrophysics and
   Cosmology, Stanford University, Menlo Park, CA 94025}
-\altaffiltext{4}{Center for Astrophysics and Space Sciences,
-  University of California at San Diego, La Jolla, CA 92093}
 \email{jwise@astro.princeton.edu}
@@
 \begin{abstract}
+
+  Population III stars first form in dark matter halos with masses
+  around $10^6 \Ms$.  By definition, they are metal-free, and their
+  protostellar collapse is driven by molecular hydrogen cooling in the
+  gas-phase, leading to a massive characteristic mass $\sim 100~\Ms$
+  and suppressed fragmentation.  Population II stars with lower
+  characteristic masses form when the star-forming gas reaches a
+  critical metallicity of $10^{-6} - 10^{-3}~Z_\odot$, depending on
+  whether dust cooling is important.  We present adaptive mesh
+  refinement radiation hydrodynamics simulations that
+  self-consistently follow the transition from Population III to II
+  star formation.  We model stellar radiative feedback with adaptive
+  ray tracing.  A top-heavy initial mass function for the Population
+  III stars is considered, resulting in a plausible distribution of
+  pair-instability supernovae and associated metal enrichment.
+  \textbf{Add results.}
 
@@
 
+The first (Pop III) stars are metal-free and have a large
+characteristic mass and suppressed fragmentation in its protostellar
+collapse \citep{refs}.  A fraction of these stars enrich the
+surrounding intergalactic medium (IGM) when they go supernova, which
+can happen in stars $\lsim40~\Ms$ in Type II supernovae (SNe) or in
+stars roughly between 140 \Ms~and 260 \Ms~in pair-instability SNe
+\citep[PISNe;][]{Heger02}.  The host halo and the neighboring halos
+are then enriched with this ejecta.  There exists a critical
+metallicity that is $\sim 10^{-6} Z_\odot$ if dust cooling is
+efficient \citep{refs} and $\sim 10^{-3.5} Z_\odot$ otherwise
+\citep{refs}, where the gas can cool rapidly, lowering its Jeans mass.
+An intermediate characteristic mass of $\sim10~\Ms$ can be occur if
+the gas cooling is suppressed to the cosmic microwave background (CMB)
+temperature \citep{ref}.  The resulting Population II star cluster
+will thus have a lower characteristic stellar mass than its metal-free
+progenitors \citep{refs}.  In the local universe, stars in the Milky
+Way halo and dwarf spheroidal (dSph) galaxies may be connected to
+these first stellar clusters.  In the halo of the Milky Way, the most
+metal-poor stars have a metallicity floor of [Z/H] = ??? \citep{ref},
+and in dwarf spheroidal (dSph) galaxies this floor is a factor of 10
+higher \citep{refs}.
+
+The transition from Pop III to Pop II star formation is solely
+dependent on the propagation of metals from the SNe remnants into
+future sites of star formation.  Their flows are complex because of
+the interactions between the SN blastwave, cosmological accretion and
+halo mergers, and nearby stellar feedback.  In minihalos ($M_{\rm h}
+\sim 10^6~\Ms$), radiation from the massive Pop III drives a 30
+\kms~shock, which is 10 times greater than the escape velocity of the
+halo, and leaves behind a warm ($3 \times 10^4$ K) and diffuse (0.5
+\cubecm) medium \citep{refs}.  The latter feature aids in the
+expansion of the blastwave because it delays the transition to the
+Sedov-Taylor and snowplow phases.  In PISNe, approximately half of the
+metals stay in the IGM with an metal bubble size of a few kpc.  The
+remaining metals fall back into the host halo.  The blastwave may
+induce star formation in nearby halos through the compression of the
+gas \citep{refs}; however timescales for metal mixing into the dense
+gas are many dynamical times \citep{refs} for shock velocities $\lsim
+100~\kms$.
+
+Numerical simulations are useful to detangle and study these
+complexities and the transition from Pop III to II stars.  In this
+Letter, we present the simulations that include both types of star
+formation, its radiative feedback, and its SNe feedback.  We utilize
+an initial mass function (IMF) for individual Pop III stars, based on
+the latest simulation results.  The methods used here incorporate and
+link together recent results from metal-enriched and metal-free star
+formation, the critical metallicity, pair-instability supernovae, and
+fine-structure metal line cooling.  Furthermore we spatially
+distinguish metal enrichment from Pop II and Pop III stars as their
+abundance patterns differ significantly \citep{ref}.  This is the
+first time that all of these processes have been interconnected in a
+simulation that resolves minihalos to study the transition to Pop II
+star formation self-consistently.  We describe our simulation setup
+and our adopted star formation models in \S \ref{sec:setup} and
+present our results in \S \ref{sec:results}.  We discuss the
+implications of our findings and conclude in the last section.
+
+\section{Simulation Setup}
+\label{sec:setup}
+
+\section{Results}
+\label{sec:results}
+
+\section{Discussion and Summary}
+
 \acknowledgments
@@
 
-\clearpage
+%\clearpage
 %\input biblio.tex

### 2010-08-25 ms.tex
Started the method section.

@@
   Michael L. Norman\altaffilmark{3},
-  Tom Abel\altaffilmark{4}}
+  Tom Abel\altaffilmark{4},
+  Britton D. Smith \altaffilmark{5}}
 
@@
   Cosmology, Stanford University, Menlo Park, CA 94025}
+\altaffiltext{5}{Michigan State University}
 \email{jwise@astro.princeton.edu}
@@
 fine-structure metal line cooling.  Furthermore we spatially
-distinguish metal enrichment from Pop II and Pop III stars as their
-abundance patterns differ significantly \citep{ref}.  This is the
-first time that all of these processes have been interconnected in a
-simulation that resolves minihalos to study the transition to Pop II
+distinguish metal enrichment from Pop II and Pop III stars.  This is
+the first time that all of these processes have been interconnected in
+a simulation that resolves minihalos to study the transition to Pop II
 star formation self-consistently.  We describe our simulation setup
@@
 
-\section{Simulation Setup}
+\section{Method}
 \label{sec:setup}
+
+In this section, we first describe our simulation setup.  We then
+detail the star formation models used in these simulations and how we
+model stellar radiation and SNe feedback.
+
+\subsection{Simulation setup}
+
+We use the adaptive mesh refinement (AMR) code \enzo~\citep{refs} that
+employs our implementation of adaptive ray tracing for radiation
+transport \citep{refs}.  To resolve minihalos with at least 100 dark
+matter (DM) particles and follow the formation of the first generation
+of dwarf galaxies, we use a simulation box of 1 Mpc that has a
+resolution of $256^3$.  This gives us a DM mass resolution of 1840
+\Ms.  We refine the grid on baryon overdensities of $3 \times
+2^{-0.2l}$, where $l$ is the AMR level, resulting in a
+super-Lagrangian behavior.  We also refine on a DM overdensity of $3
+\times 2^l$ and always resolve the local Jeans length by at least 4
+cells.  The latter criterion avoids any artifical fragmentation during
+gaseous collapses \citep{Truelove97}.  We initialize the simulation
+with \textsl{grafic} \citep{Bertschinger01} at $z = ???$ and use the
+cosmological parameters from the 7-year WMAP data \citep{ref}:
+$\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h
+= 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$ with the variables having
+their usual definitions.
+
+We peform two simulations with the same initial conditions.  They
+differ only in that one considers primordial cooling, and the other
+considers additional cooling in metal-enriched gas.  For primordial
+cooling, we use a non-equilbrium chemistry solver with 9 species of
+hydrogen, helium, and molecular hydrogen.  For metal cooling, we use a
+cooling curve that is calculated from CLOUDY \citep{ref} and using the
+method of \citet{ref}.  It is tabulated based on density, temperature,
+electron fraction, and metallicity.
+
+\subsection{Star formation}
+
+Simulations have shown that the characteristic mass of Pop III stars
+$M_{\rm char} \sim 100~\Ms$.  They form in molecular clouds that
+coexist with the dark matter halo center with limited fragmentation
+occurring during their collapse; however \citet{Turk10} has recently
+shown that Pop III binaries may form in a fraction of such halos.
+Furthermore, detailed one-dimensional calculations have shown that
+their IMF should follow a Kroupa-like IMF that has a Salpeter slope at
+the high-mass end and an exponential cut-off below $M_{\rm char}$
+\citep{refs}.
+
+For Pop III stars, we use the same star formation model as
+\citet{Abel07} and \citet{Wise08_Gal} but now the stellar mass is
+randomly sampled from an IMF with a functional form of
+%
+\begin{equation}
+\label{eqn:imf}
+f(M)dM = ...
+\end{equation}
+%
+For reproducibility, we initialize both simulations with the same
+random seed and record the number of times the random number generator
+\citep[Mersenne twister;][]{ref} has been called.
+
+\subsection{Stellar feedback}
 

### 2010-09-01 ms.tex
Adding to the star formation section.

@@
 
-\shorttitle{TRANSITION TO POPULATION II}
+\shorttitle{POPULATION III STAR EPOCH}
 \shortauthors{WISE ET AL.}
@@
 
-We use the adaptive mesh refinement (AMR) code \enzo~\citep{refs} that
-employs our implementation of adaptive ray tracing for radiation
-transport \citep{refs}.  To resolve minihalos with at least 100 dark
-matter (DM) particles and follow the formation of the first generation
-of dwarf galaxies, we use a simulation box of 1 Mpc that has a
-resolution of $256^3$.  This gives us a DM mass resolution of 1840
-\Ms.  We refine the grid on baryon overdensities of $3 \times
-2^{-0.2l}$, where $l$ is the AMR level, resulting in a
-super-Lagrangian behavior.  We also refine on a DM overdensity of $3
-\times 2^l$ and always resolve the local Jeans length by at least 4
-cells.  The latter criterion avoids any artifical fragmentation during
-gaseous collapses \citep{Truelove97}.  We initialize the simulation
-with \textsl{grafic} \citep{Bertschinger01} at $z = ???$ and use the
-cosmological parameters from the 7-year WMAP data \citep{ref}:
-$\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h
-= 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$ with the variables having
-their usual definitions.
+We use the adaptive mesh refinement (AMR) code
+\enzo~\citep{BryanNorman97, OShea2004} that employs our implementation
+of adaptive ray tracing for radiation transport \citep{Wise11}.  To
+resolve minihalos with at least 100 dark matter (DM) particles and
+follow the formation of the first generation of dwarf galaxies, we use
+a simulation box of 1 Mpc that has a resolution of $256^3$.  This
+gives us a DM mass resolution of 1840 \Ms.  We refine the grid on
+baryon overdensities of $3 \times 2^{-0.2l}$, where $l$ is the AMR
+level, resulting in a super-Lagrangian behavior.  We also refine on a
+DM overdensity of $3 \times 2^l$ and always resolve the local Jeans
+length by at least 4 cells.  The latter criterion avoids any artifical
+fragmentation during gaseous collapses \citep{Truelove97}.  We
+initialize the simulation with \textsl{grafic} \citep{Bertschinger01}
+at $z = ???$ and use the cosmological parameters from the 7-year WMAP
+data \citep{ref}: $\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$,
+$\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$
+with the variables having their usual definitions.
 
@@
 cooling curve that is calculated from CLOUDY \citep{ref} and using the
-method of \citet{ref}.  It is tabulated based on density, temperature,
-electron fraction, and metallicity.
+method of \citet{2008MNRAS.385.1443S}.  It is tabulated based on
+density, temperature, electron fraction, and metallicity.
 
 \subsection{Star formation}
+
+We distinguish Pop II and Pop III star formation by the metallicity of
+the cold ($T < 10^3$ K) star forming gas in the molecular clouds.  Pop
+II stars are formed if [Z/H] $> -4$, and Pop III stars are formed
+otherwise.  We do not consider Pop III.2 stars and intermediate mass
+stars from CMB-limited cooling.
 
@@
 coexist with the dark matter halo center with limited fragmentation
-occurring during their collapse; however \citet{Turk10} has recently
-shown that Pop III binaries may form in a fraction of such halos.
-Furthermore, detailed one-dimensional calculations have shown that
-their IMF should follow a Kroupa-like IMF that has a Salpeter slope at
-the high-mass end and an exponential cut-off below $M_{\rm char}$
-\citep{refs}.
+occurring during their collapse; however \citet{2009Sci...325..601T}
+has recently shown that Pop III binaries may form in a fraction of
+such halos.  Furthermore, detailed one-dimensional calculations have
+shown that their IMF should follow a Kroupa-like IMF that has a
+Salpeter slope at the high-mass end and an exponential cut-off below
+$M_{\rm char}$ \citep{refs}.
 
 For Pop III stars, we use the same star formation model as
-\citet{Abel07} and \citet{Wise08_Gal} but now the stellar mass is
+\citet{Abel07} and \citet{Wise08_Gal} where each star particle
+represents a single star.  Instead of using a fixed stellar mass, we
 randomly sampled from an IMF with a functional form of
@@
 \label{eqn:imf}
-f(M)dM = ...
+f(M)dM = M^{-1.3} \exp\left[-\left(\frac{M_{\rm char}}{M}\right)^{1.6}\right]
 \end{equation}
 %
-For reproducibility, we initialize both simulations with the same
-random seed and record the number of times the random number generator
-\citep[Mersenne twister;][]{ref} has been called.
+to determine the stellar mass.  Above $M_{\rm char}$, it behaves as a
+Salpeter IMF but is exponentially cutoff below that mass
+\citep{Chabrier03, Clark09}.  For reproducibility, we initialize both
+simulations with the same random seed and record the number of times
+the random number generator \citep[Mersenne twister;][]{ref} has been
+called for use when restarting the simulations.
 

### 2010-09-01 ms.tex
Adding references.

@@
 characteristic mass and suppressed fragmentation in its protostellar
-collapse \citep{refs}.  A fraction of these stars enrich the
-surrounding intergalactic medium (IGM) when they go supernova, which
-can happen in stars $\lsim40~\Ms$ in Type II supernovae (SNe) or in
-stars roughly between 140 \Ms~and 260 \Ms~in pair-instability SNe
-\citep[PISNe;][]{Heger02}.  The host halo and the neighboring halos
-are then enriched with this ejecta.  There exists a critical
-metallicity that is $\sim 10^{-6} Z_\odot$ if dust cooling is
-efficient \citep{refs} and $\sim 10^{-3.5} Z_\odot$ otherwise
-\citep{refs}, where the gas can cool rapidly, lowering its Jeans mass.
-An intermediate characteristic mass of $\sim10~\Ms$ can be occur if
-the gas cooling is suppressed to the cosmic microwave background (CMB)
-temperature \citep{ref}.  The resulting Population II star cluster
-will thus have a lower characteristic stellar mass than its metal-free
-progenitors \citep{refs}.  In the local universe, stars in the Milky
-Way halo and dwarf spheroidal (dSph) galaxies may be connected to
-these first stellar clusters.  In the halo of the Milky Way, the most
-metal-poor stars have a metallicity floor of [Z/H] = ??? \citep{ref},
-and in dwarf spheroidal (dSph) galaxies this floor is a factor of 10
-higher \citep{refs}.
+collapse \citep{Abel00, ABN02, Bromm02, Yoshida03, OShea07a}.  A
+fraction of these stars enrich the surrounding intergalactic medium
+(IGM) when they go supernova, which can happen in stars $\lsim40~\Ms$
+in Type II supernovae (SNe) or in stars roughly between 140 \Ms~and
+260 \Ms~in pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}.
+The host halo and the neighboring halos are then enriched with this
+ejecta.  There exists a critical metallicity that is $\sim 10^{-6}
+Z_\odot$ if dust cooling is efficient \citep{refs} and $\sim 10^{-3.5}
+Z_\odot$ otherwise \citep{Bromm01, 2009ApJ...691..441S}, where the gas
+can cool rapidly, lowering its Jeans mass.  An intermediate
+characteristic mass of $\sim10~\Ms$ can be occur if the gas cooling is
+suppressed to the cosmic microwave background (CMB) temperature
+\citep{Larson, Tumlinson04, 2009ApJ...691..441S}.  The resulting
+Population II star cluster will thus have a lower characteristic
+stellar mass than its metal-free progenitors.  In the local universe,
+stars in the Milky Way halo and dwarf spheroidal (dSph) galaxies may
+be connected to these first stellar clusters.  In the halo of the
+Milky Way, the most metal-poor stars have a metallicity floor of [Z/H]
+= ???  \citep{ref}, and in dwarf spheroidal (dSph) galaxies this floor
+is a factor of 10 higher \citep{refs}.
 
@@
 halo, and leaves behind a warm ($3 \times 10^4$ K) and diffuse (0.5
-\cubecm) medium \citep{refs}.  The latter feature aids in the
-expansion of the blastwave because it delays the transition to the
-Sedov-Taylor and snowplow phases.  In PISNe, approximately half of the
-metals stay in the IGM with an metal bubble size of a few kpc.  The
-remaining metals fall back into the host halo.  The blastwave may
-induce star formation in nearby halos through the compression of the
-gas \citep{refs}; however timescales for metal mixing into the dense
-gas are many dynamical times \citep{refs} for shock velocities $\lsim
-100~\kms$.
+\cubecm) medium \citep{Kitayama04, Whalen04, Abel07}.  The latter
+feature aids in the expansion of the blastwave because it delays the
+transition to the Sedov-Taylor and snowplow phases.  In PISNe,
+approximately half of the metals stay in the IGM with an metal bubble
+size of a few kpc.  The remaining metals fall back into the host halo.
+The blastwave may induce star formation in nearby halos through the
+compression of the gas \citep{Ferrara98}; however timescales for metal
+mixing into the dense gas are many dynamical times \citep{Cen07} for
+shock velocities $\lsim 100~\kms$.
 
@@
 \enzo~\citep{BryanNorman97, OShea2004} that employs our implementation
-of adaptive ray tracing for radiation transport \citep{Wise11}.  To
+of adaptive ray tracing for radiation transport \citep{Wise10}.  To
 resolve minihalos with at least 100 dark matter (DM) particles and
@@
 hydrogen, helium, and molecular hydrogen.  For metal cooling, we use a
-cooling curve that is calculated from CLOUDY \citep{ref} and using the
-method of \citet{2008MNRAS.385.1443S}.  It is tabulated based on
+cooling curve that is calculated from CLOUDY \citep{CLOUDY} and using
+the method of \citet{2008MNRAS.385.1443S}.  It is tabulated based on
 density, temperature, electron fraction, and metallicity.

### 2010-09-07 ms.tex
Added some references and some sentences to Star Formation.

@@
 characteristic mass and suppressed fragmentation in its protostellar
-collapse \citep{Abel00, ABN02, Bromm02, Yoshida03, OShea07a}.  A
+collapse \citep{Abel00, ABN02, Bromm02_P3, Yoshida03, OShea07a}.  A
 fraction of these stars enrich the surrounding intergalactic medium
@@
 ejecta.  There exists a critical metallicity that is $\sim 10^{-6}
-Z_\odot$ if dust cooling is efficient \citep{refs} and $\sim 10^{-3.5}
-Z_\odot$ otherwise \citep{Bromm01, 2009ApJ...691..441S}, where the gas
-can cool rapidly, lowering its Jeans mass.  An intermediate
-characteristic mass of $\sim10~\Ms$ can be occur if the gas cooling is
-suppressed to the cosmic microwave background (CMB) temperature
-\citep{Larson, Tumlinson04, 2009ApJ...691..441S}.  The resulting
-Population II star cluster will thus have a lower characteristic
-stellar mass than its metal-free progenitors.  In the local universe,
-stars in the Milky Way halo and dwarf spheroidal (dSph) galaxies may
-be connected to these first stellar clusters.  In the halo of the
-Milky Way, the most metal-poor stars have a metallicity floor of [Z/H]
-= ???  \citep{ref}, and in dwarf spheroidal (dSph) galaxies this floor
-is a factor of 10 higher \citep{refs}.
+Z_\odot$ if dust cooling is efficient \citep{Omukai05,
+  Schneider06_Frag, clark08} and $\sim 10^{-3.5} Z_\odot$ otherwise
+\citep{Bromm01, 2009ApJ...691..441S}, where the gas can cool rapidly,
+lowering its Jeans mass.  An intermediate characteristic mass of
+$\sim10~\Ms$ can be occur if the gas cooling is suppressed to the
+cosmic microwave background (CMB) temperature \citep{Larson98,
+  Tumlinson07_IMF, 2009ApJ...691..441S}.  The resulting Population II
+star cluster will thus have a lower characteristic stellar mass than
+its metal-free progenitors.  In the local universe, stars in the Milky
+Way halo and dwarf spheroidal (dSph) galaxies may be connected to
+these first stellar clusters.  In the halo of the Milky Way, the most
+metal-poor stars have a metallicity floor of [Z/H] = ???  \citep{ref},
+and in dwarf spheroidal (dSph) galaxies this floor is a factor of 10
+higher \citep{refs}.
 
@@
 \end{equation}
-%
 to determine the stellar mass.  Above $M_{\rm char}$, it behaves as a
@@
 the random number generator \citep[Mersenne twister;][]{ref} has been
-called for use when restarting the simulations.
+called for use when restarting the simulations.  Although the Pop III
+star formation history (SFH) is identical for a given $N$ stars, the
+Pop III SFH for a given halo can be different between the two
+simulations.  This happens because the order in which halos form Pop
+III stars can be altered from enhanced star formation and feedback
+from nearby Pop II star clusters, as we will demonstrate in this
+Letter.
 

### 2010-09-07 ms.tex
Adding stellar feedback section and completing star formation section.

@@
 initialize the simulation with \textsl{grafic} \citep{Bertschinger01}
-at $z = ???$ and use the cosmological parameters from the 7-year WMAP
-data \citep{ref}: $\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$,
+at $z = 130$ and use the cosmological parameters from the 7-year WMAP
+data \citep{WMAP7}: $\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$,
 $\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$
@@
 \citet{Abel07} and \citet{Wise08_Gal} where each star particle
-represents a single star.  Instead of using a fixed stellar mass, we
+represents a single star.  The critical overdensity in which a star
+forms is $5 \times 10^5$.  Instead of using a fixed stellar mass, we
 randomly sampled from an IMF with a functional form of
@@
 
+We treat Pop II star formation with the same prescription as
+\citet{Wise09}, which is a modified version of the widely used
+\citet{Cen92} method but accounts for the fact that the molecular
+clouds are resolved.  The critical overdensity is the same as the Pop
+III star formation model.  In each star-forming region, a fraction
+$c_* = 0.07$ of the cold gas ($T < 10^3$ K) is removed from the grid
+and deposited into the star particle.  Each star particle lives for 20
+Myr, the lifetime of an OB star.  These stars generate the majority of
+the ionizing radiation and SNe feedback in stellar clusters, thus we
+ignore lower mass stars.  We discuss our treatment of stellar feedback
+next.
+
 \subsection{Stellar feedback}
+
+The mass-dependent luminosities and lifetimes of the Pop III stars are
+taken from \citet{Schaerer02}.  The radiation field is evolved with
+with adaptive ray tracing \citep{Abel02, Wise10} and is coupled
+self-consistently to the hydrodynamics.  These stars die as
+pair-instability SNe (PISNe) if they are in the mass range 140--260
+\Ms \citep{Heger02}.  We use the explosion energy from
+\citeauthor{Heger02}, where we fit the following function to their
+models, $E_{\rm PISN} = 10^{51} \times [5.0 + 1.304 (M_{\rm He} -
+64)]$, where $M_{\rm He} = (13/24) \times (M_\star - 20) \Ms$ is the
+helium core mass and $M_\star$ is the stellar mass.
+
+The Pop II stars emit 6000 hydrogen ionizing photons per baryon over
+their lifetime, and we do not consider singly- and doubly-ionizing
+helium photons.  We note that low-metallicity stars generate up to a
+factor of four more ionizing photons than a solar metallicity
+population \citep{Schaerer03} and might be underestimating the
+radiative feedback.  Nonetheless this study provides an excellent
+first insight in the transition to Pop II star formation, as the metal
+enrichment is the key ingredient here.  For SN feedback, these stars
+generate $6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$ of energy after
+living for 4 Myr, which is injected into spheres with a radius of 10
+pc.  If the resolution of the grid is less than 10/3 pc, we deposit
+the energy into a $3^3$ cube surrounding the star particle.
 

### 2010-09-08 ms.tex
Added references to halo and dSph metallicities.  Removed references to metal cooling.

@@
   Tom Abel\altaffilmark{4},
-  Britton D. Smith \altaffilmark{5}}
+  Matthew J. Turk\altaffilmark{3}}
 
@@
   Cosmology, Stanford University, Menlo Park, CA 94025}
-\altaffiltext{5}{Michigan State University}
+%\altaffiltext{5}{Michigan State University}
 \email{jwise@astro.princeton.edu}
@@
 these first stellar clusters.  In the halo of the Milky Way, the most
-metal-poor stars have a metallicity floor of [Z/H] = ???  \citep{ref},
-and in dwarf spheroidal (dSph) galaxies this floor is a factor of 10
-higher \citep{refs}.
+metal-poor stars have a metallicity floor of [Z/H] = -4
+\citep{Beers05}, and in dwarf spheroidal (dSph) galaxies this floor is
+a factor of 10 higher \citep{Tolstoy04, Helmi06}.  \textbf{Check for
+  more recent references.}
 
@@
 link together recent results from metal-enriched and metal-free star
-formation, the critical metallicity, pair-instability supernovae, and
-fine-structure metal line cooling.  Furthermore we spatially
-distinguish metal enrichment from Pop II and Pop III stars.  This is
-the first time that all of these processes have been interconnected in
-a simulation that resolves minihalos to study the transition to Pop II
-star formation self-consistently.  We describe our simulation setup
-and our adopted star formation models in \S \ref{sec:setup} and
-present our results in \S \ref{sec:results}.  We discuss the
-implications of our findings and conclude in the last section.
+formation, the critical metallicity, and pair-instability supernovae.
+Furthermore we spatially distinguish metal enrichment from Pop II and
+Pop III stars.  This is the first time that all of these processes
+have been interconnected in a simulation that resolves minihalos to
+study the transition to Pop II star formation self-consistently.  We
+describe our simulation setup and our adopted star formation models in
+\S \ref{sec:setup} and present our results in \S \ref{sec:results}.
+We discuss the implications of our findings and conclude in the last
+section.
 
@@
 
-We peform two simulations with the same initial conditions.  They
-differ only in that one considers primordial cooling, and the other
-considers additional cooling in metal-enriched gas.  For primordial
-cooling, we use a non-equilbrium chemistry solver with 9 species of
-hydrogen, helium, and molecular hydrogen.  For metal cooling, we use a
-cooling curve that is calculated from CLOUDY \citep{CLOUDY} and using
-the method of \citet{2008MNRAS.385.1443S}.  It is tabulated based on
-density, temperature, electron fraction, and metallicity.
+We use a non-equilbrium chemistry solver with 9 species of hydrogen,
+helium, and molecular hydrogen \citep{Abel97}.  We will follow-up this
+study with one that considers radiative cooling from metal-enriched
+gas, using rates that are calculated from CLOUDY \citep{CLOUDY} and
+the method of \citet{2008MNRAS.385.1443S}.
+
+% We peform two simulations with the same initial conditions.  They
+% differ only in that one considers primordial cooling, and the other
+% considers additional cooling in metal-enriched gas.  For primordial
+% cooling, we use a non-equilbrium chemistry solver with 9 species of
+% hydrogen, helium, and molecular hydrogen.  For metal cooling, we use a
+% cooling curve that is calculated from CLOUDY \citep{CLOUDY} and using
+% the method of \citet{2008MNRAS.385.1443S}.  It is tabulated based on
+% density, temperature, electron fraction, and metallicity.
 
@@
 the random number generator \citep[Mersenne twister;][]{ref} has been
-called for use when restarting the simulations.  Although the Pop III
-star formation history (SFH) is identical for a given $N$ stars, the
-Pop III SFH for a given halo can be different between the two
-simulations.  This happens because the order in which halos form Pop
-III stars can be altered from enhanced star formation and feedback
-from nearby Pop II star clusters, as we will demonstrate in this
-Letter.
+called for use when restarting the simulations.
+
+%%% FOR THE COMPARISON BETWEEN RUNS WITH AND WITHOUT METAL COOLING %%%
+%
+% Although the Pop III star formation history (SFH) is identical for a
+% given $N$ stars, the Pop III SFH for a given halo can be different
+% between the two simulations.  This happens because the order in which
+% halos form Pop III stars can be altered from enhanced star formation
+% and feedback from nearby Pop II star clusters, as we will demonstrate
+% in this Letter.
 
@@
 and deposited into the star particle.  Each star particle lives for 20
-Myr, the lifetime of an OB star.  These stars generate the majority of
-the ionizing radiation and SNe feedback in stellar clusters, thus we
-ignore lower mass stars.  We discuss our treatment of stellar feedback
-next.
+Myr, the maximum lifetime of an OB star.  These stars generate the
+majority of the ionizing radiation and SNe feedback in stellar
+clusters, thus we ignore lower mass stars.  We discuss our treatment
+of stellar feedback next.
 
@@
 
+\subsection{Metal enrichment history}
+
+\subsection{Population III star formation history}
+
+\subsection{Population II stellar populations}
+
 \section{Discussion and Summary}

### 2010-09-11 ms.tex
Changed subsection title.
Included all cited references.  Put bullet points for result subsections.

@@
 
-\shorttitle{POPULATION III STAR EPOCH}
+\shorttitle{THE BIRTH OF A GALAXY}
 \shortauthors{WISE ET AL.}
 
-\title{How Short Lived is the Population III Epoch?}
+\title{The Birth of a Galaxy: Self-consistent transition to Population
+  II Star Formation}
 
@@
 compression of the gas \citep{Ferrara98}; however timescales for metal
-mixing into the dense gas are many dynamical times \citep{Cen07} for
+mixing into the dense gas are many dynamical times \citep{Cen08} for
 shock velocities $\lsim 100~\kms$.
@@
 We use the adaptive mesh refinement (AMR) code
-\enzo~\citep{BryanNorman97, OShea2004} that employs our implementation
-of adaptive ray tracing for radiation transport \citep{Wise10}.  To
-resolve minihalos with at least 100 dark matter (DM) particles and
-follow the formation of the first generation of dwarf galaxies, we use
-a simulation box of 1 Mpc that has a resolution of $256^3$.  This
-gives us a DM mass resolution of 1840 \Ms.  We refine the grid on
-baryon overdensities of $3 \times 2^{-0.2l}$, where $l$ is the AMR
-level, resulting in a super-Lagrangian behavior.  We also refine on a
-DM overdensity of $3 \times 2^l$ and always resolve the local Jeans
-length by at least 4 cells.  The latter criterion avoids any artifical
-fragmentation during gaseous collapses \citep{Truelove97}.  We
-initialize the simulation with \textsl{grafic} \citep{Bertschinger01}
-at $z = 130$ and use the cosmological parameters from the 7-year WMAP
-data \citep{WMAP7}: $\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$,
-$\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$
-with the variables having their usual definitions.
+\enzo~\citep{BryanNorman1997, OShea2004} that employs our
+implementation of adaptive ray tracing for radiation transport
+\citep{Wise10}.  To resolve minihalos with at least 100 dark matter
+(DM) particles and follow the formation of the first generation of
+dwarf galaxies, we use a simulation box of 1 Mpc that has a resolution
+of $256^3$.  This gives us a DM mass resolution of 1840 \Ms.  We
+refine the grid on baryon overdensities of $3 \times 2^{-0.2l}$, where
+$l$ is the AMR level, resulting in a super-Lagrangian behavior.  We
+also refine on a DM overdensity of $3 \times 2^l$ and always resolve
+the local Jeans length by at least 4 cells.  The latter criterion
+avoids any artifical fragmentation during gaseous collapses
+\citep{Truelove97}.  We initialize the simulation with \textsl{grafic}
+\citep{Bertschinger01} at $z = 130$ and use the cosmological
+parameters from the 7-year WMAP data \citep{WMAP7}: $\Omega_M =
+0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$,
+$\sigma_8 = 0.81$, and $n = 0.963$ with the variables having their
+usual definitions.
 
@@
 has recently shown that Pop III binaries may form in a fraction of
-such halos.  Furthermore, detailed one-dimensional calculations have
-shown that their IMF should follow a Kroupa-like IMF that has a
-Salpeter slope at the high-mass end and an exponential cut-off below
-$M_{\rm char}$ \citep{refs}.
+such halos.
+
+% Furthermore, detailed one-dimensional calculations have shown that
+% their IMF should follow a Kroupa-like IMF that has a Salpeter slope
+% at the high-mass end and an exponential cut-off below $M_{\rm char}$
+% \citep{refs}.
 
@@
 simulations with the same random seed and record the number of times
-the random number generator \citep[Mersenne twister;][]{ref} has been
-called for use when restarting the simulations.
+the random number generator \citep[Mersenne twister;][]{MTwister} has
+been called for use when restarting the simulations.
 
@@
 taken from \citet{Schaerer02}.  The radiation field is evolved with
-with adaptive ray tracing \citep{Abel02, Wise10} and is coupled
+with adaptive ray tracing \citep{Abel02_RT, Wise10} and is coupled
 self-consistently to the hydrodynamics.  These stars die as
 pair-instability SNe (PISNe) if they are in the mass range 140--260
-\Ms \citep{Heger02}.  We use the explosion energy from
-\citeauthor{Heger02}, where we fit the following function to their
-models, $E_{\rm PISN} = 10^{51} \times [5.0 + 1.304 (M_{\rm He} -
-64)]$, where $M_{\rm He} = (13/24) \times (M_\star - 20) \Ms$ is the
-helium core mass and $M_\star$ is the stellar mass.
+\Ms \citep{Heger03}.  We use the explosion energy from
+\citet{Heger02}, where we fit the following function to their models,
+$E_{\rm PISN} = 10^{51} \times [5.0 + 1.304 (M_{\rm He} - 64)]$, where
+$M_{\rm He} = (13/24) \times (M_\star - 20) \Ms$ is the helium core
+mass and $M_\star$ is the stellar mass.
 
@@
 
-\subsection{Metal enrichment history}
+Here we present the gaseous and stellar evolution of two selected
+halos in the simulation, starting with the birth of the first Pop III
+star in its merger history.  We then compare the nature of star
+formation in these two halos.
+
+\subsection{Halo evolution}
+
+\li Describe the evolution of the baryon fraction and metallicity from
+PISN and Type II SNe metals in the two halos.
 
@@
 
+\li Report on the Pop III stars forming in halo progenitors
+
 \subsection{Population II stellar populations}
+
+\li Present results on the star formation history and the physical
+reasons for the features seen in the SFH and metallicities.
+
+\li Present the stellar metallicity distribution at the final time
+
+\subsection{Environments for starbursts and quiescent star formation}
+
+\li Present the environment for bursting and quiescent star formation
+history
 
@@
 
-J.H.W. is supported by the Hubble Fellowship etc.  The majority of the
-analysis and plots were done with \texttt{yt} \citep{yt}.
+Support for this work was provided by NASA through Hubble Fellowship
+grant \#120-6370 awarded by the Space Telescope Science Institute,
+which is operated by the Association of Universities for Research in
+Astronomy, Inc., for NASA, under contract NAS 5-26555.  Computational
+resources were provided by NASA/NCCS award SMD-09-1439.  The majority
+of the analysis and plots were done with \texttt{yt} \citep{yt}.
 

### 2010-10-04 ms.tex
Added preliminary versions of figures 1 and 2.  Debating whether to discuss a third (gas-poor) halo.

@@
 
-\title{The Birth of a Galaxy: Self-consistent transition to Population
-  II Star Formation}
+\title{The Birth of a Galaxy: Population III Progenitors and
+  Metal-enriched Stellar Populations}
 
@@
 
-Here we present the gaseous and stellar evolution of two selected
-halos in the simulation, starting with the birth of the first Pop III
-star in its merger history.  We then compare the nature of star
-formation in these two halos.
+Here we present the gaseous and stellar evolution of three selected
+halos in the simulation: (1) a halo that never recovers a gas
+reservior after a PISN, (2) one that experiences a series of major
+mergers, and (3) one that has an early mass buildup but no major
+mergers after $z=12$.  The halos are referred to by these numbers.  We
+start with the birth of the first Pop III star in its merger history.
+We then compare the nature of star formation in these halos.
+
+\li Should we present the gas-poor halo?
 
@@
 
+\begin{figure}
+  \epsscale{1.15}
+  \plotone{f1}
+  \caption{\label{fig:evo}}
+  \epsscale{1}
+\end{figure}
+
+\begin{figure*}
+  \plotone{f2}
+  \caption{\label{fig:projections}}
+\end{figure*}
+
 \li Describe the evolution of the baryon fraction and metallicity from
 PISN and Type II SNe metals in the two halos.
+
+\li Need to run the halo analysis on smaller halos to capture the
+entire merger histories.
 

### 2010-10-12 ms.tex
Added figures 3 and 4.  Updated figures 1 and 2 to z=7.
First draft of first results subsection, halo evolution.

@@
 with adaptive ray tracing \citep{Abel02_RT, Wise10} and is coupled
-self-consistently to the hydrodynamics.  These stars die as
-pair-instability SNe (PISNe) if they are in the mass range 140--260
-\Ms \citep{Heger03}.  We use the explosion energy from
-\citet{Heger02}, where we fit the following function to their models,
-$E_{\rm PISN} = 10^{51} \times [5.0 + 1.304 (M_{\rm He} - 64)]$, where
-$M_{\rm He} = (13/24) \times (M_\star - 20) \Ms$ is the helium core
-mass and $M_\star$ is the stellar mass.
+self-consistently to the hydrodynamics.  We model the \hh~dissociating
+radiation with an optically-thin, inverse square profile, centered on
+all stars.  These stars die as pair-instability SNe (PISNe) if they
+are in the mass range 140--260 \Ms \citep{Heger03}.  We use the
+explosion energy from \citet{Heger02}, where we fit the following
+function to their models, $E_{\rm PISN} = 10^{51} \times [5.0 + 1.304
+(M_{\rm He} - 64)]$, where $M_{\rm He} = (13/24) \times (M_\star - 20)
+\Ms$ is the helium core mass and $M_\star$ is the stellar mass.
 
@@
 
-Here we present the gaseous and stellar evolution of three selected
-halos in the simulation: (1) a halo that never recovers a gas
-reservior after a PISN, (2) one that experiences a series of major
-mergers, and (3) one that has an early mass buildup but no major
-mergers after $z=12$.  The halos are referred to by these numbers.  We
-start with the birth of the first Pop III star in its merger history.
-We then compare the nature of star formation in these halos.
+\begin{figure*}
+  \plotone{f3}
+  \caption{\label{fig:projections} Density-weighted projections of gas
+    density (top), temperature (middle), and metallicity (bottom).
+    The left column shows the entire simulation volume, where the
+    center and right columns focus on the intense and quiet halos,
+    respectively.  The metallicity projections are a composite picture
+    of metals originating from Pop III (red) and Pop II (blue) stars.}
+\end{figure*}
 
-\li Should we present the gas-poor halo?
+Here we present the gaseous and stellar evolution of two selected
+halos in the simulation: one that has an early mass buildup but no
+major mergers after $z=12$, and one that experiences a series of major
+mergers between $z=10$ and $z=7$.  We name the halos ``quiet'' and
+``intense'', respectively.  We start with the birth of the first Pop
+III star in its merger history.  We then compare the nature of star
+formation in these halos.
+
+We illustrate the state of the simulation at $z=7$ in Figure
+\ref{fig:projections} with density weighted projections of gas
+density, temperature, and metallicity, showing the entire box and
+focusing on the two halos of interest.  The quiet and intense halos
+are located in the bottom center and bottom right of the full box,
+respectively.
 
@@
   \plotone{f1}
-  \caption{\label{fig:evo}}
+  \caption{\label{fig:evo} Evolution of the total halo mass (top),
+    stellar mass (middle), and gas fraction (bottom) of the quiet
+    (dashed) and intense (solid) halos.}
   \epsscale{1}
@@
 
-\begin{figure*}
+\begin{figure}
+  \epsscale{1.15}
   \plotone{f2}
-  \caption{\label{fig:projections}}
-\end{figure*}
+  \caption{\label{fig:Zevo} Average stellar metallicities and gas
+    metallicities enriched by Pop II and Pop III SNe of the
+    intense (top) and quiet (bottom) halos.}
+  \epsscale{1}
+\end{figure}
 
-\li Describe the evolution of the baryon fraction and metallicity from
-PISN and Type II SNe metals in the two halos.
+%\li Describe the evolution of the baryon fraction and metallicity from
+%PISN and Type II SNe metals in the two halos.
 
-\li Need to run the halo analysis on smaller halos to capture the
-entire merger histories.
+Figure \ref{fig:evo} shows the total, metal-enriched stellar, and gas
+mass history of the most massive progenitors of both halos.  The quiet
+halo undergoes a series of major mergers at $z > 12$, growing by a
+factor of 30 to $2.5 \times 10^7 \Ms$ within 150 Myr.  Afterwards it
+only grows by a factor of 3 by $z=7$ mainly through smooth accretion
+from the filaments and IGM.  It is the most massive halo in the
+simulation between redshifts 13 and 10.  At the same time, the intense
+halo has a relatively small mass $M = 10^7 \Ms$, but it is contained
+in a biased region on a comoving scale of 50 kpc with $\sim30$ halos
+with $M > 10^6 \Ms$.  After $z=10$, these halos hierarchically merge
+to form a $10^9 \Ms$ halo at $z=7$ with two major mergers at redshifts
+10 and 7.9, seen in the rapid increases in total mass in Figure
+\ref{fig:evo}.  The merger history of the two halos are not atypical
+as dark matter halos can experience both quiescent and vigorous mass
+accretion rates in their buildup.
+
+Both halos star forming Pop II stars when $M = 10^7 \Ms$.  This is
+consistent with the filtering mass $M_f$ of high-redshift halos when
+it accretes mainly from a pre-heated IGM \citep{gnedin98, gnedin00,
+  Wise08_Gal}.  The quiet halo forms $10^5 \Ms$ of stars by $z=9$.
+This initial starburst photo-evaporates the majority of its molecular
+clouds, in addition to heating and ionizing the surrounding IGM out to
+a radius of 10--15 kpc at $z=9$.  These respectively reduce the
+in-situ and external cold gas supply that could feed future star
+formation.
+
+The gas fractions of both halos are depleted from 0.15 to 0.08 by
+outflowing shocks driven by ionization fronts in their initial
+starbursts.  The quiet halo never recovers to the cosmic fraction
+$\Omega_b/\Omega_M$ for the following reason.  The lack of major
+mergers of halos above the filtering mass leads to a small gas
+fraction, cold gas reservoir, and stellar mass at later times.  This
+plays a large role in gas accretion because halos with $M < M_f$ will
+be likely photo-evaporated, hosting diffuse warm gas reservoirs
+instead of cold dense cores.  During this quienscent period, the halo
+mainly accretes warm diffuse gas from the filaments and IGM.  In
+contrast, the intense halo grows from major mergers of halos with $M >
+M_f$.  The progenitor halos involved in the major mergers are able to
+host molecular clouds and have, in general, higher gas fractions.
+Between $z=10$ and $z=8$, the gas fraction increases from 0.07 to 0.12
+until it rapidly jumps to 0.14 when a gas-rich major merger occurs.
+The stellar mass accordingly increases with the ample supply of cold
+gas during this period.  The gas fraction then decreases slightly by
+0.01 when galactic outflows are generated from the starburst
+associated with this major merger.
+
+The evolution of the stellar and gas metallicity of both halos are
+illustrated in Figure \ref{fig:Zevo}.  PISNe from Pop III stars enrich
+the nearby IGM out to a radius of 10 kpc and provides a metallicity
+floor of $[Z_3/H] \sim -3$ in both halos, given $M_{\rm char} = 100
+\Ms$.  The metallicity from Pop II SNe initially enrich the ISM of
+both halos to an average $[\bar{Z}_2/H]$ between --3.5 and --3.  The
+quiet halo is enriched to $[\bar{Z}_2/H] \sim -2.5$ until the
+metal-poor inflows balance the metal-rich galactic outflows, which are
+directed in the polar directions of the gas disk.  This is apparent in
+the metallicity projections in Figure \ref{fig:projections}.  The
+average stellar metallicities is equal or slightly higher up to 0.5
+dex than $[\bar{Z}_2/H]$.
+
+At $z \sim 8$, the metallicity of the intense halo dramatically
+self-enriches itself by a factor of 30 to $[\bar{Z}_2/H] = 1.5$ during
+a starburst.  Because this halo is located in a large-scale
+overdensity, the ejecta falls back into the halo after reaching
+distances up to 20 comoving kpc, in turn keeping the halo gas
+metallicity high because the inflows are relatively metal-rich
+themselves.  Interestingly the first few Pop II star clusters have
+[Z/H] between --1 and --2 and dominate the average stellar metallicity
+at $z > 8$.  We further detail the formation of these clusters in
+\S\ref{sec:pop}.  After the $z=8$ starburst, the average stellar
+metallicity follows the average gas metallicity within 0.1 dex.
 
@@
 
+The most massive progenitor of the quiet halo interestingly never
+hosts a Pop III star.  Instead a nearby halo forms a Pop III star,
+which (randomly) produces a PISNe at $z=16$.  The associated blastwave
+overruns the most massive progenitor, and the dense core survives this
+event and is enriched by this PISN.
+
 \subsection{Population II stellar populations}
+\label{sec:pop}
+
+\begin{figure*}
+  \plottwo{f4a}{f4b}
+  \caption{\label{fig:pops} The scatter plots show the star formation
+    history of the intense (left) and quiet (right) halos as a
+    function of metallicity at $z=7$.  Each circle represents a star
+    cluster, whose area is proportional to its mass.  The open circles
+    in the upper right represent sizes of $10^3$, $10^4$, and $10^5$
+    \Ms~star clusters.  The upper histogram collects the star formation
+    history into 25 equal temporal bins.  The right histogram depicts
+    the stellar metallicity distribution.}
+\end{figure*}
 
@@
 resources were provided by NASA/NCCS award SMD-09-1439.  The majority
-of the analysis and plots were done with \texttt{yt} \citep{yt}.
+of the analysis and plots were done with \texttt{yt}
+\citep{yt_full_paper}.
 

### 2010-10-13 ms.tex
Wrote Pop III section, started on Pop II section.

@@
 these first stellar clusters.  In the halo of the Milky Way, the most
-metal-poor stars have a metallicity floor of [Z/H] = -4
+metal-poor stars have a metallicity floor of [Z/H] = --4
 \citep{Beers05}, and in dwarf spheroidal (dSph) galaxies this floor is
@@
 $\sigma_8 = 0.81$, and $n = 0.963$ with the variables having their
-usual definitions.
+usual definitions.  The size of the box limits the simulation to an
+ending point of $z=7$.
 
@@
 We distinguish Pop II and Pop III star formation by the metallicity of
-the cold ($T < 10^3$ K) star forming gas in the molecular clouds.  Pop
-II stars are formed if [Z/H] $> -4$, and Pop III stars are formed
-otherwise.  We do not consider Pop III.2 stars and intermediate mass
-stars from CMB-limited cooling.
+the densest cell in the molecular cloud.  Pop II stars are formed if
+[Z/H] $> -4$, and Pop III stars are formed otherwise.  We do not
+consider Pop III.2 stars and intermediate mass stars from CMB-limited
+cooling.
 
@@
 Salpeter IMF but is exponentially cutoff below that mass
-\citep{Chabrier03, Clark09}.  For reproducibility, we initialize both
-simulations with the same random seed and record the number of times
-the random number generator \citep[Mersenne twister;][]{MTwister} has
-been called for use when restarting the simulations.
+\citep{Chabrier03, Clark09}.  For reproducibility, we record the
+number of times the random number generator \citep[Mersenne
+  twister;][]{MTwister} has been called for use when restarting the
+simulations.
 
@@
   \caption{\label{fig:projections} Density-weighted projections of gas
-    density (top), temperature (middle), and metallicity (bottom).
-    The left column shows the entire simulation volume, where the
-    center and right columns focus on the intense and quiet halos,
+    density (top), temperature (middle), and metallicity (bottom) at
+    $z=7$.  The left column shows the entire simulation volume, where
+    the center and right columns focus on the intense and quiet halos,
     respectively.  The metallicity projections are a composite picture
@@
 \subsection{Halo evolution}
+\label{sec:halo}
 
@@
 At $z \sim 8$, the metallicity of the intense halo dramatically
-self-enriches itself by a factor of 30 to $[\bar{Z}_2/H] = 1.5$ during
-a starburst.  Because this halo is located in a large-scale
+self-enriches itself by a factor of 30 to $[\bar{Z}_2/H] = -1.5$
+during a starburst.  Because this halo is located in a large-scale
 overdensity, the ejecta falls back into the halo after reaching
@@
 
-\li Report on the Pop III stars forming in halo progenitors
+\textit{Quiet halo}.--- The most massive progenitor interestingly
+never hosts a Pop III star.  Instead a nearby halo forms a Pop III
+star, which (randomly) produces a PISNe at $z=15.6$.  The associated
+blastwave overruns the most massive progenitor, and the dense core
+survives this event and is enriched by this PISN, triggering the
+transition to Pop II star formation.  Other progenitors host three Pop
+III stars, forming at $z = 15.4, 14.2, 13.8$, with the latter
+producing a PISN.  Metal enrichment from these two PISNe and latter
+intrinsic Pop II SF quench all Pop III star formation in this halo.
 
-The most massive progenitor of the quiet halo interestingly never
-hosts a Pop III star.  Instead a nearby halo forms a Pop III star,
-which (randomly) produces a PISNe at $z=16$.  The associated blastwave
-overruns the most massive progenitor, and the dense core survives this
-event and is enriched by this PISN.
+\textit{Intense halo}.--- The progenitors host a total of 56 Pop III
+stars with 21 producing PISNe.  The first forms in a $6 \times 10^5
+\Ms$ halo at $z=19$.  Pop III stars form on a regular interval in the
+halo's progenitors until $z=9$ when most of these halos enter the
+metal-rich bubble surrounding the intense halo.  There are two Pop III
+stars forming at $z=7.7$ with [Z/H] = --5.7, whose molecular clouds
+were enriched by external blastwaves that only partially enriched the
+dense regions \citep{Cen08}.  The most massive progenitors of the
+intense halo cease to form Pop III stars at $z<12$ because of nearby
+or intrinsic PISNe.
 
@@
 
-\li Present results on the star formation history and the physical
-reasons for the features seen in the SFH and metallicities.
+%% \li Present results on the star formation history and the physical
+%% reasons for the features seen in the SFH and metallicities.
+%%
+%% \li Present the stellar metallicity distribution at the final time
 
-\li Present the stellar metallicity distribution at the final time
+Figure \ref{fig:pops} shows the star formation history of both halos.
+From this plot, the metallicity distribution, star formation rates,
+and metallicity evolution and spread at a given time can all be
+extracted from these data.
+
+\textit{Quiet halo}.--- 
+A nearby PISNe provides a metallicity floor of [Z/H] = --2.8 at which
+metallicity the first Pop II stars form.  The stellar metallicity
+evolution exhibits what is expected from a relatively isolated system
+with the stellar feedback steadily enriching the ISM, resulting in a
+correlation between stellar age and metallicity.  After $z=10$ the
+metallicities plateau at [Z/H] = --2.1 for reasons discussed in
+\S\ref{sec:halo}.  Around $z=7.5$, a 25:1 minor merger occurs, and the
+gas inside the satellite halo is compressed, triggering metal-poor,
+[Z/H] = --3.2, SF during its nearest approach.  This halo infalls
+through a filament, where most of metal enrichment in the quiet halo
+occurs in bi-polar flows perpendicular to the galaxy disk and
+filament.  The filament and thus this satellite halo remains
+relatively metal-poor.  The bi-polar outflows and metal-poor filaments
+are seen in the metallicity projections in Figure
+\ref{fig:projections}.
+
+\textit{Intense halo}.---
 

### 2010-10-13 ms.tex
Completed first draft of paper.

@@
 
-\title{The Birth of a Galaxy: Population III Progenitors and
-  Metal-enriched Stellar Populations}
+\title{The Birth of a Galaxy: Population III Metal Enrichment and
+  Population II Stellar Populations}
 
@@
   Cosmology, Stanford University, Menlo Park, CA 94025}
-%\altaffiltext{5}{Michigan State University}
 \email{jwise@astro.princeton.edu}
@@
   III stars is considered, resulting in a plausible distribution of
-  pair-instability supernovae and associated metal enrichment.
-  \textbf{Add results.}
+  pair-instability supernovae and associated metal enrichment.  We
+  find that the gas fraction recovers from 5 percent to nearly the
+  cosmic fraction in halos with merger histories rich in halos above
+  $10^7 \Ms$.  A single pair-instability supernova is sufficient to
+  enrich the host halo to a metallicity floor of $10^{-3} Z_\odot$ and
+  to transition to Population II star formation.  Neighboring halos
+  are enriched to metallicities 10--100 times lower as the enriching
+  blastwaves mainly bypass them.  Stellar metallicities trace gas
+  metallicities within 0.2 dex.  We find that stellar metallicities do
+  not necessarily trace stellar ages, as mergers of halos with
+  established stellar populations can create superpositions of $t-Z$
+  evolutionary tracks.  We see a bimodal metallicity distribution that
+  is created after a starburst occurs when the halo can cool
+  efficiently through atomic line cooling.
 
@@
 metal-poor stars have a metallicity floor of [Z/H] = --4
-\citep{Beers05}, and in dwarf spheroidal (dSph) galaxies this floor is
-a factor of 10 higher \citep{Tolstoy04, Helmi06}.  \textbf{Check for
-  more recent references.}
+\citep{Beers05}.  In dwarf spheroidal (dSph) galaxies, this floor is a
+factor of 10 higher \citep{Tolstoy04, Helmi06}, however several metal
+poor stars with $-4 < [\mathrm{Z/H}] < -3$ have been recently
+discovered in dSphs \citep{Tafelmeyer10, Frebel10_Obs}.
 
@@
 implementation of adaptive ray tracing for radiation transport
-\citep{Wise10}.  To resolve minihalos with at least 100 dark matter
-(DM) particles and follow the formation of the first generation of
-dwarf galaxies, we use a simulation box of 1 Mpc that has a resolution
-of $256^3$.  This gives us a DM mass resolution of 1840 \Ms.  We
-refine the grid on baryon overdensities of $3 \times 2^{-0.2l}$, where
-$l$ is the AMR level, resulting in a super-Lagrangian behavior.  We
-also refine on a DM overdensity of $3 \times 2^l$ and always resolve
-the local Jeans length by at least 4 cells.  The latter criterion
-avoids any artifical fragmentation during gaseous collapses
-\citep{Truelove97}.  We initialize the simulation with \textsl{grafic}
+\citep{Wise10}.  We have modified \enzo~to use the HLLC Riemann solver
+\citep{Toro94_HLLC} for additional stability in strong shocks.  To
+resolve minihalos with at least 100 dark matter (DM) particles and
+follow the formation of the first generation of dwarf galaxies, we use
+a simulation box of 1 Mpc that has a resolution of $256^3$.  This
+gives us a DM mass resolution of 1840 \Ms.  We refine the grid on
+baryon overdensities of $3 \times 2^{-0.2l}$, where $l$ is the AMR
+level, resulting in a super-Lagrangian behavior.  We also refine on a
+DM overdensity of $3 \times 2^l$ and always resolve the local Jeans
+length by at least 4 cells.  The latter criterion avoids any
+artificial fragmentation during gaseous collapses \citep{Truelove97}.
+We initialize the simulation with \textsl{grafic}
 \citep{Bertschinger01} at $z = 130$ and use the cosmological
@@
 
-We use a non-equilbrium chemistry solver with 9 species of hydrogen,
+We use a non-equilibrium chemistry solver with 9 species of hydrogen,
 helium, and molecular hydrogen \citep{Abel97}.  We will follow-up this
@@
 occurring during their collapse; however \citet{2009Sci...325..601T}
-has recently shown that Pop III binaries may form in a fraction of
-such halos.
+and \citet{Stacy10_Binary} have recently shown that Pop III binaries
+may form in a fraction of such halos.
 
@@
 \begin{figure*}
+  \epsscale{0.8}
   \plotone{f3}
+  \epsscale{1}
   \caption{\label{fig:projections} Density-weighted projections of gas
@@
 are located in the bottom center and bottom right of the full box,
-respectively.
+respectively.  Radiative and mechanical feedback create a multi-phase
+medium inside these halos, which are embedded in a warm and ionized
+IGM.
 
-\subsection{Halo evolution}
+\subsection{Mass evolution}
 \label{sec:halo}
@@
     (dashed) and intense (solid) halos.}
-  \epsscale{1}
-\end{figure}
-
-\begin{figure}
-  \epsscale{1.15}
-  \plotone{f2}
-  \caption{\label{fig:Zevo} Average stellar metallicities and gas
-    metallicities enriched by Pop II and Pop III SNe of the
-    intense (top) and quiet (bottom) halos.}
   \epsscale{1}
@@
 it accretes mainly from a pre-heated IGM \citep{gnedin98, gnedin00,
-  Wise08_Gal}.  The quiet halo forms $10^5 \Ms$ of stars by $z=9$.
-This initial starburst photo-evaporates the majority of its molecular
-clouds, in addition to heating and ionizing the surrounding IGM out to
-a radius of 10--15 kpc at $z=9$.  These respectively reduce the
-in-situ and external cold gas supply that could feed future star
-formation.
+  Wise08_Gal}.  Afterwards these halos can cool efficiently through
+molecular and atomic hydrogen cooling, sustaining constant and
+sometimes bursty star formation.  The latter characteristic is equated
+with the definition of a galaxy.  The quiet halo forms $10^5 \Ms$ of
+stars by $z=9$.  This initial starburst photo-evaporates the majority
+of its molecular clouds, in addition to heating and ionizing the
+surrounding IGM out to a radius of 10--15 kpc at $z=9$.  These
+respectively reduce the in-situ and external cold gas supply that
+could feed future star formation.
 
@@
 be likely photo-evaporated, hosting diffuse warm gas reservoirs
-instead of cold dense cores.  During this quienscent period, the halo
+instead of cold dense cores.  During this quiescent period, the halo
 mainly accretes warm diffuse gas from the filaments and IGM.  In
@@
 associated with this major merger.
+
+\subsection{Metallicity evolution}
+
+\label{sec:Zevo}
+\begin{figure}
+  \epsscale{1.15}
+  \plotone{f2}
+  \caption{\label{fig:Zevo} Mass-weighted stellar metallicities and
+    gas metallicities enriched by Pop II and Pop III SNe of the
+    intense (top) and quiet (bottom) halos.}
+  \epsscale{1}
+\end{figure}
 
@@
 metallicity high because the inflows are relatively metal-rich
-themselves.  Interestingly the first few Pop II star clusters have
-[Z/H] between --1 and --2 and dominate the average stellar metallicity
-at $z > 8$.  We further detail the formation of these clusters in
-\S\ref{sec:pop}.  After the $z=8$ starburst, the average stellar
-metallicity follows the average gas metallicity within 0.1 dex.
+themselves.  The first few Pop II star clusters have [Z/H] between --1
+and --2 and dominate the average stellar metallicity at $z > 8$.
+After the $z \sim 8$ starburst, the average stellar metallicity
+follows the average gas metallicity within 0.1 dex.
 
@@
 never hosts a Pop III star.  Instead a nearby halo forms a Pop III
-star, which (randomly) produces a PISNe at $z=15.6$.  The associated
-blastwave overruns the most massive progenitor, and the dense core
-survives this event and is enriched by this PISN, triggering the
-transition to Pop II star formation.  Other progenitors host three Pop
-III stars, forming at $z = 15.4, 14.2, 13.8$, with the latter
-producing a PISN.  Metal enrichment from these two PISNe and latter
-intrinsic Pop II SF quench all Pop III star formation in this halo.
+star, which (randomly) produces a PISNe at $z=16$.  The blastwave
+overruns the most massive progenitor, and the dense core survives this
+event and is enriched by this PISN, triggering the transition to Pop
+II star formation.  Other progenitors host three Pop III stars,
+forming at $z = 15.4, 14.2, 13.8$, with the latter producing a PISN.
+Metal enrichment from these two PISNe and Pop II SF quench Pop III
+star formation in this halo.
 
@@
   \caption{\label{fig:pops} The scatter plots show the star formation
-    history of the intense (left) and quiet (right) halos as a
+    history of the quiet (left) and intense (right) halos as a
     function of metallicity at $z=7$.  Each circle represents a star
@@
     in the upper right represent sizes of $10^3$, $10^4$, and $10^5$
-    \Ms~star clusters.  The upper histogram collects the star formation
-    history into 25 equal temporal bins.  The right histogram depicts
-    the stellar metallicity distribution.}
+    \Ms~star clusters.  The dashed lines in the right panel guide the
+    eye to two stellar populations that were formed in two satellite
+    halos, merging at $z=7.5$.  The upper histogram collects the star
+    formation history into 25 equal temporal bins.  The right
+    histogram depicts the stellar metallicity distribution.}
 \end{figure*}
@@
 
-\textit{Quiet halo}.--- 
-A nearby PISNe provides a metallicity floor of [Z/H] = --2.8 at which
-metallicity the first Pop II stars form.  The stellar metallicity
-evolution exhibits what is expected from a relatively isolated system
-with the stellar feedback steadily enriching the ISM, resulting in a
-correlation between stellar age and metallicity.  After $z=10$ the
-metallicities plateau at [Z/H] = --2.1 for reasons discussed in
-\S\ref{sec:halo}.  Around $z=7.5$, a 25:1 minor merger occurs, and the
-gas inside the satellite halo is compressed, triggering metal-poor,
-[Z/H] = --3.2, SF during its nearest approach.  This halo infalls
-through a filament, where most of metal enrichment in the quiet halo
-occurs in bi-polar flows perpendicular to the galaxy disk and
-filament.  The filament and thus this satellite halo remains
-relatively metal-poor.  The bi-polar outflows and metal-poor filaments
-are seen in the metallicity projections in Figure
-\ref{fig:projections}.
+\textit{Quiet halo}.--- A nearby PISNe provides a metallicity floor of
+[Z/H] = --2.8 at which metallicity the first Pop II stars form.  The
+stellar metallicity evolution exhibits what is expected from a
+relatively isolated system with the stellar feedback steadily
+enriching the ISM, resulting in a correlation between stellar age and
+metallicity.  After $z=10$ the metallicities plateau at [Z/H] = --2.1
+for reasons discussed in \S\ref{sec:halo}.  The SFR peaks at $z=10$
+and decreases as the cold gas reservoir is depleted.  Around $z=7.5$,
+a 25:1 minor merger occurs, and the gas inside the satellite halo is
+compressed, triggering metal-poor, [Z/H] = --3.2, SF during its
+nearest approach.  This halo infalls through a filament, where most of
+metal enrichment in the quiet halo occurs in bi-polar flows
+perpendicular to the galaxy disk and filament.  The filament and thus
+this satellite halo remains relatively metal-poor.  The bi-polar
+outflows and metal-poor filaments are seen in the metallicity
+projections in Figure \ref{fig:projections}.  Stars with [Z/H] $<$ --3
+compose 1.6 percent of the total stellar mass.
 
-\textit{Intense halo}.---
+\textit{Intense halo}.--- In contrast with the quiet halo, the intense
+halo undergoes a few major mergers of halos with an established
+stellar population.  This creates a superposition of age-metallicity
+tracks in the SFH, seen in the complexity of Figure \ref{fig:pops}.
+The first two Pop II stellar clusters have an unusually high
+metallicity [Z/H] $\sim$ --1, which occurs when a PISN blastwave
+trigger star formation in two neighboring halos.  Most of the early
+star formation occurs around [Z/H] = --2.5.  At $z=9$, the halo's
+virial temperature reaches \tento{4} K.  This combined with a 10:1
+merger creates a starburst that quickly enriches the halo to [Z/H] =
+--1.5 by $z=8$.  The halo continues to enrich itself with further SF
+until $z=7$.  The spikes in the scatter plot correspond to SN
+triggered star formation in nearby molecular clouds that are enriched
+up to a factor of 10 with respect to the ISM.  However the mass
+fraction of these metal-rich, SN triggered clusters are small compared
+to the total stellar mass.  The starburst at $z=9$ creates a bimodal
+metallicity distribution with peaks at [Z/H] = --2.4 and --1.2 with
+the metal-rich component mainly being created after the starburst.
+Two systems with sizable stellar components merge into the halo at $z
+\sim 8$, and their stellar populations are still discernible in the
+metallicity-age plot, whose tracks are noted by dashed lines.  Stars
+with [Z/H] $<$ --3 compose 1.8 percent of the total stellar mass.
 
-\subsection{Environments for starbursts and quiescent star formation}
+\section{Discussion and Conclusions}
 
-\li Present the environment for bursting and quiescent star formation
-history
+In this paper, we focus on the birth of two galaxies prior to
+reionization with a cosmological AMR radiation hydrodynamics
+simulation.  Supernovae from Pop III stars provide the necessary heavy
+elements for the transition to a Population II stellar population,
+which we have directly simulated.  These two galaxies have a 10--15\%
+probability in surviving as present-day ``fossil'' galaxies
+\citep{Gnedin06}, otherwise they will be incorporated into galactic
+stellar halos.
 
-\section{Discussion and Summary}
+We find that one PISN is sufficient to enrich the star-forming halo
+and surrounding $\sim 5$ kpc to a metallicity of 10$^{-3} Z_\odot$,
+given a Pop III characteristic mass of 100~\Ms.  If the first stars
+have a lower characteristic mass that favor hypernovae
+\citep{Tumlinson07_IMF}, then this metallicity floor should be lowered
+by a factor of $\sim 10$ because (1) the metal ejecta is lowered by a
+factor of $\sim 50$ and the mixing mass is decreased by a factor of
+$(E_{\rm hyp}/E_{\rm PISN})^{3/5}$ in the Sedov-Taylor solution, where
+$(E_{\rm hyp}/E_{\rm PISN}) \sim 0.1$ is the ratio of explosion
+energies of a hypernova and PISN.  In the case where this metallicity
+floor is less than the critical metallicity, then the next starburst
+will further enrich the ISM, solidifying the transition to Pop II star
+formation.  We conclude that it only takes one, at most two, SNe from
+Pop III stars in the halo progenitors to complete the transition to
+Population II \citep[see also][]{Frebel10}.  The question of whether
+the critical metallicity is \tento{-6} or \tento{-3.5} $Z_\odot$ is
+most applicable to nearby halos where the heavy elements mix slowly
+into dense cores as the blastwave overtakes it.  Less than two percent
+of stars have [Z/H] $< -3$ in both systems, consistent with
+observations of metal-poor stars in the halo and dSphs
+\citep[e.g.][]{Beers05, Frebel10_Obs}.
+
+We also find that the merger history plays an important role in
+supplying gas into halos after its first epoch of star formation,
+mergers of halos below the filtering mass are inefficient in providing
+gas whereas the opposite is true for merging halos above the filtering
+mass.  Halos do not necessarily need $\tvir \ge 10^4$ K to form
+significant stellar populations; however SFRs dramatically increase,
+and thus metal enrichment, when this threshold is reached.  Halos with
+mostly gas-poor mergers or a quiet merger history result in a
+monotonic increase in metallicity with time.  Star formation histories
+become more complex with multiple metallicity-age tracks if the halo
+experiences mergers with other halos that have an established stellar
+population.  Furthermore star formation that is triggered by
+blastwaves interacting with molecular clouds can have metallicities up
+to a factor of 10 higher than the main starburst.  Lastly we find that
+a starburst at $\tvir = 10^4$ K enriches the host halo enough to
+create a bimodal metallicity distribution, where the metal-poor
+component is created before the burst.  Note that mergers of stellar
+populations can also create a similar bimodal distribution.  Such
+distributions are observed in dSphs \citep[e.g.][]{Battaglia10}.
+
+We have shown that it is possible to simulate the formation of a
+high-redshift dwarf galaxy and its entire star formation history,
+which provides invaluable insight on the first galaxies and the role
+of metal-free stars in the early universe.  There exists a wealth of
+information in this simulation, and we plan to follow up this
+preliminary report with more detailed analysis of the metal enrichment
+of the IGM, global star formation rates, and observational connections
+with high-redshift galaxies and Local Group dwarf galaxies in the near
+future.
 
@@
 Astronomy, Inc., for NASA, under contract NAS 5-26555.  Computational
-resources were provided by NASA/NCCS award SMD-09-1439.  The majority
-of the analysis and plots were done with \texttt{yt}
-\citep{yt_full_paper}.
+resources were provided by NASA/NCCS award SMD-09-1439.
+J.~H.~W. thanks Renyue Cen, Amina Helmi, Marco Spaans, and Eline
+Tolstoy for enlightening discussions.  The majority of the analysis
+and plots were done with \texttt{yt} \citep{yt_full_paper}.
 

### 2010-10-14 ms.tex
Made corrections to the first draft after read-thru.

@@
   whether dust cooling is important.  We present adaptive mesh
-  refinement radiation hydrodynamics simulations that
-  self-consistently follow the transition from Population III to II
-  star formation.  We model stellar radiative feedback with adaptive
-  ray tracing.  A top-heavy initial mass function for the Population
-  III stars is considered, resulting in a plausible distribution of
-  pair-instability supernovae and associated metal enrichment.  We
-  find that the gas fraction recovers from 5 percent to nearly the
-  cosmic fraction in halos with merger histories rich in halos above
-  $10^7 \Ms$.  A single pair-instability supernova is sufficient to
-  enrich the host halo to a metallicity floor of $10^{-3} Z_\odot$ and
-  to transition to Population II star formation.  Neighboring halos
-  are enriched to metallicities 10--100 times lower as the enriching
-  blastwaves mainly bypass them.  Stellar metallicities trace gas
-  metallicities within 0.2 dex.  We find that stellar metallicities do
-  not necessarily trace stellar ages, as mergers of halos with
-  established stellar populations can create superpositions of $t-Z$
-  evolutionary tracks.  We see a bimodal metallicity distribution that
-  is created after a starburst occurs when the halo can cool
-  efficiently through atomic line cooling.
+  refinement radiation hydrodynamics simulations that follows the
+  transition from Population III to II star formation.  We model
+  stellar radiative feedback with adaptive ray tracing.  A top-heavy
+  initial mass function for the Population III stars is considered,
+  resulting in a plausible distribution of pair-instability supernovae
+  and associated metal enrichment.  We find that the gas fraction
+  recovers from 5 percent to nearly the cosmic fraction in halos with
+  merger histories rich in halos above $10^7 \Ms$.  A single
+  pair-instability supernova is sufficient to enrich the host halo to
+  a metallicity floor of $10^{-3} Z_\odot$ and to transition to
+  Population II star formation.  Neighboring halos are enriched to
+  metallicities 10--100 times lower as the enriching blastwaves mainly
+  bypass them.  Stellar metallicities trace gas metallicities within
+  0.2 dex.  We find that stellar metallicities do not necessarily
+  trace stellar ages, as mergers of halos with established stellar
+  populations can create superpositions of $t-Z$ evolutionary tracks.
+  A bimodal metallicity distribution is created after a starburst
+  occurs when the halo can cool efficiently through atomic line
+  cooling.
 
@@
 
-The transition from Pop III to Pop II star formation is solely
+The transition from Pop III to Pop II star formation (SF) is solely
 dependent on the propagation of metals from the SNe remnants into
-future sites of star formation.  Their flows are complex because of
-the interactions between the SN blastwave, cosmological accretion and
-halo mergers, and nearby stellar feedback.  In minihalos ($M_{\rm h}
-\sim 10^6~\Ms$), radiation from the massive Pop III drives a 30
-\kms~shock, which is 10 times greater than the escape velocity of the
-halo, and leaves behind a warm ($3 \times 10^4$ K) and diffuse (0.5
-\cubecm) medium \citep{Kitayama04, Whalen04, Abel07}.  The latter
-feature aids in the expansion of the blastwave because it delays the
-transition to the Sedov-Taylor and snowplow phases.  In PISNe,
-approximately half of the metals stay in the IGM with an metal bubble
-size of a few kpc.  The remaining metals fall back into the host halo.
-The blastwave may induce star formation in nearby halos through the
-compression of the gas \citep{Ferrara98}; however timescales for metal
-mixing into the dense gas are many dynamical times \citep{Cen08} for
-shock velocities $\lsim 100~\kms$.
+future sites of SF.  Their flows are complex because of the
+interactions between the SN blastwave, cosmological accretion and halo
+mergers, and nearby stellar feedback.  In minihalos ($M_{\rm h} \sim
+10^6~\Ms$), radiation from the massive Pop III drives a 30 \kms~shock,
+which is 10 times greater than the escape velocity of the halo, and
+leaves behind a warm ($3 \times 10^4$ K) and diffuse (0.5 \cubecm)
+medium \citep{Kitayama04, Whalen04, Abel07}.  This aids in the
+expansion of the blastwave because it delays the transition to the
+Sedov-Taylor and snowplow phases.  In PISNe, approximately half of the
+metals stay in the IGM with an metal bubble size of a few kpc.  The
+remaining metals fall back into the host halo.  The blastwave may
+induce SF in nearby halos through the compression of the gas
+\citep{Ferrara98}; however timescales for metal mixing into the dense
+gas are many dynamical times \citep{Cen08} for shock velocities $\lsim
+100~\kms$.
 
@@
 complexities and the transition from Pop III to II stars.  In this
-Letter, we present the simulations that include both types of star
-formation, its radiative feedback, and its SNe feedback.  We utilize
-an initial mass function (IMF) for individual Pop III stars, based on
-the latest simulation results.  The methods used here incorporate and
-link together recent results from metal-enriched and metal-free star
+Letter, we present the simulations that include both types of SF, and
+their radiative and mechanical feedback.  We utilize an initial mass
+function (IMF) for individual Pop III stars, based on the latest
+simulation results.  The methods used here incorporate and link
+together recent results from metal-enriched and metal-free star
 formation, the critical metallicity, and pair-instability supernovae.
@@
 Pop III stars.  This is the first time that all of these processes
-have been interconnected in a simulation that resolves minihalos to
-study the transition to Pop II star formation self-consistently.  We
-describe our simulation setup and our adopted star formation models in
-\S \ref{sec:setup} and present our results in \S \ref{sec:results}.
-We discuss the implications of our findings and conclude in the last
+have been interconnected in a simulation that resolves star-forming
+minihalos to study the transition to Pop II star formation.  We
+describe our simulation setup and our adopted SF models in \S
+\ref{sec:setup} and present our results in \S \ref{sec:results}.  We
+discuss the implications of our findings and conclude in the last
 section.
@@
 In this section, we first describe our simulation setup.  We then
-detail the star formation models used in these simulations and how we
-model stellar radiation and SNe feedback.
+detail the SF models used here and how we model radiative and SNe
+feedback.
 
@@
 We use the adaptive mesh refinement (AMR) code
-\enzo~\citep{BryanNorman1997, OShea2004} that employs our
-implementation of adaptive ray tracing for radiation transport
-\citep{Wise10}.  We have modified \enzo~to use the HLLC Riemann solver
-\citep{Toro94_HLLC} for additional stability in strong shocks.  To
-resolve minihalos with at least 100 dark matter (DM) particles and
-follow the formation of the first generation of dwarf galaxies, we use
-a simulation box of 1 Mpc that has a resolution of $256^3$.  This
-gives us a DM mass resolution of 1840 \Ms.  We refine the grid on
-baryon overdensities of $3 \times 2^{-0.2l}$, where $l$ is the AMR
-level, resulting in a super-Lagrangian behavior.  We also refine on a
-DM overdensity of $3 \times 2^l$ and always resolve the local Jeans
-length by at least 4 cells.  The latter criterion avoids any
-artificial fragmentation during gaseous collapses \citep{Truelove97}.
-We initialize the simulation with \textsl{grafic}
+\enzo~v2.0\footnote[\dag]{\texttt{lca.ucsd.edu/enzo, unstable
+    changeset b86d8ba026d6}} \citep{BryanNorman1997, OShea2004}, which
+has been modified to use a HLLC Riemann solver \citep{Toro94_HLLC} for
+additional stability in strong shocks.  To resolve minihalos with at
+least 100 dark matter (DM) particles and follow the formation of the
+first generation of dwarf galaxies, we use a simulation box of 1 Mpc
+that has a resolution of $256^3$.  This gives us a DM mass resolution
+of 1840 \Ms.  We refine the grid on baryon overdensities of $3 \times
+2^{-0.2l}$, where $l$ is the AMR level, resulting in a
+super-Lagrangian behavior.  We also refine on a DM overdensity of $3
+\times 2^l$ and always resolve the local Jeans length by at least 4
+cells, avoiding artificial fragmentation during gaseous collapses
+\citep{Truelove97}.  We initialize the simulation with \textsl{grafic}
 \citep{Bertschinger01} at $z = 130$ and use the cosmological
@@
 $\sigma_8 = 0.81$, and $n = 0.963$ with the variables having their
-usual definitions.  The size of the box limits the simulation to an
-ending point of $z=7$.
+usual definitions.  We stop the simulation at $z=7$.
 
@@
 study with one that considers radiative cooling from metal-enriched
-gas, using rates that are calculated from CLOUDY \citep{CLOUDY} and
-the method of \citet{2008MNRAS.385.1443S}.
+gas, using the method of \citet{2008MNRAS.385.1443S}.
 
@@
 
-We distinguish Pop II and Pop III star formation by the metallicity of
-the densest cell in the molecular cloud.  Pop II stars are formed if
-[Z/H] $> -4$, and Pop III stars are formed otherwise.  We do not
-consider Pop III.2 stars and intermediate mass stars from CMB-limited
-cooling.
+We distinguish Pop II and Pop III SF by the metallicity of the densest
+cell in the molecular cloud.  Pop II stars are formed if [Z/H] $> -4$,
+and Pop III stars are formed otherwise.  We do not consider Pop III.2
+stars and intermediate mass stars from CMB-limited cooling.
 
@@
 
-For Pop III stars, we use the same star formation model as
-\citet{Abel07} and \citet{Wise08_Gal} where each star particle
-represents a single star.  The critical overdensity in which a star
-forms is $5 \times 10^5$.  Instead of using a fixed stellar mass, we
-randomly sampled from an IMF with a functional form of
+For Pop III stars, we use the same SF model as \citet{Abel07} and
+\citet{Wise08_Gal} where each star particle represents a single star.
+The critical overdensity in which a star forms is $5 \times 10^5$.
+Instead of using a fixed stellar mass, we randomly sampled from an IMF
+with a functional form of
 %
@@
 
-We treat Pop II star formation with the same prescription as
-\citet{Wise09}, which is a modified version of the widely used
-\citet{Cen92} method but accounts for the fact that the molecular
-clouds are resolved.  The critical overdensity is the same as the Pop
-III star formation model.  In each star-forming region, a fraction
-$c_* = 0.07$ of the cold gas ($T < 10^3$ K) is removed from the grid
+We treat Pop II SF with the same prescription as \citet{Wise09}, which
+is a modified version of the \citet{Cen92} method but accounts for the
+fact that the molecular clouds are resolved.  The critical overdensity
+is the same as the Pop III SF model.  In each star-forming region,
+seven percent of the cold gas ($T < 10^3$ K) is removed from the grid
 and deposited into the star particle.  Each star particle lives for 20
@@
 majority of the ionizing radiation and SNe feedback in stellar
-clusters, thus we ignore lower mass stars.  We discuss our treatment
-of stellar feedback next.
+clusters, thus we ignore lower mass stars.
 
@@
 radiative feedback.  Nonetheless this study provides an excellent
-first insight in the transition to Pop II star formation, as the metal
-enrichment is the key ingredient here.  For SN feedback, these stars
-generate $6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$ of energy after
-living for 4 Myr, which is injected into spheres with a radius of 10
-pc.  If the resolution of the grid is less than 10/3 pc, we deposit
-the energy into a $3^3$ cube surrounding the star particle.
+first insight in the transition to Pop II SF, as the metal enrichment
+is the key ingredient here.  For SN feedback, these stars generate
+$6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$ of energy after living
+for 4 Myr, which is injected into spheres with a radius of 10 pc.  If
+the resolution of the grid is less than 10/3 pc, we deposit the energy
+into a $3^3$ cube surrounding the star particle.
 
@@
     $z=7$.  The left column shows the entire simulation volume, where
-    the center and right columns focus on the intense and quiet halos,
-    respectively.  The metallicity projections are a composite picture
-    of metals originating from Pop III (red) and Pop II (blue) stars.}
+    the center and right columns focus on the intense and quiet halos.
+    The metallicity projections are a composite picture of metals
+    originating from Pop III (red) and Pop II (blue) stars with purple
+    indicating a mixture of the two.}
 \end{figure*}
@@
 mergers between $z=10$ and $z=7$.  We name the halos ``quiet'' and
-``intense'', respectively.  We start with the birth of the first Pop
-III star in its merger history.  We then compare the nature of star
-formation in these halos.
+``intense'', respectively.  We start with the mass accretion history
+and enrichment of the halos.  We then compare the nature of the
+stellar populations in these halos.
 
@@
 simulation between redshifts 13 and 10.  At the same time, the intense
-halo has a relatively small mass $M = 10^7 \Ms$, but it is contained
-in a biased region on a comoving scale of 50 kpc with $\sim30$ halos
-with $M > 10^6 \Ms$.  After $z=10$, these halos hierarchically merge
-to form a $10^9 \Ms$ halo at $z=7$ with two major mergers at redshifts
-10 and 7.9, seen in the rapid increases in total mass in Figure
+halo has a mass $M = 3 \times 10^6 \Ms$, but it is contained in a
+biased region on a comoving scale of 50 kpc with $\sim25$ halos with
+$M \sim 10^6 \Ms$.  After $z=10$, these halos hierarchically merge to
+form a $10^9 \Ms$ halo at $z=7$ with two major mergers at redshifts 10
+and 7.9, seen in the rapid increases in total mass in Figure
 \ref{fig:evo}.  The merger history of the two halos are not atypical
@@
 
-Both halos star forming Pop II stars when $M = 10^7 \Ms$.  This is
+Both halos start forming Pop II stars when $M = 10^7 \Ms$.  This is
 consistent with the filtering mass $M_f$ of high-redshift halos when
@@
   Wise08_Gal}.  Afterwards these halos can cool efficiently through
-molecular and atomic hydrogen cooling, sustaining constant and
-sometimes bursty star formation.  The latter characteristic is equated
-with the definition of a galaxy.  The quiet halo forms $10^5 \Ms$ of
-stars by $z=9$.  This initial starburst photo-evaporates the majority
-of its molecular clouds, in addition to heating and ionizing the
-surrounding IGM out to a radius of 10--15 kpc at $z=9$.  These
-respectively reduce the in-situ and external cold gas supply that
-could feed future star formation.
+\hh~cooling, sustaining constant and sometimes bursty SF.  The latter
+characteristics are equated with the definition of a galaxy.  The
+quiet halo forms $10^5 \Ms$ of stars by $z=9$.  This initial starburst
+photo-evaporates the majority of its molecular clouds, in addition to
+heating and ionizing the surrounding IGM out to a radius of 10--15 kpc
+at $z=9$.  These respectively reduce the in-situ and external cold gas
+supply that could feed future SF.
 
 The gas fractions of both halos are depleted from 0.15 to 0.08 by
-outflowing shocks driven by ionization fronts in their initial
-starbursts.  The quiet halo never recovers to the cosmic fraction
-$\Omega_b/\Omega_M$ for the following reason.  The lack of major
-mergers of halos above the filtering mass leads to a small gas
-fraction, cold gas reservoir, and stellar mass at later times.  This
-plays a large role in gas accretion because halos with $M < M_f$ will
-be likely photo-evaporated, hosting diffuse warm gas reservoirs
-instead of cold dense cores.  During this quiescent period, the halo
-mainly accretes warm diffuse gas from the filaments and IGM.  In
-contrast, the intense halo grows from major mergers of halos with $M >
-M_f$.  The progenitor halos involved in the major mergers are able to
-host molecular clouds and have, in general, higher gas fractions.
-Between $z=10$ and $z=8$, the gas fraction increases from 0.07 to 0.12
-until it rapidly jumps to 0.14 when a gas-rich major merger occurs.
-The stellar mass accordingly increases with the ample supply of cold
-gas during this period.  The gas fraction then decreases slightly by
-0.01 when galactic outflows are generated from the starburst
-associated with this major merger.
+outflowing shocks driven by ionization fronts and blastwaves in their
+initial starbursts.  The quiet halo never recovers to the cosmic
+fraction $\Omega_b/\Omega_M$ for the following reason.  The lack of
+major mergers of halos above the filtering mass leads to a small gas
+fraction because halos with $M < M_f$ are likely photo-evaporated,
+hosting diffuse warm gas reservoirs instead of cold dense cores.
+During this quiescent period, the halo mainly accretes warm diffuse
+gas from the filaments and IGM.  In contrast, the intense halo grows
+from major mergers of halos with $M > M_f$.  The progenitor halos
+involved in the major mergers are able to host molecular clouds and
+have, in general, higher gas fractions.  Between $z=10$ and $z=8$, the
+gas fraction increases from 0.07 to 0.12 until it jumps to 0.14 when a
+gas-rich major merger occurs.  The stellar mass accordingly increases
+with the ample supply of gas during this period.  The gas fraction
+then decreases by 0.01 when galactic outflows are generated from the
+starburst associated with this major merger.
 
@@
 the nearby IGM out to a radius of 10 kpc and provides a metallicity
-floor of $[Z_3/H] \sim -3$ in both halos, given $M_{\rm char} = 100
-\Ms$.  The metallicity from Pop II SNe initially enrich the ISM of
-both halos to an average $[\bar{Z}_2/H]$ between --3.5 and --3.  The
-quiet halo is enriched to $[\bar{Z}_2/H] \sim -2.5$ until the
-metal-poor inflows balance the metal-rich galactic outflows, which are
-directed in the polar directions of the gas disk.  This is apparent in
-the metallicity projections in Figure \ref{fig:projections}.  The
-average stellar metallicities is equal or slightly higher up to 0.5
-dex than $[\bar{Z}_2/H]$.
+floor of $[Z_3/H] \sim -3$, given $M_{\rm char} = 100 \Ms$.  The
+metallicity from Pop II SNe initially enrich the ISM of both halos to
+an average $[\bar{Z}_2/H]$ between --3.5 and --3.  The quiet halo is
+enriched to $[\bar{Z}_2/H] \sim -2.5$ until the metal-poor inflows
+balance the metal-rich galactic outflows, which are directed in the
+polar directions of the gas disk, keeping the adjacent filaments
+metal-poor.  These features and a well-mixed ISM
+\citep[cf.][]{Wise08_Gal, Greif10} are apparent in the metallicity
+projections in Figure \ref{fig:projections}.  The average stellar
+metallicities is equal or slightly higher up to 0.5 dex than
+$[\bar{Z}_2/H]$.
 
-At $z \sim 8$, the metallicity of the intense halo dramatically
-self-enriches itself by a factor of 30 to $[\bar{Z}_2/H] = -1.5$
-during a starburst.  Because this halo is located in a large-scale
-overdensity, the ejecta falls back into the halo after reaching
-distances up to 20 comoving kpc, in turn keeping the halo gas
-metallicity high because the inflows are relatively metal-rich
-themselves.  The first few Pop II star clusters have [Z/H] between --1
-and --2 and dominate the average stellar metallicity at $z > 8$.
-After the $z \sim 8$ starburst, the average stellar metallicity
-follows the average gas metallicity within 0.1 dex.
+In the intense halo, the first few Pop II star clusters have [Z/H]
+between --1 and --2 and dominate the average stellar metallicity at $z
+> 8$.  Afterwards the metallicity increases itself by a factor of 30
+to $[\bar{Z}_2/H] = -1.5$ through self-enrichment from a starburst.
+Because this halo is located in a large-scale overdensity, most of the
+ejecta falls back into the halo after reaching distances up to 20
+comoving kpc, in turn keeping the halo gas metallicity high because
+the inflows are relatively metal-rich themselves.  After the $z \sim
+8$ starburst, the average stellar metallicity follows the average gas
+metallicity within 0.1 dex.
 
@@
 event and is enriched by this PISN, triggering the transition to Pop
-II star formation.  Other progenitors host three Pop III stars,
-forming at $z = 15.4, 14.2, 13.8$, with the latter producing a PISN.
-Metal enrichment from these two PISNe and Pop II SF quench Pop III
-star formation in this halo.
+II SF.  Other progenitors host three Pop III stars, forming at $z =
+15.4, 14.2, 13.8$, with the latter producing a PISN.  Metal enrichment
+from these two PISNe and Pop II SF quench Pop III SF in this halo.
 
@@
 were enriched by external blastwaves that only partially enriched the
-dense regions \citep{Cen08}.  The most massive progenitors of the
-intense halo cease to form Pop III stars at $z<12$ because of nearby
-or intrinsic PISNe.
+dense regions \citep{Cen08}.  These sites may form Pop III stars if
+dust cooling is efficient below \tento{-4} $Z_\odot$.  The most
+massive progenitors of the intense halo cease to form Pop III stars at
+$z<12$ because of nearby or intrinsic PISNe.
 
@@
   \plottwo{f4a}{f4b}
-  \caption{\label{fig:pops} The scatter plots show the star formation
-    history of the quiet (left) and intense (right) halos as a
-    function of metallicity at $z=7$.  Each circle represents a star
-    cluster, whose area is proportional to its mass.  The open circles
-    in the upper right represent sizes of $10^3$, $10^4$, and $10^5$
-    \Ms~star clusters.  The dashed lines in the right panel guide the
-    eye to two stellar populations that were formed in two satellite
-    halos, merging at $z=7.5$.  The upper histogram collects the star
-    formation history into 25 equal temporal bins.  The right
-    histogram depicts the stellar metallicity distribution.}
+  \caption{\label{fig:pops} The scatter plots show the SF history of
+    the quiet (left) and intense (right) halos as a function of
+    metallicity at $z=7$.  Each circle represents a star cluster,
+    whose area is proportional to its mass.  The open circles in the
+    upper right represent sizes of $10^3$, $10^4$, and $10^5$ \Ms~star
+    clusters.  The dashed lines in the right panel guide the eye to
+    two stellar populations that were formed in two satellite halos,
+    merging at $z=7.5$.  The upper histogram collects the SF history
+    into 25 equal temporal bins.  The right histogram depicts the
+    stellar metallicity distribution.}
 \end{figure*}
@@
 
-Figure \ref{fig:pops} shows the star formation history of both halos.
-From this plot, the metallicity distribution, star formation rates,
-and metallicity evolution and spread at a given time can all be
-extracted from these data.
+Figure \ref{fig:pops} shows the SF history (SFH) of both halos.  The
+metallicity distribution, SF rates, and metallicity evolution and
+spread at a given time can all be extracted from these data.
 
@@
 [Z/H] = --2.8 at which metallicity the first Pop II stars form.  The
-stellar metallicity evolution exhibits what is expected from a
-relatively isolated system with the stellar feedback steadily
-enriching the ISM, resulting in a correlation between stellar age and
-metallicity.  After $z=10$ the metallicities plateau at [Z/H] = --2.1
-for reasons discussed in \S\ref{sec:halo}.  The SFR peaks at $z=10$
-and decreases as the cold gas reservoir is depleted.  Around $z=7.5$,
-a 25:1 minor merger occurs, and the gas inside the satellite halo is
-compressed, triggering metal-poor, [Z/H] = --3.2, SF during its
-nearest approach.  This halo infalls through a filament, where most of
-metal enrichment in the quiet halo occurs in bi-polar flows
-perpendicular to the galaxy disk and filament.  The filament and thus
-this satellite halo remains relatively metal-poor.  The bi-polar
-outflows and metal-poor filaments are seen in the metallicity
-projections in Figure \ref{fig:projections}.  Stars with [Z/H] $<$ --3
-compose 1.6 percent of the total stellar mass.
+stellar metallicity evolution exhibits what is expected from an
+isolated system with the stellar feedback steadily enriching the ISM,
+resulting in a correlation between stellar age and metallicity.  After
+$z=10$ the metallicities plateau at [Z/H] = --2.1 for reasons
+discussed in \S\ref{sec:halo}.  The SFR peaks at $z=10$ and decreases
+as the cold gas reservoir is depleted.  Around $z=7.5$, a 25:1 minor
+merger occurs, and the gas inside the satellite halo is compressed,
+triggering metal-poor, [Z/H] = --3.2, SF during its nearest approach.
+This halo infalls through a filament, where most of metal enrichment
+in the quiet halo occurs in bi-polar flows perpendicular to the galaxy
+disk and filament.  The filament and thus this satellite halo remains
+relatively metal-poor.  Stars with [Z/H] $<$ --3 compose 1.6 percent
+of the total stellar mass.
 
 \textit{Intense halo}.--- In contrast with the quiet halo, the intense
-halo undergoes a few major mergers of halos with an established
-stellar population.  This creates a superposition of age-metallicity
-tracks in the SFH, seen in the complexity of Figure \ref{fig:pops}.
-The first two Pop II stellar clusters have an unusually high
-metallicity [Z/H] $\sim$ --1, which occurs when a PISN blastwave
-trigger star formation in two neighboring halos.  Most of the early
-star formation occurs around [Z/H] = --2.5.  At $z=9$, the halo's
-virial temperature reaches \tento{4} K.  This combined with a 10:1
-merger creates a starburst that quickly enriches the halo to [Z/H] =
---1.5 by $z=8$.  The halo continues to enrich itself with further SF
-until $z=7$.  The spikes in the scatter plot correspond to SN
-triggered star formation in nearby molecular clouds that are enriched
-up to a factor of 10 with respect to the ISM.  However the mass
-fraction of these metal-rich, SN triggered clusters are small compared
-to the total stellar mass.  The starburst at $z=9$ creates a bimodal
-metallicity distribution with peaks at [Z/H] = --2.4 and --1.2 with
-the metal-rich component mainly being created after the starburst.
-Two systems with sizable stellar components merge into the halo at $z
-\sim 8$, and their stellar populations are still discernible in the
-metallicity-age plot, whose tracks are noted by dashed lines.  Stars
-with [Z/H] $<$ --3 compose 1.8 percent of the total stellar mass.
+halo undergoes a few mergers of halos with an established stellar
+population.  This creates a superposition of age-metallicity tracks in
+the SFH, seen in the complexity of Figure \ref{fig:pops}.  The first
+two Pop II stellar clusters have an unusually high metallicity [Z/H]
+$\sim$ --1, which occurs when a PISN blastwave triggers SF in two
+neighboring halos.  Most of the early SF occurs around [Z/H] = --2.5.
+At $z=9$, the halo's virial temperature reaches \tento{4} K.  This
+combined with a 10:1 merger creates a starburst that quickly enriches
+the halo to [Z/H] = --1.5 by $z=8$.  The halo continues to enrich
+itself with further SF until $z=7$.  The spikes in the scatter plot
+correspond to SN triggered SF in nearby molecular clouds
+that are enriched up to a factor of 10 with respect to the ISM.
+However the mass fraction of these metal-rich, SN triggered clusters
+are small compared to the total stellar mass.  The starburst at $z=9$
+creates a bimodal metallicity distribution with peaks at [Z/H] = --2.4
+and --1.2 with the metal-rich component mainly being created after the
+starburst.  Two systems with sizable stellar components merge into the
+halo at $z \sim 8$, and their stellar populations are still
+discernible in the metallicity-age plot, whose tracks are noted by
+dashed lines.  Stars with [Z/H] $<$ --3 compose 1.8 percent of the
+total stellar mass.
 
@@
 by a factor of $\sim 10$ because (1) the metal ejecta is lowered by a
-factor of $\sim 50$ and the mixing mass is decreased by a factor of
-$(E_{\rm hyp}/E_{\rm PISN})^{3/5}$ in the Sedov-Taylor solution, where
-$(E_{\rm hyp}/E_{\rm PISN}) \sim 0.1$ is the ratio of explosion
-energies of a hypernova and PISN.  In the case where this metallicity
-floor is less than the critical metallicity, then the next starburst
-will further enrich the ISM, solidifying the transition to Pop II star
-formation.  We conclude that it only takes one, at most two, SNe from
-Pop III stars in the halo progenitors to complete the transition to
-Population II \citep[see also][]{Frebel10}.  The question of whether
-the critical metallicity is \tento{-6} or \tento{-3.5} $Z_\odot$ is
-most applicable to nearby halos where the heavy elements mix slowly
-into dense cores as the blastwave overtakes it.  Less than two percent
-of stars have [Z/H] $< -3$ in both systems, consistent with
-observations of metal-poor stars in the halo and dSphs
+factor of $\sim 50$ and (2) the mixing mass is approximately decreased
+by a factor of $(E_{\rm hyp}/E_{\rm PISN})^{3/5}$ in the Sedov-Taylor
+solution, where $(E_{\rm hyp}/E_{\rm PISN}) \sim 0.1$ is the ratio of
+explosion energies of a hypernova and PISN.  In the case where this
+metallicity floor is less than the critical metallicity, then the next
+instance of SF will further enrich the ISM, solidifying the transition
+to Pop II SF.  We conclude that it only takes one, at most two, SNe
+from Pop III stars in the halo progenitors to complete the transition
+to Population II \citep[see also][]{Frebel10}.  The question of
+whether the critical metallicity is \tento{-6} or \tento{-3.5}
+$Z_\odot$ is most applicable to nearby halos where the heavy elements
+mix slowly into dense cores as the blastwave overtakes it.  Less than
+two percent of stars have [Z/H] $< -3$ in both systems, consistent
+with observations of metal-poor stars in the halo and dSphs
 \citep[e.g.][]{Beers05, Frebel10_Obs}.
@@
 We also find that the merger history plays an important role in
-supplying gas into halos after its first epoch of star formation,
-mergers of halos below the filtering mass are inefficient in providing
-gas whereas the opposite is true for merging halos above the filtering
+supplying gas into halos after its first epoch of SF.  Mergers of
+halos below the filtering mass are inefficient in providing gas
+whereas the opposite is true for merging halos above the filtering
 mass.  Halos do not necessarily need $\tvir \ge 10^4$ K to form
@@
 mostly gas-poor mergers or a quiet merger history result in a
-monotonic increase in metallicity with time.  Star formation histories
-become more complex with multiple metallicity-age tracks if the halo
-experiences mergers with other halos that have an established stellar
-population.  Furthermore star formation that is triggered by
-blastwaves interacting with molecular clouds can have metallicities up
-to a factor of 10 higher than the main starburst.  Lastly we find that
-a starburst at $\tvir = 10^4$ K enriches the host halo enough to
-create a bimodal metallicity distribution, where the metal-poor
-component is created before the burst.  Note that mergers of stellar
-populations can also create a similar bimodal distribution.  Such
-distributions are observed in dSphs \citep[e.g.][]{Battaglia10}.
+monotonic increase in metallicity with time.  SFHs become more complex
+with multiple metallicity-age tracks if the halo experiences mergers
+with other halos that have an established stellar population.
+Furthermore SF that is triggered by blastwaves interacting with
+molecular clouds can have metallicities up to a factor of 10 higher
+than the main starburst.  Lastly we find that a starburst at $\tvir =
+10^4$ K enriches the host halo enough to create a bimodal metallicity
+distribution, where the metal-poor component is created before the
+burst.  Note that mergers of stellar populations can also create a
+similar bimodal distribution.  Such distributions are observed in
+dSphs \citep[e.g.][]{Battaglia10}.
 
 We have shown that it is possible to simulate the formation of a
-high-redshift dwarf galaxy and its entire star formation history,
-which provides invaluable insight on the first galaxies and the role
-of metal-free stars in the early universe.  There exists a wealth of
-information in this simulation, and we plan to follow up this
-preliminary report with more detailed analysis of the metal enrichment
-of the IGM, global star formation rates, and observational connections
-with high-redshift galaxies and Local Group dwarf galaxies in the near
-future.
+high-redshift dwarf galaxy and its entire SFH with radiative and
+mechanical feedback.  This provides invaluable insight on the first
+galaxies and the role of metal-free stars in the early universe.
+There exists a wealth of information in this simulation, and we plan
+to follow up this preliminary report with more detailed analysis of
+the metal enrichment of the IGM, global SF rates, and observational
+connections with high-redshift galaxies and Local Group dwarf galaxies
+in the near future.
 

### 2010-10-19 ms.tex
Incorporated changes from Matt's and Tom's comments.

@@
   characteristic masses form when the star-forming gas reaches a
-  critical metallicity of $10^{-6} - 10^{-3}~Z_\odot$, depending on
+  critical metallicity of $10^{-6} - 10^{-3.5}~Z_\odot$, depending on
   whether dust cooling is important.  We present adaptive mesh
@@
 Sedov-Taylor and snowplow phases.  In PISNe, approximately half of the
-metals stay in the IGM with an metal bubble size of a few kpc.  The
+metals stay in the IGM with a metal bubble size of a few kpc.  The
 remaining metals fall back into the host halo.  The blastwave may
@@
 We use the adaptive mesh refinement (AMR) code
-\enzo~v2.0\footnote[\dag]{\texttt{lca.ucsd.edu/enzo, unstable
+\enzo~v2.0\footnote[\dag]{\texttt{enzo.googlecode.com, unstable
     changeset b86d8ba026d6}} \citep{BryanNorman1997, OShea2004}, which
@@
 taken from \citet{Schaerer02}.  The radiation field is evolved with
-with adaptive ray tracing \citep{Abel02_RT, Wise10} and is coupled
+adaptive ray tracing \citep{Abel02_RT, Wise10} and is coupled
 self-consistently to the hydrodynamics.  We model the \hh~dissociating
@@
 all stars.  These stars die as pair-instability SNe (PISNe) if they
-are in the mass range 140--260 \Ms \citep{Heger03}.  We use the
+are in the mass range 140--260 \Ms~\citep{Heger03}.  We use the
 explosion energy from \citet{Heger02}, where we fit the following
@@
     $z=7$.  The left column shows the entire simulation volume, where
-    the center and right columns focus on the intense and quiet halos.
-    The metallicity projections are a composite picture of metals
+    the center and right columns focus on the intense and quiet halos,
+    which are marked by arrows in the upper-left panel.  The
+    metallicity projections are a composite picture of metals
     originating from Pop III (red) and Pop II (blue) stars with purple
@@
 
-\begin{figure}
+\begin{figure*}
   \epsscale{1.15}
-  \plotone{f1}
-  \caption{\label{fig:evo} Evolution of the total halo mass (top),
-    stellar mass (middle), and gas fraction (bottom) of the quiet
-    (dashed) and intense (solid) halos.}
+  \plottwo{f1}{f2}
+  \caption{\label{fig:evo} (a) Evolution of the total halo
+    mass (top), stellar mass (middle), and gas fraction (bottom) of
+    the quiet (dashed) and intense (solid) halos.  (b)
+    Mass-weighted stellar metallicities and gas metallicities enriched
+    by Pop II and Pop III SNe of the intense (top) and quiet (bottom)
+    halos.}
   \epsscale{1}
-\end{figure}
+\end{figure*}
 
@@
 
-Figure \ref{fig:evo} shows the total, metal-enriched stellar, and gas
+Figure \ref{fig:evo}a shows the total, metal-enriched stellar, and gas
 mass history of the most massive progenitors of both halos.  The quiet
@@
 and 7.9, seen in the rapid increases in total mass in Figure
-\ref{fig:evo}.  The merger history of the two halos are not atypical
+\ref{fig:evo}a.  The merger history of the two halos are not atypical
 as dark matter halos can experience both quiescent and vigorous mass
@@
 
-\label{sec:Zevo}
-\begin{figure}
-  \epsscale{1.15}
-  \plotone{f2}
-  \caption{\label{fig:Zevo} Mass-weighted stellar metallicities and
-    gas metallicities enriched by Pop II and Pop III SNe of the
-    intense (top) and quiet (bottom) halos.}
-  \epsscale{1}
-\end{figure}
-
 The evolution of the stellar and gas metallicity of both halos are
-illustrated in Figure \ref{fig:Zevo}.  PISNe from Pop III stars enrich
+illustrated in Figure \ref{fig:evo}b.  PISNe from Pop III stars enrich
 the nearby IGM out to a radius of 10 kpc and provides a metallicity
@@
 halo's progenitors until $z=9$ when most of these halos enter the
-metal-rich bubble surrounding the intense halo.  There are two Pop III
-stars forming at $z=7.7$ with [Z/H] = --5.7, whose molecular clouds
-were enriched by external blastwaves that only partially enriched the
-dense regions \citep{Cen08}.  These sites may form Pop III stars if
-dust cooling is efficient below \tento{-4} $Z_\odot$.  The most
-massive progenitors of the intense halo cease to form Pop III stars at
-$z<12$ because of nearby or intrinsic PISNe.
+metal-rich bubble surrounding the intense halo.  There are two stars
+forming at $z=7.7$ with [Z/H] = --5.7, whose molecular clouds were
+enriched by external blastwaves that only partially enriched the dense
+regions.  This falls into the metallicity range where fragmentation
+occurs only if dust cooling is efficient below \tento{-4} $Z_\odot$.
+The most massive progenitors of the intense halo cease to form Pop III
+stars at $z<12$ because of nearby or intrinsic PISNe.
 
@@
 with observations of metal-poor stars in the halo and dSphs
-\citep[e.g.][]{Beers05, Frebel10_Obs}.
+\citep[e.g.][]{Beers05, Battaglia10}.
 

### 2010-10-19 science_ms.tex
Adding first pass at science manuscript

--- 2010-10-19 ms.tex
@@
-\documentclass[apjl]{emulateapj}
-%\documentclass[12pt,preprint]{aastex}
+% Use only LaTeX2e, calling the article.cls class and 12-point type.
+
+\documentclass[12pt]{article}
 
 \usepackage{graphicx}
-\usepackage{epsfig}
-\usepackage{natbib}
-\usepackage[section] {placeins}
-\bibliographystyle{apj}
-\citestyle{apj}
 
-%%%%%%%% Begin custom definitions %%%%%%%%%%%%%
+\newcommand\aap{{A\&A}}% 
+         % Astronomy and Astrophysics 
+\newcommand\aaps{{A\&AS}}% 
+         % Astronomy and Astrophysics, Supplement 
+\newcommand\aj{{AJ}}% 
+         % Astronomical Journal 
+\newcommand\araa{{ARA\&A}}% 
+         % Annual Review of Astron and Astrophys 
+\newcommand\apj{{ApJ}}% 
+         % Astrophysical Journal 
+\newcommand\apjl{{ApJ}}% 
+         % Astrophysical Journal, Letters 
+\newcommand\apjs{{ApJS}}% 
+         % Astrophysical Journal, Supplement 
+\newcommand\mnras{{MNRAS}}% 
+         % Monthly Notices of the RAS 
+\newcommand\nat{{Nature}}% 
+         % Nature 
+\newcommand\pasp{{PASP}}% 
+         % Publications of the ASP 
+\newcommand{\cubecm}{\ifmmode{{\rm cm^{-3}}}\else{cm$^{-3}$}\fi}
+\newcommand{\lsim}{\lower0.3em\hbox{$\,\buildrel <\over\sim\,$}}
+\newcommand{\gsim}{\lower0.3em\hbox{$\,\buildrel >\over\sim\,$}}
+\newcommand{\kms}{\ifmmode{{\rm km~s^{-1}}}\else{km s$^{-1}$}\fi}
+\newcommand{\hh}{H$_2$}
+\newcommand{\Ms}{\ifmmode{M_\odot}\else{$M_\odot$}\fi}
+\newcommand\tento[1]{$10^{#1}$}
+\newcommand{\tvir}{\ifmmode{T_{\rm{vir}}}\else{$T_{\rm{vir}}$}\fi}
 
-\input macros.tex
+% Users of the {thebibliography} environment or BibTeX should use the
+% scicite.sty package, downloadable from *Science* at
+% www.sciencemag.org/about/authors/prep/TeX_help/ .
+% This package should properly format in-text
+% reference calls and reference-list numbers.
 
-%%%%%%%% End custom definitions %%%%%%%%%%
+%% We will uncomment this later
+%\usepackage{scicite}
+\bibliographystyle{Science}
 
-\begin{document}
+% Use times if you have the font installed; otherwise, comment out the
+% following line.
 
-\shorttitle{THE BIRTH OF A GALAXY}
-\shortauthors{WISE ET AL.}
+\usepackage{times}
+
+% The preamble here sets up a lot of new/revised commands and
+% environments.  It's annoying, but please do *not* try to strip these
+% out into a separate .sty file (which could lead to the loss of some
+% information when we convert the file to other formats).  Instead, keep
+% them in the preamble of your main LaTeX source file.
+
+% The following parameters seem to provide a reasonable page setup.
+
+\topmargin 0.0cm
+\oddsidemargin 0.2cm
+\textwidth 16cm 
+\textheight 21cm
+\footskip 1.0cm
+
+%The next command sets up an environment for the abstract to your paper.
+
+\newenvironment{sciabstract}{%
+\begin{quote} \bf}
+{\end{quote}}
+
+% If your reference list includes text notes as well as references,
+% include the following line; otherwise, comment it out.
+
+\renewcommand\refname{References and Notes}
+
+% The following lines set up an environment for the last note in the
+% reference list, which commonly includes acknowledgments of funding,
+% help, etc.  It's intended for users of BibTeX or the {thebibliography}
+% environment.  Users who are hand-coding their references at the end
+% using a list environment such as {enumerate} can simply add another
+% item at the end, and it will be numbered automatically.
+
+\newcounter{lastnote}
+\newenvironment{scilastnote}{%
+\setcounter{lastnote}{\value{enumiv}}%
+\addtocounter{lastnote}{+1}%
+\begin{list}%
+{\arabic{lastnote}.}
+{\setlength{\leftmargin}{.22in}}
+{\setlength{\labelsep}{.5em}}}
+{\end{list}}
+
+% Include your paper's title here
 
@@
 
-\author{John H. Wise\altaffilmark{1,2}, 
-  Michael L. Norman\altaffilmark{3},
-  Tom Abel\altaffilmark{4},
-  Matthew J. Turk\altaffilmark{3}}
+% Place the author information here.  Please hand-code the contact
+% information and notecalls; do *not* use \footnote commands.  Let the
+% author contact information appear immediately below the author names
+% as shown.  We would also prefer that you don't change the type-size
+% settings shown here.
 
-\altaffiltext{1}{Department of Astrophysical Sciences, Princeton
-  University, Peyton Hall, Ivy Lane, Princeton, NJ 08544}
-\altaffiltext{2}{Hubble Fellow}
-\altaffiltext{3}{Center for Astrophysics and Space Sciences,
-  University of California at San Diego, La Jolla, CA 92093}
-\altaffiltext{4}{Kavli Institute for Particle Astrophysics and
-  Cosmology, Stanford University, Menlo Park, CA 94025}
-\email{jwise@astro.princeton.edu}
+\author
+{John H.~Wise,$^{1,2\ast}$ Michael L.~Norman,$^{3}$ Tom Abel$^{4}$,
+Matthew J.~Turk$^{3}$\\
+\\
+\normalsize{$^{1}$Department of Astrophysical Sciences, Princeton
+University,}\\
+\normalsize{Peyton Hall, Ivy Lane, Princeton, NJ 08544}\\
+\normalsize{$^{2}$Hubble Fellow}\\
+\normalsize{$^{3}$Center for Astrophysics and Space Sciences,}\\
+\normalsize{University of California at San Diego, La Jolla, CA 92093}\\
+\normalsize{$^{4}$Kavli Institute for Particle Astrophysics and
+  Cosmology, }\\
+\normalsize{Stanford University, Menlo Park, CA 94025}\\
+\\
+\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:
+jwise@astro.princeton.edu}
+}
 
-\begin{abstract}
+% Include the date command, but leave its argument blank.
 
+\date{}
+
+%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%
+
+\begin{document}
+
+% Double-space the manuscript.
+
+\baselineskip24pt
+
+% Make the title.
+
+\maketitle
+
+% Place your abstract within the special {sciabstract} environment.
+
+\begin{sciabstract}
   Population III stars first form in dark matter halos with masses
-  around $10^6 \Ms$.  By definition, they are metal-free, and their
+  around $10^6~\Ms$.  By definition, they are metal-free, and their
   protostellar collapse is driven by molecular hydrogen cooling in the
@@
   recovers from 5 percent to nearly the cosmic fraction in halos with
-  merger histories rich in halos above $10^7 \Ms$.  A single
+  merger histories rich in halos above $10^7~\Ms$.  A single
   pair-instability supernova is sufficient to enrich the host halo to
-  a metallicity floor of $10^{-3} Z_\odot$ and to transition to
+  a metallicity floor of $10^{-3}~Z_\odot$ and to transition to
   Population II star formation.  Neighboring halos are enriched to
@@
   cooling.
+\end{sciabstract}
 
-\end{abstract}
+% In setting up this template for *Science* papers, we've used both
+% the \section* command and the \paragraph* command for topical
+% divisions.  Which you use will of course depend on the type of paper
+% you're writing.  Review Articles tend to have displayed headings, for
+% which \section* is more appropriate; Research Articles, when they have
+% formal topical divisions at all, tend to signal them with bold text
+% that runs into the paragraph, for which \paragraph* is the right
+% choice.  Either way, use the asterisk (*) modifier, as shown, to
+% suppress numbering.
 
-\keywords{cosmology --- methods: numerical --- hydrodynamics ---
-  radiative transfer --- star formation}
-
-\section{Motivation}
+\section*{Motivation}
 
@@
 characteristic mass and suppressed fragmentation in its protostellar
-collapse \citep{Abel00, ABN02, Bromm02_P3, Yoshida03, OShea07a}.  A
+collapse \cite{Abel00, ABN02, Bromm02_P3, Yoshida03, OShea07a}.  A
 fraction of these stars enrich the surrounding intergalactic medium
-(IGM) when they go supernova, which can happen in stars $\lsim40~\Ms$
+(IGM) when they go supernova, which can happen in stars $\lsim 40~\Ms$
 in Type II supernovae (SNe) or in stars roughly between 140 \Ms~and
-260 \Ms~in pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}.
+260 \Ms~in pair-instability SNe (PISNe; \cite{2002ApJ...567..532H}).
 The host halo and the neighboring halos are then enriched with this
 ejecta.  There exists a critical metallicity that is $\sim 10^{-6}
-Z_\odot$ if dust cooling is efficient \citep{Omukai05,
+Z_\odot$ if dust cooling is efficient \cite{Omukai05,
   Schneider06_Frag, clark08} and $\sim 10^{-3.5} Z_\odot$ otherwise
-\citep{Bromm01, 2009ApJ...691..441S}, where the gas can cool rapidly,
+\cite{Bromm01, 2009ApJ...691..441S}, where the gas can cool rapidly,
 lowering its Jeans mass.  An intermediate characteristic mass of
 $\sim10~\Ms$ can be occur if the gas cooling is suppressed to the
-cosmic microwave background (CMB) temperature \citep{Larson98,
+cosmic microwave background (CMB) temperature \cite{Larson98,
   Tumlinson07_IMF, 2009ApJ...691..441S}.  The resulting Population II
@@
 metal-poor stars have a metallicity floor of [Z/H] = --4
-\citep{Beers05}.  In dwarf spheroidal (dSph) galaxies, this floor is a
-factor of 10 higher \citep{Tolstoy04, Helmi06}, however several metal
+\cite{Beers05}.  In dwarf spheroidal (dSph) galaxies, this floor is a
+factor of 10 higher \cite{Tolstoy04, Helmi06}, however several metal
 poor stars with $-4 < [\mathrm{Z/H}] < -3$ have been recently
-discovered in dSphs \citep{Tafelmeyer10, Frebel10_Obs}.
+discovered in dSphs \cite{Tafelmeyer10, Frebel10_Obs}.
 
@@
 leaves behind a warm ($3 \times 10^4$ K) and diffuse (0.5 \cubecm)
-medium \citep{Kitayama04, Whalen04, Abel07}.  This aids in the
+medium \cite{Kitayama04, Whalen04, Abel07}.  This aids in the
 expansion of the blastwave because it delays the transition to the
@@
 induce SF in nearby halos through the compression of the gas
-\citep{Ferrara98}; however timescales for metal mixing into the dense
-gas are many dynamical times \citep{Cen08} for shock velocities $\lsim
-100~\kms$.
+\cite{Ferrara98}; however timescales for metal mixing into the dense gas are
+many dynamical times \cite{Cen08} for shock velocities $\lsim100~\kms$.
 
@@
 
-\section{Method}
+\section*{Method}
 \label{sec:setup}
@@
 
-\subsection{Simulation setup}
+\subsection*{Simulation setup}
 
 We use the adaptive mesh refinement (AMR) code
-\enzo~v2.0\footnote[\dag]{\texttt{enzo.googlecode.com, unstable
-    changeset b86d8ba026d6}} \citep{BryanNorman1997, OShea2004}, which
-has been modified to use a HLLC Riemann solver \citep{Toro94_HLLC} for
-additional stability in strong shocks.  To resolve minihalos with at
-least 100 dark matter (DM) particles and follow the formation of the
-first generation of dwarf galaxies, we use a simulation box of 1 Mpc
-that has a resolution of $256^3$.  This gives us a DM mass resolution
-of 1840 \Ms.  We refine the grid on baryon overdensities of $3 \times
-2^{-0.2l}$, where $l$ is the AMR level, resulting in a
-super-Lagrangian behavior.  We also refine on a DM overdensity of $3
-\times 2^l$ and always resolve the local Jeans length by at least 4
-cells, avoiding artificial fragmentation during gaseous collapses
-\citep{Truelove97}.  We initialize the simulation with \textsl{grafic}
-\citep{Bertschinger01} at $z = 130$ and use the cosmological
-parameters from the 7-year WMAP data \citep{WMAP7}: $\Omega_M =
-0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$,
-$\sigma_8 = 0.81$, and $n = 0.963$ with the variables having their
-usual definitions.  We stop the simulation at $z=7$.
+enzo~v2.0\footnote{\texttt{enzo.googlecode.com, unstable changeset
+b86d8ba026d6}} \cite{BryanNorman1997, OShea2004}, which has been modified to
+use a HLLC Riemann solver \cite{Toro94_HLLC} for additional stability in strong
+shocks.  To resolve minihalos with at least 100 dark matter (DM) particles and
+follow the formation of the first generation of dwarf galaxies, we use a
+simulation box of 1 Mpc that has a resolution of $256^3$.  This gives us a DM
+mass resolution of 1840 \Ms.  We refine the grid on baryon overdensities of $3
+\times 2^{-0.2l}$, where $l$ is the AMR level, resulting in a super-Lagrangian
+behavior.  We also refine on a DM overdensity of $3 \times 2^l$ and always
+resolve the local Jeans length by at least 4 cells, avoiding artificial
+fragmentation during gaseous collapses \cite{Truelove97}.  We initialize the
+simulation with \textsl{grafic} \cite{Bertschinger01} at $z = 130$ and use the
+cosmological parameters from the 7-year WMAP data \cite{WMAP7}: $\Omega_M =
+0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 =
+0.81$, and $n = 0.963$ with the variables having their usual definitions.  We
+stop the simulation at $z=7$.
 
 We use a non-equilibrium chemistry solver with 9 species of hydrogen,
-helium, and molecular hydrogen \citep{Abel97}.  We will follow-up this
+helium, and molecular hydrogen \cite{Abel97}.  We will follow-up this
 study with one that considers radiative cooling from metal-enriched
-gas, using the method of \citet{2008MNRAS.385.1443S}.
+gas, using the method of \cite{2008MNRAS.385.1443S}.
 
@@
 % hydrogen, helium, and molecular hydrogen.  For metal cooling, we use a
-% cooling curve that is calculated from CLOUDY \citep{CLOUDY} and using
-% the method of \citet{2008MNRAS.385.1443S}.  It is tabulated based on
+% cooling curve that is calculated from CLOUDY \cite{CLOUDY} and using
+% the method of \cite{2008MNRAS.385.1443S}.  It is tabulated based on
 % density, temperature, electron fraction, and metallicity.
 
-\subsection{Star formation}
+\subsection*{Star formation}
 
@@
 coexist with the dark matter halo center with limited fragmentation
-occurring during their collapse; however \citet{2009Sci...325..601T}
-and \citet{Stacy10_Binary} have recently shown that Pop III binaries
+occurring during their collapse; however \cite{2009Sci...325..601T}
+and \cite{Stacy10_Binary} have recently shown that Pop III binaries
 may form in a fraction of such halos.
@@
 % at the high-mass end and an exponential cut-off below $M_{\rm char}$
-% \citep{refs}.
+% \cite{refs}.
 
-For Pop III stars, we use the same SF model as \citet{Abel07} and
-\citet{Wise08_Gal} where each star particle represents a single star.
+For Pop III stars, we use the same SF model as \cite{Abel07} and
+\cite{Wise08_Gal} where each star particle represents a single star.
 The critical overdensity in which a star forms is $5 \times 10^5$.
@@
 Salpeter IMF but is exponentially cutoff below that mass
-\citep{Chabrier03, Clark09}.  For reproducibility, we record the
-number of times the random number generator \citep[Mersenne
-  twister;][]{MTwister} has been called for use when restarting the
-simulations.
+\cite{Chabrier03, Clark09}.  For reproducibility, we record the
+number of times the random number generator (Mersenne twister; \cite{MTwister})
+has been called for use when restarting the simulations.
 
@@
 
-We treat Pop II SF with the same prescription as \citet{Wise09}, which
-is a modified version of the \citet{Cen92} method but accounts for the
+We treat Pop II SF with the same prescription as \cite{Wise09}, which
+is a modified version of the \cite{Cen92} method but accounts for the
 fact that the molecular clouds are resolved.  The critical overdensity
@@
 
-\subsection{Stellar feedback}
+\subsection*{Stellar feedback}
 
 The mass-dependent luminosities and lifetimes of the Pop III stars are
-taken from \citet{Schaerer02}.  The radiation field is evolved with
-adaptive ray tracing \citep{Abel02_RT, Wise10} and is coupled
+taken from \cite{Schaerer02}.  The radiation field is evolved with
+adaptive ray tracing \cite{Abel02_RT, Wise10} and is coupled
 self-consistently to the hydrodynamics.  We model the \hh~dissociating
@@
 all stars.  These stars die as pair-instability SNe (PISNe) if they
-are in the mass range 140--260 \Ms~\citep{Heger03}.  We use the
-explosion energy from \citet{Heger02}, where we fit the following
+are in the mass range 140--260 \Ms~\cite{Heger03}.  We use the
+explosion energy from \cite{Heger02}, where we fit the following
 function to their models, $E_{\rm PISN} = 10^{51} \times [5.0 + 1.304
@@
 factor of four more ionizing photons than a solar metallicity
-population \citep{Schaerer03} and might be underestimating the
+population \cite{Schaerer03} and might be underestimating the
 radiative feedback.  Nonetheless this study provides an excellent
@@
 
-\section{Results}
+\section*{Results}
 \label{sec:results}
-
-\begin{figure*}
-  \epsscale{0.8}
-  \plotone{f3}
-  \epsscale{1}
-  \caption{\label{fig:projections} Density-weighted projections of gas
-    density (top), temperature (middle), and metallicity (bottom) at
-    $z=7$.  The left column shows the entire simulation volume, where
-    the center and right columns focus on the intense and quiet halos,
-    which are marked by arrows in the upper-left panel.  The
-    metallicity projections are a composite picture of metals
-    originating from Pop III (red) and Pop II (blue) stars with purple
-    indicating a mixture of the two.}
-\end{figure*}
 
@@
 
-\subsection{Mass evolution}
+\subsection*{Mass evolution}
 \label{sec:halo}
-
-\begin{figure*}
-  \epsscale{1.15}
-  \plottwo{f1}{f2}
-  \caption{\label{fig:evo} (a) Evolution of the total halo
-    mass (top), stellar mass (middle), and gas fraction (bottom) of
-    the quiet (dashed) and intense (solid) halos.  (b)
-    Mass-weighted stellar metallicities and gas metallicities enriched
-    by Pop II and Pop III SNe of the intense (top) and quiet (bottom)
-    halos.}
-  \epsscale{1}
-\end{figure*}
 
@@
 consistent with the filtering mass $M_f$ of high-redshift halos when
-it accretes mainly from a pre-heated IGM \citep{gnedin98, gnedin00,
+it accretes mainly from a pre-heated IGM \cite{gnedin98, gnedin00,
   Wise08_Gal}.  Afterwards these halos can cool efficiently through
@@
 
-\subsection{Metallicity evolution}
+\subsection*{Metallicity evolution}
 
@@
 metal-poor.  These features and a well-mixed ISM
-\citep[cf.][]{Wise08_Gal, Greif10} are apparent in the metallicity
+(cf.~\cite{Wise08_Gal, Greif10}) are apparent in the metallicity
 projections in Figure \ref{fig:projections}.  The average stellar
@@
 
-\subsection{Population III star formation history}
+\subsection*{Population III star formation history}
 
@@
 
-\subsection{Population II stellar populations}
+\subsection*{Population II stellar populations}
 \label{sec:pop}
-
-\begin{figure*}
-  \plottwo{f4a}{f4b}
-  \caption{\label{fig:pops} The scatter plots show the SF history of
-    the quiet (left) and intense (right) halos as a function of
-    metallicity at $z=7$.  Each circle represents a star cluster,
-    whose area is proportional to its mass.  The open circles in the
-    upper right represent sizes of $10^3$, $10^4$, and $10^5$ \Ms~star
-    clusters.  The dashed lines in the right panel guide the eye to
-    two stellar populations that were formed in two satellite halos,
-    merging at $z=7.5$.  The upper histogram collects the SF history
-    into 25 equal temporal bins.  The right histogram depicts the
-    stellar metallicity distribution.}
-\end{figure*}
 
@@
 
-\section{Discussion and Conclusions}
+\section*{Discussion and Conclusions}
 
@@
 probability in surviving as present-day ``fossil'' galaxies
-\citep{Gnedin06}, otherwise they will be incorporated into galactic
+\cite{Gnedin06}, otherwise they will be incorporated into galactic
 stellar halos.
@@
 have a lower characteristic mass that favor hypernovae
-\citep{Tumlinson07_IMF}, then this metallicity floor should be lowered
+\cite{Tumlinson07_IMF}, then this metallicity floor should be lowered
 by a factor of $\sim 10$ because (1) the metal ejecta is lowered by a
@@
 from Pop III stars in the halo progenitors to complete the transition
-to Population II \citep[see also][]{Frebel10}.  The question of
+to Population II \cite{Frebel10}.  The question of
 whether the critical metallicity is \tento{-6} or \tento{-3.5}
@@
 with observations of metal-poor stars in the halo and dSphs
-\citep[e.g.][]{Beers05, Battaglia10}.
+\cite{Beers05, Battaglia10}.
 
@@
 similar bimodal distribution.  Such distributions are observed in
-dSphs \citep[e.g.][]{Battaglia10}.
+dSphs \cite{Battaglia10}.
 
@@
 
-\acknowledgments
+% Your references go at the end of the main text, and before the
+% figures.  For this document we've used BibTeX, the .bib file
+% scibib.bib, and the .bst file Science.bst.  The package scicite.sty
+% was included to format the reference numbers according to *Science*
+% style.
 
-Support for this work was provided by NASA through Hubble Fellowship
+\bibliography{ms}
+
+% Following is a new environment, {scilastnote}, that's defined in the
+% preamble and that allows authors to add a reference at the end of the
+% list that's not signaled in the text; such references are used in
+% *Science* for acknowledgments of funding, help, etc.
+
+\begin{scilastnote}
+\item Support for this work was provided by NASA through Hubble Fellowship
 grant \#120-6370 awarded by the Space Telescope Science Institute,
@@
 J.~H.~W. thanks Renyue Cen, Amina Helmi, Marco Spaans, and Eline
-Tolstoy for enlightening discussions.  The majority of the analysis
-and plots were done with \texttt{yt} \citep{yt_full_paper}.
+Tolstoy for enlightening discussions.
+\end{scilastnote}
 
-%\clearpage
-%\input biblio.tex
-\bibliography{ms}
+% For your review copy (i.e., the file you initially send in for
+% evaluation), you can use the {figure} environment and the
+% \includegraphics command to stream your figures into the text, placing
+% all figures at the end.  For the final, revised manuscript for
+% acceptance and production, however, PostScript or other graphics
+% should not be streamed into your compliled file.  Instead, set
+% captions as simple paragraphs (with a \noindent tag), setting them
+% off from the rest of the text with a \clearpage as shown  below, and
+% submit figures as separate files according to the Art Department's
+% instructions.
+
+\clearpage
+\begin{figure*}
+\includegraphics[width=0.88\textwidth]{f3.eps}
+  \caption{\label{fig:projections} Density-weighted projections of gas
+    density (top), temperature (middle), and metallicity (bottom) at
+    $z=7$.  The left column shows the entire simulation volume, where
+    the center and right columns focus on the intense and quiet halos,
+    which are marked by arrows in the upper-left panel.  The
+    metallicity projections are a composite picture of metals
+    originating from Pop III (red) and Pop II (blue) stars with purple
+    indicating a mixture of the two.}
+\end{figure*}
+
+\clearpage
+\begin{figure*}
+% Need to include f2.eps
+\includegraphics[width=0.88\textwidth]{f1.eps}
+  \caption{\label{fig:evo} (a) Evolution of the total halo
+    mass (top), stellar mass (middle), and gas fraction (bottom) of
+    the quiet (dashed) and intense (solid) halos.  (b)
+    Mass-weighted stellar metallicities and gas metallicities enriched
+    by Pop II and Pop III SNe of the intense (top) and quiet (bottom)
+    halos.}
+\end{figure*}
+
+\clearpage
+\begin{figure*}
+% Needs f4b.eps
+\includegraphics[width=0.88\textwidth]{f4a.eps}
+  \caption{\label{fig:pops} The scatter plots show the SF history of
+    the quiet (left) and intense (right) halos as a function of
+    metallicity at $z=7$.  Each circle represents a star cluster,
+    whose area is proportional to its mass.  The open circles in the
+    upper right represent sizes of $10^3$, $10^4$, and $10^5$ \Ms~star
+    clusters.  The dashed lines in the right panel guide the eye to
+    two stellar populations that were formed in two satellite halos,
+    merging at $z=7.5$.  The upper histogram collects the SF history
+    into 25 equal temporal bins.  The right histogram depicts the
+    stellar metallicity distribution.}
+\end{figure*}
+
+%\noindent {\bf Fig. 1.} Please do not use figure environments to set
+%up your figures in the final (post-peer-review) draft, do not include graphics in your
+%source code, and do not cite figures in the text using \LaTeX\
+%\verb+\ref+ commands.  Instead, simply refer to the figure numbers in
+%the text per {\it Science\/} style, and include the list of captions at
+%the end of the document, coded as ordinary paragraphs as shown in the
+%\texttt{scifile.tex} template file.  Your actual figure files should
+%be submitted separately.
+
+%\include{som}
 

### 2010-10-19 science_ms.tex
Adding in supporting online material, moved the methods to that.  The TeXcount perl script suggests another ~400 words should be pulled from the manuscript.

@@
 %% We will uncomment this later
-%\usepackage{scicite}
+\usepackage{scicite}
 \bibliographystyle{Science}
@@
 complexities and the transition from Pop III to II stars.  In this
-Letter, we present the simulations that include both types of SF, and
+Report, we present the simulations that include both types of SF, and
 their radiative and mechanical feedback.  We utilize an initial mass
@@
 have been interconnected in a simulation that resolves star-forming
-minihalos to study the transition to Pop II star formation.  We
-describe our simulation setup and our adopted SF models in \S
-\ref{sec:setup} and present our results in \S \ref{sec:results}.  We
-discuss the implications of our findings and conclude in the last
-section.
-
-\section*{Method}
-\label{sec:setup}
-
-In this section, we first describe our simulation setup.  We then
-detail the SF models used here and how we model radiative and SNe
-feedback.
-
-\subsection*{Simulation setup}
-
-We use the adaptive mesh refinement (AMR) code
-enzo~v2.0\footnote{\texttt{enzo.googlecode.com, unstable changeset
-b86d8ba026d6}} \cite{BryanNorman1997, OShea2004}, which has been modified to
-use a HLLC Riemann solver \cite{Toro94_HLLC} for additional stability in strong
-shocks.  To resolve minihalos with at least 100 dark matter (DM) particles and
-follow the formation of the first generation of dwarf galaxies, we use a
-simulation box of 1 Mpc that has a resolution of $256^3$.  This gives us a DM
-mass resolution of 1840 \Ms.  We refine the grid on baryon overdensities of $3
-\times 2^{-0.2l}$, where $l$ is the AMR level, resulting in a super-Lagrangian
-behavior.  We also refine on a DM overdensity of $3 \times 2^l$ and always
-resolve the local Jeans length by at least 4 cells, avoiding artificial
-fragmentation during gaseous collapses \cite{Truelove97}.  We initialize the
-simulation with \textsl{grafic} \cite{Bertschinger01} at $z = 130$ and use the
-cosmological parameters from the 7-year WMAP data \cite{WMAP7}: $\Omega_M =
-0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 =
-0.81$, and $n = 0.963$ with the variables having their usual definitions.  We
-stop the simulation at $z=7$.
-
-We use a non-equilibrium chemistry solver with 9 species of hydrogen,
-helium, and molecular hydrogen \cite{Abel97}.  We will follow-up this
-study with one that considers radiative cooling from metal-enriched
-gas, using the method of \cite{2008MNRAS.385.1443S}.
-
-% We peform two simulations with the same initial conditions.  They
-% differ only in that one considers primordial cooling, and the other
-% considers additional cooling in metal-enriched gas.  For primordial
-% cooling, we use a non-equilbrium chemistry solver with 9 species of
-% hydrogen, helium, and molecular hydrogen.  For metal cooling, we use a
-% cooling curve that is calculated from CLOUDY \cite{CLOUDY} and using
-% the method of \cite{2008MNRAS.385.1443S}.  It is tabulated based on
-% density, temperature, electron fraction, and metallicity.
-
-\subsection*{Star formation}
-
-We distinguish Pop II and Pop III SF by the metallicity of the densest
-cell in the molecular cloud.  Pop II stars are formed if [Z/H] $> -4$,
-and Pop III stars are formed otherwise.  We do not consider Pop III.2
-stars and intermediate mass stars from CMB-limited cooling.
-
-Simulations have shown that the characteristic mass of Pop III stars
-$M_{\rm char} \sim 100~\Ms$.  They form in molecular clouds that
-coexist with the dark matter halo center with limited fragmentation
-occurring during their collapse; however \cite{2009Sci...325..601T}
-and \cite{Stacy10_Binary} have recently shown that Pop III binaries
-may form in a fraction of such halos.
-
-% Furthermore, detailed one-dimensional calculations have shown that
-% their IMF should follow a Kroupa-like IMF that has a Salpeter slope
-% at the high-mass end and an exponential cut-off below $M_{\rm char}$
-% \cite{refs}.
-
-For Pop III stars, we use the same SF model as \cite{Abel07} and
-\cite{Wise08_Gal} where each star particle represents a single star.
-The critical overdensity in which a star forms is $5 \times 10^5$.
-Instead of using a fixed stellar mass, we randomly sampled from an IMF
-with a functional form of
-%
-\begin{equation}
-\label{eqn:imf}
-f(M)dM = M^{-1.3} \exp\left[-\left(\frac{M_{\rm char}}{M}\right)^{1.6}\right]
-\end{equation}
-to determine the stellar mass.  Above $M_{\rm char}$, it behaves as a
-Salpeter IMF but is exponentially cutoff below that mass
-\cite{Chabrier03, Clark09}.  For reproducibility, we record the
-number of times the random number generator (Mersenne twister; \cite{MTwister})
-has been called for use when restarting the simulations.
-
-%%% FOR THE COMPARISON BETWEEN RUNS WITH AND WITHOUT METAL COOLING %%%
-%
-% Although the Pop III star formation history (SFH) is identical for a
-% given $N$ stars, the Pop III SFH for a given halo can be different
-% between the two simulations.  This happens because the order in which
-% halos form Pop III stars can be altered from enhanced star formation
-% and feedback from nearby Pop II star clusters, as we will demonstrate
-% in this Letter.
-
-We treat Pop II SF with the same prescription as \cite{Wise09}, which
-is a modified version of the \cite{Cen92} method but accounts for the
-fact that the molecular clouds are resolved.  The critical overdensity
-is the same as the Pop III SF model.  In each star-forming region,
-seven percent of the cold gas ($T < 10^3$ K) is removed from the grid
-and deposited into the star particle.  Each star particle lives for 20
-Myr, the maximum lifetime of an OB star.  These stars generate the
-majority of the ionizing radiation and SNe feedback in stellar
-clusters, thus we ignore lower mass stars.
-
-\subsection*{Stellar feedback}
-
-The mass-dependent luminosities and lifetimes of the Pop III stars are
-taken from \cite{Schaerer02}.  The radiation field is evolved with
-adaptive ray tracing \cite{Abel02_RT, Wise10} and is coupled
-self-consistently to the hydrodynamics.  We model the \hh~dissociating
-radiation with an optically-thin, inverse square profile, centered on
-all stars.  These stars die as pair-instability SNe (PISNe) if they
-are in the mass range 140--260 \Ms~\cite{Heger03}.  We use the
-explosion energy from \cite{Heger02}, where we fit the following
-function to their models, $E_{\rm PISN} = 10^{51} \times [5.0 + 1.304
-(M_{\rm He} - 64)]$, where $M_{\rm He} = (13/24) \times (M_\star - 20)
-\Ms$ is the helium core mass and $M_\star$ is the stellar mass.
-
-The Pop II stars emit 6000 hydrogen ionizing photons per baryon over
-their lifetime, and we do not consider singly- and doubly-ionizing
-helium photons.  We note that low-metallicity stars generate up to a
-factor of four more ionizing photons than a solar metallicity
-population \cite{Schaerer03} and might be underestimating the
-radiative feedback.  Nonetheless this study provides an excellent
-first insight in the transition to Pop II SF, as the metal enrichment
-is the key ingredient here.  For SN feedback, these stars generate
-$6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$ of energy after living
-for 4 Myr, which is injected into spheres with a radius of 10 pc.  If
-the resolution of the grid is less than 10/3 pc, we deposit the energy
-into a $3^3$ cube surrounding the star particle.
+minihalos to study the transition to Pop II star formation.
 
@@
 
-In this paper, we focus on the birth of two galaxies prior to
+In this Report, we focus on the birth of two galaxies prior to
 reionization with a cosmological AMR radiation hydrodynamics

### 2010-10-19 science_som.tex
Adding in supporting online material, moved the methods to that.  The TeXcount perl script suggests another ~400 words should be pulled from the manuscript.

--- 2010-10-19 ms.tex
@@
-\documentclass[apjl]{emulateapj}
-%\documentclass[12pt,preprint]{aastex}
+% Use only LaTeX2e, calling the article.cls class and 12-point type.
+
+\documentclass[12pt]{article}
 
 \usepackage{graphicx}
-\usepackage{epsfig}
-\usepackage{natbib}
-\usepackage[section] {placeins}
-\bibliographystyle{apj}
-\citestyle{apj}
 
-%%%%%%%% Begin custom definitions %%%%%%%%%%%%%
+\newcommand\aap{{A\&A}}% 
+         % Astronomy and Astrophysics 
+\newcommand\aaps{{A\&AS}}% 
+         % Astronomy and Astrophysics, Supplement 
+\newcommand\aj{{AJ}}% 
+         % Astronomical Journal 
+\newcommand\araa{{ARA\&A}}% 
+         % Annual Review of Astron and Astrophys 
+\newcommand\apj{{ApJ}}% 
+         % Astrophysical Journal 
+\newcommand\apjl{{ApJ}}% 
+         % Astrophysical Journal, Letters 
+\newcommand\apjs{{ApJS}}% 
+         % Astrophysical Journal, Supplement 
+\newcommand\mnras{{MNRAS}}% 
+         % Monthly Notices of the RAS 
+\newcommand\nat{{Nature}}% 
+         % Nature 
+\newcommand\pasp{{PASP}}% 
+         % Publications of the ASP 
+\newcommand{\cubecm}{\ifmmode{{\rm cm^{-3}}}\else{cm$^{-3}$}\fi}
+\newcommand{\lsim}{\lower0.3em\hbox{$\,\buildrel <\over\sim\,$}}
+\newcommand{\gsim}{\lower0.3em\hbox{$\,\buildrel >\over\sim\,$}}
+\newcommand{\kms}{\ifmmode{{\rm km~s^{-1}}}\else{km s$^{-1}$}\fi}
+\newcommand{\hh}{H$_2$}
+\newcommand{\Ms}{\ifmmode{M_\odot}\else{$M_\odot$}\fi}
+\newcommand\tento[1]{$10^{#1}$}
+\newcommand{\tvir}{\ifmmode{T_{\rm{vir}}}\else{$T_{\rm{vir}}$}\fi}
 
-\input macros.tex
+% Users of the {thebibliography} environment or BibTeX should use the
+% scicite.sty package, downloadable from *Science* at
+% www.sciencemag.org/about/authors/prep/TeX_help/ .
+% This package should properly format in-text
+% reference calls and reference-list numbers.
 
-%%%%%%%% End custom definitions %%%%%%%%%%
+%% We will uncomment this later
+\usepackage{scicite}
+\bibliographystyle{Science}
+
+% Use times if you have the font installed; otherwise, comment out the
+% following line.
+
+%\usepackage{times}
+
+% The preamble here sets up a lot of new/revised commands and
+% environments.  It's annoying, but please do *not* try to strip these
+% out into a separate .sty file (which could lead to the loss of some
+% information when we convert the file to other formats).  Instead, keep
+% them in the preamble of your main LaTeX source file.
+
+% The following parameters seem to provide a reasonable page setup.
+
+\topmargin 0.0cm
+\oddsidemargin 0.2cm
+\textwidth 16cm 
+\textheight 21cm
+\footskip 1.0cm
 
@@
 
-\shorttitle{THE BIRTH OF A GALAXY}
-\shortauthors{WISE ET AL.}
+% Double-space the manuscript.
 
-\title{The Birth of a Galaxy: Population III Metal Enrichment and
-  Population II Stellar Populations}
+\baselineskip24pt
 
-\author{John H. Wise\altaffilmark{1,2}, 
-  Michael L. Norman\altaffilmark{3},
-  Tom Abel\altaffilmark{4},
-  Matthew J. Turk\altaffilmark{3}}
+\section*{Supporting Online Material}
 
-\altaffiltext{1}{Department of Astrophysical Sciences, Princeton
-  University, Peyton Hall, Ivy Lane, Princeton, NJ 08544}
-\altaffiltext{2}{Hubble Fellow}
-\altaffiltext{3}{Center for Astrophysics and Space Sciences,
-  University of California at San Diego, La Jolla, CA 92093}
-\altaffiltext{4}{Kavli Institute for Particle Astrophysics and
-  Cosmology, Stanford University, Menlo Park, CA 94025}
-\email{jwise@astro.princeton.edu}
-
-\begin{abstract}
-
-  Population III stars first form in dark matter halos with masses
-  around $10^6 \Ms$.  By definition, they are metal-free, and their
-  protostellar collapse is driven by molecular hydrogen cooling in the
-  gas-phase, leading to a massive characteristic mass $\sim 100~\Ms$
-  and suppressed fragmentation.  Population II stars with lower
-  characteristic masses form when the star-forming gas reaches a
-  critical metallicity of $10^{-6} - 10^{-3.5}~Z_\odot$, depending on
-  whether dust cooling is important.  We present adaptive mesh
-  refinement radiation hydrodynamics simulations that follows the
-  transition from Population III to II star formation.  We model
-  stellar radiative feedback with adaptive ray tracing.  A top-heavy
-  initial mass function for the Population III stars is considered,
-  resulting in a plausible distribution of pair-instability supernovae
-  and associated metal enrichment.  We find that the gas fraction
-  recovers from 5 percent to nearly the cosmic fraction in halos with
-  merger histories rich in halos above $10^7 \Ms$.  A single
-  pair-instability supernova is sufficient to enrich the host halo to
-  a metallicity floor of $10^{-3} Z_\odot$ and to transition to
-  Population II star formation.  Neighboring halos are enriched to
-  metallicities 10--100 times lower as the enriching blastwaves mainly
-  bypass them.  Stellar metallicities trace gas metallicities within
-  0.2 dex.  We find that stellar metallicities do not necessarily
-  trace stellar ages, as mergers of halos with established stellar
-  populations can create superpositions of $t-Z$ evolutionary tracks.
-  A bimodal metallicity distribution is created after a starburst
-  occurs when the halo can cool efficiently through atomic line
-  cooling.
-
-\end{abstract}
-
-\keywords{cosmology --- methods: numerical --- hydrodynamics ---
-  radiative transfer --- star formation}
-
-\section{Motivation}
-
-The first (Pop III) stars are metal-free and have a large
-characteristic mass and suppressed fragmentation in its protostellar
-collapse \citep{Abel00, ABN02, Bromm02_P3, Yoshida03, OShea07a}.  A
-fraction of these stars enrich the surrounding intergalactic medium
-(IGM) when they go supernova, which can happen in stars $\lsim40~\Ms$
-in Type II supernovae (SNe) or in stars roughly between 140 \Ms~and
-260 \Ms~in pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}.
-The host halo and the neighboring halos are then enriched with this
-ejecta.  There exists a critical metallicity that is $\sim 10^{-6}
-Z_\odot$ if dust cooling is efficient \citep{Omukai05,
-  Schneider06_Frag, clark08} and $\sim 10^{-3.5} Z_\odot$ otherwise
-\citep{Bromm01, 2009ApJ...691..441S}, where the gas can cool rapidly,
-lowering its Jeans mass.  An intermediate characteristic mass of
-$\sim10~\Ms$ can be occur if the gas cooling is suppressed to the
-cosmic microwave background (CMB) temperature \citep{Larson98,
-  Tumlinson07_IMF, 2009ApJ...691..441S}.  The resulting Population II
-star cluster will thus have a lower characteristic stellar mass than
-its metal-free progenitors.  In the local universe, stars in the Milky
-Way halo and dwarf spheroidal (dSph) galaxies may be connected to
-these first stellar clusters.  In the halo of the Milky Way, the most
-metal-poor stars have a metallicity floor of [Z/H] = --4
-\citep{Beers05}.  In dwarf spheroidal (dSph) galaxies, this floor is a
-factor of 10 higher \citep{Tolstoy04, Helmi06}, however several metal
-poor stars with $-4 < [\mathrm{Z/H}] < -3$ have been recently
-discovered in dSphs \citep{Tafelmeyer10, Frebel10_Obs}.
-
-The transition from Pop III to Pop II star formation (SF) is solely
-dependent on the propagation of metals from the SNe remnants into
-future sites of SF.  Their flows are complex because of the
-interactions between the SN blastwave, cosmological accretion and halo
-mergers, and nearby stellar feedback.  In minihalos ($M_{\rm h} \sim
-10^6~\Ms$), radiation from the massive Pop III drives a 30 \kms~shock,
-which is 10 times greater than the escape velocity of the halo, and
-leaves behind a warm ($3 \times 10^4$ K) and diffuse (0.5 \cubecm)
-medium \citep{Kitayama04, Whalen04, Abel07}.  This aids in the
-expansion of the blastwave because it delays the transition to the
-Sedov-Taylor and snowplow phases.  In PISNe, approximately half of the
-metals stay in the IGM with a metal bubble size of a few kpc.  The
-remaining metals fall back into the host halo.  The blastwave may
-induce SF in nearby halos through the compression of the gas
-\citep{Ferrara98}; however timescales for metal mixing into the dense
-gas are many dynamical times \citep{Cen08} for shock velocities $\lsim
-100~\kms$.
-
-Numerical simulations are useful to detangle and study these
-complexities and the transition from Pop III to II stars.  In this
-Letter, we present the simulations that include both types of SF, and
-their radiative and mechanical feedback.  We utilize an initial mass
-function (IMF) for individual Pop III stars, based on the latest
-simulation results.  The methods used here incorporate and link
-together recent results from metal-enriched and metal-free star
-formation, the critical metallicity, and pair-instability supernovae.
-Furthermore we spatially distinguish metal enrichment from Pop II and
-Pop III stars.  This is the first time that all of these processes
-have been interconnected in a simulation that resolves star-forming
-minihalos to study the transition to Pop II star formation.  We
-describe our simulation setup and our adopted SF models in \S
-\ref{sec:setup} and present our results in \S \ref{sec:results}.  We
-discuss the implications of our findings and conclude in the last
-section.
-
-\section{Method}
+\section*{Method}
 \label{sec:setup}
@@
 % and feedback from nearby Pop II star clusters, as we will demonstrate
-% in this Letter.
+% in this Report.
 
-We treat Pop II SF with the same prescription as \citet{Wise09}, which
-is a modified version of the \citet{Cen92} method but accounts for the
+We treat Pop II SF with the same prescription as \cite{Wise09}, which
+is a modified version of the \cite{Cen92} method but accounts for the
 fact that the molecular clouds are resolved.  The critical overdensity
@@
 
-\section{Results}
-\label{sec:results}
-
-\begin{figure*}
-  \epsscale{0.8}
-  \plotone{f3}
-  \epsscale{1}
-  \caption{\label{fig:projections} Density-weighted projections of gas
-    density (top), temperature (middle), and metallicity (bottom) at
-    $z=7$.  The left column shows the entire simulation volume, where
-    the center and right columns focus on the intense and quiet halos,
-    which are marked by arrows in the upper-left panel.  The
-    metallicity projections are a composite picture of metals
-    originating from Pop III (red) and Pop II (blue) stars with purple
-    indicating a mixture of the two.}
-\end{figure*}
-
-Here we present the gaseous and stellar evolution of two selected
-halos in the simulation: one that has an early mass buildup but no
-major mergers after $z=12$, and one that experiences a series of major
-mergers between $z=10$ and $z=7$.  We name the halos ``quiet'' and
-``intense'', respectively.  We start with the mass accretion history
-and enrichment of the halos.  We then compare the nature of the
-stellar populations in these halos.
-
-We illustrate the state of the simulation at $z=7$ in Figure
-\ref{fig:projections} with density weighted projections of gas
-density, temperature, and metallicity, showing the entire box and
-focusing on the two halos of interest.  The quiet and intense halos
-are located in the bottom center and bottom right of the full box,
-respectively.  Radiative and mechanical feedback create a multi-phase
-medium inside these halos, which are embedded in a warm and ionized
-IGM.
-
-\subsection{Mass evolution}
-\label{sec:halo}
-
-\begin{figure*}
-  \epsscale{1.15}
-  \plottwo{f1}{f2}
-  \caption{\label{fig:evo} (a) Evolution of the total halo
-    mass (top), stellar mass (middle), and gas fraction (bottom) of
-    the quiet (dashed) and intense (solid) halos.  (b)
-    Mass-weighted stellar metallicities and gas metallicities enriched
-    by Pop II and Pop III SNe of the intense (top) and quiet (bottom)
-    halos.}
-  \epsscale{1}
-\end{figure*}
-
-%\li Describe the evolution of the baryon fraction and metallicity from
-%PISN and Type II SNe metals in the two halos.
-
-Figure \ref{fig:evo}a shows the total, metal-enriched stellar, and gas
-mass history of the most massive progenitors of both halos.  The quiet
-halo undergoes a series of major mergers at $z > 12$, growing by a
-factor of 30 to $2.5 \times 10^7 \Ms$ within 150 Myr.  Afterwards it
-only grows by a factor of 3 by $z=7$ mainly through smooth accretion
-from the filaments and IGM.  It is the most massive halo in the
-simulation between redshifts 13 and 10.  At the same time, the intense
-halo has a mass $M = 3 \times 10^6 \Ms$, but it is contained in a
-biased region on a comoving scale of 50 kpc with $\sim25$ halos with
-$M \sim 10^6 \Ms$.  After $z=10$, these halos hierarchically merge to
-form a $10^9 \Ms$ halo at $z=7$ with two major mergers at redshifts 10
-and 7.9, seen in the rapid increases in total mass in Figure
-\ref{fig:evo}a.  The merger history of the two halos are not atypical
-as dark matter halos can experience both quiescent and vigorous mass
-accretion rates in their buildup.
-
-Both halos start forming Pop II stars when $M = 10^7 \Ms$.  This is
-consistent with the filtering mass $M_f$ of high-redshift halos when
-it accretes mainly from a pre-heated IGM \citep{gnedin98, gnedin00,
-  Wise08_Gal}.  Afterwards these halos can cool efficiently through
-\hh~cooling, sustaining constant and sometimes bursty SF.  The latter
-characteristics are equated with the definition of a galaxy.  The
-quiet halo forms $10^5 \Ms$ of stars by $z=9$.  This initial starburst
-photo-evaporates the majority of its molecular clouds, in addition to
-heating and ionizing the surrounding IGM out to a radius of 10--15 kpc
-at $z=9$.  These respectively reduce the in-situ and external cold gas
-supply that could feed future SF.
-
-The gas fractions of both halos are depleted from 0.15 to 0.08 by
-outflowing shocks driven by ionization fronts and blastwaves in their
-initial starbursts.  The quiet halo never recovers to the cosmic
-fraction $\Omega_b/\Omega_M$ for the following reason.  The lack of
-major mergers of halos above the filtering mass leads to a small gas
-fraction because halos with $M < M_f$ are likely photo-evaporated,
-hosting diffuse warm gas reservoirs instead of cold dense cores.
-During this quiescent period, the halo mainly accretes warm diffuse
-gas from the filaments and IGM.  In contrast, the intense halo grows
-from major mergers of halos with $M > M_f$.  The progenitor halos
-involved in the major mergers are able to host molecular clouds and
-have, in general, higher gas fractions.  Between $z=10$ and $z=8$, the
-gas fraction increases from 0.07 to 0.12 until it jumps to 0.14 when a
-gas-rich major merger occurs.  The stellar mass accordingly increases
-with the ample supply of gas during this period.  The gas fraction
-then decreases by 0.01 when galactic outflows are generated from the
-starburst associated with this major merger.
-
-\subsection{Metallicity evolution}
-
-The evolution of the stellar and gas metallicity of both halos are
-illustrated in Figure \ref{fig:evo}b.  PISNe from Pop III stars enrich
-the nearby IGM out to a radius of 10 kpc and provides a metallicity
-floor of $[Z_3/H] \sim -3$, given $M_{\rm char} = 100 \Ms$.  The
-metallicity from Pop II SNe initially enrich the ISM of both halos to
-an average $[\bar{Z}_2/H]$ between --3.5 and --3.  The quiet halo is
-enriched to $[\bar{Z}_2/H] \sim -2.5$ until the metal-poor inflows
-balance the metal-rich galactic outflows, which are directed in the
-polar directions of the gas disk, keeping the adjacent filaments
-metal-poor.  These features and a well-mixed ISM
-\citep[cf.][]{Wise08_Gal, Greif10} are apparent in the metallicity
-projections in Figure \ref{fig:projections}.  The average stellar
-metallicities is equal or slightly higher up to 0.5 dex than
-$[\bar{Z}_2/H]$.
-
-In the intense halo, the first few Pop II star clusters have [Z/H]
-between --1 and --2 and dominate the average stellar metallicity at $z
-> 8$.  Afterwards the metallicity increases itself by a factor of 30
-to $[\bar{Z}_2/H] = -1.5$ through self-enrichment from a starburst.
-Because this halo is located in a large-scale overdensity, most of the
-ejecta falls back into the halo after reaching distances up to 20
-comoving kpc, in turn keeping the halo gas metallicity high because
-the inflows are relatively metal-rich themselves.  After the $z \sim
-8$ starburst, the average stellar metallicity follows the average gas
-metallicity within 0.1 dex.
-
-\subsection{Population III star formation history}
-
-\textit{Quiet halo}.--- The most massive progenitor interestingly
-never hosts a Pop III star.  Instead a nearby halo forms a Pop III
-star, which (randomly) produces a PISNe at $z=16$.  The blastwave
-overruns the most massive progenitor, and the dense core survives this
-event and is enriched by this PISN, triggering the transition to Pop
-II SF.  Other progenitors host three Pop III stars, forming at $z =
-15.4, 14.2, 13.8$, with the latter producing a PISN.  Metal enrichment
-from these two PISNe and Pop II SF quench Pop III SF in this halo.
-
-\textit{Intense halo}.--- The progenitors host a total of 56 Pop III
-stars with 21 producing PISNe.  The first forms in a $6 \times 10^5
-\Ms$ halo at $z=19$.  Pop III stars form on a regular interval in the
-halo's progenitors until $z=9$ when most of these halos enter the
-metal-rich bubble surrounding the intense halo.  There are two stars
-forming at $z=7.7$ with [Z/H] = --5.7, whose molecular clouds were
-enriched by external blastwaves that only partially enriched the dense
-regions.  This falls into the metallicity range where fragmentation
-occurs only if dust cooling is efficient below \tento{-4} $Z_\odot$.
-The most massive progenitors of the intense halo cease to form Pop III
-stars at $z<12$ because of nearby or intrinsic PISNe.
-
-\subsection{Population II stellar populations}
-\label{sec:pop}
-
-\begin{figure*}
-  \plottwo{f4a}{f4b}
-  \caption{\label{fig:pops} The scatter plots show the SF history of
-    the quiet (left) and intense (right) halos as a function of
-    metallicity at $z=7$.  Each circle represents a star cluster,
-    whose area is proportional to its mass.  The open circles in the
-    upper right represent sizes of $10^3$, $10^4$, and $10^5$ \Ms~star
-    clusters.  The dashed lines in the right panel guide the eye to
-    two stellar populations that were formed in two satellite halos,
-    merging at $z=7.5$.  The upper histogram collects the SF history
-    into 25 equal temporal bins.  The right histogram depicts the
-    stellar metallicity distribution.}
-\end{figure*}
-
-%% \li Present results on the star formation history and the physical
-%% reasons for the features seen in the SFH and metallicities.
-%%
-%% \li Present the stellar metallicity distribution at the final time
-
-Figure \ref{fig:pops} shows the SF history (SFH) of both halos.  The
-metallicity distribution, SF rates, and metallicity evolution and
-spread at a given time can all be extracted from these data.
-
-\textit{Quiet halo}.--- A nearby PISNe provides a metallicity floor of
-[Z/H] = --2.8 at which metallicity the first Pop II stars form.  The
-stellar metallicity evolution exhibits what is expected from an
-isolated system with the stellar feedback steadily enriching the ISM,
-resulting in a correlation between stellar age and metallicity.  After
-$z=10$ the metallicities plateau at [Z/H] = --2.1 for reasons
-discussed in \S\ref{sec:halo}.  The SFR peaks at $z=10$ and decreases
-as the cold gas reservoir is depleted.  Around $z=7.5$, a 25:1 minor
-merger occurs, and the gas inside the satellite halo is compressed,
-triggering metal-poor, [Z/H] = --3.2, SF during its nearest approach.
-This halo infalls through a filament, where most of metal enrichment
-in the quiet halo occurs in bi-polar flows perpendicular to the galaxy
-disk and filament.  The filament and thus this satellite halo remains
-relatively metal-poor.  Stars with [Z/H] $<$ --3 compose 1.6 percent
-of the total stellar mass.
-
-\textit{Intense halo}.--- In contrast with the quiet halo, the intense
-halo undergoes a few mergers of halos with an established stellar
-population.  This creates a superposition of age-metallicity tracks in
-the SFH, seen in the complexity of Figure \ref{fig:pops}.  The first
-two Pop II stellar clusters have an unusually high metallicity [Z/H]
-$\sim$ --1, which occurs when a PISN blastwave triggers SF in two
-neighboring halos.  Most of the early SF occurs around [Z/H] = --2.5.
-At $z=9$, the halo's virial temperature reaches \tento{4} K.  This
-combined with a 10:1 merger creates a starburst that quickly enriches
-the halo to [Z/H] = --1.5 by $z=8$.  The halo continues to enrich
-itself with further SF until $z=7$.  The spikes in the scatter plot
-correspond to SN triggered SF in nearby molecular clouds
-that are enriched up to a factor of 10 with respect to the ISM.
-However the mass fraction of these metal-rich, SN triggered clusters
-are small compared to the total stellar mass.  The starburst at $z=9$
-creates a bimodal metallicity distribution with peaks at [Z/H] = --2.4
-and --1.2 with the metal-rich component mainly being created after the
-starburst.  Two systems with sizable stellar components merge into the
-halo at $z \sim 8$, and their stellar populations are still
-discernible in the metallicity-age plot, whose tracks are noted by
-dashed lines.  Stars with [Z/H] $<$ --3 compose 1.8 percent of the
-total stellar mass.
-
-\section{Discussion and Conclusions}
-
-In this paper, we focus on the birth of two galaxies prior to
-reionization with a cosmological AMR radiation hydrodynamics
-simulation.  Supernovae from Pop III stars provide the necessary heavy
-elements for the transition to a Population II stellar population,
-which we have directly simulated.  These two galaxies have a 10--15\%
-probability in surviving as present-day ``fossil'' galaxies
-\citep{Gnedin06}, otherwise they will be incorporated into galactic
-stellar halos.
-
-We find that one PISN is sufficient to enrich the star-forming halo
-and surrounding $\sim 5$ kpc to a metallicity of 10$^{-3} Z_\odot$,
-given a Pop III characteristic mass of 100~\Ms.  If the first stars
-have a lower characteristic mass that favor hypernovae
-\citep{Tumlinson07_IMF}, then this metallicity floor should be lowered
-by a factor of $\sim 10$ because (1) the metal ejecta is lowered by a
-factor of $\sim 50$ and (2) the mixing mass is approximately decreased
-by a factor of $(E_{\rm hyp}/E_{\rm PISN})^{3/5}$ in the Sedov-Taylor
-solution, where $(E_{\rm hyp}/E_{\rm PISN}) \sim 0.1$ is the ratio of
-explosion energies of a hypernova and PISN.  In the case where this
-metallicity floor is less than the critical metallicity, then the next
-instance of SF will further enrich the ISM, solidifying the transition
-to Pop II SF.  We conclude that it only takes one, at most two, SNe
-from Pop III stars in the halo progenitors to complete the transition
-to Population II \citep[see also][]{Frebel10}.  The question of
-whether the critical metallicity is \tento{-6} or \tento{-3.5}
-$Z_\odot$ is most applicable to nearby halos where the heavy elements
-mix slowly into dense cores as the blastwave overtakes it.  Less than
-two percent of stars have [Z/H] $< -3$ in both systems, consistent
-with observations of metal-poor stars in the halo and dSphs
-\citep[e.g.][]{Beers05, Battaglia10}.
-
-We also find that the merger history plays an important role in
-supplying gas into halos after its first epoch of SF.  Mergers of
-halos below the filtering mass are inefficient in providing gas
-whereas the opposite is true for merging halos above the filtering
-mass.  Halos do not necessarily need $\tvir \ge 10^4$ K to form
-significant stellar populations; however SFRs dramatically increase,
-and thus metal enrichment, when this threshold is reached.  Halos with
-mostly gas-poor mergers or a quiet merger history result in a
-monotonic increase in metallicity with time.  SFHs become more complex
-with multiple metallicity-age tracks if the halo experiences mergers
-with other halos that have an established stellar population.
-Furthermore SF that is triggered by blastwaves interacting with
-molecular clouds can have metallicities up to a factor of 10 higher
-than the main starburst.  Lastly we find that a starburst at $\tvir =
-10^4$ K enriches the host halo enough to create a bimodal metallicity
-distribution, where the metal-poor component is created before the
-burst.  Note that mergers of stellar populations can also create a
-similar bimodal distribution.  Such distributions are observed in
-dSphs \citep[e.g.][]{Battaglia10}.
-
-We have shown that it is possible to simulate the formation of a
-high-redshift dwarf galaxy and its entire SFH with radiative and
-mechanical feedback.  This provides invaluable insight on the first
-galaxies and the role of metal-free stars in the early universe.
-There exists a wealth of information in this simulation, and we plan
-to follow up this preliminary report with more detailed analysis of
-the metal enrichment of the IGM, global SF rates, and observational
-connections with high-redshift galaxies and Local Group dwarf galaxies
-in the near future.
-
-\acknowledgments
-
-Support for this work was provided by NASA through Hubble Fellowship
-grant \#120-6370 awarded by the Space Telescope Science Institute,
-which is operated by the Association of Universities for Research in
-Astronomy, Inc., for NASA, under contract NAS 5-26555.  Computational
-resources were provided by NASA/NCCS award SMD-09-1439.
-J.~H.~W. thanks Renyue Cen, Amina Helmi, Marco Spaans, and Eline
-Tolstoy for enlightening discussions.  The majority of the analysis
-and plots were done with \texttt{yt} \citep{yt_full_paper}.
-
-%\clearpage
-%\input biblio.tex
 \bibliography{ms}

### 2010-10-20 science_ms.tex
Changed abstract to be more Science-like.

@@
 \begin{sciabstract}
-  Population III stars first form in dark matter halos with masses
-  around $10^6~\Ms$.  By definition, they are metal-free, and their
-  protostellar collapse is driven by molecular hydrogen cooling in the
-  gas-phase, leading to a massive characteristic mass $\sim 100~\Ms$
-  and suppressed fragmentation.  Population II stars with lower
-  characteristic masses form when the star-forming gas reaches a
-  critical metallicity of $10^{-6} - 10^{-3.5}~Z_\odot$, depending on
-  whether dust cooling is important.  We present adaptive mesh
-  refinement radiation hydrodynamics simulations that follows the
-  transition from Population III to II star formation.  We model
-  stellar radiative feedback with adaptive ray tracing.  A top-heavy
-  initial mass function for the Population III stars is considered,
-  resulting in a plausible distribution of pair-instability supernovae
-  and associated metal enrichment.  We find that the gas fraction
-  recovers from 5 percent to nearly the cosmic fraction in halos with
-  merger histories rich in halos above $10^7~\Ms$.  A single
-  pair-instability supernova is sufficient to enrich the host halo to
-  a metallicity floor of $10^{-3}~Z_\odot$ and to transition to
-  Population II star formation.  Neighboring halos are enriched to
-  metallicities 10--100 times lower as the enriching blastwaves mainly
-  bypass them.  Stellar metallicities trace gas metallicities within
-  0.2 dex.  We find that stellar metallicities do not necessarily
-  trace stellar ages, as mergers of halos with established stellar
-  populations can create superpositions of $t-Z$ evolutionary tracks.
-  A bimodal metallicity distribution is created after a starburst
-  occurs when the halo can cool efficiently through atomic line
-  cooling.
+  Supernova explosions from the first stars in the universe, which are
+  predicted to be very massive, chemically enriched the intergalactic
+  medium, originally a primordial mix of hydrogen and helium.  A
+  fraction of these metals propagate into star-forming regions,
+  providing more efficient cooling mechanisms and, in turn, increasing
+  gaseous fragmentation in the first stellar clusters.  Here, we
+  report on the birth of two high-redshift dwarf galaxies in a
+  cosmological radiation hydrodynamics simulation.  We find that only
+  one supernova is sufficient to enrich the nearby star-forming gas
+  with a floor of 1/1,000 of the solar metallicity ratio, preventing
+  any further metal-free star formation within 10 kpc of the past
+  explosion.  We follow the entire star formation history of these
+  galaxies, providing robust models to interpret the stellar
+  populations of nearby dwarf galaxies and future observations of
+  high-redshift dwarf galaxies.
 \end{sciabstract}

### 2010-10-20 science_ms.tex
Revised version after another reading.

@@
 characteristic mass and suppressed fragmentation in its protostellar
-collapse \cite{Abel00, ABN02, Bromm02_P3, Yoshida03, OShea07a}.  A
-fraction of these stars enrich the surrounding intergalactic medium
-(IGM) when they go supernova, which can happen in stars $\lsim 40~\Ms$
-in Type II supernovae (SNe) or in stars roughly between 140 \Ms~and
-260 \Ms~in pair-instability SNe (PISNe; \cite{2002ApJ...567..532H}).
-The host halo and the neighboring halos are then enriched with this
-ejecta.  There exists a critical metallicity that is $\sim 10^{-6}
-Z_\odot$ if dust cooling is efficient \cite{Omukai05,
-  Schneider06_Frag, clark08} and $\sim 10^{-3.5} Z_\odot$ otherwise
-\cite{Bromm01, 2009ApJ...691..441S}, where the gas can cool rapidly,
-lowering its Jeans mass.  An intermediate characteristic mass of
-$\sim10~\Ms$ can be occur if the gas cooling is suppressed to the
-cosmic microwave background (CMB) temperature \cite{Larson98,
-  Tumlinson07_IMF, 2009ApJ...691..441S}.  The resulting Population II
-star cluster will thus have a lower characteristic stellar mass than
-its metal-free progenitors.  In the local universe, stars in the Milky
-Way halo and dwarf spheroidal (dSph) galaxies may be connected to
-these first stellar clusters.  In the halo of the Milky Way, the most
-metal-poor stars have a metallicity floor of [Z/H] = --4
-\cite{Beers05}.  In dwarf spheroidal (dSph) galaxies, this floor is a
-factor of 10 higher \cite{Tolstoy04, Helmi06}, however several metal
-poor stars with $-4 < [\mathrm{Z/H}] < -3$ have been recently
-discovered in dSphs \cite{Tafelmeyer10, Frebel10_Obs}.
+collapse \cite{ABN02, Bromm02_P3, Yoshida03, OShea07a}.  A fraction of
+these stars enrich the surrounding intergalactic medium (IGM) when
+they go supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
+supernovae (SNe) or in stars roughly between 140 \Ms~and 260 \Ms~in
+pair-instability SNe (PISNe; \cite{2002ApJ...567..532H}).  The host
+halo and the neighboring halos are then enriched with this ejecta.
+There exists a critical metallicity that is $\sim 10^{-6} Z_\odot$ if
+dust cooling is efficient \cite{Omukai05, Schneider06_Frag, clark08}
+and $\sim 10^{-3.5} Z_\odot$ otherwise \cite{Bromm01,
+  2009ApJ...691..441S}, where the gas can cool rapidly, lowering its
+Jeans mass.  An intermediate characteristic mass of $\sim10~\Ms$ can
+be occur if the gas cooling is suppressed to the cosmic microwave
+background (CMB) temperature \cite{Larson98, Tumlinson07_IMF,
+  2009ApJ...691..441S}.  The resulting Population II star cluster will
+thus have a lower characteristic stellar mass than its metal-free
+progenitors.  These first stellar clusters may be connected to stars
+in the Milky Way halo and nearby dwarf spheroidal (dSph) galaxies,
+both with a metallicity floor of [Z/H] = --4 \cite{Beers05,
+  Tafelmeyer10, Frebel10_Obs}.
 
@@
 interactions between the SN blastwave, cosmological accretion and halo
-mergers, and nearby stellar feedback.  In minihalos ($M_{\rm h} \sim
-10^6~\Ms$), radiation from the massive Pop III drives a 30 \kms~shock,
-which is 10 times greater than the escape velocity of the halo, and
-leaves behind a warm ($3 \times 10^4$ K) and diffuse (0.5 \cubecm)
-medium \cite{Kitayama04, Whalen04, Abel07}.  This aids in the
+mergers, and nearby stellar feedback.  In minihalos ($M \sim
+10^6~\Ms$), radiation from a massive Pop III star can drive a 30
+\kms~shock, which is 10 times greater than the escape velocity of the
+halo, and leaves behind a warm ($3 \times 10^4$ K) and diffuse (0.5
+\cubecm) medium \cite{Kitayama04, Whalen04, Abel07}.  This aids in the
 expansion of the blastwave because it delays the transition to the
 Sedov-Taylor and snowplow phases.  In PISNe, approximately half of the
-metals stay in the IGM with a metal bubble size of a few kpc.  The
-remaining metals fall back into the host halo.  The blastwave may
-induce SF in nearby halos through the compression of the gas
-\cite{Ferrara98}; however timescales for metal mixing into the dense gas are
-many dynamical times \cite{Cen08} for shock velocities $\lsim100~\kms$.
+metals stay in the IGM with a metal bubble size of a few kpc
+\cite{Wise08_Gal, Greif10}.  The blastwave may induce SF in nearby
+halos through the compression of the gas \cite{Ferrara98}, and
+timescales for metal mixing into the dense gas are many dynamical
+times \cite{Cen08} for shock velocities $\lsim100~\kms$.
 
@@
 Report, we present the simulations that include both types of SF, and
-their radiative and mechanical feedback.  We utilize an initial mass
-function (IMF) for individual Pop III stars, based on the latest
-simulation results.  The methods used here incorporate and link
-together recent results from metal-enriched and metal-free star
-formation, the critical metallicity, and pair-instability supernovae.
-Furthermore we spatially distinguish metal enrichment from Pop II and
-Pop III stars.  This is the first time that all of these processes
-have been interconnected in a simulation that resolves star-forming
-minihalos to study the transition to Pop II star formation.
+their radiative and mechanical feedback.  The methods used here
+incorporate and link together recent results from metal-enriched and
+metal-free star formation, the critical metallicity, and
+pair-instability supernovae.  This is the first simulation that can
+resolve star-forming minihalos while following the transition to Pop
+II star formation in the first galaxies.
 
@@
 mergers between $z=10$ and $z=7$.  We name the halos ``quiet'' and
-``intense'', respectively.  We start with the mass accretion history
-and enrichment of the halos.  We then compare the nature of the
-stellar populations in these halos.
+``intense'', respectively.
+
+% We start with the mass accretion history and enrichment of the
+% halos.  We then compare the nature of the stellar populations in
+% these halos.
 
@@
 density, temperature, and metallicity, showing the entire box and
-focusing on the two halos of interest.  The quiet and intense halos
-are located in the bottom center and bottom right of the full box,
-respectively.  Radiative and mechanical feedback create a multi-phase
-medium inside these halos, which are embedded in a warm and ionized
-IGM.
+focusing on the two halos of interest.  Radiative and mechanical
+feedback create a multi-phase medium inside these halos, which are
+embedded in a warm and ionized IGM.
 
@@
 
-The gas fractions of both halos are depleted from 0.15 to 0.08 by
-outflowing shocks driven by ionization fronts and blastwaves in their
-initial starbursts.  The quiet halo never recovers to the cosmic
-fraction $\Omega_b/\Omega_M$ for the following reason.  The lack of
-major mergers of halos above the filtering mass leads to a small gas
+The gas fractions of both halos decrease from 0.15 to 0.08 by outflows
+driven by ionization fronts and blastwaves in their initial
+starbursts.  The quiet halo never recovers to the cosmic fraction
+$\Omega_b/\Omega_M$ for the following reason.  The lack of major
+mergers of halos above the filtering mass leads to a small gas
 fraction because halos with $M < M_f$ are likely photo-evaporated,
 hosting diffuse warm gas reservoirs instead of cold dense cores.
-During this quiescent period, the halo mainly accretes warm diffuse
-gas from the filaments and IGM.  In contrast, the intense halo grows
-from major mergers of halos with $M > M_f$.  The progenitor halos
-involved in the major mergers are able to host molecular clouds and
-have, in general, higher gas fractions.  Between $z=10$ and $z=8$, the
-gas fraction increases from 0.07 to 0.12 until it jumps to 0.14 when a
-gas-rich major merger occurs.  The stellar mass accordingly increases
-with the ample supply of gas during this period.  The gas fraction
-then decreases by 0.01 when galactic outflows are generated from the
+After $z=10$, the halo mainly accretes warm diffuse gas from the
+filaments and IGM.  In contrast, the intense halo grows from major
+mergers of halos with $M > M_f$.  The progenitor halos involved in the
+major mergers are able to host molecular clouds and have, in general,
+higher gas fractions.  Between $z=10$ and $z=8$, the gas fraction
+increases from 0.07 to 0.12 until it jumps to 0.14 when a gas-rich
+major merger occurs.  The stellar mass accordingly increases with the
+ample supply of gas during this period.  The gas fraction then
+decreases by 0.01 when galactic outflows are generated from the
 starburst associated with this major merger.
@@
 \subsection*{Metallicity evolution}
+\label{sec:zevo}
 
@@
 the nearby IGM out to a radius of 10 kpc and provides a metallicity
-floor of $[Z_3/H] \sim -3$, given $M_{\rm char} = 100 \Ms$.  The
-metallicity from Pop II SNe initially enrich the ISM of both halos to
-an average $[\bar{Z}_2/H]$ between --3.5 and --3.  The quiet halo is
-enriched to $[\bar{Z}_2/H] \sim -2.5$ until the metal-poor inflows
-balance the metal-rich galactic outflows, which are directed in the
-polar directions of the gas disk, keeping the adjacent filaments
-metal-poor.  These features and a well-mixed ISM
-(cf.~\cite{Wise08_Gal, Greif10}) are apparent in the metallicity
-projections in Figure \ref{fig:projections}.  The average stellar
-metallicities is equal or slightly higher up to 0.5 dex than
-$[\bar{Z}_2/H]$.
+floor of $[Z_3/H] \sim -3$.  The metallicity from Pop II SNe initially
+enrich the ISM of both halos to an average $[\bar{Z}_2/H]$ between
+--3.5 and --3.
 
-In the intense halo, the first few Pop II star clusters have [Z/H]
-between --1 and --2 and dominate the average stellar metallicity at $z
-> 8$.  Afterwards the metallicity increases itself by a factor of 30
-to $[\bar{Z}_2/H] = -1.5$ through self-enrichment from a starburst.
-Because this halo is located in a large-scale overdensity, most of the
-ejecta falls back into the halo after reaching distances up to 20
-comoving kpc, in turn keeping the halo gas metallicity high because
-the inflows are relatively metal-rich themselves.  After the $z \sim
-8$ starburst, the average stellar metallicity follows the average gas
-metallicity within 0.1 dex.
+\textit{Quiet halo}.--- Afterwards an equilbrium of $[\bar{Z}_2/H]
+\sim -2.5$ is established between metal-rich outflows and metal-poor
+inflows.  Galactic outflows are directed in the polar directions of
+the gas disk, keeping the adjacent filaments metal-poor.  These
+features and a well-mixed ISM (cf.~\cite{Wise08_Gal, Greif10}) are
+apparent in the metallicity projections in Figure
+\ref{fig:projections}.  The average stellar metallicity is within 0.5
+dex of $[\bar{Z}_2/H]$.
+
+\textit{Intense halo}.--- The first few Pop II star clusters have
+$[Z/H]$ between --1 and --2 and dominate the average stellar
+metallicity at $z > 8$.  Afterwards the metallicity increases by a
+factor of 30 to $[\bar{Z}_2/H] = -1.5$ through self-enrichment from a
+starburst.  Because this halo is located in a large-scale overdensity,
+most of the ejecta falls back into the halo after reaching distances
+up to 20 comoving kpc, in turn keeping the halo gas metallicity high
+because the inflows are relatively metal-rich themselves.  After the
+$z \sim 8$ starburst, the average stellar metallicity follows the
+average gas metallicity within 0.1 dex.
 
@@
 regions.  This falls into the metallicity range where fragmentation
-occurs only if dust cooling is efficient below \tento{-4} $Z_\odot$.
+could occur if dust cooling is efficient below \tento{-4} $Z_\odot$.
 The most massive progenitors of the intense halo cease to form Pop III
@@
 $z=10$ the metallicities plateau at [Z/H] = --2.1 for reasons
-discussed in \S\ref{sec:halo}.  The SFR peaks at $z=10$ and decreases
+discussed in \S\ref{sec:zevo}.  The SFR peaks at $z=10$ and decreases
 as the cold gas reservoir is depleted.  Around $z=7.5$, a 25:1 minor
@@
 the SFH, seen in the complexity of Figure \ref{fig:pops}.  The first
-two Pop II stellar clusters have an unusually high metallicity [Z/H]
-$\sim$ --1, which occurs when a PISN blastwave triggers SF in two
-neighboring halos.  Most of the early SF occurs around [Z/H] = --2.5.
-At $z=9$, the halo's virial temperature reaches \tento{4} K.  This
+two Pop II stellar clusters have an unexpectedly high metallicity
+[Z/H] $\sim$ --1, which occurs when a PISN blastwave triggers SF in
+two neighboring halos.  Most of the early SF have [Z/H] = --2.5.  At
+$z=9$, the halo's virial temperature reaches \tento{4} K.  This
 combined with a 10:1 merger creates a starburst that quickly enriches
@@
 itself with further SF until $z=7$.  The spikes in the scatter plot
-correspond to SN triggered SF in nearby molecular clouds
-that are enriched up to a factor of 10 with respect to the ISM.
-However the mass fraction of these metal-rich, SN triggered clusters
-are small compared to the total stellar mass.  The starburst at $z=9$
-creates a bimodal metallicity distribution with peaks at [Z/H] = --2.4
-and --1.2 with the metal-rich component mainly being created after the
-starburst.  Two systems with sizable stellar components merge into the
-halo at $z \sim 8$, and their stellar populations are still
-discernible in the metallicity-age plot, whose tracks are noted by
-dashed lines.  Stars with [Z/H] $<$ --3 compose 1.8 percent of the
-total stellar mass.
+correspond to SN triggered SF in nearby molecular clouds that are
+enriched up to a factor of 10 with respect to the ISM.  However their
+mass fraction are small compared to the total stellar mass.  The
+starburst at $z=9$ creates a bimodal metallicity distribution with
+peaks at [Z/H] = --2.4 and --1.2 with the metal-rich component mainly
+being created after the starburst.  Two systems with sizable stellar
+components merge into the halo at $z \sim 8$, and their stellar
+populations are still discernible in the metallicity-age plot, whose
+tracks are noted by dashed lines.  Stars with [Z/H] $<$ --3 compose
+1.8 percent of the total stellar mass.
 
@@
 and surrounding $\sim 5$ kpc to a metallicity of 10$^{-3} Z_\odot$,
-given a Pop III characteristic mass of 100~\Ms.  If the first stars
-have a lower characteristic mass that favor hypernovae
-\cite{Tumlinson07_IMF}, then this metallicity floor should be lowered
-by a factor of $\sim 10$ because (1) the metal ejecta is lowered by a
-factor of $\sim 50$ and (2) the mixing mass is approximately decreased
-by a factor of $(E_{\rm hyp}/E_{\rm PISN})^{3/5}$ in the Sedov-Taylor
-solution, where $(E_{\rm hyp}/E_{\rm PISN}) \sim 0.1$ is the ratio of
-explosion energies of a hypernova and PISN.  In the case where this
-metallicity floor is less than the critical metallicity, then the next
-instance of SF will further enrich the ISM, solidifying the transition
-to Pop II SF.  We conclude that it only takes one, at most two, SNe
-from Pop III stars in the halo progenitors to complete the transition
-to Population II \cite{Frebel10}.  The question of
-whether the critical metallicity is \tento{-6} or \tento{-3.5}
-$Z_\odot$ is most applicable to nearby halos where the heavy elements
-mix slowly into dense cores as the blastwave overtakes it.  Less than
-two percent of stars have [Z/H] $< -3$ in both systems, consistent
-with observations of metal-poor stars in the halo and dSphs
-\cite{Beers05, Battaglia10}.
+given $M_{\rm char} = 100~\Ms$.  If the first stars have a lower
+characteristic mass that favor hypernovae \cite{Tumlinson07_IMF}, then
+this metallicity floor should be lowered by a factor of $\sim 10$
+because (1) the metal ejecta is lowered by a factor of $\sim 50$ and
+(2) the mixing mass is approximately decreased by a factor of $(E_{\rm
+  hyp}/E_{\rm PISN})^{3/5}$ in the Sedov-Taylor solution, where
+$(E_{\rm hyp}/E_{\rm PISN}) \sim 0.1$ is the ratio of explosion
+energies of a hypernova and PISN.  In the case where this metallicity
+floor is less than the critical metallicity, then the next instance of
+SF will further enrich the ISM, solidifying the transition to Pop II
+SF.  We conclude that it only takes one, at most two, SNe from Pop III
+stars in the halo progenitors to complete the transition to Population
+II \cite{Frebel10}.  The question of whether the critical metallicity
+is \tento{-6} or \tento{-3.5} $Z_\odot$ is most applicable to nearby
+halos where the heavy elements mix slowly into dense cores as the
+blastwave overtakes it.  Less than two percent of stars have [Z/H] $<
+-3$ in both systems, consistent with observations of metal-poor stars
+in the halo and dSphs \cite{Beers05, Battaglia10}.
 
@@
   the center and right columns focus on the intense and quiet halos,
-    which are marked by arrows in the upper-left panel.  The
-    metallicity projections are a composite picture of metals
-    originating from Pop III (red) and Pop II (blue) stars with purple
+  which are marked by left and right arrows in the upper-left panel.
+  The metallicity projections are a composite picture of metals
+  originating from Pop III (red) and Pop II (blue) stars with magenta
   indicating a mixture of the two.}
@@
 \includegraphics[width=0.88\textwidth]{f1.eps}
-  \caption{\label{fig:evo} (a) Evolution of the total halo
-    mass (top), stellar mass (middle), and gas fraction (bottom) of
-    the quiet (dashed) and intense (solid) halos.  (b)
-    Mass-weighted stellar metallicities and gas metallicities enriched
-    by Pop II and Pop III SNe of the intense (top) and quiet (bottom)
-    halos.}
+\caption{\label{fig:evo} (a) Evolution of the total halo mass (top),
+  stellar mass (middle), and gas fraction (bottom) of the quiet
+  (dashed) and intense (solid) halos.  (b) Mass-weighted stellar
+  metallicities and gas metallicities enriched by Pop II and Pop III
+  SNe of the intense (top) and quiet (bottom) halos.}
 \end{figure*}
@@
 \includegraphics[width=0.88\textwidth]{f4a.eps}
-  \caption{\label{fig:pops} The scatter plots show the SF history of
-    the quiet (left) and intense (right) halos as a function of
-    metallicity at $z=7$.  Each circle represents a star cluster,
-    whose area is proportional to its mass.  The open circles in the
-    upper right represent sizes of $10^3$, $10^4$, and $10^5$ \Ms~star
-    clusters.  The dashed lines in the right panel guide the eye to
-    two stellar populations that were formed in two satellite halos,
-    merging at $z=7.5$.  The upper histogram collects the SF history
-    into 25 equal temporal bins.  The right histogram depicts the
-    stellar metallicity distribution.}
+\caption{\label{fig:pops} The scatter plots show the SF history of the
+  quiet (left) and intense (right) halos as a function of metallicity
+  at $z=7$.  Each circle represents a star cluster, whose area is
+  proportional to its mass.  The open circles in the upper right
+  represent sizes of $10^3$, $10^4$, and $10^5$ \Ms~star clusters.
+  The dashed lines in the right panel guide the eye to two stellar
+  populations that were formed in two satellite halos, merging at
+  $z=7.5$.  The upper histogram shows the SF rate.  The right
+  histogram depicts the stellar metallicity distribution.}
 \end{figure*}

### 2010-10-20 science_som.tex
Revised version after another reading.

@@
 
-In this section, we first describe our simulation setup.  We then
-detail the SF models used here and how we model radiative and SNe
-feedback.
+Here, we first describe our simulation setup.  We then detail the SF
+models used here and how we model radiative and SNe feedback.
 
@@
 enzo~v2.0\footnote{\texttt{enzo.googlecode.com, unstable changeset
-b86d8ba026d6}} \cite{BryanNorman1997, OShea2004}, which has been modified to
-use a HLLC Riemann solver \cite{Toro94_HLLC} for additional stability in strong
-shocks.  To resolve minihalos with at least 100 dark matter (DM) particles and
-follow the formation of the first generation of dwarf galaxies, we use a
-simulation box of 1 Mpc that has a resolution of $256^3$.  This gives us a DM
-mass resolution of 1840 \Ms.  We refine the grid on baryon overdensities of $3
-\times 2^{-0.2l}$, where $l$ is the AMR level, resulting in a super-Lagrangian
-behavior.  We also refine on a DM overdensity of $3 \times 2^l$ and always
-resolve the local Jeans length by at least 4 cells, avoiding artificial
-fragmentation during gaseous collapses \cite{Truelove97}.  We initialize the
-simulation with \textsl{grafic} \cite{Bertschinger01} at $z = 130$ and use the
-cosmological parameters from the 7-year WMAP data \cite{WMAP7}: $\Omega_M =
-0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 =
-0.81$, and $n = 0.963$ with the variables having their usual definitions.  We
-stop the simulation at $z=7$.
+    b86d8ba026d6}} \cite{BryanNorman1997, OShea2004}, which has been
+modified to use a HLLC Riemann solver \cite{Toro94_HLLC} for
+additional stability in strong shocks.  To resolve minihalos with at
+least 100 dark matter (DM) particles and follow the formation of the
+first generation of dwarf galaxies, we use a simulation box of 1 Mpc
+that has a resolution of $256^3$.  This gives us a DM mass resolution
+of 1840 \Ms.  We refine the grid on baryon overdensities of $3 \times
+2^{-0.2l}$, where $l$ is the AMR level, resulting in a
+super-Lagrangian behavior.  We also refine on a DM overdensity of $3
+\times 2^l$ and always resolve the local Jeans length by at least 4
+cells, avoiding artificial fragmentation during gaseous collapses
+\cite{Truelove97}.  We initialize the simulation with \textsl{grafic}
+\cite{Bertschinger01} at $z = 130$ and use the cosmological parameters
+from the 7-year WMAP data \cite{WMAP7}: $\Omega_M = 0.266$,
+$\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 =
+0.81$, and $n = 0.963$ with the variables having their usual
+definitions.  We stop the simulation at $z=7$.
 
 We use a non-equilibrium chemistry solver with 9 species of hydrogen,
-helium, and molecular hydrogen \cite{Abel97}.  We will follow-up this
-study with one that considers radiative cooling from metal-enriched
-gas, using the method of \cite{2008MNRAS.385.1443S}.
+helium, and molecular hydrogen \cite{Abel97}.  We spatially
+distinguish metal enrichment from Pop II and Pop III stars.  We will
+follow-up this study with one that considers radiative cooling from
+metal-enriched gas, using the method of \cite{2008MNRAS.385.1443S}.
 
@@
 
-We distinguish Pop II and Pop III SF by the metallicity of the densest
-cell in the molecular cloud.  Pop II stars are formed if [Z/H] $> -4$,
-and Pop III stars are formed otherwise.  We do not consider Pop III.2
-stars and intermediate mass stars from CMB-limited cooling.
+We distinguish Pop II and Pop III SF by the total metallicity of the
+densest cell in the molecular cloud.  Pop II stars are formed if [Z/H]
+$> -4$, and Pop III stars are formed otherwise.  We do not consider
+Pop III.2 stars and intermediate mass stars from CMB-limited cooling.
 
@@
 
-For Pop III stars, we use the same SF model as \cite{Abel07} and
-\cite{Wise08_Gal} where each star particle represents a single star.
-The critical overdensity in which a star forms is $5 \times 10^5$.
-Instead of using a fixed stellar mass, we randomly sampled from an IMF
-with a functional form of
+For Pop III stars, we use the same SF model as \cite{Wise08_Gal} where
+each star particle represents a single star, forming at an overdensity
+of $5 \times 10^5$.  Instead of using a fixed stellar mass, we randomly
+sampled from an IMF with a functional form of
 %
@@
 Salpeter IMF but is exponentially cutoff below that mass
-\cite{Chabrier03, Clark09}.  For reproducibility, we record the
-number of times the random number generator (Mersenne twister; \cite{MTwister})
-has been called for use when restarting the simulations.
+\cite{Chabrier03, Clark09}.  For reproducibility, we record the number
+of times the random number generator (Mersenne twister;
+\cite{MTwister}) has been called for use when restarting the
+simulations.
 
@@
 seven percent of the cold gas ($T < 10^3$ K) is removed from the grid
-and deposited into the star particle.  Each star particle lives for 20
-Myr, the maximum lifetime of an OB star.  These stars generate the
-majority of the ionizing radiation and SNe feedback in stellar
-clusters, thus we ignore lower mass stars.
+and deposited into the star particle that lives for 20 Myr, the
+maximum lifetime of an OB star.  These stars generate the majority of
+the ionizing radiation and SNe feedback in stellar clusters, thus we
+ignore lower mass stars.
 
@@
 
-The mass-dependent luminosities and lifetimes of the Pop III stars are
-taken from \cite{Schaerer02}.  The radiation field is evolved with
-adaptive ray tracing \cite{Abel02_RT, Wise10} and is coupled
-self-consistently to the hydrodynamics.  We model the \hh~dissociating
-radiation with an optically-thin, inverse square profile, centered on
-all stars.  These stars die as pair-instability SNe (PISNe) if they
-are in the mass range 140--260 \Ms~\cite{Heger03}.  We use the
-explosion energy from \cite{Heger02}, where we fit the following
-function to their models, $E_{\rm PISN} = 10^{51} \times [5.0 + 1.304
-(M_{\rm He} - 64)]$, where $M_{\rm He} = (13/24) \times (M_\star - 20)
-\Ms$ is the helium core mass and $M_\star$ is the stellar mass.
+We use mass-dependent luminosities and lifetimes of the Pop III stars
+from \cite{Schaerer02}.  The radiation field is evolved with adaptive
+ray tracing \cite{Abel02_RT, Wise10} and is coupled self-consistently
+to the hydrodynamics.  We model the \hh~dissociating radiation with an
+optically-thin, inverse square profile, centered on all stars.  These
+stars die as pair-instability SNe (PISNe) if they are in the mass
+range 140--260 \Ms~\cite{Heger03}.  We use the explosion energy from
+\cite{Heger02}, where we fit the following function to their models,
+$E_{\rm PISN} = 10^{51} \times [5.0 + 1.304 (M_{\rm He} - 64)]$, where
+$M_{\rm He} = (13/24) \times (M_\star - 20) \Ms$ is the helium core
+(and equivalently the ejecta) mass and $M_\star$ is the stellar mass.
 
@@
 is the key ingredient here.  For SN feedback, these stars generate
-$6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$ of energy after living
-for 4 Myr, which is injected into spheres with a radius of 10 pc.  If
-the resolution of the grid is less than 10/3 pc, we deposit the energy
+$6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$ after living for 4 Myr,
+which is injected into spheres with a radius of 10 pc.  If the
+resolution of the grid is less than 10/3 pc, we deposit the energy
 into a $3^3$ cube surrounding the star particle.

### 2010-10-21 merge_eps.py
Merged together eps files into a composite ones to replace the plottwo{} in the apj format.  Fixed the figure filenames to reflect their new figure numbers.

@@ -1,0 +1,9 @@
+from pyx import *
+
+files = ["f4a.eps", "f4b.eps"]
+newfile = "f4"  # omit .eps
+
+c = canvas.canvas()
+c.insert(epsfile.epsfile(0,0,files[0]))
+c.insert(epsfile.epsfile(20.5,0,files[1]))
+c.writeEPSfile(newfile)

### 2010-10-25 science_ms.tex
Merged together eps files into a composite ones to replace the plottwo{} in the apj format.  Fixed the figure filenames to reflect their new figure numbers.
Added sentence in abstract about DLAs.  Removed some discussion about the importance of the merger history since this is already discussed in the results.

@@
   any further metal-free star formation within 10 kpc of the past
-  explosion.  We follow the entire star formation history of these
-  galaxies, providing robust models to interpret the stellar
-  populations of nearby dwarf galaxies and future observations of
-  high-redshift dwarf galaxies.
+  explosion.  This provides a natural explanation for the observed
+  floor on damped Lyman alpha (DLA) systems metallicities reported in
+  the literature, which is of this order.  We follow the entire star
+  formation history of these galaxies, providing robust models to
+  interpret the stellar populations of nearby dwarf galaxies and
+  future observations of high-redshift dwarf galaxies.
 \end{sciabstract}
@@
 whereas the opposite is true for merging halos above the filtering
-mass.  Halos do not necessarily need $\tvir \ge 10^4$ K to form
-significant stellar populations; however SFRs dramatically increase,
-and thus metal enrichment, when this threshold is reached.  Halos with
-mostly gas-poor mergers or a quiet merger history result in a
-monotonic increase in metallicity with time.  SFHs become more complex
-with multiple metallicity-age tracks if the halo experiences mergers
-with other halos that have an established stellar population.
-Furthermore SF that is triggered by blastwaves interacting with
-molecular clouds can have metallicities up to a factor of 10 higher
-than the main starburst.  Lastly we find that a starburst at $\tvir =
-10^4$ K enriches the host halo enough to create a bimodal metallicity
-distribution, where the metal-poor component is created before the
-burst.  Note that mergers of stellar populations can also create a
-similar bimodal distribution.  Such distributions are observed in
-dSphs \cite{Battaglia10}.
+mass.  
+% Halos do not necessarily need $\tvir \ge 10^4$ K to form significant
+% stellar populations; however SFRs dramatically increase, and thus
+% metal enrichment, when this threshold is reached.  Halos with mostly
+% gas-poor mergers or a quiet merger history result in a monotonic
+% increase in metallicity with time.  SFHs become more complex with
+% multiple metallicity-age tracks if the halo experiences mergers with
+% other halos that have an established stellar population.  Furthermore
+% SF that is triggered by blastwaves interacting with molecular clouds
+% can have metallicities up to a factor of 10 higher than the main
+% starburst.
+Starbursts at $\tvir = 10^4$ K can enrich the host halo enough to
+create a bimodal metallicity distribution, where the metal-poor
+component is created before the burst.  Note that mergers of stellar
+populations can also create a similar bimodal distribution.  Such
+distributions are observed in dSphs \cite{Battaglia10}.
 
@@
 \begin{figure*}
-\includegraphics[width=0.88\textwidth]{f3.eps}
+\includegraphics[width=\textwidth]{f1.eps}
 \caption{\label{fig:projections} Density-weighted projections of gas
@@
 % Need to include f2.eps
-\includegraphics[width=0.88\textwidth]{f1.eps}
+\includegraphics[width=\textwidth]{f2.eps}
 \caption{\label{fig:evo} (a) Evolution of the total halo mass (top),
@@
 \begin{figure*}
-% Needs f4b.eps
-\includegraphics[width=0.88\textwidth]{f4a.eps}
+\includegraphics[width=\textwidth]{f3.eps}
 \caption{\label{fig:pops} The scatter plots show the SF history of the

### 2010-10-25 science_ms.tex
Removed quiet and intense halo paragraph labels.  This wouldn't work with the unlabeled sections in Science.

@@
 
-\textit{Quiet halo}.--- Afterwards an equilbrium of $[\bar{Z}_2/H]
-\sim -2.5$ is established between metal-rich outflows and metal-poor
-inflows.  Galactic outflows are directed in the polar directions of
-the gas disk, keeping the adjacent filaments metal-poor.  These
-features and a well-mixed ISM (cf.~\cite{Wise08_Gal, Greif10}) are
-apparent in the metallicity projections in Figure
-\ref{fig:projections}.  The average stellar metallicity is within 0.5
-dex of $[\bar{Z}_2/H]$.
+In the quiet halo, an equilbrium of $[\bar{Z}_2/H] \sim -2.5$ is
+established between metal-rich outflows and metal-poor inflows.
+Galactic outflows are directed in the polar directions of the gas
+disk, keeping the adjacent filaments metal-poor.  These features and a
+well-mixed ISM (cf.~\cite{Wise08_Gal, Greif10}) are apparent in the
+metallicity projections in Figure \ref{fig:projections}.  The average
+stellar metallicity is within 0.5 dex of $[\bar{Z}_2/H]$.
 
-\textit{Intense halo}.--- The first few Pop II star clusters have
-$[Z/H]$ between --1 and --2 and dominate the average stellar
-metallicity at $z > 8$.  Afterwards the metallicity increases by a
-factor of 30 to $[\bar{Z}_2/H] = -1.5$ through self-enrichment from a
-starburst.  Because this halo is located in a large-scale overdensity,
-most of the ejecta falls back into the halo after reaching distances
-up to 20 comoving kpc, in turn keeping the halo gas metallicity high
-because the inflows are relatively metal-rich themselves.  After the
-$z \sim 8$ starburst, the average stellar metallicity follows the
-average gas metallicity within 0.1 dex.
+In the intense halos, the first few Pop II star clusters have $[Z/H]$
+between --1 and --2 and dominate the average stellar metallicity at $z
+> 8$.  Afterwards the metallicity increases by a factor of 30 to
+$[\bar{Z}_2/H] = -1.5$ through self-enrichment from a starburst.
+Because this halo is located in a large-scale overdensity, most of the
+ejecta falls back into the halo after reaching distances up to 20
+comoving kpc, in turn keeping the halo gas metallicity high because
+the inflows are relatively metal-rich themselves.  After the $z \sim
+8$ starburst, the average stellar metallicity follows the average gas
+metallicity within 0.1 dex.
 
@@
 
-\textit{Quiet halo}.--- The most massive progenitor interestingly
-never hosts a Pop III star.  Instead a nearby halo forms a Pop III
-star, which (randomly) produces a PISNe at $z=16$.  The blastwave
-overruns the most massive progenitor, and the dense core survives this
-event and is enriched by this PISN, triggering the transition to Pop
-II SF.  Other progenitors host three Pop III stars, forming at $z =
-15.4, 14.2, 13.8$, with the latter producing a PISN.  Metal enrichment
-from these two PISNe and Pop II SF quench Pop III SF in this halo.
+The most massive progenitor of the quiet halo interestingly never
+hosts a Pop III star.  Instead a nearby halo forms a Pop III star,
+which (randomly) produces a PISNe at $z=16$.  The blastwave overruns
+the most massive progenitor, and the dense core survives this event
+and is enriched by this PISN, triggering the transition to Pop II SF.
+Other progenitors host three Pop III stars, forming at $z = 15.4,
+14.2, 13.8$, with the latter producing a PISN.  Metal enrichment from
+these two PISNe and Pop II SF quench Pop III SF in this halo.
 
-\textit{Intense halo}.--- The progenitors host a total of 56 Pop III
-stars with 21 producing PISNe.  The first forms in a $6 \times 10^5
-\Ms$ halo at $z=19$.  Pop III stars form on a regular interval in the
+The progenitors of the intense halo host a total of 56 Pop III stars
+with 21 producing PISNe.  The first forms in a $6 \times 10^5 \Ms$
+halo at $z=19$.  Pop III stars form on a regular interval in the
 halo's progenitors until $z=9$ when most of these halos enter the
@@
 
-\textit{Quiet halo}.--- A nearby PISNe provides a metallicity floor of
-[Z/H] = --2.8 at which metallicity the first Pop II stars form.  The
+A nearby PISNe provides a metallicity floor of [Z/H] = --2.8 in the
+quiet halo at which metallicity the first Pop II stars form.  The
 stellar metallicity evolution exhibits what is expected from an
@@
 $z=10$ the metallicities plateau at [Z/H] = --2.1 for reasons
-discussed in \S\ref{sec:zevo}.  The SFR peaks at $z=10$ and decreases
-as the cold gas reservoir is depleted.  Around $z=7.5$, a 25:1 minor
-merger occurs, and the gas inside the satellite halo is compressed,
+previously discussed.  The SFR peaks at $z=10$ and decreases as the
+cold gas reservoir is depleted.  Around $z=7.5$, a 25:1 minor merger
+occurs, and the gas inside the satellite halo is compressed,
 triggering metal-poor, [Z/H] = --3.2, SF during its nearest approach.
@@
 
-\textit{Intense halo}.--- In contrast with the quiet halo, the intense
-halo undergoes a few mergers of halos with an established stellar
-population.  This creates a superposition of age-metallicity tracks in
-the SFH, seen in the complexity of Figure \ref{fig:pops}.  The first
-two Pop II stellar clusters have an unexpectedly high metallicity
-[Z/H] $\sim$ --1, which occurs when a PISN blastwave triggers SF in
-two neighboring halos.  Most of the early SF have [Z/H] = --2.5.  At
-$z=9$, the halo's virial temperature reaches \tento{4} K.  This
-combined with a 10:1 merger creates a starburst that quickly enriches
-the halo to [Z/H] = --1.5 by $z=8$.  The halo continues to enrich
-itself with further SF until $z=7$.  The spikes in the scatter plot
-correspond to SN triggered SF in nearby molecular clouds that are
-enriched up to a factor of 10 with respect to the ISM.  However their
-mass fraction are small compared to the total stellar mass.  The
-starburst at $z=9$ creates a bimodal metallicity distribution with
-peaks at [Z/H] = --2.4 and --1.2 with the metal-rich component mainly
-being created after the starburst.  Two systems with sizable stellar
-components merge into the halo at $z \sim 8$, and their stellar
-populations are still discernible in the metallicity-age plot, whose
-tracks are noted by dashed lines.  Stars with [Z/H] $<$ --3 compose
-1.8 percent of the total stellar mass.
+In contrast with the quiet halo, the intense halo undergoes a few
+mergers of halos with an established stellar population.  This creates
+a superposition of age-metallicity tracks in the SFH, seen in the
+complexity of Figure \ref{fig:pops}.  The first two Pop II stellar
+clusters have an unexpectedly high metallicity [Z/H] $\sim$ --1, which
+occurs when a PISN blastwave triggers SF in two neighboring halos.
+Most of the early SF have [Z/H] = --2.5.  At $z=9$, the halo's virial
+temperature reaches \tento{4} K.  This combined with a 10:1 merger
+creates a starburst that quickly enriches the halo to [Z/H] = --1.5 by
+$z=8$.  The halo continues to enrich itself with further SF until
+$z=7$.  The spikes in the scatter plot correspond to SN triggered SF
+in nearby molecular clouds that are enriched up to a factor of 10 with
+respect to the ISM.  However their mass fraction are small compared to
+the total stellar mass.  The starburst at $z=9$ creates a bimodal
+metallicity distribution with peaks at [Z/H] = --2.4 and --1.2 with
+the metal-rich component mainly being created after the starburst.
+Two systems with sizable stellar components merge into the halo at $z
+\sim 8$, and their stellar populations are still discernible in the
+metallicity-age plot, whose tracks are noted by dashed lines.  Stars
+with [Z/H] $<$ --3 compose 1.8 percent of the total stellar mass.
 

### 2010-10-25 science_ms.tex
Added some discussion on the ionized bubble (estimated) radius around the z=8.6 galaxy and connection to DLAs.

@@
 \cite{Gnedin06}, otherwise they will be incorporated into galactic
-stellar halos.
+stellar halos.  A $z=8.55$ galaxy was recently spectroscopically
+confirmed that is contained in an ionized bubble with radius 0.1--0.5
+Mpc with an uncharacterized population of galaxies contributing to the
+local ionizing radiation field \cite{Lehnert10_z8.6}.  The galaxies
+simulated here might represent this population.
 
@@
 and surrounding $\sim 5$ kpc to a metallicity of 10$^{-3} Z_\odot$,
-given $M_{\rm char} = 100~\Ms$.  If the first stars have a lower
-characteristic mass that favor hypernovae \cite{Tumlinson07_IMF}, then
-this metallicity floor should be lowered by a factor of $\sim 10$
-because (1) the metal ejecta is lowered by a factor of $\sim 50$ and
-(2) the mixing mass is approximately decreased by a factor of $(E_{\rm
-  hyp}/E_{\rm PISN})^{3/5}$ in the Sedov-Taylor solution, where
-$(E_{\rm hyp}/E_{\rm PISN}) \sim 0.1$ is the ratio of explosion
-energies of a hypernova and PISN.  In the case where this metallicity
-floor is less than the critical metallicity, then the next instance of
-SF will further enrich the ISM, solidifying the transition to Pop II
-SF.  We conclude that it only takes one, at most two, SNe from Pop III
-stars in the halo progenitors to complete the transition to Population
-II \cite{Frebel10}.  The question of whether the critical metallicity
-is \tento{-6} or \tento{-3.5} $Z_\odot$ is most applicable to nearby
+given $M_{\rm char} = 100~\Ms$.  DLA systems have a metallicity floor
+on the same order \cite{DLAs}, and metal enrichment from Pop III SNe
+provides a possible explaination.
+
+If the first stars have a lower characteristic mass that favor
+hypernovae \cite{Tumlinson07_IMF}, then this metallicity floor should
+be lowered by a factor of $\sim 10$ because (1) the metal ejecta is
+lowered by a factor of $\sim 50$ and (2) the mixing mass is
+approximately decreased by a factor of $(E_{\rm hyp}/E_{\rm
+  PISN})^{3/5}$ in the Sedov-Taylor solution, where $(E_{\rm
+  hyp}/E_{\rm PISN}) \sim 0.1$ is the ratio of explosion energies of a
+hypernova and PISN.  In the case where this metallicity floor is less
+than the critical metallicity, then the next instance of SF will
+further enrich the ISM, solidifying the transition to Pop II SF.  We
+conclude that it only takes one, at most two, SNe from Pop III stars
+in the halo progenitors to complete the transition to Population II
+\cite{Frebel10}.  The question of whether the critical metallicity is
+\tento{-6} or \tento{-3.5} $Z_\odot$ is most applicable to nearby
 halos where the heavy elements mix slowly into dense cores as the

### 2010-10-27 science_ms.tex
Adding DLA and z=8.6 galaxy references.

@@
 metal-free star formation, the critical metallicity, and
-pair-instability supernovae.  This is the first simulation that can
-resolve star-forming minihalos while following the transition to Pop
-II star formation in the first galaxies.
+pair-instability supernovae.  This is the first time it has been
+possible to link the formation and feedback of the first stars to
+protogalaxies resolving the important scales and including the most
+important physical effects.
 
@@
 ``intense'', respectively.
+
+\textbf{Add some interesting stats about the simulation.}
 
@@
 given $M_{\rm char} = 100~\Ms$.  DLA systems have a metallicity floor
-on the same order \cite{DLAs}, and metal enrichment from Pop III SNe
-provides a possible explaination.
+on the same order \cite{Wolfe05_Review}, and metal enrichment from Pop
+III SNe provides a possible explanation.
 

### 2010-10-27 science_ms.tex
Added figure of halo mass fn and galaxy luminosities.
Added some details about the simulation.  Revised after another proofreading.  Removed a paragraph in the discussion.  Within 80 words of the word limit, including the acknowledgements.  I think this should be fine.

@@
 \author
-{John H.~Wise,$^{1,2\ast}$ Michael L.~Norman,$^{3}$ Tom Abel$^{4}$,
-Matthew J.~Turk$^{3}$\\
+{John H.~Wise,$^{1,2\ast}$ Matthew J.~Turk$^{3}$, Michael
+  L.~Norman,$^{3}$ Tom Abel$^{4}$\\
 \\
@@
 in the Milky Way halo and nearby dwarf spheroidal (dSph) galaxies,
-both with a metallicity floor of [Z/H] = --4 \cite{Beers05,
-  Tafelmeyer10, Frebel10_Obs}.
+both with a metallicity floor of [Z/H]\footnote{We use the
+  conventional notation, [Z/H] $\equiv$ log(Z/H) -
+  log(Z$_\odot$/H$_\odot$)} = --4 \cite{Beers05, Tafelmeyer10,
+  Frebel10_Obs}.
 
@@
 possible to link the formation and feedback of the first stars to
-protogalaxies resolving the important scales and including the most
+protogalaxies, resolving the important scales and including the most
 important physical effects.
@@
 mergers between $z=10$ and $z=7$.  We name the halos ``quiet'' and
-``intense'', respectively.
-
-\textbf{Add some interesting stats about the simulation.}
+``intense'', respectively.  The entire simulation contains 38 galaxies
+with 3640 Pop II stellar clusters and captures the formation of 333
+Pop III stars.  The halo mass function and galaxy luminosities are
+plotted in Figure \ref{fig:massfn}.  This simulation has $1.4 \times
+10^8$ computational elements and a maximal spatial resolution of 0.1
+pc.
 
@@
 as dark matter halos can experience both quiescent and vigorous mass
-accretion rates in their buildup.
+accretion rates.
 
@@
   Wise08_Gal}.  Afterwards these halos can cool efficiently through
-\hh~cooling, sustaining constant and sometimes bursty SF.  The latter
-characteristics are equated with the definition of a galaxy.  The
-quiet halo forms $10^5 \Ms$ of stars by $z=9$.  This initial starburst
-photo-evaporates the majority of its molecular clouds, in addition to
-heating and ionizing the surrounding IGM out to a radius of 10--15 kpc
-at $z=9$.  These respectively reduce the in-situ and external cold gas
-supply that could feed future SF.
+\hh~cooling, sustaining constant and sometimes bursting SF.  The
+latter characteristics are equated with the definition of a galaxy.
+The quiet halo forms $10^5 \Ms$ of stars by $z=9$.  This initial
+starburst photo-evaporates the majority of its molecular clouds, in
+addition to heating and ionizing the surrounding IGM out to a radius
+of 10--15 kpc at $z=9$.  These respectively reduce the in-situ and
+external cold gas supply that could feed future SF.
 
@@
 mergers of halos with $M > M_f$.  The progenitor halos involved in the
-major mergers are able to host molecular clouds and have, in general,
-higher gas fractions.  Between $z=10$ and $z=8$, the gas fraction
-increases from 0.07 to 0.12 until it jumps to 0.14 when a gas-rich
-major merger occurs.  The stellar mass accordingly increases with the
-ample supply of gas during this period.  The gas fraction then
-decreases by 0.01 when galactic outflows are generated from the
-starburst associated with this major merger.
+major mergers are able to host molecular clouds and have higher gas
+fractions.  Between $z=10$ and $z=8$, the gas fraction increases from
+0.07 to 0.12 until it jumps to 0.14 when a gas-rich major merger
+occurs.  The stellar mass accordingly increases with the ample supply
+of gas during this period.  The gas fraction then decreases by 0.01
+when galactic outflows are generated from the starburst associated
+with this major merger.
 
@@
 
-In the quiet halo, an equilbrium of $[\bar{Z}_2/H] \sim -2.5$ is
+In the quiet halo, an equilibrium of $[\bar{Z}_2/H] \sim -2.5$ is
 established between metal-rich outflows and metal-poor inflows.
@@
 
-In the intense halos, the first few Pop II star clusters have $[Z/H]$
+In the intense halo, the first few Pop II star clusters have $[Z/H]$
 between --1 and --2 and dominate the average stellar metallicity at $z
@@
 ejecta falls back into the halo after reaching distances up to 20
-comoving kpc, in turn keeping the halo gas metallicity high because
-the inflows are relatively metal-rich themselves.  After the $z \sim
-8$ starburst, the average stellar metallicity follows the average gas
+comoving kpc, keeping the halo gas metallicity high because the
+inflows are relatively metal-rich themselves.  After the $z \sim 8$
+starburst, the average stellar metallicity follows the average gas
 metallicity within 0.1 dex.
@@
 14.2, 13.8$, with the latter producing a PISN.  Metal enrichment from
-these two PISNe and Pop II SF quench Pop III SF in this halo.
+these two PISNe and Pop II SF quench Pop III SF in this halo.  The
+progenitors of the intense halo host a total of 56 Pop III stars with
+21 producing PISNe.  The first forms in a $6 \times 10^5 \Ms$ halo at
+$z=19$.  Pop III stars form on a regular interval in the halo's
+progenitors until $z=9$ when most of these halos enter the metal-rich
+bubble surrounding the intense halo.
 
-The progenitors of the intense halo host a total of 56 Pop III stars
-with 21 producing PISNe.  The first forms in a $6 \times 10^5 \Ms$
-halo at $z=19$.  Pop III stars form on a regular interval in the
-halo's progenitors until $z=9$ when most of these halos enter the
-metal-rich bubble surrounding the intense halo.  There are two stars
-forming at $z=7.7$ with [Z/H] = --5.7, whose molecular clouds were
-enriched by external blastwaves that only partially enriched the dense
-regions.  This falls into the metallicity range where fragmentation
-could occur if dust cooling is efficient below \tento{-4} $Z_\odot$.
-The most massive progenitors of the intense halo cease to form Pop III
-stars at $z<12$ because of nearby or intrinsic PISNe.
+% There are two stars forming at $z=7.7$ with [Z/H] = --5.7, whose
+% molecular clouds were enriched by external blastwaves that only
+% partially enriched the dense regions.  This falls into the metallicity
+% range where fragmentation could occur if dust cooling is efficient
+% below \tento{-4} $Z_\odot$.  The most massive progenitors of the
+% intense halo cease to form Pop III stars at $z<12$ because of nearby
+% or intrinsic PISNe.
 
@@
 
-Figure \ref{fig:pops} shows the SF history (SFH) of both halos.  The
-metallicity distribution, SF rates, and metallicity evolution and
-spread at a given time can all be extracted from these data.
-
-A nearby PISNe provides a metallicity floor of [Z/H] = --2.8 in the
-quiet halo at which metallicity the first Pop II stars form.  The
-stellar metallicity evolution exhibits what is expected from an
-isolated system with the stellar feedback steadily enriching the ISM,
-resulting in a correlation between stellar age and metallicity.  After
-$z=10$ the metallicities plateau at [Z/H] = --2.1 for reasons
-previously discussed.  The SFR peaks at $z=10$ and decreases as the
-cold gas reservoir is depleted.  Around $z=7.5$, a 25:1 minor merger
-occurs, and the gas inside the satellite halo is compressed,
-triggering metal-poor, [Z/H] = --3.2, SF during its nearest approach.
-This halo infalls through a filament, where most of metal enrichment
-in the quiet halo occurs in bi-polar flows perpendicular to the galaxy
-disk and filament.  The filament and thus this satellite halo remains
-relatively metal-poor.  Stars with [Z/H] $<$ --3 compose 1.6 percent
-of the total stellar mass.
+Figure \ref{fig:pops} shows the SF history (SFH), metallicity
+distribution, and SF rates of both halos.  A nearby PISNe provides a
+metallicity floor of [Z/H] = --2.8 in the quiet halo at which
+metallicity the first Pop II stars form.  The stellar metallicity
+evolution exhibits what is expected from an isolated system with the
+stellar feedback steadily enriching the ISM, resulting in a
+correlation between stellar age and metallicity.  After $z=10$ the
+metallicities plateau at [Z/H] = --2.1 for reasons previously
+discussed.  The SFR peaks at $z=10$ and decreases as the cold gas
+reservoir is depleted.  Around $z=7.5$, a 25:1 minor merger occurs,
+and the gas inside the satellite halo is compressed, triggering
+metal-poor, [Z/H] = --3.2, SF during its nearest approach.  This halo
+remains metal-poor because most of metal enrichment in the quiet halo
+occurs in bi-polar flows perpendicular to the galaxy disk and
+filament.  Stars with [Z/H] $<$ --3 compose 1.6 percent of the total
+stellar mass.
 
@@
 creates a starburst that quickly enriches the halo to [Z/H] = --1.5 by
-$z=8$.  The halo continues to enrich itself with further SF until
-$z=7$.  The spikes in the scatter plot correspond to SN triggered SF
-in nearby molecular clouds that are enriched up to a factor of 10 with
-respect to the ISM.  However their mass fraction are small compared to
-the total stellar mass.  The starburst at $z=9$ creates a bimodal
-metallicity distribution with peaks at [Z/H] = --2.4 and --1.2 with
-the metal-rich component mainly being created after the starburst.
-Two systems with sizable stellar components merge into the halo at $z
-\sim 8$, and their stellar populations are still discernible in the
-metallicity-age plot, whose tracks are noted by dashed lines.  Stars
-with [Z/H] $<$ --3 compose 1.8 percent of the total stellar mass.
+$z=8$.  The halo continues to enrich itself afterwards.  The spikes in
+the scatter plot correspond to SN triggered SF in nearby molecular
+clouds that are enriched up to a factor of 10 with respect to the ISM.
+However their mass fraction are small compared to the total stellar
+mass.  The starburst at $z=9$ creates a bimodal metallicity
+distribution with peaks at [Z/H] = --2.4 and --1.2 with the metal-rich
+component mainly being created after the starburst.  Two systems with
+sizable stellar components merge into the halo at $z \sim 8$, and
+their stellar populations are still discernible in the metallicity-age
+plot.  Stars with [Z/H] $<$ --3 compose 1.8 percent of the total
+stellar mass.
 
@@
 
-We also find that the merger history plays an important role in
-supplying gas into halos after its first epoch of SF.  Mergers of
-halos below the filtering mass are inefficient in providing gas
-whereas the opposite is true for merging halos above the filtering
-mass.  
-% Halos do not necessarily need $\tvir \ge 10^4$ K to form significant
-% stellar populations; however SFRs dramatically increase, and thus
-% metal enrichment, when this threshold is reached.  Halos with mostly
-% gas-poor mergers or a quiet merger history result in a monotonic
-% increase in metallicity with time.  SFHs become more complex with
-% multiple metallicity-age tracks if the halo experiences mergers with
-% other halos that have an established stellar population.  Furthermore
-% SF that is triggered by blastwaves interacting with molecular clouds
-% can have metallicities up to a factor of 10 higher than the main
-% starburst.
-Starbursts at $\tvir = 10^4$ K can enrich the host halo enough to
-create a bimodal metallicity distribution, where the metal-poor
-component is created before the burst.  Note that mergers of stellar
-populations can also create a similar bimodal distribution.  Such
-distributions are observed in dSphs \cite{Battaglia10}.
+% We also find that the merger history plays an important role in
+% supplying gas into halos after its first epoch of SF.  Mergers of
+% halos below the filtering mass are inefficient in providing gas
+% whereas the opposite is true for merging halos above the filtering
+% mass.  Halos do not necessarily need $\tvir \ge 10^4$ K to form
+% significant stellar populations; however SFRs dramatically increase,
+% and thus metal enrichment, when this threshold is reached.  Halos
+% with mostly gas-poor mergers or a quiet merger history result in a
+% monotonic increase in metallicity with time.  SFHs become more
+% complex with multiple metallicity-age tracks if the halo experiences
+% mergers with other halos that have an established stellar
+% population.  Furthermore SF that is triggered by blastwaves
+% interacting with molecular clouds can have metallicities up to a
+% factor of 10 higher than the main starburst.  Starbursts at $\tvir =
+% 10^4$ K can enrich the host halo enough to create a bimodal
+% metallicity distribution, where the metal-poor component is created
+% before the burst.  Note that mergers of stellar populations can also
+% create a similar bimodal distribution, which are observed in dSphs
+% \cite{Battaglia10}.
 
@@
 high-redshift dwarf galaxy and its entire SFH with radiative and
-mechanical feedback.  This provides invaluable insight on the first
-galaxies and the role of metal-free stars in the early universe.
+mechanical feedback.  These results provide invaluable insight on the
+first galaxies and the role of metal-free stars in the early universe.
 There exists a wealth of information in this simulation, and we plan
@@
 % instructions.
+
+\clearpage
+\begin{figure*}
+\includegraphics[width=0.6\textwidth]{Lstar.eps}
+\caption{\label{fig:massfn} \textbf{Top}: Halo mass function of the
+  simulation compared with the analytical fit (solid) of
+  \cite{Warren06}.  \textbf{Bottom}: Total Pop II luminosities of
+  halos with constant mass-to-light ratios overplotted.}
+\end{figure*}
 

### 2010-10-28 science_ms.tex
Combined the Pop III and II SF sections and shortened the 3rd paragraph of the "mass evolution" section.

@@
 driven by ionization fronts and blastwaves in their initial
-starbursts.  The quiet halo never recovers to the cosmic fraction
-$\Omega_b/\Omega_M$ for the following reason.  The lack of major
-mergers of halos above the filtering mass leads to a small gas
-fraction because halos with $M < M_f$ are likely photo-evaporated,
-hosting diffuse warm gas reservoirs instead of cold dense cores.
-After $z=10$, the halo mainly accretes warm diffuse gas from the
-filaments and IGM.  In contrast, the intense halo grows from major
-mergers of halos with $M > M_f$.  The progenitor halos involved in the
-major mergers are able to host molecular clouds and have higher gas
-fractions.  Between $z=10$ and $z=8$, the gas fraction increases from
-0.07 to 0.12 until it jumps to 0.14 when a gas-rich major merger
-occurs.  The stellar mass accordingly increases with the ample supply
-of gas during this period.  The gas fraction then decreases by 0.01
-when galactic outflows are generated from the starburst associated
-with this major merger.
+starbursts.  The quiet halo does not have a major merger with any halo
+with $M > M_f$, leading to a small final gas fraction.  These low-mass
+halos are photo-evaporated, hosting diffuse warm gas reservoirs
+instead of cold dense cores.  After $z=10$, the halo mainly accretes
+warm diffuse gas from the filaments and IGM.  In contrast, the intense
+halo grows from major mergers of halos with $M > M_f$.  The progenitor
+halos involved in the major mergers are able to host molecular clouds
+and have higher gas fractions.  Between $z=10$ and $z=8$, the gas
+fraction increases from 0.07 to 0.12 until it jumps to 0.14 when a
+gas-rich major merger occurs.  The stellar mass accordingly increases
+with the ample supply of gas during this period.
+
+% The gas fraction then decreases by 0.01 when galactic outflows are
+% generated from the starburst associated with this major merger.
 
@@
 
-\subsection*{Population III star formation history}
+\subsection*{Star formation history}
+\label{sec:pop}
 
@@
 
-\subsection*{Population II stellar populations}
-\label{sec:pop}
+%\subsection*{Population II stellar populations}
+%\label{sec:pop}
 

### 2010-10-31 science_ms.tex
Minor change.
Shortened abstract to 125 words.

@@
 
-\title{The Birth of a Galaxy: Population III Metal Enrichment and
+\title{The Birth of a Galaxy: Primordial Metal Enrichment and
   Population II Stellar Populations}
@@
   predicted to be very massive, chemically enriched the intergalactic
-  medium, originally a primordial mix of hydrogen and helium.  A
-  fraction of these metals propagate into star-forming regions,
-  providing more efficient cooling mechanisms and, in turn, increasing
-  gaseous fragmentation in the first stellar clusters.  Here, we
-  report on the birth of two high-redshift dwarf galaxies in a
-  cosmological radiation hydrodynamics simulation.  We find that only
-  one supernova is sufficient to enrich the nearby star-forming gas
-  with a floor of 1/1,000 of the solar metallicity ratio, preventing
-  any further metal-free star formation within 10 kpc of the past
-  explosion.  This provides a natural explanation for the observed
-  floor on damped Lyman alpha (DLA) systems metallicities reported in
-  the literature, which is of this order.  We follow the entire star
-  formation history of these galaxies, providing robust models to
-  interpret the stellar populations of nearby dwarf galaxies and
-  future observations of high-redshift dwarf galaxies.
+  medium, providing the necessary elements for forming the first
+  galaxies.  We report on the birth of two high-redshift dwarf
+  galaxies in a cosmological radiation hydrodynamics simulation.  We
+  find that only one supernova is sufficient to enrich the nearby
+  star-forming gas with a floor of 1/1,000 of the solar metallicity
+  ratio, preventing any metal-free star formation within 10 kpc of the
+  past explosion.  This provides a natural explanation for the
+  observed floor on damped Lyman alpha systems metallicities.  We
+  follow the entire star formation history of these galaxies,
+  providing robust models to interpret the stellar populations of
+  nearby dwarf galaxies and future observations of high-redshift dwarf
+  galaxies.
 \end{sciabstract}
@@
 the nearby IGM out to a radius of 10 kpc and provides a metallicity
-floor of $[Z_3/H] \sim -3$.  The metallicity from Pop II SNe initially
-enrich the ISM of both halos to an average $[\bar{Z}_2/H]$ between
---3.5 and --3.
+floor of $[Z_3/H] \sim -3$.  Ejecta from Pop II SNe initially enrich
+the ISM of both halos to an average $[\bar{Z}_2/H]$ between --3.5 and
+--3.
 

### 2010-10-31 science_ms.tex
Added blurb about JWST.
Fixing another typo.  Adding cover letter text that I wrote to support our paper during the initial submission.

@@
 complexities and the transition from Pop III to II stars.  In this
-Report, we present the simulations that include both types of SF, and
+Report, we present a simulation that includes both types of SF, and
 their radiative and mechanical feedback.  The methods used here
@@
 local ionizing radiation field \cite{Lehnert10_z8.6}.  The galaxies
-simulated here might represent this population.
+simulated here might represent this population and should be detected
+with the upcoming \textit{James Webb Space Telescope}.
 

### 2010-11-07 ms.tex
Converted back to ApJ format.

@@
 \usepackage{natbib}
-\usepackage[section] {placeins}
+%\usepackage[section] {placeins}
 \bibliographystyle{apj}
@@
 
-\title{The Birth of a Galaxy: Population III Metal Enrichment and
+\title{The Birth of a Galaxy: Primoridal Metal Enrichment and
   Population II Stellar Populations}
@@
 \author{John H. Wise\altaffilmark{1,2}, 
+  Matthew J. Turk\altaffilmark{3},
   Michael L. Norman\altaffilmark{3},
-  Tom Abel\altaffilmark{4},
-  Matthew J. Turk\altaffilmark{3}}
+  Tom Abel\altaffilmark{4}}
 
@@
   a metallicity floor of $10^{-3} Z_\odot$ and to transition to
-  Population II star formation.  Neighboring halos are enriched to
-  metallicities 10--100 times lower as the enriching blastwaves mainly
-  bypass them.  Stellar metallicities trace gas metallicities within
-  0.2 dex.  We find that stellar metallicities do not necessarily
-  trace stellar ages, as mergers of halos with established stellar
-  populations can create superpositions of $t-Z$ evolutionary tracks.
-  A bimodal metallicity distribution is created after a starburst
-  occurs when the halo can cool efficiently through atomic line
-  cooling.
+  Population II star formation.  This provides a natural explanation
+  for the observed floor on damped Lyman alpha (DLA) systems
+  metallicities reported in the literature, which is of this order.
+  Neighboring halos are enriched to metallicities 10--100 times lower
+  as the enriching blastwaves mainly bypass them.  Stellar
+  metallicities trace gas metallicities within 0.2 dex.  We find that
+  stellar metallicities do not necessarily trace stellar ages, as
+  mergers of halos with established stellar populations can create
+  superpositions of $t-Z$ evolutionary tracks.  A bimodal metallicity
+  distribution is created after a starburst occurs when the halo can
+  cool efficiently through atomic line cooling.
 
@@
 characteristic mass and suppressed fragmentation in its protostellar
-collapse \citep{Abel00, ABN02, Bromm02_P3, Yoshida03, OShea07a}.  A
-fraction of these stars enrich the surrounding intergalactic medium
-(IGM) when they go supernova, which can happen in stars $\lsim40~\Ms$
-in Type II supernovae (SNe) or in stars roughly between 140 \Ms~and
-260 \Ms~in pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}.
-The host halo and the neighboring halos are then enriched with this
-ejecta.  There exists a critical metallicity that is $\sim 10^{-6}
-Z_\odot$ if dust cooling is efficient \citep{Omukai05,
-  Schneider06_Frag, clark08} and $\sim 10^{-3.5} Z_\odot$ otherwise
-\citep{Bromm01, 2009ApJ...691..441S}, where the gas can cool rapidly,
-lowering its Jeans mass.  An intermediate characteristic mass of
-$\sim10~\Ms$ can be occur if the gas cooling is suppressed to the
-cosmic microwave background (CMB) temperature \citep{Larson98,
-  Tumlinson07_IMF, 2009ApJ...691..441S}.  The resulting Population II
-star cluster will thus have a lower characteristic stellar mass than
-its metal-free progenitors.  In the local universe, stars in the Milky
-Way halo and dwarf spheroidal (dSph) galaxies may be connected to
-these first stellar clusters.  In the halo of the Milky Way, the most
-metal-poor stars have a metallicity floor of [Z/H] = --4
-\citep{Beers05}.  In dwarf spheroidal (dSph) galaxies, this floor is a
-factor of 10 higher \citep{Tolstoy04, Helmi06}, however several metal
-poor stars with $-4 < [\mathrm{Z/H}] < -3$ have been recently
-discovered in dSphs \citep{Tafelmeyer10, Frebel10_Obs}.
+collapse \citep{ABN02, Bromm02_P3, Yoshida03, OShea07a}.  A fraction of
+these stars enrich the surrounding intergalactic medium (IGM) when
+they go supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
+supernovae (SNe) or in stars roughly between 140 \Ms~and 260 \Ms~in
+pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}.  The host
+halo and the neighboring halos are then enriched with this ejecta.
+There exists a critical metallicity that is $\sim 10^{-6} Z_\odot$ if
+dust cooling is efficient \citep{Omukai05, Schneider06_Frag, clark08}
+and $\sim 10^{-3.5} Z_\odot$ otherwise \citep{Bromm01,
+  2009ApJ...691..441S}, where the gas can cool rapidly, lowering its
+Jeans mass.  An intermediate characteristic mass of $\sim10~\Ms$ can
+be occur if the gas cooling is suppressed to the cosmic microwave
+background (CMB) temperature \citep{Larson98, Tumlinson07_IMF,
+  2009ApJ...691..441S}.  The resulting Population II star cluster will
+thus have a lower characteristic stellar mass than its metal-free
+progenitors.  These first stellar clusters may be connected to stars
+in the Milky Way halo and nearby dwarf spheroidal (dSph) galaxies,
+both with a metallicity floor of [Z/H]\footnote[\dag]{We use the
+  conventional notation, [Z/H] $\equiv$ log(Z/H) -
+  log(Z$_\odot$/H$_\odot$)} = --4 \citep{Beers05, Tafelmeyer10,
+  Frebel10_Obs}.
 
@@
 interactions between the SN blastwave, cosmological accretion and halo
-mergers, and nearby stellar feedback.  In minihalos ($M_{\rm h} \sim
-10^6~\Ms$), radiation from the massive Pop III drives a 30 \kms~shock,
-which is 10 times greater than the escape velocity of the halo, and
-leaves behind a warm ($3 \times 10^4$ K) and diffuse (0.5 \cubecm)
-medium \citep{Kitayama04, Whalen04, Abel07}.  This aids in the
+mergers, and nearby stellar feedback.  In minihalos ($M \sim
+10^6~\Ms$), radiation from a massive Pop III star can drive a 30
+\kms~shock, which is 10 times greater than the escape velocity of the
+halo, and leaves behind a warm ($3 \times 10^4$ K) and diffuse (0.5
+\cubecm) medium \citep{Kitayama04, Whalen04, Abel07}.  This aids in the
 expansion of the blastwave because it delays the transition to the
 Sedov-Taylor and snowplow phases.  In PISNe, approximately half of the
-metals stay in the IGM with a metal bubble size of a few kpc.  The
-remaining metals fall back into the host halo.  The blastwave may
-induce SF in nearby halos through the compression of the gas
-\citep{Ferrara98}; however timescales for metal mixing into the dense
-gas are many dynamical times \citep{Cen08} for shock velocities $\lsim
-100~\kms$.
+metals stay in the IGM with a metal bubble size of a few kpc
+\citep{Wise08_Gal, Greif10}.  The blastwave may induce SF in nearby
+halos through the compression of the gas \citep{Ferrara98}, and
+timescales for metal mixing into the dense gas are many dynamical
+times \citep{Cen08} for shock velocities $\lsim100~\kms$.
 
@@
 Letter, we present the simulations that include both types of SF, and
-their radiative and mechanical feedback.  We utilize an initial mass
-function (IMF) for individual Pop III stars, based on the latest
-simulation results.  The methods used here incorporate and link
-together recent results from metal-enriched and metal-free star
-formation, the critical metallicity, and pair-instability supernovae.
-Furthermore we spatially distinguish metal enrichment from Pop II and
-Pop III stars.  This is the first time that all of these processes
-have been interconnected in a simulation that resolves star-forming
-minihalos to study the transition to Pop II star formation.  We
-describe our simulation setup and our adopted SF models in \S
-\ref{sec:setup} and present our results in \S \ref{sec:results}.  We
-discuss the implications of our findings and conclude in the last
-section.
+their radiative and mechanical feedback.  The methods used here
+incorporate and link together recent results from metal-enriched and
+metal-free star formation, the critical metallicity, and
+pair-instability supernovae.  This is the first time it has been
+possible to link the formation and feedback of the first stars to
+protogalaxies, resolving the important scales and including the most
+important physical effects.  We describe our simulation setup and our
+adopted SF models in \S \ref{sec:setup} and present our results in \S
+\ref{sec:results}.  We discuss the implications of our findings and
+conclude in the last section.
 
@@
 We use the adaptive mesh refinement (AMR) code
-\enzo~v2.0\footnote[\dag]{\texttt{enzo.googlecode.com, unstable
+enzo~v2.0\footnote[\ddag]{\texttt{enzo.googlecode.com, unstable
     changeset b86d8ba026d6}} \citep{BryanNorman1997, OShea2004}, which
@@
 \citep{Truelove97}.  We initialize the simulation with \textsl{grafic}
-\citep{Bertschinger01} at $z = 130$ and use the cosmological
-parameters from the 7-year WMAP data \citep{WMAP7}: $\Omega_M =
-0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$,
-$\sigma_8 = 0.81$, and $n = 0.963$ with the variables having their
-usual definitions.  We stop the simulation at $z=7$.
+\citep{Bertschinger01} at $z = 130$ and use the cosmological parameters
+from the 7-year WMAP data \citep{WMAP7}: $\Omega_M = 0.266$,
+$\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 =
+0.81$, and $n = 0.963$ with the variables having their usual
+definitions.  We stop the simulation at $z=7$.
 
 We use a non-equilibrium chemistry solver with 9 species of hydrogen,
-helium, and molecular hydrogen \citep{Abel97}.  We will follow-up this
-study with one that considers radiative cooling from metal-enriched
-gas, using the method of \citet{2008MNRAS.385.1443S}.
+helium, and molecular hydrogen \citep{Abel97}.  We spatially
+distinguish metal enrichment from Pop II and Pop III stars.  We will
+follow-up this study with one that considers radiative cooling from
+metal-enriched gas, using the method of \citet{2008MNRAS.385.1443S}.
 
@@
 % cooling curve that is calculated from CLOUDY \citep{CLOUDY} and using
-% the method of \citet{2008MNRAS.385.1443S}.  It is tabulated based on
+% the method of \citep{2008MNRAS.385.1443S}.  It is tabulated based on
 % density, temperature, electron fraction, and metallicity.
@@
 
-We distinguish Pop II and Pop III SF by the metallicity of the densest
-cell in the molecular cloud.  Pop II stars are formed if [Z/H] $> -4$,
-and Pop III stars are formed otherwise.  We do not consider Pop III.2
-stars and intermediate mass stars from CMB-limited cooling.
+\begin{figure}
+\epsscale{1.15}
+\plotone{Lstar.eps}
+\epsscale{1}
+\caption{\label{fig:massfn} \textit{Top}: Halo mass function of the
+  simulation compared with the analytical fit (solid) of
+  \citet{Warren06}.  \textit{Bottom}: Total Pop II luminosities of
+  halos with constant mass-to-light ratios overplotted.}
+\end{figure}
+
+We distinguish Pop II and Pop III SF by the total metallicity of the
+densest cell in the molecular cloud.  Pop II stars are formed if [Z/H]
+$> -4$, and Pop III stars are formed otherwise.  We do not consider
+Pop III.2 stars and intermediate mass stars from CMB-limited cooling.
 
@@
 % at the high-mass end and an exponential cut-off below $M_{\rm char}$
-% \citep{refs}.
+% \cite{refs}.
 
-For Pop III stars, we use the same SF model as \citet{Abel07} and
-\citet{Wise08_Gal} where each star particle represents a single star.
-The critical overdensity in which a star forms is $5 \times 10^5$.
-Instead of using a fixed stellar mass, we randomly sampled from an IMF
-with a functional form of
+For Pop III stars, we use the same SF model as \citet{Wise08_Gal} where
+each star particle represents a single star, forming at an overdensity
+of $5 \times 10^5$.  Instead of using a fixed stellar mass, we randomly
+sampled from an IMF with a functional form of
 %
@@
 Salpeter IMF but is exponentially cutoff below that mass
-\citep{Chabrier03, Clark09}.  For reproducibility, we record the
-number of times the random number generator \citep[Mersenne
-  twister;][]{MTwister} has been called for use when restarting the
+\citep{Chabrier03, Clark09}.  For reproducibility, we record the number
+of times the random number generator (Mersenne twister;
+\citet{MTwister}) has been called for use when restarting the
 simulations.
@@
 
-The mass-dependent luminosities and lifetimes of the Pop III stars are
-taken from \citet{Schaerer02}.  The radiation field is evolved with
-adaptive ray tracing \citep{Abel02_RT, Wise10} and is coupled
-self-consistently to the hydrodynamics.  We model the \hh~dissociating
-radiation with an optically-thin, inverse square profile, centered on
-all stars.  These stars die as pair-instability SNe (PISNe) if they
-are in the mass range 140--260 \Ms~\citep{Heger03}.  We use the
-explosion energy from \citet{Heger02}, where we fit the following
-function to their models, $E_{\rm PISN} = 10^{51} \times [5.0 + 1.304
-(M_{\rm He} - 64)]$, where $M_{\rm He} = (13/24) \times (M_\star - 20)
-\Ms$ is the helium core mass and $M_\star$ is the stellar mass.
+\begin{figure*}
+\epsscale{1.15}
+\plotone{f1.eps}
+\epsscale{1}
+\caption{\label{fig:projections} Density-weighted projections of gas
+  density (top), temperature (middle), and metallicity (bottom) at
+  $z=7$.  The left column shows the entire simulation volume, where
+  the center and right columns focus on the intense and quiet halos,
+  which are marked by left and right arrows in the upper-left panel.
+  The metallicity projections are a composite picture of metals
+  originating from Pop III (red) and Pop II (blue) stars with magenta
+  indicating a mixture of the two.}
+\end{figure*}
+
+We use mass-dependent luminosities and lifetimes of the Pop III stars
+from \citet{Schaerer02}.  The radiation field is evolved with adaptive
+ray tracing \citep{Abel02_RT, Wise10} and is coupled self-consistently
+to the hydrodynamics.  We model the \hh~dissociating radiation with an
+optically-thin, inverse square profile, centered on all stars.  These
+stars die as pair-instability SNe (PISNe) if they are in the mass
+range 140--260 \Ms~\citep{Heger03}.  We use the explosion energy from
+\citet{Heger02}, where we fit the following function to their models,
+$E_{\rm PISN} = 10^{51} \times [5.0 + 1.304 (M_{\rm He} - 64)]$, where
+$M_{\rm He} = (13/24) \times (M_\star - 20) \Ms$ is the helium core
+(and equivalently the ejecta) mass and $M_\star$ is the stellar mass.
 
@@
 is the key ingredient here.  For SN feedback, these stars generate
-$6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$ of energy after living
-for 4 Myr, which is injected into spheres with a radius of 10 pc.  If
-the resolution of the grid is less than 10/3 pc, we deposit the energy
+$6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$ after living for 4 Myr,
+which is injected into spheres with a radius of 10 pc.  If the
+resolution of the grid is less than 10/3 pc, we deposit the energy
 into a $3^3$ cube surrounding the star particle.
+
+\begin{figure*}
+\epsscale{1.15}
+\plotone{f2.eps}
+\epsscale{1}
+\caption{\label{fig:evo} (a) Evolution of the total halo mass (top),
+  stellar mass (middle), and gas fraction (bottom) of the quiet
+  (dashed) and intense (solid) halos.  (b) Mass-weighted stellar
+  metallicities and gas metallicities enriched by Pop II and Pop III
+  SNe of the intense (top) and quiet (bottom) halos.}
+\end{figure*}
 
@@
 \label{sec:results}
-
-\begin{figure*}
-  \epsscale{0.8}
-  \plotone{f3}
-  \epsscale{1}
-  \caption{\label{fig:projections} Density-weighted projections of gas
-    density (top), temperature (middle), and metallicity (bottom) at
-    $z=7$.  The left column shows the entire simulation volume, where
-    the center and right columns focus on the intense and quiet halos,
-    which are marked by arrows in the upper-left panel.  The
-    metallicity projections are a composite picture of metals
-    originating from Pop III (red) and Pop II (blue) stars with purple
-    indicating a mixture of the two.}
-\end{figure*}
 
@@
 mergers between $z=10$ and $z=7$.  We name the halos ``quiet'' and
-``intense'', respectively.  We start with the mass accretion history
-and enrichment of the halos.  We then compare the nature of the
-stellar populations in these halos.
+``intense'', respectively.  The entire simulation contains 38 galaxies
+with 3640 Pop II stellar clusters and captures the formation of 333
+Pop III stars.  The halo mass function and galaxy luminosities are
+plotted in Figure \ref{fig:massfn}.  This simulation has $1.4 \times
+10^8$ computational elements and a maximal spatial resolution of 0.1
+pc.
+
+% We start with the mass accretion history and enrichment of the
+% halos.  We then compare the nature of the stellar populations in
+% these halos.
 
@@
 density, temperature, and metallicity, showing the entire box and
-focusing on the two halos of interest.  The quiet and intense halos
-are located in the bottom center and bottom right of the full box,
-respectively.  Radiative and mechanical feedback create a multi-phase
-medium inside these halos, which are embedded in a warm and ionized
-IGM.
+focusing on the two halos of interest.  Radiative and mechanical
+feedback create a multi-phase medium inside these halos, which are
+embedded in a warm and ionized IGM.
+
+\begin{figure*}
+\epsscale{1.1}
+\plotone{f3.eps}
+\epsscale{1}
+\caption{\label{fig:pops} The scatter plots show the SF history of the
+  quiet (left) and intense (right) halos as a function of metallicity
+  at $z=7$.  Each circle represents a star cluster, whose area is
+  proportional to its mass.  The open circles in the upper right
+  represent sizes of $10^3$, $10^4$, and $10^5$ \Ms~star clusters.
+  The dashed lines in the right panel guide the eye to two stellar
+  populations that were formed in two satellite halos, merging at
+  $z=7.5$.  The upper histogram shows the SF rate.  The right
+  histogram depicts the stellar metallicity distribution.}
+\end{figure*}
 
@@
 \label{sec:halo}
-
-\begin{figure*}
-  \epsscale{1.15}
-  \plottwo{f1}{f2}
-  \caption{\label{fig:evo} (a) Evolution of the total halo
-    mass (top), stellar mass (middle), and gas fraction (bottom) of
-    the quiet (dashed) and intense (solid) halos.  (b)
-    Mass-weighted stellar metallicities and gas metallicities enriched
-    by Pop II and Pop III SNe of the intense (top) and quiet (bottom)
-    halos.}
-  \epsscale{1}
-\end{figure*}
 
@@
   Wise08_Gal}.  Afterwards these halos can cool efficiently through
-\hh~cooling, sustaining constant and sometimes bursty SF.  The latter
-characteristics are equated with the definition of a galaxy.  The
-quiet halo forms $10^5 \Ms$ of stars by $z=9$.  This initial starburst
-photo-evaporates the majority of its molecular clouds, in addition to
-heating and ionizing the surrounding IGM out to a radius of 10--15 kpc
-at $z=9$.  These respectively reduce the in-situ and external cold gas
-supply that could feed future SF.
+\hh~cooling, sustaining constant and sometimes bursting SF.  The
+latter characteristics are equated with the definition of a galaxy.
+The quiet halo forms $10^5 \Ms$ of stars by $z=9$.  This initial
+starburst photo-evaporates the majority of its molecular clouds, in
+addition to heating and ionizing the surrounding IGM out to a radius
+of 10--15 kpc at $z=9$.  These respectively reduce the in-situ and
+external cold gas supply that could feed future SF.
 
-The gas fractions of both halos are depleted from 0.15 to 0.08 by
-outflowing shocks driven by ionization fronts and blastwaves in their
-initial starbursts.  The quiet halo never recovers to the cosmic
-fraction $\Omega_b/\Omega_M$ for the following reason.  The lack of
-major mergers of halos above the filtering mass leads to a small gas
-fraction because halos with $M < M_f$ are likely photo-evaporated,
-hosting diffuse warm gas reservoirs instead of cold dense cores.
-During this quiescent period, the halo mainly accretes warm diffuse
-gas from the filaments and IGM.  In contrast, the intense halo grows
-from major mergers of halos with $M > M_f$.  The progenitor halos
-involved in the major mergers are able to host molecular clouds and
-have, in general, higher gas fractions.  Between $z=10$ and $z=8$, the
-gas fraction increases from 0.07 to 0.12 until it jumps to 0.14 when a
+The gas fractions of both halos decrease from 0.15 to 0.08 by outflows
+driven by ionization fronts and blastwaves in their initial
+starbursts.  The quiet halo does not have a major merger with any halo
+with $M > M_f$, leading to a small final gas fraction.  These low-mass
+halos are photo-evaporated, hosting diffuse warm gas reservoirs
+instead of cold dense cores.  After $z=10$, the halo mainly accretes
+warm diffuse gas from the filaments and IGM.  In contrast, the intense
+halo grows from major mergers of halos with $M > M_f$.  The progenitor
+halos involved in the major mergers are able to host molecular clouds
+and have higher gas fractions.  Between $z=10$ and $z=8$, the gas
+fraction increases from 0.07 to 0.12 until it jumps to 0.14 when a
 gas-rich major merger occurs.  The stellar mass accordingly increases
-with the ample supply of gas during this period.  The gas fraction
-then decreases by 0.01 when galactic outflows are generated from the
-starburst associated with this major merger.
+with the ample supply of gas during this period.
 
@@
 the nearby IGM out to a radius of 10 kpc and provides a metallicity
-floor of $[Z_3/H] \sim -3$, given $M_{\rm char} = 100 \Ms$.  The
-metallicity from Pop II SNe initially enrich the ISM of both halos to
-an average $[\bar{Z}_2/H]$ between --3.5 and --3.  The quiet halo is
-enriched to $[\bar{Z}_2/H] \sim -2.5$ until the metal-poor inflows
-balance the metal-rich galactic outflows, which are directed in the
-polar directions of the gas disk, keeping the adjacent filaments
-metal-poor.  These features and a well-mixed ISM
-\citep[cf.][]{Wise08_Gal, Greif10} are apparent in the metallicity
-projections in Figure \ref{fig:projections}.  The average stellar
-metallicities is equal or slightly higher up to 0.5 dex than
-$[\bar{Z}_2/H]$.
+floor of $[Z_3/H] \sim -3$.  The metallicity from Pop II SNe initially
+enrich the ISM of both halos to an average $[\bar{Z}_2/H]$ between
+--3.5 and --3.
 
-In the intense halo, the first few Pop II star clusters have [Z/H]
+In the quiet halo, an equilibrium of $[\bar{Z}_2/H] \sim -2.5$ is
+established between metal-rich outflows and metal-poor inflows.
+Galactic outflows are directed in the polar directions of the gas
+disk, keeping the adjacent filaments metal-poor.  These features and a
+well-mixed ISM \citep[cf.][]{Wise08_Gal, Greif10} are apparent in the
+metallicity projections in Figure \ref{fig:projections}.  The average
+stellar metallicity is within 0.5 dex of $[\bar{Z}_2/H]$.
+
+In the intense halo, the first few Pop II star clusters have $[Z/H]$
 between --1 and --2 and dominate the average stellar metallicity at $z
-> 8$.  Afterwards the metallicity increases itself by a factor of 30
-to $[\bar{Z}_2/H] = -1.5$ through self-enrichment from a starburst.
+> 8$.  Afterwards the metallicity increases by a factor of 30 to
+$[\bar{Z}_2/H] = -1.5$ through self-enrichment from a starburst.
 Because this halo is located in a large-scale overdensity, most of the
 ejecta falls back into the halo after reaching distances up to 20
-comoving kpc, in turn keeping the halo gas metallicity high because
-the inflows are relatively metal-rich themselves.  After the $z \sim
-8$ starburst, the average stellar metallicity follows the average gas
+comoving kpc, keeping the halo gas metallicity high because the
+inflows are relatively metal-rich themselves.  After the $z \sim 8$
+starburst, the average stellar metallicity follows the average gas
 metallicity within 0.1 dex.
 
-\subsection{Population III star formation history}
-
-\textit{Quiet halo}.--- The most massive progenitor interestingly
-never hosts a Pop III star.  Instead a nearby halo forms a Pop III
-star, which (randomly) produces a PISNe at $z=16$.  The blastwave
-overruns the most massive progenitor, and the dense core survives this
-event and is enriched by this PISN, triggering the transition to Pop
-II SF.  Other progenitors host three Pop III stars, forming at $z =
-15.4, 14.2, 13.8$, with the latter producing a PISN.  Metal enrichment
-from these two PISNe and Pop II SF quench Pop III SF in this halo.
-
-\textit{Intense halo}.--- The progenitors host a total of 56 Pop III
-stars with 21 producing PISNe.  The first forms in a $6 \times 10^5
-\Ms$ halo at $z=19$.  Pop III stars form on a regular interval in the
-halo's progenitors until $z=9$ when most of these halos enter the
-metal-rich bubble surrounding the intense halo.  There are two stars
-forming at $z=7.7$ with [Z/H] = --5.7, whose molecular clouds were
-enriched by external blastwaves that only partially enriched the dense
-regions.  This falls into the metallicity range where fragmentation
-occurs only if dust cooling is efficient below \tento{-4} $Z_\odot$.
-The most massive progenitors of the intense halo cease to form Pop III
-stars at $z<12$ because of nearby or intrinsic PISNe.
-
-\subsection{Population II stellar populations}
+\subsection{Star formation history}
 \label{sec:pop}
 
-\begin{figure*}
-  \plottwo{f4a}{f4b}
-  \caption{\label{fig:pops} The scatter plots show the SF history of
-    the quiet (left) and intense (right) halos as a function of
-    metallicity at $z=7$.  Each circle represents a star cluster,
-    whose area is proportional to its mass.  The open circles in the
-    upper right represent sizes of $10^3$, $10^4$, and $10^5$ \Ms~star
-    clusters.  The dashed lines in the right panel guide the eye to
-    two stellar populations that were formed in two satellite halos,
-    merging at $z=7.5$.  The upper histogram collects the SF history
-    into 25 equal temporal bins.  The right histogram depicts the
-    stellar metallicity distribution.}
-\end{figure*}
+The most massive progenitor of the quiet halo interestingly never
+hosts a Pop III star.  Instead a nearby halo forms a Pop III star,
+which (randomly) produces a PISNe at $z=16$.  The blastwave overruns
+the most massive progenitor, and the dense core survives this event
+and is enriched by this PISN, triggering the transition to Pop II SF.
+Other progenitors host three Pop III stars, forming at $z = 15.4,
+14.2, 13.8$, with the latter producing a PISN.  Metal enrichment from
+these two PISNe and Pop II SF quench Pop III SF in this halo.  The
+progenitors of the intense halo host a total of 56 Pop III stars with
+21 producing PISNe.  The first forms in a $6 \times 10^5 \Ms$ halo at
+$z=19$.  Pop III stars form on a regular interval in the halo's
+progenitors until $z=9$ when most of these halos enter the metal-rich
+bubble surrounding the intense halo.
 
@@
 
-Figure \ref{fig:pops} shows the SF history (SFH) of both halos.  The
-metallicity distribution, SF rates, and metallicity evolution and
-spread at a given time can all be extracted from these data.
+Figure \ref{fig:pops} shows the SF history (SFH), metallicity
+distribution, and SF rates of both halos.  A nearby PISNe provides a
+metallicity floor of [Z/H] = --2.8 in the quiet halo at which
+metallicity the first Pop II stars form.  The stellar metallicity
+evolution exhibits what is expected from an isolated system with the
+stellar feedback steadily enriching the ISM, resulting in a
+correlation between stellar age and metallicity.  After $z=10$ the
+metallicities plateau at [Z/H] = --2.1 for reasons previously
+discussed.  The SFR peaks at $z=10$ and decreases as the cold gas
+reservoir is depleted.  Around $z=7.5$, a 25:1 minor merger occurs,
+and the gas inside the satellite halo is compressed, triggering
+metal-poor, [Z/H] = --3.2, SF during its nearest approach.  This halo
+remains metal-poor because most of metal enrichment in the quiet halo
+occurs in bi-polar flows perpendicular to the galaxy disk and
+filament.  Stars with [Z/H] $<$ --3 compose 1.6 percent of the total
+stellar mass.
 
-\textit{Quiet halo}.--- A nearby PISNe provides a metallicity floor of
-[Z/H] = --2.8 at which metallicity the first Pop II stars form.  The
-stellar metallicity evolution exhibits what is expected from an
-isolated system with the stellar feedback steadily enriching the ISM,
-resulting in a correlation between stellar age and metallicity.  After
-$z=10$ the metallicities plateau at [Z/H] = --2.1 for reasons
-discussed in \S\ref{sec:halo}.  The SFR peaks at $z=10$ and decreases
-as the cold gas reservoir is depleted.  Around $z=7.5$, a 25:1 minor
-merger occurs, and the gas inside the satellite halo is compressed,
-triggering metal-poor, [Z/H] = --3.2, SF during its nearest approach.
-This halo infalls through a filament, where most of metal enrichment
-in the quiet halo occurs in bi-polar flows perpendicular to the galaxy
-disk and filament.  The filament and thus this satellite halo remains
-relatively metal-poor.  Stars with [Z/H] $<$ --3 compose 1.6 percent
-of the total stellar mass.
-
-\textit{Intense halo}.--- In contrast with the quiet halo, the intense
-halo undergoes a few mergers of halos with an established stellar
-population.  This creates a superposition of age-metallicity tracks in
-the SFH, seen in the complexity of Figure \ref{fig:pops}.  The first
-two Pop II stellar clusters have an unusually high metallicity [Z/H]
-$\sim$ --1, which occurs when a PISN blastwave triggers SF in two
-neighboring halos.  Most of the early SF occurs around [Z/H] = --2.5.
-At $z=9$, the halo's virial temperature reaches \tento{4} K.  This
-combined with a 10:1 merger creates a starburst that quickly enriches
-the halo to [Z/H] = --1.5 by $z=8$.  The halo continues to enrich
-itself with further SF until $z=7$.  The spikes in the scatter plot
-correspond to SN triggered SF in nearby molecular clouds
-that are enriched up to a factor of 10 with respect to the ISM.
-However the mass fraction of these metal-rich, SN triggered clusters
-are small compared to the total stellar mass.  The starburst at $z=9$
-creates a bimodal metallicity distribution with peaks at [Z/H] = --2.4
-and --1.2 with the metal-rich component mainly being created after the
-starburst.  Two systems with sizable stellar components merge into the
-halo at $z \sim 8$, and their stellar populations are still
-discernible in the metallicity-age plot, whose tracks are noted by
-dashed lines.  Stars with [Z/H] $<$ --3 compose 1.8 percent of the
-total stellar mass.
+In contrast with the quiet halo, the intense halo undergoes a few
+mergers of halos with an established stellar population.  This creates
+a superposition of age-metallicity tracks in the SFH, seen in the
+complexity of Figure \ref{fig:pops}.  The first two Pop II stellar
+clusters have an unexpectedly high metallicity [Z/H] $\sim$ --1, which
+occurs when a PISN blastwave triggers SF in two neighboring halos.
+Most of the early SF have [Z/H] = --2.5.  At $z=9$, the halo's virial
+temperature reaches \tento{4} K.  This combined with a 10:1 merger
+creates a starburst that quickly enriches the halo to [Z/H] = --1.5 by
+$z=8$.  The halo continues to enrich itself afterwards.  The spikes in
+the scatter plot correspond to SN triggered SF in nearby molecular
+clouds that are enriched up to a factor of 10 with respect to the ISM.
+However their mass fraction are small compared to the total stellar
+mass.  The starburst at $z=9$ creates a bimodal metallicity
+distribution with peaks at [Z/H] = --2.4 and --1.2 with the metal-rich
+component mainly being created after the starburst.  Two systems with
+sizable stellar components merge into the halo at $z \sim 8$, and
+their stellar populations are still discernible in the metallicity-age
+plot.  Stars with [Z/H] $<$ --3 compose 1.8 percent of the total
+stellar mass.
 
@@
 
-In this paper, we focus on the birth of two galaxies prior to
+In this Letter, we focus on the birth of two galaxies prior to
 reionization with a cosmological AMR radiation hydrodynamics
@@
 \citep{Gnedin06}, otherwise they will be incorporated into galactic
-stellar halos.
+stellar halos.  A $z=8.55$ galaxy was recently spectroscopically
+confirmed that is contained in an ionized bubble with radius 0.1--0.5
+Mpc with an uncharacterized population of galaxies contributing to the
+local ionizing radiation field \citep{Lehnert10_z8.6}.  The galaxies
+simulated here might represent this population.
 
@@
 and surrounding $\sim 5$ kpc to a metallicity of 10$^{-3} Z_\odot$,
-given a Pop III characteristic mass of 100~\Ms.  If the first stars
-have a lower characteristic mass that favor hypernovae
-\citep{Tumlinson07_IMF}, then this metallicity floor should be lowered
-by a factor of $\sim 10$ because (1) the metal ejecta is lowered by a
-factor of $\sim 50$ and (2) the mixing mass is approximately decreased
-by a factor of $(E_{\rm hyp}/E_{\rm PISN})^{3/5}$ in the Sedov-Taylor
-solution, where $(E_{\rm hyp}/E_{\rm PISN}) \sim 0.1$ is the ratio of
-explosion energies of a hypernova and PISN.  In the case where this
-metallicity floor is less than the critical metallicity, then the next
-instance of SF will further enrich the ISM, solidifying the transition
-to Pop II SF.  We conclude that it only takes one, at most two, SNe
-from Pop III stars in the halo progenitors to complete the transition
-to Population II \citep[see also][]{Frebel10}.  The question of
-whether the critical metallicity is \tento{-6} or \tento{-3.5}
-$Z_\odot$ is most applicable to nearby halos where the heavy elements
-mix slowly into dense cores as the blastwave overtakes it.  Less than
-two percent of stars have [Z/H] $< -3$ in both systems, consistent
-with observations of metal-poor stars in the halo and dSphs
-\citep[e.g.][]{Beers05, Battaglia10}.
+given $M_{\rm char} = 100~\Ms$.  DLA systems have a metallicity floor
+on the same order \citep{Wolfe05_Review}, and metal enrichment from Pop
+III SNe provides a possible explanation.
 
-We also find that the merger history plays an important role in
-supplying gas into halos after its first epoch of SF.  Mergers of
-halos below the filtering mass are inefficient in providing gas
-whereas the opposite is true for merging halos above the filtering
-mass.  Halos do not necessarily need $\tvir \ge 10^4$ K to form
-significant stellar populations; however SFRs dramatically increase,
-and thus metal enrichment, when this threshold is reached.  Halos with
-mostly gas-poor mergers or a quiet merger history result in a
-monotonic increase in metallicity with time.  SFHs become more complex
-with multiple metallicity-age tracks if the halo experiences mergers
-with other halos that have an established stellar population.
-Furthermore SF that is triggered by blastwaves interacting with
-molecular clouds can have metallicities up to a factor of 10 higher
-than the main starburst.  Lastly we find that a starburst at $\tvir =
-10^4$ K enriches the host halo enough to create a bimodal metallicity
-distribution, where the metal-poor component is created before the
-burst.  Note that mergers of stellar populations can also create a
-similar bimodal distribution.  Such distributions are observed in
-dSphs \citep[e.g.][]{Battaglia10}.
+If the first stars have a lower characteristic mass that favor
+hypernovae \citep{Tumlinson07_IMF}, then this metallicity floor should
+be lowered by a factor of $\sim 10$ because (1) the metal ejecta is
+lowered by a factor of $\sim 50$ and (2) the mixing mass is
+approximately decreased by a factor of $(E_{\rm hyp}/E_{\rm
+  PISN})^{3/5}$ in the Sedov-Taylor solution, where $(E_{\rm
+  hyp}/E_{\rm PISN}) \sim 0.1$ is the ratio of explosion energies of a
+hypernova and PISN.  In the case where this metallicity floor is less
+than the critical metallicity, then the next instance of SF will
+further enrich the ISM, solidifying the transition to Pop II SF.  We
+conclude that it only takes one, at most two, SNe from Pop III stars
+in the halo progenitors to complete the transition to Population II
+\citep{Frebel10}.  The question of whether the critical metallicity is
+\tento{-6} or \tento{-3.5} $Z_\odot$ is most applicable to nearby
+halos where the heavy elements mix slowly into dense cores as the
+blastwave overtakes it.  Less than two percent of stars have [Z/H] $<
+-3$ in both systems, consistent with observations of metal-poor stars
+in the halo and dSphs \citep{Beers05, Battaglia10}.
+
+% We also find that the merger history plays an important role in
+% supplying gas into halos after its first epoch of SF.  Mergers of
+% halos below the filtering mass are inefficient in providing gas
+% whereas the opposite is true for merging halos above the filtering
+% mass.  Halos do not necessarily need $\tvir \ge 10^4$ K to form
+% significant stellar populations; however SFRs dramatically increase,
+% and thus metal enrichment, when this threshold is reached.  Halos
+% with mostly gas-poor mergers or a quiet merger history result in a
+% monotonic increase in metallicity with time.  SFHs become more
+% complex with multiple metallicity-age tracks if the halo experiences
+% mergers with other halos that have an established stellar
+% population.  Furthermore SF that is triggered by blastwaves
+% interacting with molecular clouds can have metallicities up to a
+% factor of 10 higher than the main starburst.  Starbursts at $\tvir =
+% 10^4$ K can enrich the host halo enough to create a bimodal
+% metallicity distribution, where the metal-poor component is created
+% before the burst.  Note that mergers of stellar populations can also
+% create a similar bimodal distribution, which are observed in dSphs
+% \cite{Battaglia10}.
 

### 2010-11-08 ms.tex
Renamed figures to be f[1-4].eps
Applying changes that I forgot to pull.

@@
 complexities and the transition from Pop III to II stars.  In this
-Letter, we present the simulations that include both types of SF, and
+Letter, we present a simulation that includes both types of SF, and
 their radiative and mechanical feedback.  The methods used here
@@
 \epsscale{1.15}
-\plotone{Lstar.eps}
+\plotone{f1}
 \epsscale{1}
@@
 \epsscale{1.15}
-\plotone{f1.eps}
+\plotone{f2}
 \epsscale{1}
@@
 \epsscale{1.15}
-\plotone{f2.eps}
+\plotone{f3}
 \epsscale{1}
@@
 \epsscale{1.1}
-\plotone{f3.eps}
+\plotone{f4}
 \epsscale{1}
@@
 local ionizing radiation field \citep{Lehnert10_z8.6}.  The galaxies
-simulated here might represent this population.
+simulated here might represent this population and should be detected
+with the upcoming \textit{James Webb Space Telescope}.
 

### 2010-11-08 ms.tex
Under the 3500 word limit.

@@
   metallicities reported in the literature, which is of this order.
-  Neighboring halos are enriched to metallicities 10--100 times lower
-  as the enriching blastwaves mainly bypass them.  Stellar
-  metallicities trace gas metallicities within 0.2 dex.  We find that
-  stellar metallicities do not necessarily trace stellar ages, as
-  mergers of halos with established stellar populations can create
-  superpositions of $t-Z$ evolutionary tracks.  A bimodal metallicity
-  distribution is created after a starburst occurs when the halo can
-  cool efficiently through atomic line cooling.
+  We find that stellar metallicities do not necessarily trace stellar
+  ages, as mergers of halos with established stellar populations can
+  create superpositions of $t-Z$ evolutionary tracks.  A bimodal
+  metallicity distribution is created after a starburst occurs when
+  the halo can cool efficiently through atomic line cooling.
 
@@
 characteristic mass and suppressed fragmentation in its protostellar
-collapse \citep{ABN02, Bromm02_P3, Yoshida03, OShea07a}.  A fraction of
-these stars enrich the surrounding intergalactic medium (IGM) when
-they go supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
+collapse \citep{ABN02, Bromm02_P3, OShea07a}.  A fraction of these
+stars enrich the surrounding intergalactic medium (IGM) when they go
+supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
 supernovae (SNe) or in stars roughly between 140 \Ms~and 260 \Ms~in
@@
 in the Milky Way halo and nearby dwarf spheroidal (dSph) galaxies,
-both with a metallicity floor of [Z/H]\footnote[\dag]{We use the
-  conventional notation, [Z/H] $\equiv$ log(Z/H) -
-  log(Z$_\odot$/H$_\odot$)} = --4 \citep{Beers05, Tafelmeyer10,
-  Frebel10_Obs}.
+both with a metallicity floor of [Z/H] = --4 \citep{Beers05,
+  Tafelmeyer10, Frebel10_Obs}.
 
@@
 protogalaxies, resolving the important scales and including the most
-important physical effects.  We describe our simulation setup and our
-adopted SF models in \S \ref{sec:setup} and present our results in \S
-\ref{sec:results}.  We discuss the implications of our findings and
-conclude in the last section.
+important physical effects.
 
@@
 \label{sec:setup}
-
-In this section, we first describe our simulation setup.  We then
-detail the SF models used here and how we model radiative and SNe
-feedback.
 
@@
 enzo~v2.0\footnote[\ddag]{\texttt{enzo.googlecode.com, unstable
-    changeset b86d8ba026d6}} \citep{BryanNorman1997, OShea2004}, which
-has been modified to use a HLLC Riemann solver \citep{Toro94_HLLC} for
+    changeset b86d8ba026d6}} \citep{OShea2004}, which has been
+modified to use a HLLC Riemann solver \citep{Toro94_HLLC} for
 additional stability in strong shocks.  To resolve minihalos with at
@@
 cells, avoiding artificial fragmentation during gaseous collapses
-\citep{Truelove97}.  We initialize the simulation with \textsl{grafic}
-\citep{Bertschinger01} at $z = 130$ and use the cosmological parameters
-from the 7-year WMAP data \citep{WMAP7}: $\Omega_M = 0.266$,
-$\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 =
-0.81$, and $n = 0.963$ with the variables having their usual
-definitions.  We stop the simulation at $z=7$.
+\citep{Truelove97}.  This simulation has $1.4 \times 10^8$
+computational elements and a maximal spatial resolution of 0.1 pc.  We
+initialize the simulation with \textsl{grafic} \citep{Bertschinger01}
+at $z = 130$ and use the cosmological parameters from the 7-year WMAP
+data \citep{WMAP7}: $\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$,
+$\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$
+with the variables having their usual definitions.  We stop the
+simulation at $z=7$.
 
@@
 Pop III stars.  The halo mass function and galaxy luminosities are
-plotted in Figure \ref{fig:massfn}.  This simulation has $1.4 \times
-10^8$ computational elements and a maximal spatial resolution of 0.1
-pc.
+plotted in Figure \ref{fig:massfn}.
 
@@
   proportional to its mass.  The open circles in the upper right
-  represent sizes of $10^3$, $10^4$, and $10^5$ \Ms~star clusters.
-  The dashed lines in the right panel guide the eye to two stellar
-  populations that were formed in two satellite halos, merging at
-  $z=7.5$.  The upper histogram shows the SF rate.  The right
-  histogram depicts the stellar metallicity distribution.}
+  represent $10^3$, $10^4$, and $10^5$ \Ms~star clusters.  The dashed
+  lines in the right panel guide the eye to two stellar populations
+  that were formed in two satellite halos, merging at $z=7.5$.  The
+  upper histogram shows the SFR.  The right histogram depicts the
+  stellar metallicity distribution.}
 \end{figure*}
@@
 
-Support for this work was provided by NASA through Hubble Fellowship
-grant \#120-6370 awarded by the Space Telescope Science Institute,
-which is operated by the Association of Universities for Research in
-Astronomy, Inc., for NASA, under contract NAS 5-26555.  Computational
-resources were provided by NASA/NCCS award SMD-09-1439.
-J.~H.~W. thanks Renyue Cen, Amina Helmi, Marco Spaans, and Eline
-Tolstoy for enlightening discussions.  The majority of the analysis
-and plots were done with \texttt{yt} \citep{yt_full_paper}.
+J.~H.~W. is supported by NASA through Hubble Fellowship grant
+\#120-6370 awarded by the Space Telescope Science Institute, which is
+operated by the Association of Universities for Research in Astronomy,
+Inc., for NASA, under contract NAS 5-26555.  Computational resources
+were provided by NASA/NCCS award SMD-09-1439.  J.~H.~W. thanks Renyue
+Cen, Amina Helmi, Marco Spaans, and Eline Tolstoy for enlightening
+discussions.  The majority of the analysis and plots were done with
+\texttt{yt} \citep{yt_full_paper}.
 

### 2010-11-11 ms.tex
Moving Figure 4 to the next page and removing Lstar.eps.
Changed to preprint format.

@@
-\documentclass[apjl]{emulateapj}
-%\documentclass[12pt,preprint]{aastex}
+%\documentclass[apjl]{emulateapj}
+\documentclass[12pt,preprint]{aastex}
 
@@
 \usepackage{natbib}
-%\usepackage[section] {placeins}
+\usepackage[section] {placeins}
 \bibliographystyle{apj}
@@
 
-\input macros.tex
+\newcommand{\fesc}{\ifmmode{f_{\rm esc}}\else{$f_{\rm esc}$}\fi}
+\newcommand{\fescs}{\ifmmode{f_{\rm esc}^\star}\else{$f_{\rm esc}^\star$}\fi}
+\newcommand{\kms}{\ifmmode{{\rm km~s^{-1}}}\else{km s$^{-1}$}\fi}
+\newcommand{\cubecm}{\ifmmode{{\rm cm^{-3}}}\else{cm$^{-3}$}\fi}
+\newcommand{\lsim}{\lower0.3em\hbox{$\,\buildrel <\over\sim\,$}}
+\newcommand{\gsim}{\lower0.3em\hbox{$\,\buildrel >\over\sim\,$}}
+\newcommand{\li}{\noindent$\bullet$\quad}
+\newcommand{\flux}{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$}
+\newcommand{\emis}{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$}
+\newcommand{\sfr}{M$_\odot$ yr$^{-1}$ Mpc$^{-3}$}
+\newcommand{\hst}{{\it HST}}
+\newcommand{\enzo}{{\sl Enzo}}
+\newcommand{\Ms}{\ifmmode{M_\odot}\else{$M_\odot$}\fi}
+\newcommand{\mmin}{M$_{min}$}
+\newcommand{\hh}{H$_2$}
+\newcommand{\Ol}{$\Omega_\Lambda$}
+\newcommand{\Om}{$\Omega_M$}
+\newcommand{\Ob}{$\Omega_b$}
+\newcommand{\theat}{$t_{\rm{heat}}$}
+\newcommand{\tcool}{$t_{\rm{cool}}$}
+\newcommand{\rcool}{$r_{\rm{cool}}$}
+\newcommand{\tcross}{$t_{\rm{cross}}$}
+\newcommand{\tdyn}{$t_{\rm{dyn}}$}
+\newcommand{\tkh}{$t_{\rm{KH}}$}
+\newcommand{\tH}{$t_{\rm{H}}$}
+\newcommand{\tvir}{\ifmmode{T_{\rm{vir}}}\else{$T_{\rm{vir}}$}\fi}
+\newcommand{\mvir}{\ifmmode{M_{\rm{vir}}}\else{$M_{\rm{vir}}$}\fi}
+\newcommand{\rvir}{\ifmmode{r_{\rm{vir}}}\else{$r_{\rm{vir}}$}\fi}
+\newcommand{\rr}{$r_{200}$}
+\newcommand{\lya}{Ly$\alpha$}
+\newcommand{\jj}{\ifmmode{J_{21}}\else{$J_{21}$}\fi}
+\newcommand{\flw}{\ifmmode{F_{LW}}\else{$F_{LW}$}\fi}
+\newcommand{\kph}{\ifmmode{k_{\rm ph}}\else{$k_{\rm ph}$}\fi}
+\newcommand{\tv}{$\langle T \rangle_{\rm v}$}
+\newcommand{\tm}{$\langle T \rangle_{\rm m}$}
+\newcommand{\msun}{{\rm\,M_\odot}} 
+\newcommand{\lsun}{{\rm\,L_\odot}}
+\newcommand{\zsun}{{\rm\,Z_\odot}}
+\newcommand{\etal}{et al.\ }
+\newcommand\tento[1]{$10^{#1}$}
+\newcommand\step[1]{\textit{Step #1}.---}
 
@@
 We use the adaptive mesh refinement (AMR) code
-enzo~v2.0\footnote[\ddag]{\texttt{enzo.googlecode.com, unstable
-    changeset b86d8ba026d6}} \citep{OShea2004}, which has been
-modified to use a HLLC Riemann solver \citep{Toro94_HLLC} for
-additional stability in strong shocks.  To resolve minihalos with at
-least 100 dark matter (DM) particles and follow the formation of the
-first generation of dwarf galaxies, we use a simulation box of 1 Mpc
-that has a resolution of $256^3$.  This gives us a DM mass resolution
-of 1840 \Ms.  We refine the grid on baryon overdensities of $3 \times
-2^{-0.2l}$, where $l$ is the AMR level, resulting in a
-super-Lagrangian behavior.  We also refine on a DM overdensity of $3
-\times 2^l$ and always resolve the local Jeans length by at least 4
-cells, avoiding artificial fragmentation during gaseous collapses
-\citep{Truelove97}.  This simulation has $1.4 \times 10^8$
-computational elements and a maximal spatial resolution of 0.1 pc.  We
-initialize the simulation with \textsl{grafic} \citep{Bertschinger01}
-at $z = 130$ and use the cosmological parameters from the 7-year WMAP
-data \citep{WMAP7}: $\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$,
-$\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$
-with the variables having their usual definitions.  We stop the
-simulation at $z=7$.
+enzo~v2.0\footnote{\texttt{enzo.googlecode.com, changeset
+    b86d8ba026d6}} \citep{OShea2004}, which has been modified to use a
+HLLC Riemann solver \citep{Toro94_HLLC} for additional stability in
+strong shocks.  To resolve minihalos with at least 100 dark matter
+(DM) particles and follow the formation of the first generation of
+dwarf galaxies, we use a simulation box of 1 Mpc that has a resolution
+of $256^3$.  This gives us a DM mass resolution of 1840 \Ms.  We
+refine the grid on baryon overdensities of $3 \times 2^{-0.2l}$, where
+$l$ is the AMR level, resulting in a super-Lagrangian behavior.  We
+also refine on a DM overdensity of $3 \times 2^l$ and always resolve
+the local Jeans length by at least 4 cells, avoiding artificial
+fragmentation during gaseous collapses \citep{Truelove97}.  This
+simulation has $1.4 \times 10^8$ computational elements and a maximal
+spatial resolution of 0.1 pc.  We initialize the simulation with
+\textsl{grafic} \citep{Bertschinger01} at $z = 130$ and use the
+cosmological parameters from the 7-year WMAP data \citep{WMAP7}:
+$\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h
+= 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$ with the variables having
+their usual definitions.  We stop the simulation at $z=7$.
 
@@
 \begin{figure}
-\epsscale{1.15}
+%\epsscale{1.15}
 \plotone{f1}
-\epsscale{1}
+%\epsscale{1}
 \caption{\label{fig:massfn} \textit{Top}: Halo mass function of the
@@
 \begin{figure*}
-\epsscale{1.15}
+%\epsscale{1.15}
 \plotone{f2}
-\epsscale{1}
+%\epsscale{1}
 \caption{\label{fig:projections} Density-weighted projections of gas
@@
 \begin{figure*}
-\epsscale{1.15}
+%\epsscale{1.15}
 \plotone{f3}
-\epsscale{1}
+%\epsscale{1}
 \caption{\label{fig:evo} (a) Evolution of the total halo mass (top),
@@
 embedded in a warm and ionized IGM.
-
-\begin{figure*}
-\epsscale{1.1}
-\plotone{f4}
-\epsscale{1}
-\caption{\label{fig:pops} The scatter plots show the SF history of the
-  quiet (left) and intense (right) halos as a function of metallicity
-  at $z=7$.  Each circle represents a star cluster, whose area is
-  proportional to its mass.  The open circles in the upper right
-  represent $10^3$, $10^4$, and $10^5$ \Ms~star clusters.  The dashed
-  lines in the right panel guide the eye to two stellar populations
-  that were formed in two satellite halos, merging at $z=7.5$.  The
-  upper histogram shows the SFR.  The right histogram depicts the
-  stellar metallicity distribution.}
-\end{figure*}
 
@@
 metallicity within 0.1 dex.
+
+\begin{figure*}
+%\epsscale{1.1}
+\plotone{f4}
+%\epsscale{1}
+\caption{\label{fig:pops} The scatter plots show the SF history of the
+  quiet (left) and intense (right) halos as a function of metallicity
+  at $z=7$.  Each circle represents a star cluster, whose area is
+  proportional to its mass.  The open circles in the upper right
+  represent $10^3$, $10^4$, and $10^5$ \Ms~star clusters.  The dashed
+  lines in the right panel guide the eye to two stellar populations
+  that were formed in two satellite halos, merging at $z=7.5$.  The
+  upper histogram shows the SFR.  The right histogram depicts the
+  stellar metallicity distribution.}
+\end{figure*}
 
@@
 operated by the Association of Universities for Research in Astronomy,
-Inc., for NASA, under contract NAS 5-26555.  Computational resources
-were provided by NASA/NCCS award SMD-09-1439.  J.~H.~W. thanks Renyue
-Cen, Amina Helmi, Marco Spaans, and Eline Tolstoy for enlightening
-discussions.  The majority of the analysis and plots were done with
-\texttt{yt} \citep{yt_full_paper}.
+Inc., for NASA, under contract NAS 5-26555.  M.~J.~T. and
+M.~L.~N. acknowledge partial support from NASA ATFP grant NNX08AH26G.
+Computational resources were provided by NASA/NCCS award SMD-09-1439.
+J.~H.~W. thanks Renyue Cen, Amina Helmi, Marco Spaans, and Eline
+Tolstoy for enlightening discussions.  The majority of the analysis
+and plots were done with \texttt{yt} \citep{yt_full_paper}.
 
@@
 %\input biblio.tex
-\bibliography{ms}
+%\bibliography{ms}
+\begin{thebibliography}{50}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Abel} {et~al.}(1997){Abel}, {Anninos}, {Zhang}, \&
+  {Norman}}]{Abel97}
+{Abel}, T., {Anninos}, P., {Zhang}, Y., \& {Norman}, M.~L. 1997, New Astronomy,
+  2, 181
+
+\bibitem[{{Abel} {et~al.}(2002){Abel}, {Bryan}, \& {Norman}}]{ABN02}
+{Abel}, T., {Bryan}, G.~L., \& {Norman}, M.~L. 2002, Science, 295, 93
+
+\bibitem[{{Abel} \& {Wandelt}(2002)}]{Abel02_RT}
+{Abel}, T., \& {Wandelt}, B.~D. 2002, \mnras, 330, L53
+
+\bibitem[{{Abel} {et~al.}(2007){Abel}, {Wise}, \& {Bryan}}]{Abel07}
+{Abel}, T., {Wise}, J.~H., \& {Bryan}, G.~L. 2007, \apjl, 659, L87
+
+\bibitem[{{Battaglia} {et~al.}(2010){Battaglia}, {Tolstoy}, {Helmi}, {Irwin},
+  {Parisi}, {Hill}, \& {Jablonka}}]{Battaglia10}
+{Battaglia}, G., {Tolstoy}, E., {Helmi}, A., {Irwin}, M., {Parisi}, P., {Hill},
+  V., \& {Jablonka}, P. 2010, ArXiv e-prints
+
+\bibitem[{{Beers} \& {Christlieb}(2005)}]{Beers05}
+{Beers}, T.~C., \& {Christlieb}, N. 2005, \araa, 43, 531
+
+\bibitem[{{Bertschinger}(2001)}]{Bertschinger01}
+{Bertschinger}, E. 2001, \apjs, 137, 1
+
+\bibitem[{{Bromm} {et~al.}(2002){Bromm}, {Coppi}, \& {Larson}}]{Bromm02_P3}
+{Bromm}, V., {Coppi}, P.~S., \& {Larson}, R.~B. 2002, \apj, 564, 23
+
+\bibitem[{{Bromm} {et~al.}(2001){Bromm}, {Ferrara}, {Coppi}, \&
+  {Larson}}]{Bromm01}
+{Bromm}, V., {Ferrara}, A., {Coppi}, P.~S., \& {Larson}, R.~B. 2001, \mnras,
+  328, 969
+
+\bibitem[{{Cen} \& {Ostriker}(1992)}]{Cen92}
+{Cen}, R., \& {Ostriker}, J.~P. 1992, \apjl, 399, L113
+
+\bibitem[{{Cen} \& {Riquelme}(2008)}]{Cen08}
+{Cen}, R., \& {Riquelme}, M.~A. 2008, \apj, 674, 644
+
+\bibitem[{{Chabrier}(2003)}]{Chabrier03}
+{Chabrier}, G. 2003, \pasp, 115, 763
+
+\bibitem[{{Clark} {et~al.}(2009){Clark}, {Glover}, {Bonnell}, \&
+  {Klessen}}]{Clark09}
+{Clark}, P.~C., {Glover}, S.~C.~O., {Bonnell}, I.~A., \& {Klessen}, R.~S. 2009,
+  ArXiv e-prints
+
+\bibitem[{{Clark} {et~al.}(2008){Clark}, {Glover}, \& {Klessen}}]{clark08}
+{Clark}, P.~C., {Glover}, S.~C.~O., \& {Klessen}, R.~S. 2008, \apj, 672, 757
+
+\bibitem[{{Ferrara}(1998)}]{Ferrara98}
+{Ferrara}, A. 1998, \apjl, 499, L17+
+
+\bibitem[{{Frebel} \& {Bromm}(2010)}]{Frebel10}
+{Frebel}, A., \& {Bromm}, V. 2010, ArXiv e-prints
+
+\bibitem[{{Frebel} {et~al.}(2010){Frebel}, {Kirby}, \& {Simon}}]{Frebel10_Obs}
+{Frebel}, A., {Kirby}, E.~N., \& {Simon}, J.~D. 2010, \nat, 464, 72
+
+\bibitem[{{Gnedin}(2000)}]{gnedin00}
+{Gnedin}, N.~Y. 2000, \apj, 542, 535
+
+\bibitem[{{Gnedin} \& {Hui}(1998)}]{gnedin98}
+{Gnedin}, N.~Y., \& {Hui}, L. 1998, \mnras, 296, 44
+
+\bibitem[{{Gnedin} \& {Kravtsov}(2006)}]{Gnedin06}
+{Gnedin}, N.~Y., \& {Kravtsov}, A.~V. 2006, \apj, 645, 1054
+
+\bibitem[{{Greif} {et~al.}(2010){Greif}, {Glover}, {Bromm}, \&
+  {Klessen}}]{Greif10}
+{Greif}, T.~H., {Glover}, S.~C.~O., {Bromm}, V., \& {Klessen}, R.~S. 2010,
+  \apj, 716, 510
+
+\bibitem[{{Heger} {et~al.}(2003){Heger}, {Fryer}, {Woosley}, {Langer}, \&
+  {Hartmann}}]{Heger03}
+{Heger}, A., {Fryer}, C.~L., {Woosley}, S.~E., {Langer}, N., \& {Hartmann},
+  D.~H. 2003, \apj, 591, 288
+
+\bibitem[{{Heger} \& {Woosley}(2002{\natexlab{a}})}]{2002ApJ...567..532H}
+{Heger}, A., \& {Woosley}, S.~E. 2002{\natexlab{a}}, \apj, 567, 532
+
+\bibitem[{{Heger} \& {Woosley}(2002{\natexlab{b}})}]{Heger02}
+---. 2002{\natexlab{b}}, \apj, 567, 532
+
+\bibitem[{{Kitayama} {et~al.}(2004){Kitayama}, {Yoshida}, {Susa}, \&
+  {Umemura}}]{Kitayama04}
+{Kitayama}, T., {Yoshida}, N., {Susa}, H., \& {Umemura}, M. 2004, \apj, 613,
+  631
+
+\bibitem[{{Komatsu} {et~al.}(2010){Komatsu}, {Smith}, {Dunkley}, {Bennett},
+  {Gold}, {Hinshaw}, {Jarosik}, {Larson}, {Nolta}, {Page}, {Spergel},
+  {Halpern}, {Hill}, {Kogut}, {Limon}, {Meyer}, {Odegard}, {Tucker}, {Weiland},
+  {Wollack}, \& {Wright}}]{WMAP7}
+{Komatsu}, E., {Smith}, K.~M., {Dunkley}, J., {Bennett}, C.~L., {Gold}, B.,
+  {Hinshaw}, G., {Jarosik}, N., {Larson}, D., {Nolta}, M.~R., {Page}, L.,
+  {Spergel}, D.~N., {Halpern}, M., {Hill}, R.~S., {Kogut}, A., {Limon}, M.,
+  {Meyer}, S.~S., {Odegard}, N., {Tucker}, G.~S., {Weiland}, J.~L., {Wollack},
+  E., \& {Wright}, E.~L. 2010, ArXiv e-prints
+
+\bibitem[{{Larson}(1998)}]{Larson98}
+{Larson}, R.~B. 1998, \mnras, 301, 569
+
+\bibitem[{{Lehnert} {et~al.}(2010){Lehnert}, {Nesvadba}, {Cuby}, {Swinbank},
+  {Morris}, {Cl{\'e}ment}, {Evans}, {Bremer}, \& {Basa}}]{Lehnert10_z8.6}
+{Lehnert}, M.~D., {Nesvadba}, N.~P.~H., {Cuby}, J., {Swinbank}, A.~M.,
+  {Morris}, S., {Cl{\'e}ment}, B., {Evans}, C.~J., {Bremer}, M.~N., \& {Basa},
+  S. 2010, \nat, 467, 940
+
+\bibitem[{Matsumoto \& Nishimura(1998)}]{MTwister}
+Matsumoto, M., \& Nishimura, T. 1998, ACM Trans. Model. Comput. Simul., 8, 3
+
+\bibitem[{{Omukai} {et~al.}(2005){Omukai}, {Tsuribe}, {Schneider}, \&
+  {Ferrara}}]{Omukai05}
+{Omukai}, K., {Tsuribe}, T., {Schneider}, R., \& {Ferrara}, A. 2005, \apj, 626,
+  627
+
+\bibitem[{{O'Shea} {et~al.}(2004){O'Shea}, {Bryan}, {Bordner}, {Norman},
+  {Abel}, {Harkness}, \& {Kritsuk}}]{OShea2004}
+{O'Shea}, B.~W., {Bryan}, G., {Bordner}, J., {Norman}, M.~L., {Abel}, T.,
+  {Harkness}, R., \& {Kritsuk}, A. 2004, ArXiv Astrophysics e-prints
+
+\bibitem[{{O'Shea} \& {Norman}(2007)}]{OShea07a}
+{O'Shea}, B.~W., \& {Norman}, M.~L. 2007, \apj, 654, 66
+
+\bibitem[{{Schaerer}(2002)}]{Schaerer02}
+{Schaerer}, D. 2002, \aap, 382, 28
+
+\bibitem[{{Schaerer}(2003)}]{Schaerer03}
+---. 2003, \aap, 397, 527
+
+\bibitem[{{Schneider} {et~al.}(2006){Schneider}, {Omukai}, {Inoue}, \&
+  {Ferrara}}]{Schneider06_Frag}
+{Schneider}, R., {Omukai}, K., {Inoue}, A.~K., \& {Ferrara}, A. 2006, \mnras,
+  369, 1437
+
+\bibitem[{{Smith} {et~al.}(2008){Smith}, {Sigurdsson}, \&
+  {Abel}}]{2008MNRAS.385.1443S}
+{Smith}, B., {Sigurdsson}, S., \& {Abel}, T. 2008, \mnras, 385, 1443
+
+\bibitem[{{Smith} {et~al.}(2009){Smith}, {Turk}, {Sigurdsson}, {O'Shea}, \&
+  {Norman}}]{2009ApJ...691..441S}
+{Smith}, B.~D., {Turk}, M.~J., {Sigurdsson}, S., {O'Shea}, B.~W., \& {Norman},
+  M.~L. 2009, \apj, 691, 441
+
+\bibitem[{{Stacy} {et~al.}(2010){Stacy}, {Greif}, \& {Bromm}}]{Stacy10_Binary}
+{Stacy}, A., {Greif}, T.~H., \& {Bromm}, V. 2010, \mnras, 403, 45
+
+\bibitem[{{Tafelmeyer} {et~al.}(2010){Tafelmeyer}, {Jablonka}, {Hill},
+  {Shetrone}, {Tolstoy}, {Irwin}, {Battaglia}, {Helmi}, {Starkenburg}, {Venn},
+  {Abel}, {Francois}, {Kaufer}, {North}, {Primas}, \&
+  {Szeifert}}]{Tafelmeyer10}
+{Tafelmeyer}, M., {Jablonka}, P., {Hill}, V., {Shetrone}, M., {Tolstoy}, E.,
+  {Irwin}, M.~J., {Battaglia}, G., {Helmi}, A., {Starkenburg}, E., {Venn},
+  K.~A., {Abel}, T., {Francois}, P., {Kaufer}, A., {North}, P., {Primas}, F.,
+  \& {Szeifert}, T. 2010, ArXiv e-prints
+
+\bibitem[{Toro {et~al.}(1994)Toro, Spruce, \& Speares}]{Toro94_HLLC}
+Toro, E.~F., Spruce, M., \& Speares, W. 1994, Shock Waves, 4, 25,
+  10.1007/BF01414629
+
+\bibitem[{{Truelove} {et~al.}(1997){Truelove}, {Klein}, {McKee}, {Holliman},
+  {Howell}, \& {Greenough}}]{Truelove97}
+{Truelove}, J.~K., {Klein}, R.~I., {McKee}, C.~F., {Holliman}, II, J.~H.,
+  {Howell}, L.~H., \& {Greenough}, J.~A. 1997, \apjl, 489, L179+
+
+\bibitem[{{Tumlinson}(2007)}]{Tumlinson07_IMF}
+{Tumlinson}, J. 2007, \apjl, 664, L63
+
+\bibitem[{{Turk} {et~al.}(2009){Turk}, {Abel}, \&
+  {O'Shea}}]{2009Sci...325..601T}
+{Turk}, M.~J., {Abel}, T., \& {O'Shea}, B. 2009, Science, 325, 601
+
+\bibitem[{{Turk} {et~al.}(2010){Turk}, {Smith}, {Oishi}, {Skory}, {Skillman},
+  {Abel}, \& {Norman}}]{yt_full_paper}
+{Turk}, M.~J., {Smith}, B.~D.~S., {Oishi}, J.~S., {Skory}, S., {Skillman},
+  S.~W., {Abel}, T., \& {Norman}, M.~L. 2010, \apjs, submitted (October, 2010)
+
+\bibitem[{{Warren} {et~al.}(2006){Warren}, {Abazajian}, {Holz}, \&
+  {Teodoro}}]{Warren06}
+{Warren}, M.~S., {Abazajian}, K., {Holz}, D.~E., \& {Teodoro}, L. 2006, \apj,
+  646, 881
+
+\bibitem[{{Whalen} {et~al.}(2004){Whalen}, {Abel}, \& {Norman}}]{Whalen04}
+{Whalen}, D., {Abel}, T., \& {Norman}, M.~L. 2004, \apj, 610, 14
+
+\bibitem[{{Wise} \& {Abel}(2008)}]{Wise08_Gal}
+{Wise}, J.~H., \& {Abel}, T. 2008, \apj, 685, 40
+
+\bibitem[{{Wise} \& {Abel}(2010)}]{Wise10}
+---. 2010, \apjs, In preparation
+
+\bibitem[{{Wise} \& {Cen}(2009)}]{Wise09}
+{Wise}, J.~H., \& {Cen}, R. 2009, \apj, 693, 984
+
+\bibitem[{{Wolfe} {et~al.}(2005){Wolfe}, {Gawiser}, \&
+  {Prochaska}}]{Wolfe05_Review}
+{Wolfe}, A.~M., {Gawiser}, E., \& {Prochaska}, J.~X. 2005, \araa, 43, 861
+
+\end{thebibliography}
 

### 2011-01-11 ms.tex
Fixing typo in title
Starting new fuller ApJ paper with all of the halos.

--- 2010-11-08 ms.tex
@@
 
-\shorttitle{THE BIRTH OF A GALAXY}
+\shorttitle{High Redshift Dwarf Galaxies}
 \shortauthors{WISE ET AL.}
 
-\title{The Birth of a Galaxy: Primoridal Metal Enrichment and
-  Population II Stellar Populations}
+\title{Metal Enrichment and Stellar Populations of High Redshift Dwarf
+  Galaxies}
 
@@
 interactions between the SN blastwave, cosmological accretion and halo
-mergers, and nearby stellar feedback.  In minihalos ($M \sim
-10^6~\Ms$), radiation from a massive Pop III star can drive a 30
-\kms~shock, which is 10 times greater than the escape velocity of the
-halo, and leaves behind a warm ($3 \times 10^4$ K) and diffuse (0.5
-\cubecm) medium \citep{Kitayama04, Whalen04, Abel07}.  This aids in the
-expansion of the blastwave because it delays the transition to the
-Sedov-Taylor and snowplow phases.  In PISNe, approximately half of the
-metals stay in the IGM with a metal bubble size of a few kpc
-\citep{Wise08_Gal, Greif10}.  The blastwave may induce SF in nearby
-halos through the compression of the gas \citep{Ferrara98}, and
-timescales for metal mixing into the dense gas are many dynamical
-times \citep{Cen08} for shock velocities $\lsim100~\kms$.
+mergers, and nearby stellar feedback.  \textbf{Discuss prior work on
+  transition with the papers given by the previous referee.}
+
+In minihalos ($M \sim 10^6~\Ms$), radiation from a massive Pop III
+star can drive a 30 \kms~shock, which is 10 times greater than the
+escape velocity of the halo, and leaves behind a warm ($3 \times 10^4$
+K) and diffuse (0.5 \cubecm) medium \citep{Kitayama04, Whalen04,
+  Abel07}.  This aids in the expansion of the blastwave because it
+delays the transition to the Sedov-Taylor and snowplow phases.  In
+PISNe, approximately half of the metals stay in the IGM with a metal
+bubble size of a few kpc \citep{Wise08_Gal, Greif10}.  The blastwave
+may induce SF in nearby halos through the compression of the gas
+\citep{Ferrara98}, and timescales for metal mixing into the dense gas
+are many dynamical times \citep{Cen08} for shock velocities
+$\lsim100~\kms$.
 
@@
 We use the adaptive mesh refinement (AMR) code
-enzo~v2.0\footnote[\ddag]{\texttt{enzo.googlecode.com, unstable
-    changeset b86d8ba026d6}} \citep{OShea2004}, which has been
-modified to use a HLLC Riemann solver \citep{Toro94_HLLC} for
-additional stability in strong shocks.  To resolve minihalos with at
+enzo~v2.0\footnote{\texttt{enzo.googlecode.com, changeset
+    b86d8ba026d6}} \citep{OShea2004}, which has been modified to use a
+HLLC Riemann solver \citep{Toro94_HLLC} for additional stability in
+strong shocks and rarefaction waves.  To resolve minihalos with at
 least 100 dark matter (DM) particles and follow the formation of the
@@
 at $z = 130$ and use the cosmological parameters from the 7-year WMAP
-data \citep{WMAP7}: $\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$,
-$\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$
-with the variables having their usual definitions.  We stop the
-simulation at $z=7$.
-
-We use a non-equilibrium chemistry solver with 9 species of hydrogen,
-helium, and molecular hydrogen \citep{Abel97}.  We spatially
-distinguish metal enrichment from Pop II and Pop III stars.  We will
-follow-up this study with one that considers radiative cooling from
-metal-enriched gas, using the method of \citet{2008MNRAS.385.1443S}.
-
-% We peform two simulations with the same initial conditions.  They
-% differ only in that one considers primordial cooling, and the other
-% considers additional cooling in metal-enriched gas.  For primordial
-% cooling, we use a non-equilbrium chemistry solver with 9 species of
-% hydrogen, helium, and molecular hydrogen.  For metal cooling, we use a
-% cooling curve that is calculated from CLOUDY \citep{CLOUDY} and using
-% the method of \citep{2008MNRAS.385.1443S}.  It is tabulated based on
-% density, temperature, electron fraction, and metallicity.
+$\Lambda$CDM+SZ+LENS best fit \citep{WMAP7}: $\Omega_M = 0.266$,
+$\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 =
+0.81$, and $n = 0.963$ with the variables having their usual
+definitions.  We stop the simulation at $z=7$.
 
 \subsection{Star formation}
-
-\begin{figure}
-\epsscale{1.15}
-\plotone{f1}
-\epsscale{1}
-\caption{\label{fig:massfn} \textit{Top}: Halo mass function of the
-  simulation compared with the analytical fit (solid) of
-  \citet{Warren06}.  \textit{Bottom}: Total Pop II luminosities of
-  halos with constant mass-to-light ratios overplotted.}
-\end{figure}
 
@@
 \label{eqn:imf}
-f(M)dM = M^{-1.3} \exp\left[-\left(\frac{M_{\rm char}}{M}\right)^{1.6}\right]
+f(M)dM = M^{-1.3} \exp\left[-\left(\frac{M_{\rm
+        char}}{M}\right)^{1.6}\right] dM
 \end{equation}
@@
 Salpeter IMF but is exponentially cutoff below that mass
-\citep{Chabrier03, Clark09}.  For reproducibility, we record the number
-of times the random number generator (Mersenne twister;
-\citet{MTwister}) has been called for use when restarting the
-simulations.
+\citep{Chabrier03, Clark09}.
 
-%%% FOR THE COMPARISON BETWEEN RUNS WITH AND WITHOUT METAL COOLING %%%
-%
-% Although the Pop III star formation history (SFH) is identical for a
-% given $N$ stars, the Pop III SFH for a given halo can be different
-% between the two simulations.  This happens because the order in which
-% halos form Pop III stars can be altered from enhanced star formation
-% and feedback from nearby Pop II star clusters, as we will demonstrate
-% in this Letter.
+For reproducibility, we record the number of times the random number
+generator (Mersenne twister; \citet{MTwister}) has been called for use
+when restarting the simulations.  Although the Pop III star formation
+history (SFH) in the entire simulation is identical for a given $N$
+stars, the Pop III SFH for a given halo can be different between the
+two simulations.  This happens because the order in which halos form
+Pop III stars can be altered from enhanced star formation and feedback
+from nearby Pop II star clusters.
 
@@
 \subsection{Stellar feedback}
-
-\begin{figure*}
-\epsscale{1.15}
-\plotone{f2}
-\epsscale{1}
-\caption{\label{fig:projections} Density-weighted projections of gas
-  density (top), temperature (middle), and metallicity (bottom) at
-  $z=7$.  The left column shows the entire simulation volume, where
-  the center and right columns focus on the intense and quiet halos,
-  which are marked by left and right arrows in the upper-left panel.
-  The metallicity projections are a composite picture of metals
-  originating from Pop III (red) and Pop II (blue) stars with magenta
-  indicating a mixture of the two.}
-\end{figure*}
 
@@
 
-\begin{figure*}
-\epsscale{1.15}
-\plotone{f3}
-\epsscale{1}
-\caption{\label{fig:evo} (a) Evolution of the total halo mass (top),
-  stellar mass (middle), and gas fraction (bottom) of the quiet
-  (dashed) and intense (solid) halos.  (b) Mass-weighted stellar
-  metallicities and gas metallicities enriched by Pop II and Pop III
-  SNe of the intense (top) and quiet (bottom) halos.}
-\end{figure*}
+\subsection{Different physics configurations}
+
+We perform five different simulations with the same initial
+conditions.  The fiducial model considers (1) primordial cooling that
+is solved with a non-equilbrium chemistry solver with 9 species of
+hydrogen, helium, and molecular hydrogen, (2) a Pop III IMF
+characteristic mass $M_{\rm char}$ = 100 \Ms, and (3) Pop II and Pop
+III star formation.  We vary this model with the following:
+
+\begin{enumerate}
+\item Radiative cooling from metal species.  We calculate a cooling
+  curve with CLOUDY \citep{CLOUDY} and use the method of
+  \citep{2008MNRAS.385.1443S}.  Solar abundances were used in the
+  cooling curve.  It is tabulated based on density, temperature,
+  electron fraction, and metallicity.
+\item Pop III IMF characteristic mass $M_{\rm char}$ = 40 \Ms.
+\item Pop II star formation only.
+\item Pop II star formation only and no molecular hydrogen cooling.
+\end{enumerate}
 
@@
 
-Here we present the gaseous and stellar evolution of two selected
-halos in the simulation: one that has an early mass buildup but no
-major mergers after $z=12$, and one that experiences a series of major
-mergers between $z=10$ and $z=7$.  We name the halos ``quiet'' and
-``intense'', respectively.  The entire simulation contains 38 galaxies
-with 3640 Pop II stellar clusters and captures the formation of 333
-Pop III stars.  The halo mass function and galaxy luminosities are
-plotted in Figure \ref{fig:massfn}.
+\subsection{Halo mass evolution}
 
-% We start with the mass accretion history and enrichment of the
-% halos.  We then compare the nature of the stellar populations in
-% these halos.
+\subsection{Metal enrichment}
 
-We illustrate the state of the simulation at $z=7$ in Figure
-\ref{fig:projections} with density weighted projections of gas
-density, temperature, and metallicity, showing the entire box and
-focusing on the two halos of interest.  Radiative and mechanical
-feedback create a multi-phase medium inside these halos, which are
-embedded in a warm and ionized IGM.
+\subsection{Star formation}
 
-\begin{figure*}
-\epsscale{1.1}
-\plotone{f4}
-\epsscale{1}
-\caption{\label{fig:pops} The scatter plots show the SF history of the
-  quiet (left) and intense (right) halos as a function of metallicity
-  at $z=7$.  Each circle represents a star cluster, whose area is
-  proportional to its mass.  The open circles in the upper right
-  represent $10^3$, $10^4$, and $10^5$ \Ms~star clusters.  The dashed
-  lines in the right panel guide the eye to two stellar populations
-  that were formed in two satellite halos, merging at $z=7.5$.  The
-  upper histogram shows the SFR.  The right histogram depicts the
-  stellar metallicity distribution.}
-\end{figure*}
+\subsection{Negative feedback from gas loss}
 
-\subsection{Mass evolution}
-\label{sec:halo}
+\section{Comparison to Previous Work}
 
-%\li Describe the evolution of the baryon fraction and metallicity from
-%PISN and Type II SNe metals in the two halos.
+\subsection{Semi-analytical}
 
-Figure \ref{fig:evo}a shows the total, metal-enriched stellar, and gas
-mass history of the most massive progenitors of both halos.  The quiet
-halo undergoes a series of major mergers at $z > 12$, growing by a
-factor of 30 to $2.5 \times 10^7 \Ms$ within 150 Myr.  Afterwards it
-only grows by a factor of 3 by $z=7$ mainly through smooth accretion
-from the filaments and IGM.  It is the most massive halo in the
-simulation between redshifts 13 and 10.  At the same time, the intense
-halo has a mass $M = 3 \times 10^6 \Ms$, but it is contained in a
-biased region on a comoving scale of 50 kpc with $\sim25$ halos with
-$M \sim 10^6 \Ms$.  After $z=10$, these halos hierarchically merge to
-form a $10^9 \Ms$ halo at $z=7$ with two major mergers at redshifts 10
-and 7.9, seen in the rapid increases in total mass in Figure
-\ref{fig:evo}a.  The merger history of the two halos are not atypical
-as dark matter halos can experience both quiescent and vigorous mass
-accretion rates.
+\subsection{Numerical}
 
-Both halos start forming Pop II stars when $M = 10^7 \Ms$.  This is
-consistent with the filtering mass $M_f$ of high-redshift halos when
-it accretes mainly from a pre-heated IGM \citep{gnedin98, gnedin00,
-  Wise08_Gal}.  Afterwards these halos can cool efficiently through
-\hh~cooling, sustaining constant and sometimes bursting SF.  The
-latter characteristics are equated with the definition of a galaxy.
-The quiet halo forms $10^5 \Ms$ of stars by $z=9$.  This initial
-starburst photo-evaporates the majority of its molecular clouds, in
-addition to heating and ionizing the surrounding IGM out to a radius
-of 10--15 kpc at $z=9$.  These respectively reduce the in-situ and
-external cold gas supply that could feed future SF.
+\section{Discussion}
 
-The gas fractions of both halos decrease from 0.15 to 0.08 by outflows
-driven by ionization fronts and blastwaves in their initial
-starbursts.  The quiet halo does not have a major merger with any halo
-with $M > M_f$, leading to a small final gas fraction.  These low-mass
-halos are photo-evaporated, hosting diffuse warm gas reservoirs
-instead of cold dense cores.  After $z=10$, the halo mainly accretes
-warm diffuse gas from the filaments and IGM.  In contrast, the intense
-halo grows from major mergers of halos with $M > M_f$.  The progenitor
-halos involved in the major mergers are able to host molecular clouds
-and have higher gas fractions.  Between $z=10$ and $z=8$, the gas
-fraction increases from 0.07 to 0.12 until it jumps to 0.14 when a
-gas-rich major merger occurs.  The stellar mass accordingly increases
-with the ample supply of gas during this period.
+\li DLAs
 
-\subsection{Metallicity evolution}
+\li Bimodality in [Z/H] distribution in globular clusters and dSphs
 
-The evolution of the stellar and gas metallicity of both halos are
-illustrated in Figure \ref{fig:evo}b.  PISNe from Pop III stars enrich
-the nearby IGM out to a radius of 10 kpc and provides a metallicity
-floor of $[Z_3/H] \sim -3$.  Ejecta from Pop II SNe initially enrich
-the ISM of both halos to an average $[\bar{Z}_2/H]$ between --3.5 and
---3.
+\li Importance of critical metallicity in satellite halos, not in host
+halos
 
-In the quiet halo, an equilibrium of $[\bar{Z}_2/H] \sim -2.5$ is
-established between metal-rich outflows and metal-poor inflows.
-Galactic outflows are directed in the polar directions of the gas
-disk, keeping the adjacent filaments metal-poor.  These features and a
-well-mixed ISM \citep[cf.][]{Wise08_Gal, Greif10} are apparent in the
-metallicity projections in Figure \ref{fig:projections}.  The average
-stellar metallicity is within 0.5 dex of $[\bar{Z}_2/H]$.
+\li [$\alpha$/Fe] estimate
 
-In the intense halo, the first few Pop II star clusters have $[Z/H]$
-between --1 and --2 and dominate the average stellar metallicity at $z
-> 8$.  Afterwards the metallicity increases by a factor of 30 to
-$[\bar{Z}_2/H] = -1.5$ through self-enrichment from a starburst.
-Because this halo is located in a large-scale overdensity, most of the
-ejecta falls back into the halo after reaching distances up to 20
-comoving kpc, keeping the halo gas metallicity high because the
-inflows are relatively metal-rich themselves.  After the $z \sim 8$
-starburst, the average stellar metallicity follows the average gas
-metallicity within 0.1 dex.
+\li Importance of Pop III SF
 
-\subsection{Star formation history}
-\label{sec:pop}
-
-The most massive progenitor of the quiet halo interestingly never
-hosts a Pop III star.  Instead a nearby halo forms a Pop III star,
-which (randomly) produces a PISNe at $z=16$.  The blastwave overruns
-the most massive progenitor, and the dense core survives this event
-and is enriched by this PISN, triggering the transition to Pop II SF.
-Other progenitors host three Pop III stars, forming at $z = 15.4,
-14.2, 13.8$, with the latter producing a PISN.  Metal enrichment from
-these two PISNe and Pop II SF quench Pop III SF in this halo.  The
-progenitors of the intense halo host a total of 56 Pop III stars with
-21 producing PISNe.  The first forms in a $6 \times 10^5 \Ms$ halo at
-$z=19$.  Pop III stars form on a regular interval in the halo's
-progenitors until $z=9$ when most of these halos enter the metal-rich
-bubble surrounding the intense halo.
-
-%% \li Present results on the star formation history and the physical
-%% reasons for the features seen in the SFH and metallicities.
-%%
-%% \li Present the stellar metallicity distribution at the final time
-
-Figure \ref{fig:pops} shows the SF history (SFH), metallicity
-distribution, and SF rates of both halos.  A nearby PISNe provides a
-metallicity floor of [Z/H] = --2.8 in the quiet halo at which
-metallicity the first Pop II stars form.  The stellar metallicity
-evolution exhibits what is expected from an isolated system with the
-stellar feedback steadily enriching the ISM, resulting in a
-correlation between stellar age and metallicity.  After $z=10$ the
-metallicities plateau at [Z/H] = --2.1 for reasons previously
-discussed.  The SFR peaks at $z=10$ and decreases as the cold gas
-reservoir is depleted.  Around $z=7.5$, a 25:1 minor merger occurs,
-and the gas inside the satellite halo is compressed, triggering
-metal-poor, [Z/H] = --3.2, SF during its nearest approach.  This halo
-remains metal-poor because most of metal enrichment in the quiet halo
-occurs in bi-polar flows perpendicular to the galaxy disk and
-filament.  Stars with [Z/H] $<$ --3 compose 1.6 percent of the total
-stellar mass.
-
-In contrast with the quiet halo, the intense halo undergoes a few
-mergers of halos with an established stellar population.  This creates
-a superposition of age-metallicity tracks in the SFH, seen in the
-complexity of Figure \ref{fig:pops}.  The first two Pop II stellar
-clusters have an unexpectedly high metallicity [Z/H] $\sim$ --1, which
-occurs when a PISN blastwave triggers SF in two neighboring halos.
-Most of the early SF have [Z/H] = --2.5.  At $z=9$, the halo's virial
-temperature reaches \tento{4} K.  This combined with a 10:1 merger
-creates a starburst that quickly enriches the halo to [Z/H] = --1.5 by
-$z=8$.  The halo continues to enrich itself afterwards.  The spikes in
-the scatter plot correspond to SN triggered SF in nearby molecular
-clouds that are enriched up to a factor of 10 with respect to the ISM.
-However their mass fraction are small compared to the total stellar
-mass.  The starburst at $z=9$ creates a bimodal metallicity
-distribution with peaks at [Z/H] = --2.4 and --1.2 with the metal-rich
-component mainly being created after the starburst.  Two systems with
-sizable stellar components merge into the halo at $z \sim 8$, and
-their stellar populations are still discernible in the metallicity-age
-plot.  Stars with [Z/H] $<$ --3 compose 1.8 percent of the total
-stellar mass.
-
-\section{Discussion and Conclusions}
-
-In this Letter, we focus on the birth of two galaxies prior to
-reionization with a cosmological AMR radiation hydrodynamics
-simulation.  Supernovae from Pop III stars provide the necessary heavy
-elements for the transition to a Population II stellar population,
-which we have directly simulated.  These two galaxies have a 10--15\%
-probability in surviving as present-day ``fossil'' galaxies
-\citep{Gnedin06}, otherwise they will be incorporated into galactic
-stellar halos.  A $z=8.55$ galaxy was recently spectroscopically
-confirmed that is contained in an ionized bubble with radius 0.1--0.5
-Mpc with an uncharacterized population of galaxies contributing to the
-local ionizing radiation field \citep{Lehnert10_z8.6}.  The galaxies
-simulated here might represent this population and should be detected
-with the upcoming \textit{James Webb Space Telescope}.
-
-We find that one PISN is sufficient to enrich the star-forming halo
-and surrounding $\sim 5$ kpc to a metallicity of 10$^{-3} Z_\odot$,
-given $M_{\rm char} = 100~\Ms$.  DLA systems have a metallicity floor
-on the same order \citep{Wolfe05_Review}, and metal enrichment from Pop
-III SNe provides a possible explanation.
-
-If the first stars have a lower characteristic mass that favor
-hypernovae \citep{Tumlinson07_IMF}, then this metallicity floor should
-be lowered by a factor of $\sim 10$ because (1) the metal ejecta is
-lowered by a factor of $\sim 50$ and (2) the mixing mass is
-approximately decreased by a factor of $(E_{\rm hyp}/E_{\rm
-  PISN})^{3/5}$ in the Sedov-Taylor solution, where $(E_{\rm
-  hyp}/E_{\rm PISN}) \sim 0.1$ is the ratio of explosion energies of a
-hypernova and PISN.  In the case where this metallicity floor is less
-than the critical metallicity, then the next instance of SF will
-further enrich the ISM, solidifying the transition to Pop II SF.  We
-conclude that it only takes one, at most two, SNe from Pop III stars
-in the halo progenitors to complete the transition to Population II
-\citep{Frebel10}.  The question of whether the critical metallicity is
-\tento{-6} or \tento{-3.5} $Z_\odot$ is most applicable to nearby
-halos where the heavy elements mix slowly into dense cores as the
-blastwave overtakes it.  Less than two percent of stars have [Z/H] $<
--3$ in both systems, consistent with observations of metal-poor stars
-in the halo and dSphs \citep{Beers05, Battaglia10}.
-
-% We also find that the merger history plays an important role in
-% supplying gas into halos after its first epoch of SF.  Mergers of
-% halos below the filtering mass are inefficient in providing gas
-% whereas the opposite is true for merging halos above the filtering
-% mass.  Halos do not necessarily need $\tvir \ge 10^4$ K to form
-% significant stellar populations; however SFRs dramatically increase,
-% and thus metal enrichment, when this threshold is reached.  Halos
-% with mostly gas-poor mergers or a quiet merger history result in a
-% monotonic increase in metallicity with time.  SFHs become more
-% complex with multiple metallicity-age tracks if the halo experiences
-% mergers with other halos that have an established stellar
-% population.  Furthermore SF that is triggered by blastwaves
-% interacting with molecular clouds can have metallicities up to a
-% factor of 10 higher than the main starburst.  Starbursts at $\tvir =
-% 10^4$ K can enrich the host halo enough to create a bimodal
-% metallicity distribution, where the metal-poor component is created
-% before the burst.  Note that mergers of stellar populations can also
-% create a similar bimodal distribution, which are observed in dSphs
-% \cite{Battaglia10}.
-
-We have shown that it is possible to simulate the formation of a
-high-redshift dwarf galaxy and its entire SFH with radiative and
-mechanical feedback.  These results provide invaluable insight on the
-first galaxies and the role of metal-free stars in the early universe.
-There exists a wealth of information in this simulation, and we plan
-to follow up this preliminary report with more detailed analysis of
-the metal enrichment of the IGM, global SF rates, and observational
-connections with high-redshift galaxies and Local Group dwarf galaxies
-in the near future.
+\section{Summary}
 

### 2011-01-14 ms.tex
Changing to MNRAS formatting.

@@
-%\documentclass[apjl]{emulateapj}
-\documentclass[12pt,preprint]{aastex}
+\documentclass[useAMS,usenatbib]{mn2e}
 
@@
 \usepackage[section] {placeins}
-\bibliographystyle{apj}
-\citestyle{apj}
+\bibliographystyle{mn2e}
+\citestyle{mn2e}
 
@@
 \input macros.tex
+\voffset=-1.4cm
 
@@
 
-\shorttitle{High Redshift Dwarf Galaxies}
-\shortauthors{WISE ET AL.}
+\title[High Redshift Dwarf Galaxies]{Metal Enrichment and Stellar
+  Populations of High Redshift Dwarf Galaxies}
 
-\title{Metal Enrichment and Stellar Populations of High Redshift Dwarf
-  Galaxies}
+\author[Wise et al.]{John H. Wise$^1$\thanks{Hubble Fellow; e-mail:
+    jwise@astro.princeton.edu}, Matthew J. Turk$^2$, Michael
+  L. Norman$^2$, Tom Abel$^3$\\
+  $^{1}$ Department of Astrophysical Sciences, Princeton University,
+  Peyton Hall, Ivy Lane, Princeton, NJ 08544, USA\\
+  $^{2}$ Center for Astrophysics and Space Sciences,
+    University of California at San Diego, La Jolla, CA 92093, USA\\
+  $^{3}$ Kavli Institute for Particle Astrophysics and Cosmology,
+  Stanford University, Menlo Park, CA 94025, USA}
 
-\author{John H. Wise\altaffilmark{1,2}, 
-  Matthew J. Turk\altaffilmark{3},
-  Michael L. Norman\altaffilmark{3},
-  Tom Abel\altaffilmark{4}}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2010}
 
-\altaffiltext{1}{Department of Astrophysical Sciences, Princeton
-  University, Peyton Hall, Ivy Lane, Princeton, NJ 08544}
-\altaffiltext{2}{Hubble Fellow}
-\altaffiltext{3}{Center for Astrophysics and Space Sciences,
-  University of California at San Diego, La Jolla, CA 92093}
-\altaffiltext{4}{Kavli Institute for Particle Astrophysics and
-  Cosmology, Stanford University, Menlo Park, CA 94025}
-\email{jwise@astro.princeton.edu}
+\maketitle
+\label{firstpage}
 
@@
 
-\keywords{cosmology --- methods: numerical --- hydrodynamics ---
-  radiative transfer --- star formation}
+\begin{keywords}
+  cosmology --- methods: numerical --- hydrodynamics ---
+  radiative transfer --- star formation
+\end{keywords}
 
@@
 
-\acknowledgments
+\section*{Acknowledgements}
 
@@
 
-%\clearpage
-%\input biblio.tex
 \bibliography{ms}
+\bsp
+\label{lastpage}
 

### 2011-01-15 ms.tex
Adding almost all of the figures.

@@
 
+\begin{figure*}
+  \epsscale{2}
+  \plotone{bmosaic.eps}
+  \epsscale{1}
+  \caption{\label{fig:evo-mosaic} text.}
+\end{figure*}
+
 \subsection{Simulation setup}
@@
 We use the adaptive mesh refinement (AMR) code
-enzo~v2.0\footnote{\texttt{enzo.googlecode.com, changeset
+\textsc{enzo~v2.0}\footnote{\texttt{enzo.googlecode.com, changeset
     b86d8ba026d6}} \citep{OShea2004}, which has been modified to use a
@@
 computational elements and a maximal spatial resolution of 0.1 pc.  We
-initialize the simulation with \textsl{grafic} \citep{Bertschinger01}
+initialize the simulation with \textsc{grafic} \citep{Bertschinger01}
 at $z = 130$ and use the cosmological parameters from the 7-year WMAP
@@
 
+\begin{figure*}
+  \plottwo{z7-mosaic0.eps}{z7-mosaic1.eps}
+  \caption{\label{fig:z7-mosaic} Redshift 7.}
+\end{figure*}
+
+\begin{figure*}
+  \plottwo{z8-mosaic0.eps}{z8-mosaic1.eps}
+  \caption{\label{fig:z8-mosaic} Redshift 8.}
+\end{figure*}
+
+\begin{figure*}
+  \plottwo{z10-mosaic0.eps}{z10-mosaic1.eps}
+  \caption{\label{fig:z10-mosaic} Redshift 10.}
+\end{figure*}
+
 \subsection{Halo mass evolution}
+
+\begin{figure*}
+  \plottwo{history0.eps}{history5.eps}
+  \caption{\label{fig:massevo} Mass evolution.}
+\end{figure*}
 
@@
 
+\begin{figure}
+  \plotone{Zhistory.eps}
+  \caption{\label{fig:Zevo} Metal evolution.}
+\end{figure}
+
+\begin{figure}
+  \plotone{z2.eps}
+  \caption{\label{fig:z2} Halo metallicities.}
+\end{figure}
+
+\begin{figure}
+  \plotone{z3.eps}
+  \caption{\label{fig:z3} Halo metallicities.}
+\end{figure}
+
+\begin{figure}
+  \plotone{ztot.eps}
+  \caption{\label{fig:ztot} Halo metallicities.}
+\end{figure}
+
 \subsection{Star formation}
+
+\begin{figure}
+  \plotone{mlratios.eps}
+  \caption{\label{fig:ML} Mass to light ratios.}
+\end{figure}
+
+%\begin{figure}
+%  \plotone{sfh.eps}
+%  \caption{\label{fig:SFR} Star formation history.}
+%\end{figure}
 

### 2011-01-17 ms.tex
Almost finished with the introduction.  Added redshift top x-axis label to Zhistory.eps.

@@
   $^{1}$ Department of Astrophysical Sciences, Princeton University,
-  Peyton Hall, Ivy Lane, Princeton, NJ 08544, USA\\
+  Princeton, NJ 08544, USA\\
   $^{2}$ Center for Astrophysics and Space Sciences,
@@
 
-\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2010}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2011}
 
@@
 
-  Population III stars first form in dark matter halos with masses
+  Population III stars first form in dark matter haloes with masses
   around $10^6 \Ms$.  By definition, they are metal-free, and their
@@
   and associated metal enrichment.  We find that the gas fraction
-  recovers from 5 percent to nearly the cosmic fraction in halos with
-  merger histories rich in halos above $10^7 \Ms$.  A single
+  recovers from 5 percent to nearly the cosmic fraction in haloes with
+  merger histories rich in haloes above $10^7 \Ms$.  A single
   pair-instability supernova is sufficient to enrich the host halo to
@@
   We find that stellar metallicities do not necessarily trace stellar
-  ages, as mergers of halos with established stellar populations can
+  ages, as mergers of haloes with established stellar populations can
   create superpositions of $t-Z$ evolutionary tracks.  A bimodal
@@
 
-\section{Motivation}
+\section{Introduction}
 
-The first (Pop III) stars are metal-free and have a large
-characteristic mass and suppressed fragmentation in its protostellar
-collapse \citep{ABN02, Bromm02_P3, OShea07a}.  A fraction of these
-stars enrich the surrounding intergalactic medium (IGM) when they go
-supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
+The first generation of stars, so-called Population III, in the
+universe were metal-free, forming from a primordial mixture of mainly
+hydrogen and helium.  Heavy elements and dust grains were not present
+in these objects to provide an efficient cooling mechanism in the
+collapse of the host molecular cloud, whose collapses primarily rely
+on molecular hydrogen line cooling in the gas-phase.  Without any
+other cooling channels, the temperatures cannot cool below $\sim$ 200
+K, resulting in Jeans masses on the order of 100 \Ms.  Numerical
+calculations in the past decade have shown that Population III stars
+have characteristic masses between 30 and 300
+\Ms~\citep[e.g.][]{ABN02, Bromm02_P3, OShea07a}, which form in dark
+matter (DM) haloes with masses $\sim 10^6 \Ms$
+\citep[e.g.][]{MacLow86, Shapiro87, Tegmark97}.
+
+These stars have large luminosities on the order of 10$^6 \lsun$,
+surface temperatures of $\sim 10^5$ K, and lifetimes of $\sim3$ Myr
+\citep{Bond84, Schaerer02}.  Radiation during their main sequence
+creates an \hii region with $r \sim 1-3~\mathrm{kpc}$, ionizing the
+surrounding intergalactic medium as the virial radii of the host haloes
+are $r_{\rm vir} \sim 100 \mathrm{pc}$ \citep{Whalen04, Kitayama04,
+  Alvarez06, Abel07}.  The over-pressurized \hii region drives a
+$\sim$ 30 \kms~shock, which is 10 times greater than the escape
+velocity of a $10^6 \Ms$ halo.  In turn, most of the gas is expelled
+from the halo, leaving behind a warm ($3 \times 10^4$ K) and diffuse
+(0.5 \cubecm) medium.  In haloes that are encompassed by these \hii
+regions and not completely photo-evaporated \citep{refs}, the
+additional free electrons catalyze both \hh~and HD molecular line
+cooling \citep{OShea05, Johnson06, Yoshida07, McGreer08}, cooling the
+gas below $\sim$ 100 K and lowering the Jeans mass to $\sim$ 10--30
+\Ms.  These lower-mass, metal-free stars are called Population III.2,
+whereas their more massive counterparts that form in unheated regions
+are called Population III.1 stars \citep{Norman08}.
+
+A fraction of Population III stars enrich the surrounding IGM when
+they go supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
 supernovae (SNe) or in stars roughly between 140 \Ms~and 260 \Ms~in
 pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}. The host
-halo and the neighboring halos are then enriched with this ejecta.
-There exists a critical metallicity that is $\sim 10^{-6} Z_\odot$ if
-dust cooling is efficient \citep{Omukai05, Schneider06_Frag, clark08}
-and $\sim 10^{-3.5} Z_\odot$ otherwise \citep{Bromm01,
-  2009ApJ...691..441S}, where the gas can cool rapidly, lowering its
-Jeans mass.  An intermediate characteristic mass of $\sim10~\Ms$ can
-be occur if the gas cooling is suppressed to the cosmic microwave
-background (CMB) temperature \citep{Larson98, Tumlinson07_IMF,
-  2009ApJ...691..441S}.  The resulting Population II star cluster will
-thus have a lower characteristic stellar mass than its metal-free
-progenitors.  These first stellar clusters may be connected to stars
-in the Milky Way halo and nearby dwarf spheroidal (dSph) galaxies,
-both with a metallicity floor of [Z/H] = --4 \citep{Beers05,
-  Tafelmeyer10, Frebel10_Obs}.
+halo and the neighboring haloes are then enriched with this ejecta.
+The blastwave expands to a radius of a few kpc \citep{Bromm03_SN,
+  Wise08_Gal, Greif10} with approximately half of the ejecta falling
+back into the adjacent filaments and halos.  The blastwave may induce
+star formation in nearby haloes through the compression of the gas
+\citep{Ferrara98, more}, and the timescales for metal mixing into the
+dense gas are many dynamical times \citep{Cen08} for shock velocities
+$\lsim 100~\kms$.
 
-The transition from Pop III to Pop II star formation (SF) is solely
+When star-forming gas reaches some `critical metallicity' $Z_{\rm
+  cr}$, radiative cooling from metal fine-structure lines or
+\hh~formation on dust grains becomes efficient, allowing cooling to $T
+\lsim 100$ K \citep{Omukai??}.  The exact value of $Z_{\rm cr}$ has
+been constrained to be between $10^{-6} \zsun$ and $10^{-3.5} \zsun$.
+The lower limit applies if dust cooling is important in these
+scenarios \citep{Omukai05, Schneider06_Frag, clark08}, and the upper
+limit happens if metal line cooling in the gas-phase is the dominant
+process \citep{Bromm01, 2009ApJ...691..441S}.  This metal-enriched gas
+fragments and most likely forms stars with masses similar to
+present-day stellar initial mass functions (IMF), marking the local
+transition from Population III to II star formation.  Intermediate to
+these populations and possibly unique to high redshift, there exists a
+mode of massive star formation that has a characteristic mass of $\sim
+10 \Ms$ \citep{Larson98, Tumlinson07_IMF, 2009ApJ...691..441S}.  This
+happens when cooling in metal-enriched gas is limited to the cosmic
+microwave background (CMB) temperature $T_{\rm CMB} = 2.73 (1+z)$ K,
+which can be significantly higher than the cores of typical molecular
+clouds ($T \sim 10$ K).
+
+The transition from Pop III to Pop II star formation is solely
 dependent on the propagation of metals from the SNe remnants into
-future sites of SF.  Their flows are complex because of the
-interactions between the SN blastwave, cosmological accretion and halo
-mergers, and nearby stellar feedback.  \textbf{Discuss prior work on
-  transition with the papers given by the previous referee.}
+future sites of star formation.  Their flows are complex because of
+the interactions between the SN blastwave, cosmological accretion and
+halo mergers, and nearby stellar feedback.  \textbf{Discuss prior work
+  on transition with the papers given by the previous referee.}
 
-In minihalos ($M \sim 10^6~\Ms$), radiation from a massive Pop III
-star can drive a 30 \kms~shock, which is 10 times greater than the
-escape velocity of the halo, and leaves behind a warm ($3 \times 10^4$
-K) and diffuse (0.5 \cubecm) medium \citep{Kitayama04, Whalen04,
-  Abel07}.  This aids in the expansion of the blastwave because it
-delays the transition to the Sedov-Taylor and snowplow phases.  In
-PISNe, approximately half of the metals stay in the IGM with a metal
-bubble size of a few kpc \citep{Wise08_Gal, Greif10}.  The blastwave
-may induce SF in nearby halos through the compression of the gas
-\citep{Ferrara98}, and timescales for metal mixing into the dense gas
-are many dynamical times \citep{Cen08} for shock velocities
-$\lsim100~\kms$.
+%These first stellar clusters may be connected to stars in the Milky
+%Way halo and nearby dwarf spheroidal (dSph) galaxies, both with a
+%metallicity floor of [Z/H] = --4 \citep{Beers05, Tafelmeyer10,
+%Frebel10_Obs}.
+%
 
 Numerical simulations are useful to detangle and study these
-complexities and the transition from Pop III to II stars.  In this
-Letter, we present a simulation that includes both types of SF, and
-their radiative and mechanical feedback.  The methods used here
-incorporate and link together recent results from metal-enriched and
-metal-free star formation, the critical metallicity, and
-pair-instability supernovae.  This is the first time it has been
-possible to link the formation and feedback of the first stars to
-protogalaxies, resolving the important scales and including the most
-important physical effects.
+complexities and the transition from Pop III to II stars.  Here, we
+present simulations that include both modes of star formation and
+their radiative, mechanical, and chemical feedback.  The methods used
+here incorporate and link together recent results from metal-enriched
+and metal-free star formation, the critical metallicity, and
+pair-instability supernovae.  There are some uncertainities in these
+input parameters, and we thus run several simulations while varying
+these parameters.  This is the first time it has been possible to link
+the formation and feedback of the first stars to protogalaxies in a
+numerical simulation, resolving the important scales and including the
+most important physical effects.
+
+This paper is structured as follows.  Section \ref{sec:setup}
+describes our simulation setup, numerical methods for star formation
+and feedback, and different physical models considered in each
+simulation.  Next we present our results on the stellar populations
+and metal enrichement of the high-redshift dwarf galaxies in Section
+\ref{sec:results}.  Then in Section \ref{sec:models}, we show the
+changes in galactic properties and metal enrichments in each physical
+model.  In Section \ref{sec:compare}, we compare our results with
+previous work on the transition to Population II.  We then discuss the
+importance of Population III star formation on high-redshift galaxy
+formation and the implications on the interpretation of damped
+Lyman-$\alpha$ absorbers (DLAs) and galactic archaeology in Section
+\ref{sec:discuss}.  Finally in Section \ref{sec:summary}, we summarize
+our results.
 
@@
 HLLC Riemann solver \citep{Toro94_HLLC} for additional stability in
-strong shocks and rarefaction waves.  To resolve minihalos with at
+strong shocks and rarefaction waves.  To resolve minihaloes with at
 least 100 dark matter (DM) particles and follow the formation of the
@@
 and \citet{Stacy10_Binary} have recently shown that Pop III binaries
-may form in a fraction of such halos.
+may form in a fraction of such haloes.
 
@@
 For reproducibility, we record the number of times the random number
-generator (Mersenne twister; \citet{MTwister}) has been called for use
+generator \citep[Mersenne twister;][]{MTwister} has been called for use
 when restarting the simulations.  Although the Pop III star formation
@@
 stars, the Pop III SFH for a given halo can be different between the
-two simulations.  This happens because the order in which halos form
+two simulations.  This happens because the order in which haloes form
 Pop III stars can be altered from enhanced star formation and feedback
@@
 
-\begin{figure*}
+\begin{figure}
   \plottwo{history0.eps}{history5.eps}
   \caption{\label{fig:massevo} Mass evolution.}
-\end{figure*}
+\end{figure}
 
@@
 \begin{figure}
-  \plotone{z2.eps}
-  \caption{\label{fig:z2} Halo metallicities.}
-\end{figure}
-
-\begin{figure}
-  \plotone{z3.eps}
-  \caption{\label{fig:z3} Halo metallicities.}
+  \plottwo{z2.eps}{z3.eps}
+  \caption{\label{fig:zhalo} Halo metallicities.}
 \end{figure}
@@
 
+\section{Differences between Physical Models}
+\label{sec:models}
+
 \section{Comparison to Previous Work}
+\label{sec:compare}
 
@@
 \section{Discussion}
+\label{sec:discuss}
 
@@
 
-\li Importance of critical metallicity in satellite halos, not in host
-halos
+\li Importance of critical metallicity in satellite haloes, not in host
+haloes
 
@@
 \section{Summary}
+\label{sec:summary}
 
@@
 
-J.~H.~W. is supported by NASA through Hubble Fellowship grant
-\#120-6370 awarded by the Space Telescope Science Institute, which is
-operated by the Association of Universities for Research in Astronomy,
-Inc., for NASA, under contract NAS 5-26555.  M.~J.~T. and
-M.~L.~N. acknowledge partial support from NASA ATFP grant NNX08AH26G.
-Computational resources were provided by NASA/NCCS award SMD-09-1439.
 J.~H.~W. thanks Renyue Cen, Amina Helmi, Marco Spaans, and Eline
-Tolstoy for enlightening discussions.  The majority of the analysis
-and plots were done with \texttt{yt} \citep{yt_full_paper}.
+Tolstoy for enlightening discussions.  J.~H.~W. is supported by NASA
+through Hubble Fellowship grant \#120-6370 awarded by the Space
+Telescope Science Institute, which is operated by the Association of
+Universities for Research in Astronomy, Inc., for NASA, under contract
+NAS 5-26555.  M.~J.~T. and M.~L.~N. acknowledge partial support from
+NASA ATFP grant NNX08AH26G.  Computational resources were provided by
+NASA/NCCS award SMD-09-1439.  The majority of the analysis and plots
+were done with \texttt{yt} \citep{yt_full_paper}.
 

### 2011-01-17 Hamburg/wise_proceed.tex
Adding conference proceeding (really just the rejected ApJL article) for the Hamburg conference in November.

--- 2010-11-11 ms.tex
@@
-%\documentclass[apjl]{emulateapj}
-\documentclass[12pt,preprint]{aastex}
-
+% Please use the skeleton file you have received in the 
+% invitation-to-submit email, where your data are already
+% filled in. Otherwise please make sure you insert your 
+% data according to the instructions in PoSauthmanual.pdf
+\documentclass{PoS}
 \usepackage{graphicx}
@@
 
-%%%%%%%% Begin custom definitions %%%%%%%%%%%%%
+\input macros.tex
 
-\newcommand{\fesc}{\ifmmode{f_{\rm esc}}\else{$f_{\rm esc}$}\fi}
-\newcommand{\fescs}{\ifmmode{f_{\rm esc}^\star}\else{$f_{\rm esc}^\star$}\fi}
-\newcommand{\kms}{\ifmmode{{\rm km~s^{-1}}}\else{km s$^{-1}$}\fi}
-\newcommand{\cubecm}{\ifmmode{{\rm cm^{-3}}}\else{cm$^{-3}$}\fi}
-\newcommand{\lsim}{\lower0.3em\hbox{$\,\buildrel <\over\sim\,$}}
-\newcommand{\gsim}{\lower0.3em\hbox{$\,\buildrel >\over\sim\,$}}
-\newcommand{\li}{\noindent$\bullet$\quad}
-\newcommand{\flux}{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$}
-\newcommand{\emis}{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$}
-\newcommand{\sfr}{M$_\odot$ yr$^{-1}$ Mpc$^{-3}$}
-\newcommand{\hst}{{\it HST}}
-\newcommand{\enzo}{{\sl Enzo}}
-\newcommand{\Ms}{\ifmmode{M_\odot}\else{$M_\odot$}\fi}
-\newcommand{\mmin}{M$_{min}$}
-\newcommand{\hh}{H$_2$}
-\newcommand{\Ol}{$\Omega_\Lambda$}
-\newcommand{\Om}{$\Omega_M$}
-\newcommand{\Ob}{$\Omega_b$}
-\newcommand{\theat}{$t_{\rm{heat}}$}
-\newcommand{\tcool}{$t_{\rm{cool}}$}
-\newcommand{\rcool}{$r_{\rm{cool}}$}
-\newcommand{\tcross}{$t_{\rm{cross}}$}
-\newcommand{\tdyn}{$t_{\rm{dyn}}$}
-\newcommand{\tkh}{$t_{\rm{KH}}$}
-\newcommand{\tH}{$t_{\rm{H}}$}
-\newcommand{\tvir}{\ifmmode{T_{\rm{vir}}}\else{$T_{\rm{vir}}$}\fi}
-\newcommand{\mvir}{\ifmmode{M_{\rm{vir}}}\else{$M_{\rm{vir}}$}\fi}
-\newcommand{\rvir}{\ifmmode{r_{\rm{vir}}}\else{$r_{\rm{vir}}$}\fi}
-\newcommand{\rr}{$r_{200}$}
-\newcommand{\lya}{Ly$\alpha$}
-\newcommand{\jj}{\ifmmode{J_{21}}\else{$J_{21}$}\fi}
-\newcommand{\flw}{\ifmmode{F_{LW}}\else{$F_{LW}$}\fi}
-\newcommand{\kph}{\ifmmode{k_{\rm ph}}\else{$k_{\rm ph}$}\fi}
-\newcommand{\tv}{$\langle T \rangle_{\rm v}$}
-\newcommand{\tm}{$\langle T \rangle_{\rm m}$}
-\newcommand{\msun}{{\rm\,M_\odot}} 
-\newcommand{\lsun}{{\rm\,L_\odot}}
-\newcommand{\zsun}{{\rm\,Z_\odot}}
-\newcommand{\etal}{et al.\ }
-\newcommand\tento[1]{$10^{#1}$}
-\newcommand\step[1]{\textit{Step #1}.---}
+\title{Formation of the First Galaxies: Metal Enrichment and Stellar
+  Populations}
 
-%%%%%%%% End custom definitions %%%%%%%%%%
+\ShortTitle{Formation of the First Galaxies}
+
+\author{\speaker{John H. Wise}\\
+        Department of Astrophysical Sciences, Princeton University,
+        Princeton, NJ 08544, USA\\
+        E-mail: \email{jwise@astro.princeton.edu}}
+
+\author{Matthew J. Turk and Michael L. Norman\\
+        Center for Astrophysics and Space Sciences,
+        University of California at San Diego, La Jolla, CA 92093, USA\\
+        E-mail: \email{matthewturk@gmail.com}}
+
+\author{Tom Abel\\
+        Kavli Institute for Particle Astrophysics and
+        Cosmology, Stanford University, Menlo Park, CA 94025, USA\\
+        E-mail: \email{tabel@stanford.edu}}
+
+\abstract{We present adaptive mesh refinement radiation hydrodynamics
+  simulations that follows the transition from Population III to II
+  star formation.  We model stellar radiative feedback with adaptive
+  ray tracing.  A top-heavy initial mass function for the Population
+  III stars is considered, resulting in a plausible distribution of
+  pair-instability supernovae and associated metal enrichment.  We
+  find that the gas fraction recovers from 5 percent to nearly the
+  cosmic fraction in halos with merger histories rich in halos above
+  $10^7 \Ms$.  A single pair-instability supernova is sufficient to
+  enrich the host halo to a metallicity floor of $10^{-3} Z_\odot$ and
+  to transition to Population II star formation.  This provides a
+  natural explanation for the observed floor on damped Lyman alpha
+  (DLA) systems metallicities reported in the literature, which is of
+  this order.  We find that stellar metallicities do not necessarily
+  trace stellar ages, as mergers of halos with established stellar
+  populations can create superpositions of $t-Z$ evolutionary tracks.
+  A bimodal metallicity distribution is created after a starburst
+  occurs when the halo can cool efficiently through atomic line
+  cooling.}
+
+\FullConference{Cosmic Radiation Fields: Sources in the early Universe - CRF2010,\\
+		November 9-12, 2010\\
+		Desy Germany}
 
 \begin{document}
-
-\shorttitle{THE BIRTH OF A GALAXY}
-\shortauthors{WISE ET AL.}
-
-\title{The Birth of a Galaxy: Primoridal Metal Enrichment and
-  Population II Stellar Populations}
-
-\author{John H. Wise\altaffilmark{1,2}, 
-  Matthew J. Turk\altaffilmark{3},
-  Michael L. Norman\altaffilmark{3},
-  Tom Abel\altaffilmark{4}}
-
-\altaffiltext{1}{Department of Astrophysical Sciences, Princeton
-  University, Peyton Hall, Ivy Lane, Princeton, NJ 08544}
-\altaffiltext{2}{Hubble Fellow}
-\altaffiltext{3}{Center for Astrophysics and Space Sciences,
-  University of California at San Diego, La Jolla, CA 92093}
-\altaffiltext{4}{Kavli Institute for Particle Astrophysics and
-  Cosmology, Stanford University, Menlo Park, CA 94025}
-\email{jwise@astro.princeton.edu}
-
-\begin{abstract}
-
-  Population III stars first form in dark matter halos with masses
-  around $10^6 \Ms$.  By definition, they are metal-free, and their
-  protostellar collapse is driven by molecular hydrogen cooling in the
-  gas-phase, leading to a massive characteristic mass $\sim 100~\Ms$
-  and suppressed fragmentation.  Population II stars with lower
-  characteristic masses form when the star-forming gas reaches a
-  critical metallicity of $10^{-6} - 10^{-3.5}~Z_\odot$, depending on
-  whether dust cooling is important.  We present adaptive mesh
-  refinement radiation hydrodynamics simulations that follows the
-  transition from Population III to II star formation.  We model
-  stellar radiative feedback with adaptive ray tracing.  A top-heavy
-  initial mass function for the Population III stars is considered,
-  resulting in a plausible distribution of pair-instability supernovae
-  and associated metal enrichment.  We find that the gas fraction
-  recovers from 5 percent to nearly the cosmic fraction in halos with
-  merger histories rich in halos above $10^7 \Ms$.  A single
-  pair-instability supernova is sufficient to enrich the host halo to
-  a metallicity floor of $10^{-3} Z_\odot$ and to transition to
-  Population II star formation.  This provides a natural explanation
-  for the observed floor on damped Lyman alpha (DLA) systems
-  metallicities reported in the literature, which is of this order.
-  We find that stellar metallicities do not necessarily trace stellar
-  ages, as mergers of halos with established stellar populations can
-  create superpositions of $t-Z$ evolutionary tracks.  A bimodal
-  metallicity distribution is created after a starburst occurs when
-  the halo can cool efficiently through atomic line cooling.
-
-\end{abstract}
-
-\keywords{cosmology --- methods: numerical --- hydrodynamics ---
-  radiative transfer --- star formation}
 
@@
 Numerical simulations are useful to detangle and study these
-complexities and the transition from Pop III to II stars.  In this
-Letter, we present a simulation that includes both types of SF, and
-their radiative and mechanical feedback.  The methods used here
-incorporate and link together recent results from metal-enriched and
-metal-free star formation, the critical metallicity, and
-pair-instability supernovae.  This is the first time it has been
-possible to link the formation and feedback of the first stars to
-protogalaxies, resolving the important scales and including the most
-important physical effects.
+complexities and the transition from Pop III to II stars.  Here, we
+present a simulation that includes both types of SF, and their
+radiative and mechanical feedback.  The methods used here incorporate
+and link together recent results from metal-enriched and metal-free
+star formation, the critical metallicity, and pair-instability
+supernovae.  This is the first time it has been possible to link the
+formation and feedback of the first stars to protogalaxies, resolving
+the important scales and including the most important physical
+effects.
 
@@
 \begin{figure}
-%\epsscale{1.15}
+\epsscale{0.5}
 \plotone{f1}
-%\epsscale{1}
+\epsscale{1}
 \caption{\label{fig:massfn} \textit{Top}: Halo mass function of the
@@
 \label{eqn:imf}
-f(M)dM = M^{-1.3} \exp\left[-\left(\frac{M_{\rm char}}{M}\right)^{1.6}\right]
+f(M)dM = M^{-1.3} \exp\left[-\left(\frac{M_{\rm
+      char}}{M}\right)^{1.6}\right] dM
 \end{equation}
@@
 
+\section{Results}
+\label{sec:results}
+
 \begin{figure*}
@@
 \end{figure*}
-
-\section{Results}
-\label{sec:results}
 
@@
 
-In this Letter, we focus on the birth of two galaxies prior to
-reionization with a cosmological AMR radiation hydrodynamics
-simulation.  Supernovae from Pop III stars provide the necessary heavy
-elements for the transition to a Population II stellar population,
-which we have directly simulated.  These two galaxies have a 10--15\%
-probability in surviving as present-day ``fossil'' galaxies
-\citep{Gnedin06}, otherwise they will be incorporated into galactic
-stellar halos.  A $z=8.55$ galaxy was recently spectroscopically
-confirmed that is contained in an ionized bubble with radius 0.1--0.5
-Mpc with an uncharacterized population of galaxies contributing to the
-local ionizing radiation field \citep{Lehnert10_z8.6}.  The galaxies
+We focus on the birth of two galaxies prior to reionization with a
+cosmological AMR radiation hydrodynamics simulation.  Supernovae from
+Pop III stars provide the necessary heavy elements for the transition
+to a Population II stellar population, which we have directly
+simulated.  These two galaxies have a 10--15\% probability in
+surviving as present-day ``fossil'' galaxies \citep{Gnedin06},
+otherwise they will be incorporated into galactic stellar halos.  A
+$z=8.55$ galaxy was recently spectroscopically confirmed that is
+contained in an ionized bubble with radius 0.1--0.5 Mpc with an
+uncharacterized population of galaxies contributing to the local
+ionizing radiation field \citep{Lehnert10_z8.6}.  The galaxies
 simulated here might represent this population and should be detected
@@
 
-% We also find that the merger history plays an important role in
-% supplying gas into halos after its first epoch of SF.  Mergers of
-% halos below the filtering mass are inefficient in providing gas
-% whereas the opposite is true for merging halos above the filtering
-% mass.  Halos do not necessarily need $\tvir \ge 10^4$ K to form
-% significant stellar populations; however SFRs dramatically increase,
-% and thus metal enrichment, when this threshold is reached.  Halos
-% with mostly gas-poor mergers or a quiet merger history result in a
-% monotonic increase in metallicity with time.  SFHs become more
-% complex with multiple metallicity-age tracks if the halo experiences
-% mergers with other halos that have an established stellar
-% population.  Furthermore SF that is triggered by blastwaves
-% interacting with molecular clouds can have metallicities up to a
-% factor of 10 higher than the main starburst.  Starbursts at $\tvir =
-% 10^4$ K can enrich the host halo enough to create a bimodal
-% metallicity distribution, where the metal-poor component is created
-% before the burst.  Note that mergers of stellar populations can also
-% create a similar bimodal distribution, which are observed in dSphs
-% \cite{Battaglia10}.
-
 We have shown that it is possible to simulate the formation of a
@@
 
-J.~H.~W. is supported by NASA through Hubble Fellowship grant
-\#120-6370 awarded by the Space Telescope Science Institute, which is
-operated by the Association of Universities for Research in Astronomy,
-Inc., for NASA, under contract NAS 5-26555.  M.~J.~T. and
-M.~L.~N. acknowledge partial support from NASA ATFP grant NNX08AH26G.
-Computational resources were provided by NASA/NCCS award SMD-09-1439.
-J.~H.~W. thanks Renyue Cen, Amina Helmi, Marco Spaans, and Eline
-Tolstoy for enlightening discussions.  The majority of the analysis
-and plots were done with \texttt{yt} \citep{yt_full_paper}.
+J.~H.~W. thanks the organizers of the conference and is supported by
+NASA through Hubble Fellowship grant \#120-6370 awarded by the Space
+Telescope Science Institute, which is operated by the Association of
+Universities for Research in Astronomy, Inc., for NASA, under contract
+NAS 5-26555.  M.~J.~T. and M.~L.~N. acknowledge partial support from
+NASA ATFP grant NNX08AH26G.  Computational resources were provided by
+NASA/NCCS award SMD-09-1439.  J.~H.~W. thanks Renyue Cen, Amina Helmi,
+Marco Spaans, and Eline Tolstoy for enlightening discussions.  The
+majority of the analysis and plots were done with \texttt{yt}
+\citep{yt_full_paper}.
 
-%\clearpage
-%\input biblio.tex
-%\bibliography{ms}
 \begin{thebibliography}{50}

### 2011-01-19 ms.tex
Adding star formation history plot.
Finished first draft of the intro.

@@
 
-\title[High Redshift Dwarf Galaxies]{Metal Enrichment and Stellar
-  Populations of High Redshift Dwarf Galaxies}
+\title[Transition from Pop III to Dwarf Galaxies]{The Transition from
+  Massive Metal Free Stars to Dwarf Galaxies}
 
-\author[Wise et al.]{John H. Wise$^1$\thanks{Hubble Fellow; e-mail:
-    jwise@astro.princeton.edu}, Matthew J. Turk$^2$, Michael
+\author[J. H. Wise et al.]{John H. Wise$^1$\thanks{Hubble Fellow;
+    e-mail: jwise@astro.princeton.edu}, Matthew J. Turk$^2$, Michael
   L. Norman$^2$, Tom Abel$^3$\\
@@
 
-The first generation of stars, so-called Population III, in the
+The first generation of stars, so-called Population (Pop) III, in the
 universe were metal-free, forming from a primordial mixture of mainly
@@
 K, resulting in Jeans masses on the order of 100 \Ms.  Numerical
-calculations in the past decade have shown that Population III stars
+calculations in the past decade have shown that Pop III stars
 have characteristic masses between 30 and 300
@@
 creates an \hii region with $r \sim 1-3~\mathrm{kpc}$, ionizing the
-surrounding intergalactic medium as the virial radii of the host haloes
-are $r_{\rm vir} \sim 100 \mathrm{pc}$ \citep{Whalen04, Kitayama04,
-  Alvarez06, Abel07}.  The over-pressurized \hii region drives a
-$\sim$ 30 \kms~shock, which is 10 times greater than the escape
-velocity of a $10^6 \Ms$ halo.  In turn, most of the gas is expelled
-from the halo, leaving behind a warm ($3 \times 10^4$ K) and diffuse
-(0.5 \cubecm) medium.  In haloes that are encompassed by these \hii
-regions and not completely photo-evaporated \citep{refs}, the
-additional free electrons catalyze both \hh~and HD molecular line
-cooling \citep{OShea05, Johnson06, Yoshida07, McGreer08}, cooling the
-gas below $\sim$ 100 K and lowering the Jeans mass to $\sim$ 10--30
-\Ms.  These lower-mass, metal-free stars are called Population III.2,
-whereas their more massive counterparts that form in unheated regions
-are called Population III.1 stars \citep{Norman08}.
+surrounding intergalactic medium as the virial radii of the host
+haloes are $r_{\rm vir} \sim 100 \mathrm{pc}$ \citep{Whalen04,
+  Kitayama04, Alvarez06, Abel07}.  The over-pressurized \hii region
+drives a $\sim$ 30 \kms~shock, which is 10 times greater than the
+escape velocity of a $10^6 \Ms$ halo.  In turn, most of the gas is
+expelled from the halo, leaving behind a warm ($3 \times 10^4$ K) and
+diffuse (0.5 \cubecm) medium.  In haloes that are encompassed by these
+\hii regions and not completely photo-evaporated \citep{Shapiro04,
+  whalen08}, the additional free electrons catalyze both \hh~and HD
+molecular line cooling \citep{OShea05, Johnson06, Yoshida07,
+  McGreer08}, cooling the gas below $\sim$ 100 K and lowering the
+Jeans mass to $\sim$ 10--30 \Ms.  These lower-mass, metal-free stars
+are called Pop III.2, whereas their more massive counterparts
+that form in unheated regions are called Pop III.1 stars
+\citep{Norman08}.
 
-A fraction of Population III stars enrich the surrounding IGM when
+A fraction of Pop III stars enrich the surrounding IGM when
 they go supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
@@
 star formation in nearby haloes through the compression of the gas
-\citep{Ferrara98, more}, and the timescales for metal mixing into the
-dense gas are many dynamical times \citep{Cen08} for shock velocities
-$\lsim 100~\kms$.
+\citep{Shapiro87, Ferrara98, Mackey03}, and the timescales for metal
+mixing into the dense gas are many dynamical times \citep{Cen08} for
+shock velocities $\lsim 100~\kms$.
 
@@
 \hh~formation on dust grains becomes efficient, allowing cooling to $T
-\lsim 100$ K \citep{Omukai??}.  The exact value of $Z_{\rm cr}$ has
+\lsim 100$ K \citep{Omukai05}.  The exact value of $Z_{\rm cr}$ has
 been constrained to be between $10^{-6} \zsun$ and $10^{-3.5} \zsun$.
@@
 present-day stellar initial mass functions (IMF), marking the local
-transition from Population III to II star formation.  Intermediate to
+transition from Pop III to II star formation.  Intermediate to
 these populations and possibly unique to high redshift, there exists a
@@
 the interactions between the SN blastwave, cosmological accretion and
-halo mergers, and nearby stellar feedback.  \textbf{Discuss prior work
-  on transition with the papers given by the previous referee.}
+halo mergers, and nearby stellar feedback.  Spurred by the notion of a
+critical metallicity, this transition has been extensively studied
+with (i) volume-averaged semi-analytic models \citep{Scannapieco03,
+  Yoshida04, Furlanetto05_Reion}, (ii) models using hierarchical
+merger trees \citep{Tumlinson06, Tumlinson10, Salvadori07, Komiya10},
+(iii) post-processing of cosmological simulations with blastwave
+models \citep{Karlsson08, Trenti09, Trenti10}, and (iv) direct
+numerical simulations with stellar feedback \citep{Tornatore07,
+  Ricotti08, Maio10_Pop32, Maio10_Enrich}.
+
+Over the past decade, these works have refined the general picture of
+inhomogenous metal enrichment and the transition to Pop II star
+formation, and here we give a brief overview of its development.
+Considering only Pop III star formation, \citeauthor{Yoshida04}
+calculated that Pop III stars can raise the mean metallicity to $-4.5
+\lsim$ [Z/H]\footnote{We use the conventional notation, [Z/H] $\equiv
+  \log(Z/H) - \log(Z_\odot/H_\odot)$.} $\lsim -3.5$ by redshift 15 in
+the upper limit where all metal-free stars have $M = 200 \Ms$ and
+produce PISNe.  Considering both Pop III and II star formation,
+\citeauthor{Scannapieco03} found that the transition between the two
+modes is a gradual process where both modes are coeval, confirmed by
+most of the later works.  Because the host galaxies have small masses
+and are subject to negative radiative feedback through photo-heating
+and photo-dissociation, the minimum halo mass gradually increases with
+the radiation background intensity, which
+\citeauthor{Furlanetto05_Reion} found to delay metal enrichment and
+place it closer to the epoch of reionization.  \citeauthor{Trenti09}
+noted that underdense regions of the universe are still pristine at
+$z=6$ with Pop III stars still forming at these late epochs.  This
+group later expanded on these results to find that Pop II SFR becomes
+dominant at $z>25$ in the buildup of a MW-type halo.  Furthermore they
+stress the importance of a photo-dissociating radiation background
+that reduces enrichment by PISNe and increases the importance of
+metal-rich galactic outflows, where only $10^{-4} - 10^{-2}$ of PISN
+ejecta ends up in EMP stars with $M > 0.9 \Ms$.
+
+The Pop III IMF should play an important role in abundance patterns in
+extremely metal poor (EMP) stars in the Milky Way (MW) halo and the
+physics of reionization.  Using these data as constraints,
+\citeauthor{Tumlinson06} found that Pop III IMFs with log-normal
+distributions with mean masses between 8 and 42 \Ms~best fit the data.
+Furthermore he concludes that EMP stars with [Z/H] $<$ --3 have
+between 1 and 10 metal-free SN progenitors and the Pop III SFR is less
+than 1\% of the total SFR at $z=6$.  \citeauthor{Karlsson08} use
+observational data of EMP stars with their model to constrain the mass
+fraction of Pop III stars that die with a PISN is less than 40 per
+cent.  They also conclude that stars enriched primarily by PISNe have
+[Ca/H] $\gsim$ --2.6, which could have been missed by some EMP
+surveys.
 
@@
 
-Numerical simulations are useful to detangle and study these
-complexities and the transition from Pop III to II stars.  Here, we
-present simulations that include both modes of star formation and
-their radiative, mechanical, and chemical feedback.  The methods used
-here incorporate and link together recent results from metal-enriched
-and metal-free star formation, the critical metallicity, and
+Cosmological simulations are useful but computationally expensive to
+detangle and study the transition from Pop III to II star formation,
+especially the complexities ensuing from hierarchical structure
+formation, stellar feedback, and inhomogeneous chemical enrichment.
+\citeauthor{Tornatore07} employed smoothed particle hydrodynamics
+(SPH) simulations to study this problem and found that Pop III star
+formation occurs down to $z=2.5$ in underdense regions.  Their mass
+resolution did not allow them to capture star formation in minihalos
+($M_{\rm halo} \sim 10^{5-7} \Ms$) that host Pop III stars, which may
+have resulted in an underestimate of metal enrichment.  They found a
+`Pop III wave' of star formation, where Pop III star formation is
+quenched in an inside-out fashion from biased regions to voids, is
+however still valid.  \citeauthor{Ricotti08} used a Lagrangian
+moving-mesh simulation with radiative, mechanical, and chemical
+feedback that resolved minihaloes to find that (i) 1--10\% of the
+cosmic volume is chemically enriched, (ii) the gas reservoir in halos
+with $M < 10^8 \Ms$ are depleted, (iii) there is a large scatter in
+the mass-to-light (M/L) ratios of dwarf galaxies, and (iv) their
+luminosity function is relatively flat.  Most recently
+\citeauthor{Maio10_Pop32} found that the ratios of Pop III to Pop II
+SFRs are insensitive to the exact value of $Z_{\rm cr}$.  In contrast
+with \citeauthor{Ricotti08}, only $10^{-8}$ of the simulation volume
+is chemically enriched by $z=11$.  This difference of several orders
+of magnitude may result from the lack of radiative feedback, which can
+expel most of the gas from the host halo before the SN explosion.
+Supporting this idea, \citet{Whalen08_SN} found that PISN blastwaves
+in neutral halos radiate all of their energy, stalling the shock
+within the halo and suppressing outflows.
+
+Here, we present simulations that include both modes of star formation
+and their radiative, mechanical, and chemical feedback, extending the
+aforementioned previous work on the transition from Pop III to II star
+formation and the birth of the first galaxies.  The methods used here
+incorporate and link together recent results from metal-enriched and
+metal-free star formation, the critical metallicity, and
 pair-instability supernovae.  There are some uncertainities in these
@@
 model.  In Section \ref{sec:compare}, we compare our results with
-previous work on the transition to Population II.  We then discuss the
-importance of Population III star formation on high-redshift galaxy
+previous work on the transition to Pop II.  We then discuss the
+importance of Pop III star formation on high-redshift galaxy
 formation and the implications on the interpretation of damped
@@
 
-%\begin{figure}
-%  \plotone{sfh.eps}
-%  \caption{\label{fig:SFR} Star formation history.}
-%\end{figure}
+\begin{figure*}
+  \epsscale{2.0}
+  \plotone{sfh1.eps}
+  \epsscale{1.0}
+  \caption{\label{fig:SFR} Star formation history.}
+\end{figure*}
 

### 2011-01-19 ms.tex
First draft of expanded method section.

@@
 \author[J. H. Wise et al.]{John H. Wise$^1$\thanks{Hubble Fellow;
-    e-mail: jwise@astro.princeton.edu}, Matthew J. Turk$^2$, Michael
-  L. Norman$^2$, Tom Abel$^3$\\
+    e-mail: jwise@astro.princeton.edu}, Matthew J. Turk$^{2,3}$, Michael
+  L. Norman$^3$, Tom Abel$^4$\\
   $^{1}$ Department of Astrophysical Sciences, Princeton University,
-  Princeton, NJ 08544, USA\\
-  $^{2}$ Center for Astrophysics and Space Sciences,
+  Peyton Hall, Princeton, NJ 08544, USA\\
+  $^{2}$ Department of Astronomy, Columbia University, 538 West 120th
+  Street, New York, NY 10027, USA\\
+  $^{3}$ Center for Astrophysics and Space Sciences,
   University of California at San Diego, La Jolla, CA 92093, USA\\
-  $^{3}$ Kavli Institute for Particle Astrophysics and Cosmology,
+  $^{4}$ Kavli Institute for Particle Astrophysics and Cosmology,
   Stanford University, Menlo Park, CA 94025, USA}
@@
 
-\begin{figure*}
-  \epsscale{2}
-  \plotone{bmosaic.eps}
-  \epsscale{1}
-  \caption{\label{fig:evo-mosaic} text.}
-\end{figure*}
-
 \subsection{Simulation setup}
@@
 \textsc{enzo~v2.0}\footnote{\texttt{enzo.googlecode.com, changeset
-    b86d8ba026d6}} \citep{OShea2004}, which has been modified to use a
-HLLC Riemann solver \citep{Toro94_HLLC} for additional stability in
-strong shocks and rarefaction waves.  To resolve minihaloes with at
-least 100 dark matter (DM) particles and follow the formation of the
-first generation of dwarf galaxies, we use a simulation box of 1 Mpc
-that has a resolution of $256^3$.  This gives us a DM mass resolution
-of 1840 \Ms.  We refine the grid on baryon overdensities of $3 \times
-2^{-0.2l}$, where $l$ is the AMR level, resulting in a
-super-Lagrangian behavior.  We also refine on a DM overdensity of $3
-\times 2^l$ and always resolve the local Jeans length by at least 4
-cells, avoiding artificial fragmentation during gaseous collapses
-\citep{Truelove97}.  This simulation has $1.4 \times 10^8$
-computational elements and a maximal spatial resolution of 0.1 pc.  We
-initialize the simulation with \textsc{grafic} \citep{Bertschinger01}
-at $z = 130$ and use the cosmological parameters from the 7-year WMAP
-$\Lambda$CDM+SZ+LENS best fit \citep{WMAP7}: $\Omega_M = 0.266$,
-$\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 =
-0.81$, and $n = 0.963$ with the variables having their usual
-definitions.  We stop the simulation at $z=7$.
+    b86d8ba026d6}} \citep{OShea2004}.  It uses an $N$-body adaptive
+particle-mesh solver \citep{Efstathiou85} to follow the dark matter
+(DM) dynamics.  It solves the hydrodynamical equation using the
+second-order accurate piecewise parabolic method \citep{Woodward84,
+  Bryan95}, while a Riemann solver ensures accurate shock capturing
+with minimal viscosity.  We use the recently added HLLC Riemann solver
+\citep{Toro94_HLLC} for additional stability in strong shocks and
+rarefaction waves.  We use the nine-species (\hi, \hii, \hei, \heii,
+\heiii, e$^-$, \hh, \hh$^+$, H$^-$) non-equilibrium chemistry model in
+\enzo~\citep{Abel97, Anninos97} and the \hh~cooling rates from
+\citet{Glover08_Rates}.
+
+To resolve minihaloes with at least 100 dark matter (DM) particles and
+follow the formation of the first generation of dwarf galaxies, we use
+a simulation box of $L_{\rm box} = 1$ Mpc that has a resolution of
+$256^3$.  This gives us a DM mass resolution of 1840 \Ms.  We refine
+the grid on baryon overdensities of $3 \times 2^{-0.2l}$, where $l$ is
+the AMR level, resulting in a super-Lagrangian behavior \citep[also
+see][]{OShea08}.  We also refine on a DM overdensity of $3 \times 2^l$
+and always resolve the local Jeans length by at least 4 cells,
+avoiding artificial fragmentation during gaseous collapses
+\citep{Truelove97}.  If any of these critera are met in a single cell,
+it is flagged for further spatial refinement.
+
+We initialize the simulation with \textsc{grafic}
+\citep{Bertschinger01} at $z = 130$ and use the cosmological
+parameters from the 7-year WMAP $\Lambda$CDM+SZ+LENS best fit
+\citep{WMAP7}: $\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b
+= 0.0449$, $h = 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$ with the
+variables having their usual definitions.  We use a maximum refinement
+level of $l = 12$, resulting in a maximal comoving resolution of 1 pc.
+We stop the simulation at $z=7$ to avoid any large-scale modes with $r
+\sim L_{\rm box}$ entering the non-linear growth regime.  At the final
+redshift, this simulation has $1.4 \times 10^8$ computational cells.
 
@@
 
-We distinguish Pop II and Pop III SF by the total metallicity of the
+Here we describe our star formation and feedback algorithms, quoting
+the parameters used in our fidicual model.  We describe the variations
+in these parameters later in Sec. \ref{sec:config}.
+
+We consider both Pop II and III star formation in the simulation.  We
+distinguish between the two modes by the total metallicity of the
 densest cell in the molecular cloud.  Pop II stars are formed if [Z/H]
@@
 
-% Furthermore, detailed one-dimensional calculations have shown that
-% their IMF should follow a Kroupa-like IMF that has a Salpeter slope
-% at the high-mass end and an exponential cut-off below $M_{\rm char}$
-% \cite{refs}.
+For Pop III stars, we use the same SF model as \citet{Wise08_Gal}
+where each star particle represents a single star, forming at an
+overdensity of $5 \times 10^5$.  The overdense cell must have a
+converging velocity flow ($\nabla \cdot v < 0$) and be cold ($T <
+10^3$ K), similar to the original \citet{Cen92} model.  We do not use
+the $t_{\rm cool} < t_{\rm dyn}$ condition either because these
+timescales are roughly equivalent during the quasi-static collapse of
+a metal-free molecular cloud \citep[e.g.][]{OShea07a}.  Thus this
+comparison does not pose a good test whether a volume will collapse
+and form a Pop III star.  In its replacement, we require that the cell
+have a \hh~fraction $f_{\rm H2} > 5 \times 10^{-3}$ to suppress star
+formation in the presence of a strong \hh-dissociating (Lyman-Werner;
+hereafter LW) background.  Lastly we do not use the original criterion
+of a cell being Jeans unstable because the local Jeans length is
+always resolved by at least four cells in our simulation.  Once a cell
+satisifies these four criteria, the cell is flagged to form a star
+particle, acting as a radiative point source.  To conserve mass within
+the simulation, we remove half of the gas in a sphere centered on the
+overdense cell that contains twice the stellar mass.  If multiple star
+particles form in the same timestep within $r_{\rm merge} = 10$ pc,
+these particles are merged, and the resulting position is their center
+of mass.
 
-For Pop III stars, we use the same SF model as \citet{Wise08_Gal} where
-each star particle represents a single star, forming at an overdensity
-of $5 \times 10^5$.  Instead of using a fixed stellar mass, we randomly
-sampled from an IMF with a functional form of
+Instead of using a fixed stellar mass as in \citet{Wise08_Gal}, we
+randomly sampled from an IMF with a functional form of
 %
@@
 
-We treat Pop II SF with the same prescription as \citet{Wise09}, which
-is a modified version of the \citet{Cen92} method but accounts for the
-fact that the molecular clouds are resolved.  The critical overdensity
-is the same as the Pop III SF model.  In each star-forming region,
-seven percent of the cold gas ($T < 10^3$ K) is removed from the grid
-and deposited into the star particle that lives for 20 Myr, the
-maximum lifetime of an OB star.  These stars generate the majority of
-the ionizing radiation and SNe feedback in stellar clusters, thus we
-ignore lower mass stars.
+We treat Pop II star formation with the same prescription as
+\citet{Wise09}, which is similar to the Pop III prescription but
+without the \hh~fraction floor that is removed because the
+metal-enriched gas can efficiently cool even in the presence of a
+strong UV radiation field \citep[e.g.][]{Safranek10}.  This method is
+effectively a modified version of the \citet{Cen92} method but
+accounts for the fact that the molecular clouds are resolved.  In the
+simulation, we define the molecular cloud as a sphere, centered on the
+most dense cell, with a dynamical time $t_{\rm dyn} = 3$ Myr
+(corresponding to an average density $\bar{\rho}_{\rm MC} \simeq
+1000\mu \cubecm$) and a radius $R_{\rm MC}$.  In this sphere, a
+fraction $c_\star = 0.07 f_{\rm cold}$ of the cold gas ($T < 10^3$ K)
+is converted into a star particle with mass $m_\star = c_\star
+(4\pi/3) \bar{\rho}_{\rm MC} R_{\rm MC}^3$.  We then replace the
+sphere with a uniform density $\rho_{\rm MC} = (1 - c_\star) /
+(Gt_{\rm dyn}^2)$ and temperature $T = 10^4$ K, which approximates the
+initial stages of an \hii~region.  Similar to the Pop III treatment,
+we merge any newly created particles within a radius $R_{\rm merge}$.
+We set the minimum mass of a star particle to $m_{\rm \star, min} =
+1000 \Ms$.  If the initial mass does not exceed $m_{\rm \star, min}$,
+the star particle does not provide any feedback and continues to
+accrete until it reaches $m_{\rm \star, min}$.  The star particles
+live for 20 Myr, the maximum lifetime of an OB star.  These stars
+generate the majority of the ionizing radiation and SNe feedback in
+stellar clusters, thus we ignore any feedback from lower mass stars.
 
@@
 
-We use mass-dependent luminosities and lifetimes of the Pop III stars
-from \citet{Schaerer02}.  The radiation field is evolved with adaptive
-ray tracing \citep{Abel02_RT, Wise10} and is coupled self-consistently
-to the hydrodynamics.  We model the \hh~dissociating radiation with an
-optically-thin, inverse square profile, centered on all stars.  These
-stars die as pair-instability SNe (PISNe) if they are in the mass
-range 140--260 \Ms~\citep{Heger03}.  We use the explosion energy from
+The radiation field is evolved with adaptive ray tracing
+\citep{Abel02_RT, Wise10} that is based on the HEALPix framework
+\citep{HEALPix} and is coupled self-consistently to the hydrodynamics.
+Each star particle is a point source of hydrogen ionizing radiation
+with the ionizing luminosity equally split between 48 initial rays
+(HEALPix level 2).  We use a mono-chromatic spectrum for the radiation
+with the energy $E_{\rm ph}$ equaling the luminosity-weighted photon
+energy of the spectrum.  For a cosmological simulation that focuses on
+galaxies, this does not significantly affect the overall galactic
+dynamics \citep[see Sec. 6.3 in][]{Wise10}.  We do not consider helium
+singly- and doubly-ionizing radiation.  As the rays propagate from the
+source or into a high resolution AMR grid, they are adaptively split
+into 4 child rays, increasing the angular resolution of the solution,
+when the solid angle of the ray $\theta = 4\pi/(12 \times 4^{L})$ is
+larger than 1/3 of the cell area, where $L$ is the HEALPix level.  We
+model the \hh~dissociating radiation with an optically-thin, inverse
+square profile, centered on all star particles.  In halos with $M
+\gsim 10^8 \Ms$, the \hh~column density may become large enough to
+self-shield itself from LW radiation \citep{Wise08_Gal}.  Thus we may
+be underestimating the SFRs in our work.
+
+We use mass-dependent hydrogen ionizing and LW photon luminosites and
+lifetimes of the Pop III stars from \citet{Schaerer02}.  We use a
+mass-independent photon energy $E_{\rm ph} = 29.6$ eV, appropriate for
+the near-constant $10^5$ K surface temperatures of Pop III stars.
+They die as Type II SNe if $11 \le M_\star/\Ms \le 40$
+\Ms~\citep{Woosley95} and as PISNe if they are in the mass range
+140--260 \Ms~\citep{Heger03}, where $M_\star$ is the stellar mass.
+For normal Type II SNe between 11--20 \Ms, we use an explosion energy
+of \tento{51}~erg and a linear fit to the metal ejecta mass calculated
+in \citet{Nomoto06},
+%
+\begin{equation}
+  \label{eqn:typeii}
+  M_{\rm Z}/\Ms = 0.1077 + 0.3383 \times (M_\star/\Ms - 11).
+\end{equation}
+%
+We model the SNe of stars with $20 \le M_\star/\Ms \le 40$ as
+hypernova with the energies and ejecta masses also taken from
+\citeauthor{Nomoto06}, linearly interpolating their results to
+$M_\star$.  For PISNe, we use the explosion energy from
 \citet{Heger02}, where we fit the following function to their models,
-$E_{\rm PISN} = 10^{51} \times [5.0 + 1.304 (M_{\rm He} - 64)]$, where
-$M_{\rm He} = (13/24) \times (M_\star - 20) \Ms$ is the helium core
-(and equivalently the ejecta) mass and $M_\star$ is the stellar mass.
+%
+\begin{equation}
+  \label{eqn:pisn}
+  E_{\rm PISN} = 10^{51} \times [5.0 + 1.304 (M_{\rm He}/\Ms - 64)] \; \mathrm{erg},
+\end{equation}
+%
+where $M_{\rm He} = (13/24) \times (M_\star - 20) \Ms$ is the helium
+core (and equivalently the metal ejecta) mass and $M_\star$ is the
+stellar mass.  The blastwave is modeled by injecting the explosion
+energy and ejecta mass into a sphere of 10 pc, smoothed at its surface
+to improve numerical stability \citep{Wise08_Gal}.  Because we resolve
+the blastwave relatively well with several cells across at its
+initialization, the thermal energy is converted into kinetic energy
+and agrees with the Sedov-Taylor solution \citep[e.g.][]{Greif07}.
 
 The Pop II stars emit 6000 hydrogen ionizing photons per baryon over
-their lifetime, and we do not consider singly- and doubly-ionizing
-helium photons.  We note that low-metallicity stars generate up to a
-factor of four more ionizing photons than a solar metallicity
-population \citep{Schaerer03} and might be underestimating the
-radiative feedback.  Nonetheless this study provides an excellent
+their lifetime, appropriate for a [Z/H] = $-1.3$ population.  We note
+that lower-metallicity stars generate up to 60\% more ionizing photons
+and might be underestimating the radiative feedback
+\citep{Schaerer03}.  Nonetheless this study provides an excellent
 first insight in the transition to Pop II SF, as the metal enrichment
@@
 $6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$ after living for 4 Myr,
-which is injected into spheres with a radius of 10 pc.  If the
-resolution of the grid is less than 10/3 pc, we deposit the energy
-into a $3^3$ cube surrounding the star particle.
+which is injected into spheres with a radius of 10 pc, using the same
+technique as the Pop III SNe.  However if the resolution of the grid
+is less than 10/3 pc, we distribute the energy into a $3^3$ cube
+surrounding the star particle.  In addition to numerical stability,
+energy distribution across several cells instead of a single cell has
+been shown to match cosmic SFRs better in galaxy simulations at lower
+redshifts \citep{Smith10}.
 
 \subsection{Different physics configurations}
+\label{sec:config}
+
+\begin{figure}
+  \plotone{uvb.eps}
+  \caption{\label{fig:uvb} Time evolution of the Lyman-Werner
+    background, calculated with the \citet{Wise05} model.}
+\end{figure}
 
 We perform five different simulations with the same initial
-conditions.  The fiducial model considers (1) primordial cooling that
-is solved with a non-equilbrium chemistry solver with 9 species of
-hydrogen, helium, and molecular hydrogen, (2) a Pop III IMF
-characteristic mass $M_{\rm char}$ = 100 \Ms, and (3) Pop II and Pop
-III star formation.  We vary this model with the following:
+conditions.  The fiducial model considers (a) primordial cooling with
+9 species of hydrogen, helium, and molecular hydrogen, (b) a Pop III
+IMF characteristic mass $M_{\rm char}$ = 100 \Ms, and (c) Pop II and
+Pop III star formation.  We vary this model with the following
+changes:
 
-\begin{enumerate}
+\begin{itemize}
 \item Radiative cooling from metal species.  We calculate a cooling
@@
   cooling curve.  It is tabulated based on density, temperature,
-  electron fraction, and metallicity.
-\item Pop III IMF characteristic mass $M_{\rm char}$ = 40 \Ms.
-\item Pop II star formation only.
+  electron fraction, and total metallicity.
+\item Pop III IMF characteristic mass $M_{\rm char}$ = 40 \Ms.  Using
+  the abundance patterns of EMP stars and reionization as constaints,
+  the data are best fit with IMFs favoring stars with masses between
+  20--130 \Ms \citep{Umeda03, Tumlinson06}.
+\item Lyman-Werner radiation background.  We use the semi-analytical
+  model of \citet{Wise05}, updated with the 7-year WMAP parameters and
+  optical depth to Thompson scattering, to calculate the LW background
+  intensity, plotted in Figure \ref{fig:uvb}.  In this semi-analytical
+  model, we use a Pop III stellar mass of 100 \Ms, star formation
+  efficiency of 0.005, and escape fraction of 0.2 \citep{Wise09}.  The
+  LW radiation from point sources are added to the background.  For
+  computational convenience, we fit the background evolution with the
+  function
+%
+  \begin{equation}
+    \label{eqn:uvb}
+    \log J_{21}(z) = A + Bz - Cz^2 + Dz^3 - Ez^4,
+  \end{equation}
+%
+  where $(A,B,C,D,E) = (-2.356, 0.4562, 0.02680, 5.882 \times 10^{-4},
+  -5.056 \times 10^{-6})$ and $J_{21}$ is the specific intensity in
+  units of $10^{-21}$ \emis.  This fits the model data within 1\% in
+  $6 \le z \le 30$ and is consistent with $J_{21}$ values in
+  \citet{Trenti09_SFR}.
+\item Pop II star formation only.  This model provides a good
+  comparison to other works that do not consider \hh~cooling.
 \item Pop II star formation only and no molecular hydrogen cooling.
-\end{enumerate}
+  This model is useful to study the importance of treating Pop III
+  star formation and their PISNe.
+\end{itemize}
+
+\begin{figure*}
+  \epsscale{2}
+  \plotone{bmosaic.eps}
+  \epsscale{1}
+  \caption{\label{fig:evo-mosaic} Evolution of the entire simulation
+    volume at redshifts 15, 12, 10, 8, and 7 (left to right).
+    Pictured here are the density-weighted projections of density
+    (top), temperature (middle), and metallicity (bottom).  Note how
+    the stellar radiative feedback from low-mass galaxies reionize
+    the majority of the volume.  The metallicity projections are a
+    composite image of metals originating from Pop II (blue) and III
+    (red) stars with magneta indicdating a mixture of the two.}
+\end{figure*}
 

### 2011-01-20 ms.tex
Started on the results section.  Added halo mass function and galaxy luminosity plot.

@@
 \citep{Bond84, Schaerer02}.  Radiation during their main sequence
-creates an \hii region with $r \sim 1-3~\mathrm{kpc}$, ionizing the
+creates an \hii~region with $r \sim 1-3~\mathrm{kpc}$, ionizing the
 surrounding intergalactic medium as the virial radii of the host
 haloes are $r_{\rm vir} \sim 100 \mathrm{pc}$ \citep{Whalen04,
-  Kitayama04, Alvarez06, Abel07}.  The over-pressurized \hii region
+  Kitayama04, Alvarez06, Abel07}.  The over-pressurized \hii~region
 drives a $\sim$ 30 \kms~shock, which is 10 times greater than the
@@
 diffuse (0.5 \cubecm) medium.  In haloes that are encompassed by these
-\hii regions and not completely photo-evaporated \citep{Shapiro04,
+\hii~regions and not completely photo-evaporated \citep{Shapiro04,
   whalen08}, the additional free electrons catalyze both \hh~and HD
@@
   McGreer08}, cooling the gas below $\sim$ 100 K and lowering the
-Jeans mass to $\sim$ 10--30 \Ms.  These lower-mass, metal-free stars
+Jeans mass to $\sim10-30$ \Ms.  These lower-mass, metal-free stars
 are called Pop III.2, whereas their more massive counterparts
@@
   Wise08_Gal, Greif10} with approximately half of the ejecta falling
-back into the adjacent filaments and halos.  The blastwave may induce
+back into the adjacent filaments and haloes.  The blastwave may induce
 star formation in nearby haloes through the compression of the gas
@@
 formation occurs down to $z=2.5$ in underdense regions.  Their mass
-resolution did not allow them to capture star formation in minihalos
+resolution did not allow them to capture star formation in minihaloes
 ($M_{\rm halo} \sim 10^{5-7} \Ms$) that host Pop III stars, which may
@@
 feedback that resolved minihaloes to find that (i) 1--10\% of the
-cosmic volume is chemically enriched, (ii) the gas reservoir in halos
+cosmic volume is chemically enriched, (ii) the gas reservoir in haloes
 with $M < 10^8 \Ms$ are depleted, (iii) there is a large scatter in
@@
 Supporting this idea, \citet{Whalen08_SN} found that PISN blastwaves
-in neutral halos radiate all of their energy, stalling the shock
+in neutral haloes radiate all of their energy, stalling the shock
 within the halo and suppressing outflows.
@@
 numerical simulation, resolving the important scales and including the
-most important physical effects.
+most important physical effects.  This is the first paper in series
+that focuses on the formation and properties of high-redshift dwarf
+galaxies.
 
@@
 \label{sec:setup}
+
+In this section, we describe our cosmological radiation hydrodynamics
+simulation suite with sub-pc resolution, focusing on first the
+formation and feedback of Pop III stars, the transition to Pop II star
+formation, and finally the formation of the first galaxies.  We then
+detail our star formation and feedback algorithms.  We run a total of
+eight different simulations, varying physical parameters.  In the
+following description, we quote the parameters used in our fidicual
+model and describe their variations later in Sec. \ref{sec:config}.
 
@@
 \subsection{Star formation}
-
-Here we describe our star formation and feedback algorithms, quoting
-the parameters used in our fidicual model.  We describe the variations
-in these parameters later in Sec. \ref{sec:config}.
 
@@
 model the \hh~dissociating radiation with an optically-thin, inverse
-square profile, centered on all star particles.  In halos with $M
+square profile, centered on all star particles.  In haloes with $M
 \gsim 10^8 \Ms$, the \hh~column density may become large enough to
@@
 The Pop II stars emit 6000 hydrogen ionizing photons per baryon over
-their lifetime, appropriate for a [Z/H] = $-1.3$ population.  We note
-that lower-metallicity stars generate up to 60\% more ionizing photons
-and might be underestimating the radiative feedback
-\citep{Schaerer03}.  Nonetheless this study provides an excellent
-first insight in the transition to Pop II SF, as the metal enrichment
-is the key ingredient here.  For SN feedback, these stars generate
-$6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$ after living for 4 Myr,
-which is injected into spheres with a radius of 10 pc, using the same
-technique as the Pop III SNe.  However if the resolution of the grid
-is less than 10/3 pc, we distribute the energy into a $3^3$ cube
-surrounding the star particle.  In addition to numerical stability,
-energy distribution across several cells instead of a single cell has
-been shown to match cosmic SFRs better in galaxy simulations at lower
-redshifts \citep{Smith10}.
+their lifetime and $E_{\rm ph} = 21.6$ eV, appropriate for a [Z/H] =
+$-1.3$ population.  We note that lower-metallicity stars generate up
+to 60\% more ionizing photons and might be underestimating the
+radiative feedback \citep{Schaerer03}.  Nonetheless this study
+provides an excellent first insight in the transition to Pop II SF, as
+the metal enrichment is the key ingredient here.  For SN feedback,
+these stars generate $6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$
+after living for 4 Myr, which is injected into spheres with a radius
+of 10 pc, using the same technique as the Pop III SNe.  However if the
+resolution of the grid is less than 10/3 pc, we distribute the energy
+into a $3^3$ cube surrounding the star particle.  In addition to
+numerical stability, energy distribution across several cells instead
+of a single cell has been shown to match cosmic SFRs better in galaxy
+simulations at lower redshifts \citep{Smith10}.
 
@@
 
-We perform five different simulations with the same initial
+We perform eight different simulations with the same initial
 conditions.  The fiducial model considers (a) primordial cooling with
@@
 
-\begin{itemize}
+\begin{enumerate}
 \item Radiative cooling from metal species.  We calculate a cooling
@@
   electron fraction, and total metallicity.
+\item A critical metallicity of [Z/H] = --5 and --6, accounting for
+  the case where dust cooling can induce low-mass fragmentation in
+  these lower metallicities \citep{Omukai05, Schneider06_Frag}.
 \item Pop III IMF characteristic mass $M_{\rm char}$ = 40 \Ms.  Using
@@
   efficiency of 0.005, and escape fraction of 0.2 \citep{Wise09}.  The
-  LW radiation from point sources are added to the background.  For
+  LW radiation from point sources are added to the background.  The
+  intensity decreases after $z \sim 14$ because Pop II star formation
+  becomes dominant, which produce less LW specific luminosity than Pop
+  III stars that have surface temperatures of $T = 10^5$ K.  For
   computational convenience, we fit the background evolution with the
@@
   -5.056 \times 10^{-6})$ and $J_{21}$ is the specific intensity in
-  units of $10^{-21}$ \emis.  This fits the model data within 1\% in
-  $6 \le z \le 30$ and is consistent with $J_{21}$ values in
-  \citet{Trenti09_SFR}.
-\item Pop II star formation only.  This model provides a good
-  comparison to other works that do not consider \hh~cooling.
+  units of $10^{-21}$ \emis.  This fits the
+  model data within 1\% in $6 \le z \le 30$ and is consistent with
+  $J_{21}$ values in \citet{Trenti09_SFR}.
+\item Pop II star formation only.  This model is useful to study the
+  importance of treating Pop III star formation as single stars and
+  their pair-instability and Type II SNe.
 \item Pop II star formation only and no molecular hydrogen cooling.
-  This model is useful to study the importance of treating Pop III
-  star formation and their PISNe.
-\end{itemize}
+  This model provides a good comparison to larger scale simulations
+  where it is not computationally feasible to consider \hh~cooling or
+  resolve the necessary scales for Pop III star formation.
+\end{enumerate}
+
+By running several simulations with different physical scenarios, we
+can quantify the importance of each ingredient in high-redshift dwarf
+galaxy formation.  This approach is similar in spirit with many other
+galaxy formation simulation suites \citep[e.g.][]{Schaye10,
+  Maio10_Pop32}.
+
+\section{Results}
+\label{sec:results}
 
@@
 
-\section{Results}
-\label{sec:results}
+\begin{figure}
+  \plotone{Lstar.eps}
+  \caption{\label{fig:mass_fn} The top panel shows the halo mass
+    function of the simulated haloes (points) where the error bars are
+    Poisson noise and the solid line is the analytic halo mass
+    function of \citet{Warren06}.  The bottom panel depicts the galaxy
+    luminosities versus halo DM mass.  Overplotted are constant
+    mass-to-light ratios.  The large scatter at low halo masses are
+    similar to ones observed in local dSph galaxies.}
+\end{figure}
+
+Here we present the gaseous and stellar evolution of the high-redshift
+dwarf galaxies that form in our simulations.  To illustrate its global
+properties, we show the density-weighted projections of gas density,
+temperature, and metallicity at redshifts 15, 12, 10, 8, and 7 in
+Figure \ref{fig:evo-mosaic}.  Most apparent is the photo-heating of
+IGM over this redshift range, where the ionized fraction is 0.XX at
+$z=7$.  The metallicity projections show the growth of metal-enriched
+bubbles, starting first with enrichment from Pop III stars.  Then as
+time progresses, the haloes enriched within these bubbles above $Z_{\rm
+  cr}$ transition to Pop II star formation, enriching their host halo
+and surrounding IGM.  In Fig. \ref{fig:mass_fn}, we show the halo mass
+function, agreeing well with the analytic halo mass function of
+\citet{Warren06}.  We identify the haloes with a friends-of-friends
+(FOF) algorithm \citep{Davis85}.  The excess of low-mass haloes below
+$M_{\rm DM} = 2 \times 10^6 \Ms$ is most likely associated with the
+biased region in the lower-right region in the projections.
+Furthermore, the uncertainities in different analytic halo mass
+functions \citep[e.g., see][for a comparison]{Reed07} and halo
+identification are comparable than these differences.  Also in this
+Figure, we display the galaxy luminosities with respect to halo DM
+mass found with the FOF halo finder.  Our fidicual model contains 38
+galaxies with a total of 3640 Pop II star clusters and captures the
+formation of 333 Pop III stars.  Note that the most massive halo
+($M_{\rm DM} = 5.2 \times 10^8 \Ms$) is undergoing a starburst at
+$z=7$ and has a high $M/L = 3$.  The lower mass galaxies show a spread
+in M/L over two orders of magnitude, similar to the observations of
+local dSph galaxies \citep[e.g.][]{Strigari08}.
+
+We split our presentation into two sets of analyses.  In one, we focus
+on the evolution of the individual halo and galaxy properties of the
+10 most massive haloes at $z=7$ to better understand their formation
+process and progenitors.  Second, we analyze the statistics of the
+star formation and metal enrichment in all 38 galaxies.  We start by
+presenting the change in the global halo properties, followed by their
+metal enrichment histories.  Lastly we detail their star formation
+histories, metallicity distribution functions, and star formation
+rates.
+
+\subsection{Halo mass evolution}
+
+To get a visual sense of the mass accretion and metal enrichment
+history of the 10 most massive haloes, we show their density-weighted
+projections of gas density, temperature, and composite Pop II+III
+metallicity at redshifts 7, 8, and 10 in
+Fig. \ref{fig:z7-mosaic}--\ref{fig:z10-mosaic}, respectively.  One
+common feature of all of the halos represented in these Figure is that
+they are embedded in a preheated IGM with the exception of Halo 7 at
+$z=10$.  Prior radiative feedback in either the host or nearby halos
+created \hii~regions that encompass these halos.  For \hii~regions
+without sustained star formation, these so-called relic \hii~regions
+recombine and radiatively cool down to $T = 10^3$ K.  Within the
+virial radius, one can see that our simulations capture the
+multi-phase ISM.  In the density projections, the effects of
+photo-evaporation and cloud crushing are clearly seen, which are
+caused by the stellar radiative and mechanical feedback, respectively.
+The filaments adjacent to the halos are photo-heated to $T = 1-3
+\times 10^4$ K, and then their gas escapes into the IGM no longer
+being pressure equilibrium with the gravitational potential of the
+filament, i.e. Jeans smoothing.  Furthermore, neighboring halos are
+photo-evaporated \citep[see][for the level of halo
+photo-evaporation]{Wise08_Reion}, resulting in the suppression of
+gas-rich satellite haloes.  A good illustration of photo-evaporation
+in progress is the cometary structure in the bottom-center of the
+density projection of Halo 4 at $z=7$.
+
+\li Something is wrong with the progenitor finder with Halo 9 at $t =
+500$ Myr.  See the extreme jump in mass and decrease in gas fraction?
+
+In Fig. \ref{fig:massevo}, we show the total halo mass $M_{\rm tot}$,
+stellar mass $M_\star$, and gas fraction $f_{\rm gas} = M_{\rm gas} /
+M_{\rm tot}$ of the most massive halos as a function of time.  We
+define the halo as a sphere with a radius $r_{200}$, centered on the
+DM center-of-mass, with an overdensity of 200 times the cosmic mean
+density.  We identify the progenitors of these halos by searching for
+the halo in the previous output with the greatest number of shared
+particles (all particles in \enzo~have unique identification numbers).
+The mass accretion histories of the halos are not atypical from ones
+found in cosmological simulations with periods of smooth accretion
+from the IGM and filaments with major mergers occasionally occurs,
+appearing as jumps in $M_{\rm halo}(z)$.
+
+Even from these visual representations of the data, it is clear that
+almost all of the halos are gas-poor with outflows from Pop III star
+formation and PISNe having the greatest effect.
 
@@
   \plottwo{z7-mosaic0.eps}{z7-mosaic1.eps}
-  \caption{\label{fig:z7-mosaic} Redshift 7.}
+  \caption{\label{fig:z7-mosaic} Density-weighted projections of
+    density (left), temperature (center), and metallicity (right) of
+    the 10 most massive haloes at $z=7$.  The field of view is 5 proper
+    kpc, and the circles have a radius of $r_{200}$.  The composite
+    metallicity images are constructed in the same fashion as
+    Fig. \ref{fig:evo-mosaic}.}
 \end{figure*}
@@
   \plottwo{z8-mosaic0.eps}{z8-mosaic1.eps}
-  \caption{\label{fig:z8-mosaic} Redshift 8.}
+  \caption{\label{fig:z8-mosaic} Same as Fig. \ref{fig:z7-mosaic} but
+    at $z=8$, showing the progenitors of the 10 most massive haloes at
+    $z=7$.}
 \end{figure*}
@@
   \plottwo{z10-mosaic0.eps}{z10-mosaic1.eps}
-  \caption{\label{fig:z10-mosaic} Redshift 10.}
+  \caption{\label{fig:z10-mosaic} Same as Fig. \ref{fig:z8-mosaic} at
+    $z=10$.}
 \end{figure*}
-
-\subsection{Halo mass evolution}
 
@@
 
-\subsection{Negative feedback from gas loss}
+\subsection{Unique details about individual haloes}
 
@@
 \label{sec:models}
+
+\subsection{Metal cooling}
+
+\subsection{Varying the critical metallicity}
+
+\subsection{Characteristic mass of the Pop III IMF}
+
+\subsection{Lyman-Werner radiation background}
+
+\subsection{Neglecting Pop III star formation}
+
+\subsection{Neglecting Pop III star formation and \hh~formation}
 

### 2011-01-22 ms.tex
Finished a draft of halo properties evo. section.  Added table with halo z=7 properties.

@@
 A fraction of Pop III stars enrich the surrounding IGM when
-they go supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
+they go supernova, which can happen in stars $\la 40~\Ms$ in Type II
 supernovae (SNe) or in stars roughly between 140 \Ms~and 260 \Ms~in
@@
 mixing into the dense gas are many dynamical times \citep{Cen08} for
-shock velocities $\lsim 100~\kms$.
+shock velocities $\la 100~\kms$.
 
@@
 \hh~formation on dust grains becomes efficient, allowing cooling to $T
-\lsim 100$ K \citep{Omukai05}.  The exact value of $Z_{\rm cr}$ has
+\la 100$ K \citep{Omukai05}.  The exact value of $Z_{\rm cr}$ has
 been constrained to be between $10^{-6} \zsun$ and $10^{-3.5} \zsun$.
@@
 calculated that Pop III stars can raise the mean metallicity to $-4.5
-\lsim$ [Z/H]\footnote{We use the conventional notation, [Z/H] $\equiv
-  \log(Z/H) - \log(Z_\odot/H_\odot)$.} $\lsim -3.5$ by redshift 15 in
+\la$ [Z/H]\footnote{We use the conventional notation, [Z/H] $\equiv
+  \log(Z/H) - \log(Z_\odot/H_\odot)$.} $\la -3.5$ by redshift 15 in
 the upper limit where all metal-free stars have $M = 200 \Ms$ and
@@
 cent.  They also conclude that stars enriched primarily by PISNe have
-[Ca/H] $\gsim$ --2.6, which could have been missed by some EMP
+[Ca/H] $\ga$ --2.6, which could have been missed by some EMP
 surveys.
@@
 (corresponding to an average density $\bar{\rho}_{\rm MC} \simeq
-1000\mu \cubecm$) and a radius $R_{\rm MC}$.  In this sphere, a
-fraction $c_\star = 0.07 f_{\rm cold}$ of the cold gas ($T < 10^3$ K)
-is converted into a star particle with mass $m_\star = c_\star
-(4\pi/3) \bar{\rho}_{\rm MC} R_{\rm MC}^3$.  We then replace the
-sphere with a uniform density $\rho_{\rm MC} = (1 - c_\star) /
-(Gt_{\rm dyn}^2)$ and temperature $T = 10^4$ K, which approximates the
-initial stages of an \hii~region.  Similar to the Pop III treatment,
-we merge any newly created particles within a radius $R_{\rm merge}$.
-We set the minimum mass of a star particle to $m_{\rm \star, min} =
-1000 \Ms$.  If the initial mass does not exceed $m_{\rm \star, min}$,
-the star particle does not provide any feedback and continues to
-accrete until it reaches $m_{\rm \star, min}$.  The star particles
-live for 20 Myr, the maximum lifetime of an OB star.  These stars
-generate the majority of the ionizing radiation and SNe feedback in
-stellar clusters, thus we ignore any feedback from lower mass stars.
+1000\mu \cubecm$) and a radius $R_{\rm MC}$, where $\mu$ is the mean
+molecular weight.  In this sphere, a fraction $c_\star = 0.07 f_{\rm
+  cold}$ of the cold gas ($T < 10^3$ K) is converted into a star
+particle with mass $m_\star = c_\star (4\pi/3) \bar{\rho}_{\rm MC}
+R_{\rm MC}^3$.  We then replace the sphere with a uniform density
+$\rho_{\rm MC} = (1 - c_\star) / (Gt_{\rm dyn}^2)$ and temperature $T
+= 10^4$ K, which approximates the initial stages of an \hii~region.
+Similar to the Pop III treatment, we merge any newly created particles
+within a radius $R_{\rm merge}$.  We set the minimum mass of a star
+particle to $m_{\rm \star, min} = 1000 \Ms$.  If the initial mass does
+not exceed $m_{\rm \star, min}$, the star particle does not provide
+any feedback and continues to accrete until it reaches $m_{\rm \star,
+  min}$.  The star particles live for 20 Myr, the maximum lifetime of
+an OB star.  These stars generate the majority of the ionizing
+radiation and SNe feedback in stellar clusters, thus we ignore any
+feedback from lower mass stars.
 
@@
 square profile, centered on all star particles.  In haloes with $M
-\gsim 10^8 \Ms$, the \hh~column density may become large enough to
+\ga 10^8 \Ms$, the \hh~column density may become large enough to
 self-shield itself from LW radiation \citep{Wise08_Gal}.  Thus we may
@@
   \caption{\label{fig:uvb} Time evolution of the Lyman-Werner
-    background, calculated with the \citet{Wise05} model.}
+    background in units of $J_{21} = 10^{-21}$ \emis, calculated with
+    the \citet{Wise05} model.  See eq. (\ref{eqn:uvb}) for its
+    functional fit.}
 \end{figure}
@@
   optical depth to Thompson scattering, to calculate the LW background
-  intensity, plotted in Figure \ref{fig:uvb}.  In this semi-analytical
+  intensity, plotted in Fig. \ref{fig:uvb}.  In this semi-analytical
   model, we use a Pop III stellar mass of 100 \Ms, star formation
@@
 
+\input table1.tex
+
 Here we present the gaseous and stellar evolution of the high-redshift
@@
 temperature, and metallicity at redshifts 15, 12, 10, 8, and 7 in
-Figure \ref{fig:evo-mosaic}.  Most apparent is the photo-heating of
+Fig. \ref{fig:evo-mosaic}.  Most apparent is the photo-heating of
 IGM over this redshift range, where the ionized fraction is 0.XX at
@@
 10 most massive haloes at $z=7$ to better understand their formation
-process and progenitors.  Second, we analyze the statistics of the
-star formation and metal enrichment in all 38 galaxies.  We start by
-presenting the change in the global halo properties, followed by their
-metal enrichment histories.  Lastly we detail their star formation
+process and progenitors.  We list the global properties of these
+haloes at $z = 7$ in Table \ref{tab:halos}.  Second, we analyze the
+statistics of the star formation and metal enrichment in all 38
+galaxies.  We start by presenting the change in the global halo
+properties, followed by a description of their star formation
 histories, metallicity distribution functions, and star formation
-rates.
+rates.  We then present their metal enrichment and lastly comment on
+unique details of individual haloes.
 
-\subsection{Halo mass evolution}
-
-To get a visual sense of the mass accretion and metal enrichment
-history of the 10 most massive haloes, we show their density-weighted
-projections of gas density, temperature, and composite Pop II+III
-metallicity at redshifts 7, 8, and 10 in
-Fig. \ref{fig:z7-mosaic}--\ref{fig:z10-mosaic}, respectively.  One
-common feature of all of the halos represented in these Figure is that
-they are embedded in a preheated IGM with the exception of Halo 7 at
-$z=10$.  Prior radiative feedback in either the host or nearby halos
-created \hii~regions that encompass these halos.  For \hii~regions
-without sustained star formation, these so-called relic \hii~regions
-recombine and radiatively cool down to $T = 10^3$ K.  Within the
-virial radius, one can see that our simulations capture the
-multi-phase ISM.  In the density projections, the effects of
-photo-evaporation and cloud crushing are clearly seen, which are
-caused by the stellar radiative and mechanical feedback, respectively.
-The filaments adjacent to the halos are photo-heated to $T = 1-3
-\times 10^4$ K, and then their gas escapes into the IGM no longer
-being pressure equilibrium with the gravitational potential of the
-filament, i.e. Jeans smoothing.  Furthermore, neighboring halos are
-photo-evaporated \citep[see][for the level of halo
-photo-evaporation]{Wise08_Reion}, resulting in the suppression of
-gas-rich satellite haloes.  A good illustration of photo-evaporation
-in progress is the cometary structure in the bottom-center of the
-density projection of Halo 4 at $z=7$.
-
-\li Something is wrong with the progenitor finder with Halo 9 at $t =
-500$ Myr.  See the extreme jump in mass and decrease in gas fraction?
-
-In Fig. \ref{fig:massevo}, we show the total halo mass $M_{\rm tot}$,
-stellar mass $M_\star$, and gas fraction $f_{\rm gas} = M_{\rm gas} /
-M_{\rm tot}$ of the most massive halos as a function of time.  We
-define the halo as a sphere with a radius $r_{200}$, centered on the
-DM center-of-mass, with an overdensity of 200 times the cosmic mean
-density.  We identify the progenitors of these halos by searching for
-the halo in the previous output with the greatest number of shared
-particles (all particles in \enzo~have unique identification numbers).
-The mass accretion histories of the halos are not atypical from ones
-found in cosmological simulations with periods of smooth accretion
-from the IGM and filaments with major mergers occasionally occurs,
-appearing as jumps in $M_{\rm halo}(z)$.
-
-Even from these visual representations of the data, it is clear that
-almost all of the halos are gas-poor with outflows from Pop III star
-formation and PISNe having the greatest effect.
+\subsection{Time evolution of halo properties}
 
@@
 
+To get a visual sense of the mass accretion and metal enrichment
+history of the 10 most massive haloes, we show their density-weighted
+projections of gas density, temperature, and composite Pop II+III
+metallicity at redshifts 7, 8, and 10 in
+Fig. \ref{fig:z7-mosaic}--\ref{fig:z10-mosaic}, respectively.  One
+common feature of all of the halos represented in these Figures is
+that they are embedded in a preheated IGM with the exception of Halo 7
+at $z=10$.  Prior radiative feedback in either the host or nearby
+halos created \hii~regions that encompass these halos.  For
+\hii~regions without sustained star formation, these so-called relic
+\hii~regions recombine and radiatively cool down to $T = 10^3$ K.
+Within the virial radius, one can see that our simulations capture the
+multi-phase ISM.  In the density projections, the effects of
+photo-evaporation and cloud crushing are clearly seen, which are
+caused by the stellar radiative and mechanical feedback, respectively.
+The filaments adjacent to the halos are photo-heated to $T = 1-3
+\times 10^4$ K, and then their gas escapes into the IGM no longer
+being pressure equilibrium with the gravitational potential of the
+filament, i.e. Jeans smoothing.  Furthermore, neighboring halos are
+photo-evaporated \citep[see][for the level of halo
+  photo-evaporation]{Wise08_Reion}, resulting in the suppression of
+gas-rich satellite haloes.  A good illustration of photo-evaporation
+in progress is the cometary structure in the bottom-center of the
+density projection of Halo 4 at $z=7$.
+
+%% \li Something is wrong with the progenitor finder with Halo 9 at $t =
+%% 500$ Myr.  See the extreme jump in mass and decrease in gas fraction?
+
+\subsubsection{Halo mass evolution}
+
 \begin{figure}
   \plottwo{history0.eps}{history5.eps}
-  \caption{\label{fig:massevo} Mass evolution.}
+  \caption{\label{fig:massevo} Time evolution of the total halo mass
+    (top panels), stellar mass (middle panels), and gas fraction
+    (bottom panels; $M_{\rm gas} / M_{\rm tot}$) of the 10 most
+    massive halos at $z=7$.  The cosmic mean gas fraction $\Omega_b /
+    \Omega_M$ is marked by a horizontal dotted line in the bottom
+    panels.}
 \end{figure}
+
+In the top panels of Fig. \ref{fig:massevo}, we show the total halo
+mass $M_{\rm tot}$ of the most massive halos as a function of time.
+We define the halo as a sphere with a radius $r_{200}$, centered on
+the DM center-of-mass, with an overdensity of 200 times the cosmic
+mean density.  The mass accretion histories of the halos are not
+atypical from ones found in cosmological simulations with periods of
+smooth accretion from the IGM and filaments with major mergers
+occasionally occurs, appearing as jumps in $M_{\rm halo}(z)$.  The
+halo mass histories are well described by the analytic expression
+\citep{Wechsler02},
+%
+\begin{equation}
+  \label{eqn:mhalo}
+  M_{\rm halo}(a) = M_0 \exp \left[-2a_c\left(\frac{a_0}{a} -
+    1\right)\right],
+\end{equation}
+%
+where $a = 1/(1+z)$ is the scale factor, $M_0 = M_{\rm halo}(a_0)$,
+and $a_c$ describes the rate of mass accretion.  The fitted values
+values are listed in Table \ref{tab:halos} with $a_0 = 1/8$.
+
+\subsubsection{Gas fraction evolution}
+
+In the bottom panels of Fig. \ref{fig:massevo}, we show the gas
+fraction $f_{\rm gas}(z) = M_{\rm gas} / M_{\rm tot}$ of these haloes.
+The time evolution of the gas fraction is unique for each halo, but
+there are some general trends.  Before any star formation occurs in
+the halo, the gas fraction is near the cosmic fraction $\Omega_b /
+\Omega_M$.  Then afterwards it decreases because one or more of the
+three following processes (in order of decreasing impact): a PISN
+explosion within the halo, Pop III stellar radiation within the halo,
+and photo-evaporation from nearby star formation.  Cloud crushing due
+to a nearby SN blastwave is also a possiblity if the halo mass is
+small, but it is not as prevalent.  Complicating the scenario,
+external feedback can also trigger star formation as they compress the
+gas in the halo.  Even from the visual representations of the data in
+Figs. \ref{fig:z7-mosaic}--\ref{fig:z10-mosaic}, it is clear that
+almost all of the haloes and their environments are gas-poor with the
+except of the most massive halo that resides in a cosmologically
+overdense region.
+
+In the most massive halo (Halo 0), \fgas~peaks at 0.19 at $z \sim 13$
+because of a SN blastwave overrunning the halo and compressing the
+gas.  This blastwave enriches the halo and triggers Pop II star
+formation at $z=12$.  The ensuing radiative and mechanical feedback
+drives outflows from the halo, reducing \fgas~by half to 0.08 over 100
+Myr.  Afterwards this halo experiences a series of minor mergers and
+two major mergers with gas-rich haloes, raising \fgas~to 0.15 by
+$z=7$.  Halo 8 shows a similar recovery after a Pop III star forms and
+its associated PISN explodes at $z \sim 12$, driving \fgas~from 0.15
+to 0.01.  It slowly increases over the following 350 Myr to $\fgas =
+0.14$ at $z=7$ because of gas-rich mergers.  The other eight haloes
+remain relatively gas-poor ($0.05 \la \fgas \la 0.1$) after their
+first epoch of star formation.
+
+Because of the severity of gas loss from outflows created by Pop III
+stars and Jeans-smoothing of the adjacent filaments, the halo is
+dependent on mergers to replenish their gas supply
+\citep[cf.][]{Yoshida07, Wise08_Gal, Greif10}.  For a halo to accrete
+from a pre-heated IGM at a given time, it must exceed the `filtering
+mass' \citep{Hui98, Gnedin00},
+%
+\begin{equation}
+  \label{eqn:filtering}
+  M_{\rm F}^{2/3} = \frac{3}{a} \int^a_0 da^\prime M_{\rm J}^{2/3}(a^\prime)
+  \left[ 1 - \left(\frac{a^\prime}{a}\right)^{1/2} \right],
+\end{equation}
+where $M_{\rm J}$ is the time-dependent Jeans mass in the IGM.  We
+plot $M_{\rm F}$ in the pre-heated IGM\footnote{We define the
+  pre-heated IGM as regions with $x_e > 10^{-3}$ and $\rho/\bar{\rho}
+  < 10$, where $x_e$ is the electron fraction and $\bar{\rho}$ is the
+  mean cosmic density.} in Figure \ref{fig:filtering}.  Because the
+haloes that merge into Halo 0 had $M > M_{\rm F}$, its gas fraction
+recovers to nearly the cosmic fraction.  In contrast, all of the other
+massive haloes build up their masses through mergers with halos $M \la
+M_{\rm F}$ that cannot accrete from the pre-heated IGM.
+
+Halo 8 is an uncommon case of a halo with a high gas accretion rate.
+The merging haloes are still gas-rich because they have not hosted any
+(including Pop III) star formation.  They lie in the outskirts of the
+overdense region in the lower-right corner of the projections in
+Fig. \ref{fig:evo-mosaic}.  It is 4.5 proper kpc from Halo 0 at $z=7$,
+far enough away from the starbursting galaxies (the progenitors of
+Halo 0) to avoid significant photo-evaporation but is subjected to
+strong LW radiation, suppressing Pop III star formation.
+
+\subsection{Star formation}
+
+\subsubsection{Star formation histories}
+
+\subsubsection{Metallicity distribution function}
+
+\subsubsection{Star formation rates}
+
+\begin{figure}
+  \plotone{mlratios.eps}
+  \caption{\label{fig:ML} Mass to light ratios.}
+\end{figure}
+
+\begin{figure*}
+  \epsscale{2.0}
+  \plotone{sfh1.eps}
+  \epsscale{1.0}
+  \caption{\label{fig:SFR} Star formation history.}
+\end{figure*}
 
@@
 
-\subsection{Star formation}
-
-\begin{figure}
-  \plotone{mlratios.eps}
-  \caption{\label{fig:ML} Mass to light ratios.}
-\end{figure}
-
-\begin{figure*}
-  \epsscale{2.0}
-  \plotone{sfh1.eps}
-  \epsscale{1.0}
-  \caption{\label{fig:SFR} Star formation history.}
-\end{figure*}
+%% \subsection{Negative feedback}
+%% \subsubsection{Gas loss from stellar feedback}
+%% \subsubsection{Lyman-Werner radiation}
 

### 2011-01-22 table1.tex
Finished a draft of halo properties evo. section.  Added table with halo z=7 properties.

\begin{table*}
\begin{minipage}{13cm}
\caption{Halo properties of the 10 most massive halos at $z=7$ in the
  fidicual model}
\label{tab:halos}
\begin{tabular}{@{}cccccccccccc}
\hline

Halo & $M_{\rm halo}/\Ms$ & $a_c$ & $f_{\rm gas}$ & $M_\star/\Ms$ & $N_{\rm
  III}$ & $M/L$ & [Z$_2$/H] & [Z$_3$/H] & $\lambda_{\rm DM}$ &
$\lambda_{\rm g}$ \\

(1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11) \\

\hline

0 & $1.0 \times 10^9$ & & 0.135 & $2.3 \times 10^6$ & 21 & 6.5 & -1.3 &
-2.7 & 0.046 & 0.055 \\

1 & $1.5 \times 10^8$ & & 0.111 & $1.5 \times 10^5$ & 3 & 34 & -2.4 &
-2.7 & 0.15 & 0.15 \\

2 & $1.0 \times 10^8$ & & 0.058 & $1.0 \times 10^4$ & 1 & 330 & -3.6 &
-3.1 & 0.060 & 0.046 \\

3 & $8.3 \times 10^7$ & & 0.072 & $7.5 \times 10^4$ & 4 & 16 & -2.7 &
-2.9 & 0.052 & 0.077 \\

4 & $8.1 \times 10^7$ & & 0.079 & $1.4 \times 10^5$ & 2 & 38 & -2.6 &
-2.7 & 0.041 & 0.067 \\

5 & $8.1 \times 10^7$ & & 0.058 & $6.8 \times 10^3$ & 4 & 660 & -3.6 &
-2.3 & 0.073 & 0.051 \\

6 & $5.8 \times 10^7$ & & 0.099 & $1.3 \times 10^4$ & 2 & 340 & -3.7 &
-2.6 & 0.047 & 0.082 \\

7 & $3.8 \times 10^7$ & & 0.045 & $2.2 \times 10^3$ & 1 & 440 & -3.8 &
-2.9 & 0.041 & 0.037 \\

8 & $3.0 \times 10^7$ & & 0.13 & $0.0$ & 1 & $\infty$ & -2.1 & -2.8 & 0.21 &
0.82 \\

9 & $3.8 \times 10^7$ & & 0.082 & $1.1 \times 10^4$ & 1 & 110 & -3.5 &
-3.3 & 0.082 & 0.11 \\

\hline
\end{tabular}
\medskip

Column (1): Halo number.  Column (2): Total halo mass.  Column (3):
Best fit $a_c$ in the halo mass accretion history,
eq. (\ref{eqn:mhalo}).  Column (4): Gas fraction.  Column (5): Pop II
stellar mass.  Column (6): Number of Pop III stars hosted in the
progenitors of the halo.  Column (7): Mass-to-light ratio.  Columns
(8,9): Mean metallicity from Pop II SNe and PISNe, respectively.
Columns (10,11): Spin parameters of the gas and DM, respectively.

\end{minipage}
\end{table*}

### 2011-01-23 ms.tex
Split M/L and mass fn. figure.  Added Pop III SF section as the first results section.

@@
 We stop the simulation at $z=7$ to avoid any large-scale modes with $r
-\sim L_{\rm box}$ entering the non-linear growth regime.  At the final
-redshift, this simulation has $1.4 \times 10^8$ computational cells.
+\sim L_{\rm box}/2$ entering the non-linear growth regime.  At the
+final redshift, this simulation has $1.4 \times 10^8$ computational
+cells.
 
@@
   the data are best fit with IMFs favoring stars with masses between
-  20--130 \Ms \citep{Umeda03, Tumlinson06}.
+  20--130 \Ms~\citep{Umeda03, Tumlinson06}.
 \item Lyman-Werner radiation background.  We use the semi-analytical
@@
 \begin{figure}
-  \plotone{Lstar.eps}
-  \caption{\label{fig:mass_fn} The top panel shows the halo mass
-    function of the simulated haloes (points) where the error bars are
-    Poisson noise and the solid line is the analytic halo mass
-    function of \citet{Warren06}.  The bottom panel depicts the galaxy
-    luminosities versus halo DM mass.  Overplotted are constant
-    mass-to-light ratios.  The large scatter at low halo masses are
-    similar to ones observed in local dSph galaxies.}
+  \plotone{mass_fn.eps}
+  \caption{\label{fig:mass_fn} Halo DM mass function of the simulated
+    haloes (points) where the error bars are Poisson noise and the
+    solid line is the analytic halo mass function of
+    \citet{Warren06}.}
 \end{figure}
@@
 temperature, and metallicity at redshifts 15, 12, 10, 8, and 7 in
-Fig. \ref{fig:evo-mosaic}.  Most apparent is the photo-heating of
-IGM over this redshift range, where the ionized fraction is 0.XX at
-$z=7$.  The metallicity projections show the growth of metal-enriched
-bubbles, starting first with enrichment from Pop III stars.  Then as
-time progresses, the haloes enriched within these bubbles above $Z_{\rm
+Fig. \ref{fig:evo-mosaic}.  Most apparent is the photo-heating of IGM
+over this redshift range, where the ionized fraction is 0.XX at $z=7$.
+The metallicity projections show the growth of metal-enriched bubbles,
+starting first with enrichment from Pop III stars.  Then as time
+progresses, the haloes enriched within these bubbles above $Z_{\rm
   cr}$ transition to Pop II star formation, enriching their host halo
@@
 Furthermore, the uncertainities in different analytic halo mass
-functions \citep[e.g., see][for a comparison]{Reed07} and halo
-identification are comparable than these differences.  Also in this
-Figure, we display the galaxy luminosities with respect to halo DM
-mass found with the FOF halo finder.  Our fidicual model contains 38
-galaxies with a total of 3640 Pop II star clusters and captures the
-formation of 333 Pop III stars.  Note that the most massive halo
-($M_{\rm DM} = 5.2 \times 10^8 \Ms$) is undergoing a starburst at
-$z=7$ and has a high $M/L = 3$.  The lower mass galaxies show a spread
-in M/L over two orders of magnitude, similar to the observations of
-local dSph galaxies \citep[e.g.][]{Strigari08}.
+functions \citep[see][for a comparison]{Reed07} and halo
+identification are comparable than these differences.  Our fidicual
+model contains 38 galaxies with a total of 3640 Pop II star clusters
+and captures the formation of 333 Pop III stars.
 
@@
 statistics of the star formation and metal enrichment in all 38
-galaxies.  We start by presenting the change in the global halo
-properties, followed by a description of their star formation
-histories, metallicity distribution functions, and star formation
-rates.  We then present their metal enrichment and lastly comment on
-unique details of individual haloes.
+galaxies.  We first present results on the frequency of Pop III star
+formation and the chemical enrichment from their PISNe.  We then focus
+on the evolution in the global halo properties, followed by a
+description of their Pop II star formation histories, metallicity
+distribution functions, and star formation rates.  We then present
+their metal enrichment and lastly comment on unique details of
+individual haloes.
+
+\subsection{Pop III star formation}
+
+\begin{figure}
+  \plotone{z3.eps}
+  \caption{\label{fig:zhalo3} Average halo metallicity from Pop III
+    SNe as a function of total halo mass.  Inhomogenous metal
+    enrichment causes the large spread in metallicity at low masses.
+    At $M_{\rm halo} > 3 \times 10^7 \Ms$, all halos are enriched by
+    Pop III SNe above [Z/H] $>$ --4.  The y-axis error bars show the
+    25\% and 75\% percentile values because the underlying
+    distribution is not Gaussian.}
+\end{figure}
+
+\begin{figure}
+  \plotone{Zhistory.eps}
+  \caption{\label{fig:Zevo} The time evolution of the average gas
+    metallicity from Pop II SNe (dashed) and Pop III SNe (dotted) and
+    average stellar metallicity (solid) of the 10 most massive haloes.
+    Note that a metallicity floor of [Z/H] $\sim -3$ exists in every
+    halo.}
+\end{figure}
+
+\subsubsection{Number of Pop III stars}
+
+In Table \ref{tab:halos} we list the number of the Pop III stars,
+$N_{\rm III}$, that have formed in the progenitors of the 10 most
+massive haloes.  For Haloes 1--9, between one and four Pop III stars
+formed in the progenitors.  The progenitors of Halo 0 hosted 21 Pop
+III stars, which is consistent with the number of Pop III stars per
+$10^8 \Ms$ halo seen in the lower mass haloes, considering that
+several such haloes merged to form the $10^9 \Ms$ halo.
+
+Given the idea of most minihaloes host a Pop III, these numbers appear
+low.  However there are a few processes that can suppress Pop III star
+formation:
+%
+\begin{enumerate}
+\item photo-dissociation of \hh~\citep{Dekel87, Haiman00, Machacek01},
+\item photo-evaporation of minihaloes \citep{Shapiro04, whalen08}, and
+\item metal enrichment from nearby (PI)SNe \citep{Wise08_Gal, Greif10,
+  Trenti09}.
+\end{enumerate}
+We observe all of these affecting Pop III star formation in the
+simulation, confirming that negative feedback plays an important role
+in metal-free star formation.
+
+\subsubsection{Metal enrichment from pair-instability SNe}
 
@@
 
+\begin{figure}
+  \vspace{200pt}
+  \caption{\label{fig:filtering} Halo filtering mass.}
+\end{figure}
+
 In the bottom panels of Fig. \ref{fig:massevo}, we show the gas
@@
 
-\subsection{Star formation}
+\subsection{Pop II star formation}
 
-\subsubsection{Star formation histories}
+\begin{figure*}
+  \epsscale{2.0}
+  \plotone{sfh1.eps}
+  \epsscale{1.0}
+  \caption{\label{fig:SFH} The scatter plots show the Pop II star
+    formation history as a function of metallicity for the 10 most
+    massive halos.  Halo 8 is not shown because it contains no stars.
+    Each circle represents a star particle, whose area is proportional
+    to its mass.  The open circles in the upper right represent $M =
+    10^3$, $10^4$, and $10^5$ \Ms.  The dashed lines in the Halo 0
+    panel guide the eye to two stellar populations that were formed in
+    two satellite halos, merging at $z=7.5$.  The upper histogram
+    shows the star formation rate.  The right histogram depicts the
+    Pop II metallicity distribution function.}
+\end{figure*}
 
-\subsubsection{Metallicity distribution function}
-
-\subsubsection{Star formation rates}
+\begin{figure}
+  \plotone{Lstar.eps}
+  \caption{\label{fig:Lstar} Galaxy luminosities versus total halo
+    mass.  Overplotted are constant mass-to-light ratios.  The large
+    scatter at low halo masses are similar to ones observed in local
+    dSph galaxies.}
+\end{figure}
 
@@
 
-\begin{figure*}
-  \epsscale{2.0}
-  \plotone{sfh1.eps}
-  \epsscale{1.0}
-  \caption{\label{fig:SFR} Star formation history.}
-\end{figure*}
+\subsubsection{Star formation histories}
 
-\subsection{Metal enrichment}
+The scatter plots of Fig. \ref{fig:SFH} show the Pop II star formation
+history as a function of metallicity for the 10 most massive halos.
+
+We now focus on the star formation rates (SFR) and metallicity
+distribution functions (MDF) of these histories, collapsing the
+stellar population in the metallicity and time axes, respectively.
+
+\subsubsection{Star formation rates}
+
+\subsubsection{Metallicity distribution functions}
+
+\subsubsection{Mass-to-light ratios}
+\label{sec:mlratios}
+
+Note that the most massive halo ($M_{\rm tot} = 10^9 \Ms$) is
+undergoing a starburst at $z=7$ and has a relatively high $M/L = 6$.
+The lower mass galaxies show a spread in M/L over two orders of
+magnitude, similar to the Sloan Digital Sky Survey (SDSS) observations
+of local dSph galaxies \citep[e.g.][]{Strigari08}.
+
+\subsubsection{Metal enrichment}
 
 \begin{figure}
-  \plotone{Zhistory.eps}
-  \caption{\label{fig:Zevo} Metal evolution.}
-\end{figure}
-
-\begin{figure}
-  \plottwo{z2.eps}{z3.eps}
-  \caption{\label{fig:zhalo} Halo metallicities.}
+  \plotone{z2.eps}
+  \caption{\label{fig:zhalo2} Halo metallicities.}
 \end{figure}

### 2011-01-26 ms.tex
Adding some text for Pop III enrichment section.

@@
   \caption{\label{fig:evo-mosaic} Evolution of the entire simulation
-    volume at redshifts 15, 12, 10, 8, and 7 (left to right).
-    Pictured here are the density-weighted projections of density
-    (top), temperature (middle), and metallicity (bottom).  Note how
-    the stellar radiative feedback from low-mass galaxies reionize
-    the majority of the volume.  The metallicity projections are a
-    composite image of metals originating from Pop II (blue) and III
-    (red) stars with magneta indicdating a mixture of the two.}
+    volume ($L_{\rm box} = 1$ Mpc) at redshifts 15, 12, 10, 8, and 7
+    (left to right).  Pictured here are the density-weighted
+    projections of density (top), temperature (middle), and
+    metallicity (bottom).  Note how the stellar radiative feedback
+    from low-mass galaxies reionize the majority of the volume.  The
+    metallicity projections are a composite image of metals
+    originating from Pop II (blue) and III (red) stars with magneta
+    indicdating a mixture of the two.}
 \end{figure*}
@@
 \begin{figure}
+  \plotone{Zhistory.eps}
+  \caption{\label{fig:Zevo} The time evolution of the average gas
+    metallicity from Pop II SNe (dashed) and Pop III SNe (dotted) and
+    average stellar metallicity (solid) of the 10 most massive haloes.
+    Note that a metallicity floor of [Z/H] $\sim -3$ exists in every
+    halo.}
+\end{figure}
+
+\begin{figure}
   \plotone{z3.eps}
@@
     distribution is not Gaussian.}
-\end{figure}
-
-\begin{figure}
-  \plotone{Zhistory.eps}
-  \caption{\label{fig:Zevo} The time evolution of the average gas
-    metallicity from Pop II SNe (dashed) and Pop III SNe (dotted) and
-    average stellar metallicity (solid) of the 10 most massive haloes.
-    Note that a metallicity floor of [Z/H] $\sim -3$ exists in every
-    halo.}
 \end{figure}
@@
 \item photo-evaporation of minihaloes \citep{Shapiro04, whalen08}, and
-\item metal enrichment from nearby (PI)SNe \citep{Wise08_Gal, Greif10,
-  Trenti09}.
+\item metal enrichment from intrinsic and nearby (pair-instability)
+  SNe \citep{Wise08_Gal, Trenti09, Greif10}.
 \end{enumerate}
@@
 \subsubsection{Metal enrichment from pair-instability SNe}
+
+We plot the evolution of the mass-averaged gas and stellar metallicity
+in the massive halos in Fig. \ref{fig:Zevo}.  Here we focus on the
+metallicity provided from Pop III SNe, \zthree.  The most relevant
+aspect of these data is the existence of a metallicity floor $\zthree
+\sim -3$ in all of the haloes.  The haloes can either be enriched from
+hosting a PISNe or one in a nearby halo.  In the time evolution of the
+metallicity, the former scenario appears as an initial peak in
+\zthree~then gradually decreasing, which is seen in Haloes 1-3 and 6-9
+with two enrichment events occurring in Halo 6.  This peak happens
+because the halo is gas-poor from the Pop III radiative feedback with
+$M_{\rm gas} \sim 10^4$ (also see Sec. \ref{sec:fgas}) and the PISN
+provides $\sim 100 \Ms$ of heavy elements, resulting in $\zthree \sim
+0$.  The ensuing blastwave drives out the remainder of the gas,
+leaving behind a diffuse medium, enriched to $\zthree \ga -3$.
+Because the blastwave rapidly exits the halo on timescales smaller
+than the time sampling in Fig. \ref{fig:Zevo}, the maximum mean
+metallicity is missed in most haloes but is captured in Halo 2.
+
+Gas in satellite haloes and adjacent filaments are enriched to a
+lesser extent because these high-density regions are resistant to
+impinging metal-rich blastwaves \citep[cf.][]{Cen08}.  However if the
+nearby SNe is close enough when the shock velocities are still high
+($\ga 100~\kms$), the dense gas in the minihalo can be enriched to
+similar metallicities.  This scenario appears as prompt enrichment but
+without the temporary peak in metallicity as the blastwave overtakes
+the halo, and this occurs in Haloes 0, 4, and 5 with Halo 5 being
+enriched by two nearby PISNe.
+
+In Figure \ref{fig:zhalo3}, we show the average \zthree~in all haloes
+as a function of halo mass at $z =$ 7, 8, 9, and 10, and it is
+strongly dependent on halo mass.  The \zthree~error bars mark the 25\%
+and 75\% percentiles of the distribution at $M = M_{\rm halo}$ because
+the underlying distribution is not necessarily Gaussian at all halo
+masses.  Above $3 \times 10^7 \Ms$, all haloes enriched to $\zthree
+\ga -4$ with little time evolution, further illustrating the
+metallicity floor.  Below this halo mass, the distribution is roughly
+bimodal composed of pristine and metal-enriched halos.
+
+\li Add figure and describe metal filling fraction evolution.
 
@@
 \subsubsection{Gas fraction evolution}
+\label{sec:fgas}
 

### 2011-02-02 ms.tex
Adding figures for filtering mass and metal filling fractions.  Almost finished with the results section except for the halo details subsection.

@@
 final redshift, this simulation has $1.4 \times 10^8$ computational
-cells.
+cells and required 250,000 CPU hours, using 512 cores.
 
@@
 coexist with the dark matter halo center with limited fragmentation
-occurring during their collapse; however \citet{2009Sci...325..601T}
-and \citet{Stacy10_Binary} have recently shown that Pop III binaries
-may form in a fraction of such haloes.
+occurring during their collapse; however recent work have shown that
+Pop III binaries and star clusters may form in a fraction of such
+haloes \citep{2009Sci...325..601T, Stacy10_Binary, Greif11_P3Cluster}.
 
@@
 resolution of the grid is less than 10/3 pc, we distribute the energy
-into a $3^3$ cube surrounding the star particle.  In addition to
-numerical stability, energy distribution across several cells instead
-of a single cell has been shown to match cosmic SFRs better in galaxy
-simulations at lower redshifts \citep{Smith10}.
+into a $3^3$ cube surrounding the star particle.  In the same region,
+star particles also return ejected material with mass
+%
+\begin{equation}
+  \label{eqn:SNmass}
+  \Delta m_{\rm ej} = \frac{0.25 \; \Delta t \; M_\star} 
+         {t_0 - 4\;\mathrm{Myr}}
+\end{equation}
+back to the grid at every timestep on the finest AMR level.  Here
+$t_0$ = 20 Myr is the lifetime of the star particle.  This ejected gas
+has solar metallicity $Z = 0.02$, resulting in a total metal yield $y
+= 0.005$.  In addition to numerical stability, energy distribution
+across several cells instead of a single cell has been shown to match
+cosmic SFRs better in galaxy simulations at lower redshifts
+\citep{Smith10}.
 
@@
 
-We perform eight different simulations with the same initial
+We perform nine different simulations with the same initial
 conditions.  The fiducial model considers (a) primordial cooling with
 9 species of hydrogen, helium, and molecular hydrogen, (b) a Pop III
-IMF characteristic mass $M_{\rm char}$ = 100 \Ms, and (c) Pop II and
-Pop III star formation.  We vary this model with the following
-changes:
+IMF characteristic mass $M_{\rm char}$ = 100 \Ms, (c) Pop II and Pop
+III star formation, and (d) a critical metallicity of [Z/H] = --4.  We
+vary this model with the following changes:
 
 \begin{enumerate}
-\item Radiative cooling from metal species.  We calculate a cooling
-  curve with CLOUDY \citep{CLOUDY} and use the method of
+\item Additional radiative cooling from metal species.  We calculate a
+  cooling curve with CLOUDY \citep{CLOUDY} and use the method of
   \citep{2008MNRAS.385.1443S}.  Solar abundances were used in the
@@
   these lower metallicities \citep{Omukai05, Schneider06_Frag}.
+\item Higher Pop II metal yield of $y = 0.025$ that is consistent with
+  average values in the Milky Way \citep{Madau96}.
 \item Pop III IMF characteristic mass $M_{\rm char}$ = 40 \Ms.  Using
@@
     \label{eqn:uvb}
-    \log J_{21}(z) = A + Bz - Cz^2 + Dz^3 - Ez^4,
+    \log_{10} J_{21}(z) = A + Bz + Cz^2 + Dz^3 + Ez^4,
   \end{equation}
 %
-  where $(A,B,C,D,E) = (-2.356, 0.4562, 0.02680, 5.882 \times 10^{-4},
+  where $(A,B,C,D,E) = (-2.356, 0.4562, -0.02680, 5.882 \times 10^{-4},
   -5.056 \times 10^{-6})$ and $J_{21}$ is the specific intensity in
@@
 Fig. \ref{fig:evo-mosaic}.  Most apparent is the photo-heating of IGM
-over this redshift range, where the ionized fraction is 0.XX at $z=7$.
-The metallicity projections show the growth of metal-enriched bubbles,
-starting first with enrichment from Pop III stars.  Then as time
-progresses, the haloes enriched within these bubbles above $Z_{\rm
-  cr}$ transition to Pop II star formation, enriching their host halo
-and surrounding IGM.  In Fig. \ref{fig:mass_fn}, we show the halo mass
-function, agreeing well with the analytic halo mass function of
-\citet{Warren06}.  We identify the haloes with a friends-of-friends
-(FOF) algorithm \citep{Davis85}.  The excess of low-mass haloes below
-$M_{\rm DM} = 2 \times 10^6 \Ms$ is most likely associated with the
-biased region in the lower-right region in the projections.
-Furthermore, the uncertainities in different analytic halo mass
-functions \citep[see][for a comparison]{Reed07} and halo
-identification are comparable than these differences.  Our fidicual
-model contains 38 galaxies with a total of 3640 Pop II star clusters
-and captures the formation of 333 Pop III stars.
+over this redshift range, where the mass- and volume-averaged ionized
+fraction are 0.431 and 0.417 at $z=7$, respectively.  The metallicity
+projections show the growth of metal-enriched bubbles, starting first
+with enrichment from Pop III stars.  Then as time progresses, the
+haloes enriched within these bubbles above $Z_{\rm cr}$ transition to
+Pop II star formation, enriching their host halo and surrounding IGM.
+In Fig. \ref{fig:mass_fn}, we show the halo mass function, agreeing
+well with the analytic halo mass function of \citet{Warren06}.  We
+identify the haloes with a friends-of-friends (FOF) algorithm
+\citep{Davis85}.  The excess of low-mass haloes below $M_{\rm DM} = 2
+\times 10^6 \Ms$ is most likely associated with the biased region in
+the lower-right region in the projections.  Furthermore, the
+uncertainities in different analytic halo mass functions
+\citep[see][for a comparison]{Reed07} and halo identification are
+comparable than these differences.  Our fidicual model contains 38
+galaxies with a total of 3640 Pop II star clusters and captures the
+formation of 333 Pop III stars.
 
@@
 process and progenitors.  We list the global properties of these
-haloes at $z = 7$ in Table \ref{tab:halos}.  Second, we analyze the
-statistics of the star formation and metal enrichment in all 38
-galaxies.  We first present results on the frequency of Pop III star
-formation and the chemical enrichment from their PISNe.  We then focus
-on the evolution in the global halo properties, followed by a
-description of their Pop II star formation histories, metallicity
-distribution functions, and star formation rates.  We then present
-their metal enrichment and lastly comment on unique details of
-individual haloes.
-
-\subsection{Pop III star formation}
-
-\begin{figure}
-  \plotone{Zhistory.eps}
-  \caption{\label{fig:Zevo} The time evolution of the average gas
-    metallicity from Pop II SNe (dashed) and Pop III SNe (dotted) and
-    average stellar metallicity (solid) of the 10 most massive haloes.
-    Note that a metallicity floor of [Z/H] $\sim -3$ exists in every
-    halo.}
-\end{figure}
-
-\begin{figure}
-  \plotone{z3.eps}
-  \caption{\label{fig:zhalo3} Average halo metallicity from Pop III
-    SNe as a function of total halo mass.  Inhomogenous metal
-    enrichment causes the large spread in metallicity at low masses.
-    At $M_{\rm halo} > 3 \times 10^7 \Ms$, all halos are enriched by
-    Pop III SNe above [Z/H] $>$ --4.  The y-axis error bars show the
-    25\% and 75\% percentile values because the underlying
-    distribution is not Gaussian.}
-\end{figure}
-
-\subsubsection{Number of Pop III stars}
+haloes in Table \ref{tab:halos}.  Second, we analyze the statistics of
+the star formation and metal enrichment in all 38 galaxies.  We first
+present results on the frequency of Pop III star formation and the
+chemical enrichment from their PISNe.  We then focus on the evolution
+in the global halo properties, followed by a description of their Pop
+II star formation histories, metallicity distribution functions, and
+star formation rates.  We then present their metal enrichment and
+lastly comment on unique details of individual haloes.
+
+\subsection{Number of Population III stars}
 
@@
 in metal-free star formation.
-
-\subsubsection{Metal enrichment from pair-instability SNe}
-
-We plot the evolution of the mass-averaged gas and stellar metallicity
-in the massive halos in Fig. \ref{fig:Zevo}.  Here we focus on the
-metallicity provided from Pop III SNe, \zthree.  The most relevant
-aspect of these data is the existence of a metallicity floor $\zthree
-\sim -3$ in all of the haloes.  The haloes can either be enriched from
-hosting a PISNe or one in a nearby halo.  In the time evolution of the
-metallicity, the former scenario appears as an initial peak in
-\zthree~then gradually decreasing, which is seen in Haloes 1-3 and 6-9
-with two enrichment events occurring in Halo 6.  This peak happens
-because the halo is gas-poor from the Pop III radiative feedback with
-$M_{\rm gas} \sim 10^4$ (also see Sec. \ref{sec:fgas}) and the PISN
-provides $\sim 100 \Ms$ of heavy elements, resulting in $\zthree \sim
-0$.  The ensuing blastwave drives out the remainder of the gas,
-leaving behind a diffuse medium, enriched to $\zthree \ga -3$.
-Because the blastwave rapidly exits the halo on timescales smaller
-than the time sampling in Fig. \ref{fig:Zevo}, the maximum mean
-metallicity is missed in most haloes but is captured in Halo 2.
-
-Gas in satellite haloes and adjacent filaments are enriched to a
-lesser extent because these high-density regions are resistant to
-impinging metal-rich blastwaves \citep[cf.][]{Cen08}.  However if the
-nearby SNe is close enough when the shock velocities are still high
-($\ga 100~\kms$), the dense gas in the minihalo can be enriched to
-similar metallicities.  This scenario appears as prompt enrichment but
-without the temporary peak in metallicity as the blastwave overtakes
-the halo, and this occurs in Haloes 0, 4, and 5 with Halo 5 being
-enriched by two nearby PISNe.
-
-In Figure \ref{fig:zhalo3}, we show the average \zthree~in all haloes
-as a function of halo mass at $z =$ 7, 8, 9, and 10, and it is
-strongly dependent on halo mass.  The \zthree~error bars mark the 25\%
-and 75\% percentiles of the distribution at $M = M_{\rm halo}$ because
-the underlying distribution is not necessarily Gaussian at all halo
-masses.  Above $3 \times 10^7 \Ms$, all haloes enriched to $\zthree
-\ga -4$ with little time evolution, further illustrating the
-metallicity floor.  Below this halo mass, the distribution is roughly
-bimodal composed of pristine and metal-enriched halos.
-
-\li Add figure and describe metal filling fraction evolution.
 
@@
 \begin{figure}
-  \vspace{200pt}
-  \caption{\label{fig:filtering} Halo filtering mass.}
+  \plotone{mfilter.eps}
+  \caption{\label{fig:filtering} The halo filtering mass (thick solid;
+    eq. \ref{eqn:filtering}) that estimates the minimum halo mass that
+    can host star formation when accreting from a pre-heated IGM.  The
+    thick dashed lines shows the Jeans mass of the ionized regions of
+    the IGM.  We compare the halo mass histories of Haloes 0 and 4
+    (thin dotted and dot-dashed), illustrating that star formation can
+    commence after accreting sufficient mass or be suppressed when the
+    filtering mass grows faster than the halo mass.}
 \end{figure}
@@
   < 10$, where $x_e$ is the electron fraction and $\bar{\rho}$ is the
-  mean cosmic density.} in Figure \ref{fig:filtering}.  Because the
-haloes that merge into Halo 0 had $M > M_{\rm F}$, its gas fraction
-recovers to nearly the cosmic fraction.  In contrast, all of the other
-massive haloes build up their masses through mergers with halos $M \la
-M_{\rm F}$ that cannot accrete from the pre-heated IGM.
+  mean cosmic density.} in Fig. \ref{fig:filtering}.  This shows that
+Halo 0 can accrete the pre-heated IGM to form stars after $z=11$ when
+$M > M_{\rm F}$.  Halo 4 accretes most of its gas at $z>12$, always
+above the filtering mass.  Afterwards it undergoes a quiescent
+accretion period, becoming comparable to $M_{\rm F}$ and losing the
+ability to accrete pre-heated IGM.
+
+The gas fraction in Halo 0 recovers to nearly the cosmic fraction
+because the haloes that merge into Halo 0 at $z=7.5$ have $M > M_{\rm
+  F}$, allowing these merging haloes to have cold gas reservoirs.  In
+contrast, all of the other massive haloes build up their masses
+through mergers with halos $M \la M_{\rm F}$ that cannot accrete from
+the pre-heated IGM.
 
@@
 
-\subsection{Pop II star formation}
+\subsection{Star formation in dwarf galaxies}
 
@@
   \caption{\label{fig:SFH} The scatter plots show the Pop II star
-    formation history as a function of metallicity for the 10 most
-    massive halos.  Halo 8 is not shown because it contains no stars.
-    Each circle represents a star particle, whose area is proportional
-    to its mass.  The open circles in the upper right represent $M =
-    10^3$, $10^4$, and $10^5$ \Ms.  The dashed lines in the Halo 0
-    panel guide the eye to two stellar populations that were formed in
-    two satellite halos, merging at $z=7.5$.  The upper histogram
-    shows the star formation rate.  The right histogram depicts the
-    Pop II metallicity distribution function.}
+    formation history as a function of stellar age $t_\star$ with
+    respect to metallicity for the 10 most massive halos.  Halo 8 is
+    not shown because it contains no stars.  Each circle represents a
+    star particle, whose area is proportional to its mass.  The open
+    circles in the upper right represent $M = 10^3$, $10^4$, and
+    $10^5$ \Ms.  The dashed lines in the Halo 0 panel guide the eye to
+    two stellar populations that were formed in two satellite halos,
+    merging at $z=7.5$.  The upper histogram shows the star formation
+    rate with each bar representing 5 Myr.  The right histogram
+    depicts the Pop II metallicity distribution function.}
 \end{figure*}
+
+Here we present the properties of the metal-enriched stellar
+population.  The SFHs of the 10 most massive haloes are shown in
+Fig. \ref{fig:SFH} in the plane of stellar age $t_\star$ and
+metallicity as scatter plots with each point representing a star
+particle and its size proportional to its mass.  Collapsing the data
+along the time and metallicity axes gives the metallicity distribution
+function (MDF) and star formation rate, respectively, also shown in
+the Figure.
+
+\subsubsection{Star formation histories}
+\label{sec:SFH}
+
+One general trend in the most haloes is the correlation
+between metallicity and time, which is expected in the case of
+continuous enrichment from intrinsic and nearby star formation.  One
+interesting except are the formation of [Z/H] $\sim$ --1 stars very
+early in the SFHs of Haloes 0 and 3.  This occurs when a PISN
+blastwave interacts with a pristine minihalo, enriching it and then
+triggering relatively metal-rich star formation.
+
+Halo 0 experiences an intense halo merger history.  This halo begins a
+major merger at $z \sim 10$, and the gaseous structures finally
+interact at $z \sim 8.5$.  This interaction produces a starburst that
+enriches the star-forming gas, seen as a jump from [Z/H] $\sim$ --2 to
+--1.5 in the SFH.  Star formation continues to enrich the halo,
+leading to stellar metallicities [Z/H] $\sim$ --1 at $z=7$.  In
+addition to the $z \sim 10$ major merger, it encounters two haloes
+both with an established stellar component at $z \sim 7.5$.  Because
+each halo SFH is unique, they are distinguishable in the final SFH
+stellar age -- metallicity ($t-Z$) plot.  These relic stellar
+populations are distinct, which are traced with dashed lines in
+Fig. \ref{fig:SFH}, from the main $t-Z$ track.
+
+Halo 1 also contains a relic stellar population.  Its main progenitor
+follows a $t-Z$ trajectory from ($t = 300 \mathrm{Myr}, 10^{-3}
+\zsun$) to ($t = 200 \mathrm{Myr}, 10^{-2} \zsun$) and plateaus
+afterwards.  All of the stars with a lower metallicity than this track
+belonged to the lesser halo that merges at $z=7.4$.  The plateau in
+stellar metallicity is also seen in Halo 4, where self-enrichment
+steadily increases the metallicity from [Z/H] = --2.8 at $z = 15$ to
+[Z/H] = --2.0 at $z = 9.5$.  Then mass loss from metal-rich outflows
+is balanced by metal-poor inflows from the filaments, causing the
+stellar metallicity to plateau and not enrich the halo gas
+considerably further.  The remainder of the haloes do not possess
+enough star particles to gain substantial insight on their SFHs unless
+we reduce the data along a variable and study their SFRs and MDFs.
+
+\subsubsection{Star formation rates}
+
+Star formation rates above $10^{-2}$ \hsfr~begins in Halo 0 after the
+$z=9$ major merger, which also increases its virial temperature above
+\tento{4}~K, i.e. an atomic cooling halo.  The initial starburst
+inhibits star formation for 20--40 Myr, reduced by a factor of $\sim
+5$.  After this period of self-regulation, the SFR increases back to
+$\sim 10^{-2}$ \hsfr, slowly increasing to $3 \times 10^{-2}$ \hsfr~at
+$z=7$ with a burst at $z=7.4$ that accompanies another major merger.
+
+Haloes 1, 3, and 4 support star formation in bursts with SFRs $\sim
+10^{-3}$ \hsfr.  The bursts in Haloes 1, 3, and 4 have typical
+durations of 40, 5, and 10 Myr, respectively.  As in Halo 0 but more
+severe, self-regulation plays an important role in the buildup of
+their stellar populations.  Because the potential wells of these
+haloes are not deep enough to contain the dense, star-forming gas,
+star formation is quenched for tens of Myr.  The remaining haloes
+experience even more sporadic star formation events with typical rates
+below \tento{-4}~\hsfr.
+
+\subsubsection{Metallicity distribution functions}
+
+Halo 0 has the most interesting MDF with a bimodal distribution with
+the two distributions centered at [Z/H] = --1.2 and --2.4.  The more
+metal-poor population were formed either formed in the most massive
+halo progenitors before the starburst at $z \sim 8.5$ or in the two
+galaxies that merged at $z \sim 7.5$.  Rapid star formation during the
+burst caused the typical metallicities to increase almost 1 dex over
+30--50 Myr.  The dip in the MDF is caused by this rapid enrichment
+because of the small fraction of stars formed during this period.
+This bimodality is seen in the inner regions of the Sextans dSph
+galaxies with the different distributions centered at [Fe/H] = --2.8
+and --2.0 \citep{Battaglia10}.
+
+All other haloes have stellar populations that are within 1 dex of
+each other.  Incomplete metal mixing or local enrichment from SN
+bubbles cause this spread in [Z/H].  The plateaus in the $t-Z$ plane
+are distinugishable by their overabundance of stars at their maximum
+metallicity.  In Haloes 1 and 4, The total mass in stars with
+metallicities lower than the plateau is equal to the mass in the
+metallicity plateau.  Haloes with relic stellar populations from prior
+mergers cannot be disentangled from the MDF of total metallicity
+alone.  However studying the individual abundances of stars should
+reveal details about the SFH and merger history of local dwarf
+galaxies \citep{Frebel10}.
+
+\subsubsection{Mass-to-light ratios}
+\label{sec:mlratios}
 
@@
   \plotone{mlratios.eps}
-  \caption{\label{fig:ML} Mass to light ratios.}
+  \caption{\label{fig:ML} Mass to light ratios as a function of halo
+    mass at $z$ = 7, 8, 9, and 10.  Note that the ratios are largest
+    at all masses at the latest time.  The points in each set are
+    offset in the $x$-axis to increase clarity.}
 \end{figure}
 
-\subsubsection{Star formation histories}
-
-The scatter plots of Fig. \ref{fig:SFH} show the Pop II star formation
-history as a function of metallicity for the 10 most massive halos.
-
-We now focus on the star formation rates (SFR) and metallicity
-distribution functions (MDF) of these histories, collapsing the
-stellar population in the metallicity and time axes, respectively.
-
-\subsubsection{Star formation rates}
-
-\subsubsection{Metallicity distribution functions}
-
-\subsubsection{Mass-to-light ratios}
-\label{sec:mlratios}
-
-Note that the most massive halo ($M_{\rm tot} = 10^9 \Ms$) is
-undergoing a starburst at $z=7$ and has a relatively high $M/L = 6$.
-The lower mass galaxies show a spread in M/L over two orders of
-magnitude, similar to the Sloan Digital Sky Survey (SDSS) observations
-of local dSph galaxies \citep[e.g.][]{Strigari08}.
-
-\subsubsection{Metal enrichment}
+Mass-to-light ratios are crucial in interpreting observations when
+connecting the galaxy to its DM halo, and ultimately to models of
+galaxy formation.  For this paper, we use a simple model to calculate
+the total stellar luminosity of each galaxy.  In a later paper, we
+will follow up with more sophisicated models to determine more
+accurate observables.  Stars in each particle are treated an
+instantaneous burst.  Using the empirical law of main sequence
+lifetime $t_{\rm MS} \propto M^{-5/2}$, the maximum stellar mass in
+such a system is dependent only on its age, $M_{\rm up} = (t_\star /
+10\;\mathrm{Gyr})^{-2/5}$.  Then combining another scaling law $L
+\propto M^{7/2}$ and the Salpeter IMF $\psi(M) \propto M^{-\alpha}$,
+%
+\begin{eqnarray}
+  \label{eqn:lum}
+  L/M_\odot &=& \int_{M_{\rm lo}}^{M_{\rm up}} \psi(M) L(M) dM \nonumber\\
+      &\simeq& M_{\rm up}^{9/2-\alpha} (9/2 - \alpha)^{-1},
+\end{eqnarray}
+where we set $M_{\rm lo} \equiv 0$ because it is negligible in the
+luminosity.  Then the galaxy luminosity is the sum of all star
+particle luminosities, which we plot in Fig. \ref{fig:Lstar} with
+respect to halo mass.
+
+Recall that the most massive halo ($M_{\rm tot} = 10^9 \Ms$) is
+undergoing a starburst at $z=7$, translating into a relatively high
+$M/L = 6$.  The lower mass galaxies show a spread in M/L over two
+orders of magnitude, similar to the Sloan Digital Sky Survey (SDSS)
+observations of local dSph galaxies \citep[e.g.][]{Strigari08}.
+
+Fig. \ref{fig:ML} illustrates the change in the M/L ratio at four
+different epochs, $z$ = 7, 8, 9, and 10.  At $z=10$, the galaxies
+reside in haloes with $10^7 \la M/\Ms \la 10^8$ and have $\log
+(\mathrm{M/L}) \sim 2 \pm 0.5$.  At redshift 8 and 9, stellar feedback
+reduce the cold gas reservoirs for star formation, thus increasing the
+average M/L values with the largest change at the lowest halo masses.
+At $z=7$, stellar feedback and a pre-heated IGM begin to have a
+noticable effect on all galaxies except for the most massive galaxy in
+a $10^9 \Ms$ halo.  In these low mass galaxies,
+$\langle\mathrm{M/L}\rangle \sim 1000$, trending slightly downward
+with halo mass.  Also the spread of M/L is larger than at earlier
+times because of differing galaxy environments.  Galaxies with higher
+M/L ratios lie in biased regions, and the lower M/L galaxies are
+isolated and avoid negative radiative feedback from neighboring
+galaxies.
+
+\subsection{Metal enrichment from pair-instability SNe}
+
+\begin{figure}
+  \plotone{Zhistory.eps}
+  \caption{\label{fig:Zevo} The time evolution of the average gas
+    metallicity from Pop II SNe (dashed) and Pop III SNe (dotted) and
+    average stellar metallicity (solid) of the 10 most massive haloes.
+    Note that a metallicity floor of [Z/H] $\sim -3$ exists in every
+    halo.}
+\end{figure}
+
+\begin{figure}
+  \plotone{z3.eps}
+  \caption{\label{fig:zhalo3} Average halo metallicity from Pop III
+    SNe as a function of total halo mass.  Inhomogenous metal
+    enrichment causes the large spread in metallicity at low masses.
+    At $M_{\rm halo} > 3 \times 10^7 \Ms$, all halos are enriched by
+    Pop III SNe above [Z/H] $>$ --4.  The y-axis error bars show the
+    25\% and 75\% percentile values because the underlying
+    distribution is not Gaussian.}
+\end{figure}
+
+\begin{figure}
+  \plotone{z3fill.eps}
+  \caption{\label{fig:z3fill} Mass fraction (thick lines) and volume
+    filling fraction (thin lines) of material enriched by Pop III SNe
+    above \zthree~= (-6, -5, -4, -3).}
+\end{figure}
+
+We plot the evolution of the mass-averaged gas and stellar metallicity
+in the massive halos in Fig. \ref{fig:Zevo}.  Here we focus on the
+metallicity provided from Pop III SNe, \zthree.  The most relevant
+aspect of these data is the existence of a metallicity floor $\zthree
+\sim -3$ in all of the haloes.  The haloes can either be enriched from
+hosting a PISNe or one in a nearby halo.  In the time evolution of the
+metallicity, the former scenario appears as an initial peak in
+\zthree~then gradually decreasing, which is seen in Haloes 1-3 and 6-9
+with two enrichment events occurring in Halo 6.  This peak happens
+because the halo is gas-poor from the Pop III radiative feedback with
+$M_{\rm gas} \sim 10^4$ (also see Sec. \ref{sec:fgas}) and the PISN
+provides $\sim 100 \Ms$ of heavy elements, resulting in $\zthree \sim
+0$.  The ensuing blastwave drives out the remainder of the gas,
+leaving behind a diffuse medium, enriched to $\zthree \ga -3$.
+Because the blastwave rapidly exits the halo on timescales smaller
+than the time sampling in Fig. \ref{fig:Zevo}, the maximum mean
+metallicity is missed in most haloes but is captured in Halo 2.
+
+Gas in satellite haloes and adjacent filaments are enriched to a
+lesser extent because these high-density regions are resistant to
+impinging metal-rich blastwaves \citep[cf.][]{Cen08}.  However if the
+nearby SNe is close enough when the shock velocities are still high
+($\ga 100~\kms$), the dense gas in the minihalo can be enriched to
+similar metallicities.  This scenario appears as prompt enrichment but
+without the temporary peak in metallicity as the blastwave overtakes
+the halo, and this occurs in Haloes 0, 4, and 5 with Halo 5 being
+enriched by two nearby PISNe.
+
+In Fig. \ref{fig:zhalo3}, we show the average \zthree~in all haloes as
+a function of halo mass at $z =$ 7, 8, 9, and 10, and it is strongly
+dependent on halo mass.  The \zthree~error bars mark the 25\% and 75\%
+percentiles of the distribution at $M = M_{\rm halo}$ because the
+underlying distribution is not necessarily Gaussian at all halo
+masses.  Above $3 \times 10^7 \Ms$, all haloes enriched to $\zthree
+\ga -4$ with little time evolution, further illustrating the
+metallicity floor.  Below this halo mass, the distribution is roughly
+bimodal composed of pristine and metal-enriched halos.
+
+Fig. \ref{fig:z3fill} depicts the volume filling fraction $f_{\rm
+  v,III}$ and mass fraction $f_{\rm m,III}$ of gas enriched above
+metallicities \zthree~= (--6, --5, --4, --3).  The first PISN occurs
+at $z = 16.5$, initially enriching $10^{-4}$ ($10^{-3}$) of the
+simulation volume (mass).  The enriched gas mass (volume) fraction
+with $\zthree > -6$ rises steadily with time to reach 0.14 (0.038) at
+$z=7$.  The gas fraction enriched above \zthree~= (--5, --4, --3) are
+15\%, 30\%, and 50\% lower, respectively, and these differences vary
+little with time after the initial enrichment.  The ratio of the mass-
+and volume-weighted enriched fractions $f_{\rm m,III}/f_{\rm v,III}
+\sim 4$, which indicates the average overdensity in an enriched
+region.  It also demonstrates that metal enrichment is an `inside-out'
+process with the overdense regions being enriched first with the voids
+an filaments later, similar to reionization.
+
+\subsection{Metal enrichment from Pop II core collapse SNe}
+
+\begin{figure}
+  \plotone{ztot.eps}
+  \caption{\label{fig:ztot} The fraction of haloes above an average
+    gas metallicity of [Z/H] = --5 (top), --4 (middle), and --3
+    (bottom) as a function of halo mass at $z$ = 7, 8, 10, and 12.}
+\end{figure}
+
+\begin{figure}
+  \plotone{z2fill.eps}
+  \caption{\label{fig:z2fill} Mass fraction (thick lines) and volume
+    filling fraction (thin lines) of material enriched by Pop II SNe
+    above \ztwo~= (-6, -5, -4, -3).}
+\end{figure}
 
@@
   \plotone{z2.eps}
-  \caption{\label{fig:zhalo2} Halo metallicities.}
+  \caption{\label{fig:zhalo2} Average halo metallicity from Pop II SNe
+    as a function of total halo mass.  Inhomogenous metal enrichment
+    causes the large spread in metallicity at low masses.  At $M_{\rm
+      halo} > 3 \times 10^7 \Ms$, halos can host Pop II star formation
+    that self-enrich the gas, resulting in $\langle[Z_2/H]\rangle \sim
+    -3$ at $M_{\rm halo} = 10^8 \Ms$.  The y-axis error bars show the
+    25\% and 75\% percentile values because the underlying
+    distribution is not Gaussian.}
 \end{figure}
 
-\begin{figure}
-  \plotone{ztot.eps}
-  \caption{\label{fig:ztot} Halo metallicities.}
-\end{figure}
+After Pop III star formation has ended in a region, Pop II stars then
+form and further enrich the galaxy and its neighborhood.
+Fig. \ref{fig:Zevo} also shows the average gas, \ztwo, and stellar,
+[Z$_\star$/H], metallicities from Pop II SNe.  All haloes experience
+an initial enrichment from Pop II stars to $-4 \la \ztwo \la -3$.
+They are either initially enriched by intrinsic star formation or
+external blastwaves.  This can be determined by comparing the onset of
+metal enrichment in the gas and stars.  If the gas metallicity becomes
+non-zero before the stellar metallicity (i.e. the start of Pop II star
+formation), the halo was enriched from an external source.  This
+happens most notably in Haloes 2, 3, and 7 with disprenacies of
+100--200 Myr between the time when stellar and gas metallicities
+become non-zero.
+
+Halo 0 remains at \ztwo~= --3 before the starburst $z \sim 8.5$ and
+then is subsequently and quickly enriched to \ztwo~= --2.  The
+continuous star formation steadily enriches the gas to an average
+\ztwo~= --1.3 by $z=7$.  All of the other haloes do not possess a deep
+enough potential well to support such a starburst, and their
+metallicites remain nearly constant with the expection of the haloes
+with $\ztwo < -3$ that can have flucutations on the order of 0.5 dex
+because averages of these low mass fractions are sensitive to even
+small changes.  The metallicities from Pop II stars are equal or
+smaller than Pop III stars in these low mass halos.
+
+In general, the stellar metallicities follow the same trends as the
+gas metallicities with the exception of Haloes 0 and 3.  Some of the
+first metal-enriched stars were triggered by PISN blastwaves and have
+relatively high [Z/H] $\sim$ --1 that skew the average above the gas
+metallicity.  Subsequent star formation in these haloes have [Z/H]
+values comparable to the average gas metallicity.  Haloes 2, 5, 6, and
+9 have stellar metallicities that are dominated by PISNe enrichment,
+seen as [Z$_\star$/H] = \zthree~when star formation commences in
+Fig. \ref{fig:Zevo}.  Later star formation do not enrich the gas
+considerably further as the outflows are not bound to the halo.
+
+Fig. \ref{fig:ztot} quantifies the fraction of haloes at a given mass
+are enriched above a mean total metallicity [Z/H] = --3, --4, and --5
+at redshifts 7, 8, 10, and 12.  The minihaloes with $M \sim 10^6$ are
+primarily enriched by PISNe and are nearly equal to the metal volume
+filling fraction, shown in Fig. \ref{fig:z3fill}, for all metallicity
+cuts.  The fraction linearly increases to approximately 0.6 for [Z/H]
+= --3 and 0.8 for the [Z/H] = --4 and --5 cuts at a halo mass of
+\tento{7}\Ms because these larger haloes have a higher probability
+that one of its progenitors hosted a PISN.  For the lower two
+metallicity cuts, the fraction continues to increase until all of the
+haloes are enriched above $3 \times 10^7 \Ms$ and $10^8 \Ms$ for [Z/H]
+= --4 and --5, respectively.  These trends are redshift independent
+for the data shown here because the halo mass (with respect to the
+filtering mass) is driving factor in controlling star formation and
+metal production.  For the metallicity cut of [Z/H] = --3, there is
+considerable noise from redshift to redshift.  But at redshift 7, all
+of the haloes above \tento{8}\Ms are enriched above this level except
+for Halo 2 (there are only 2 halos in the $2 \times 10^8 \Ms$ bin),
+because it hosts too little star formation for significant
+self-enrichment to occur.
+
+Next the volume filling fraction $f_{\rm v,II}$ and mass fraction
+$f_{\rm v,II}$ of gas that are enriched above \ztwo~= --6, --5, --4,
+and --3 is shown in Fig. \ref{fig:z2fill} as a function of time.  The
+first Pop II stars only enrich $2 \times 10^{-3}$ of the volume above
+\ztwo~= -- 6, increasing to 5.2 per cent by $z=7$.  The volume
+fraction for the lesser metallicity cuts are 4.3, 3.4, 2.5, and 1.7
+per cent.  Core collapse SNe from Pop II stars enrich about 3 times
+less volume than PISNe as the associated metal bubbles do not expand
+very far from the haloes.  Hence they are located in comsologically
+overdense regions.  This is quantified again by evalulating the ratio
+$f_{\rm v,II}/f_{\rm m,II} = (9.4, 11, 15, 25, 66)$ with increasing
+metallicity cuts at $z=7$.  In comparison, this ratio was nearly
+constant across metallicity cuts for PISNe.
+
+Lastly we plot the average \ztwo~values versus halo mass for all halos
+at $z$ = 7, 8, 9, and 10 in Fig. \ref{fig:zhalo2}.  Below $3 \times
+10^7 \Ms$ regardless of redshift, the majority of the haloes are
+pristine, as shown in Fig. \ref{fig:ztot}, with the spread arising
+from inhomogenous metal enrichment.  At higher halo masses, the mean
+metallicity increases to $\ztwo \sim -5$ at $3 \times 10^7 \Ms$ and to
+$\ztwo = -3$ by $10^8 \Ms$.  The most massive haloes have
+metallicities above $10^{-2} \zsun$.  The typical enrichment halo mass
+by Pop II SNe, where most of the haloes are enriched to $Z_{\rm cr}$,
+is $\sim 10^8 \Ms$, slightly higher than the Pop III enrichment mass
+$\sim 3 \times 10^7 \Ms$ (see Fig. \ref{fig:zhalo3}).
 
@@
 
+Here we discuss some notable details about individual haloes that did
+not fit into the previous sections.
+
+\halo{0}
+
+\halo{1}
+
+\halo{2}
+
+\halo{3}
+
+\halo{4}
+
+\halo{5}
+
+\halo{6}
+
+\halo{7}
+
+\halo{8}
+
+\halo{9}
+
 \section{Differences between Physical Models}
@@
 \subsection{Metal cooling}
+
+\subsection{Higher Pop II metal yields}
 
@@
 
+\appendix
+
+\section[]{Dependence on Numerical Resolution}
+
 \end{document}

### 2011-02-09 ms.tex
Adding halo details and arXiv numbers to references.

@@
 are enriched above a mean total metallicity [Z/H] = --3, --4, and --5
-at redshifts 7, 8, 10, and 12.  The minihaloes with $M \sim 10^6$ are
-primarily enriched by PISNe and are nearly equal to the metal volume
-filling fraction, shown in Fig. \ref{fig:z3fill}, for all metallicity
-cuts.  The fraction linearly increases to approximately 0.6 for [Z/H]
-= --3 and 0.8 for the [Z/H] = --4 and --5 cuts at a halo mass of
-\tento{7}\Ms because these larger haloes have a higher probability
-that one of its progenitors hosted a PISN.  For the lower two
-metallicity cuts, the fraction continues to increase until all of the
-haloes are enriched above $3 \times 10^7 \Ms$ and $10^8 \Ms$ for [Z/H]
-= --4 and --5, respectively.  These trends are redshift independent
-for the data shown here because the halo mass (with respect to the
-filtering mass) is driving factor in controlling star formation and
-metal production.  For the metallicity cut of [Z/H] = --3, there is
-considerable noise from redshift to redshift.  But at redshift 7, all
-of the haloes above \tento{8}\Ms are enriched above this level except
-for Halo 2 (there are only 2 halos in the $2 \times 10^8 \Ms$ bin),
-because it hosts too little star formation for significant
-self-enrichment to occur.
+at redshifts 7, 8, 10, and 12.  The minihaloes with $M \sim 10^6 \Ms$
+are primarily enriched by PISNe and are nearly equal to the metal
+volume filling fraction, shown in Fig. \ref{fig:z3fill}, for all
+metallicity cuts.  The fraction linearly increases to approximately
+0.6 for [Z/H] = --3 and 0.8 for the [Z/H] = --4 and --5 cuts at a halo
+mass of \tento{7}\Ms~because these larger haloes have a higher
+probability that one of its progenitors hosted a PISN.  For the lower
+two metallicity cuts, the fraction continues to increase until all of
+the haloes are enriched above $3 \times 10^7 \Ms$ and $10^8 \Ms$ for
+[Z/H] = --4 and --5, respectively.  These trends are redshift
+independent for the data shown here because the halo mass (with
+respect to the filtering mass) is driving factor in controlling star
+formation and metal production.  For the metallicity cut of [Z/H] =
+--3, there is considerable noise from redshift to redshift.  But at
+redshift 7, all of the haloes above \tento{8}\Ms~are enriched above
+this level except for Halo 2 (there are only 2 halos in the $2 \times
+10^8 \Ms$ bin), because it hosts too little star formation for
+significant self-enrichment to occur.
 
@@
 
-\halo{0}
-
-\halo{1}
-
-\halo{2}
-
-\halo{3}
-
-\halo{4}
-
-\halo{5}
-
-\halo{6}
-
-\halo{7}
-
-\halo{8}
-
-\halo{9}
+\halo{3} Fig. \ref{fig:Zevo} shows that metal enrichment from Pop II
+stars occurs 10 Myr after a PISN.  In this case, PISN remnant did not
+escape from the halo \citep[cf.][]{Whalen08_SN}, leaving the halo
+metal-enriched and relatively gas-rich.  This gas later formed 3000
+\Ms~of Pop II stars in two stellar clusters with very different
+metallicities of [Z/H] = --3.5 and --1.2 seen in Fig. \ref{fig:SFH}.
+Because this triggered star formation was weak, it does not
+significantly enrich further, only reaching a metallicity of $\ztwo
+\sim -4.5$ before the galaxy hosts a starburst at $z = 9.5$.
+
+\halo{4} A nearby minihalo initially enriched the most massive
+progenitor, triggering Pop II star formation without hosting a Pop III
+star at $z=15$ when the halo mass was only $5 \times 10^6 \Ms$.  This
+halo experiences a series of major and minor mergers at $z > 10$ and
+very little afterwards.  The lack of mergers allows a gas and stellar
+disc to form, unlike all of the other galaxies in the simulation.  SNe
+feedback creates a bipolar outflow, perpendicular to the disc, that
+enriches the surrounding IGM but not the halo itself.
+
+\halo{7} Triggerred star formation similar to Halo 3 occurs in this
+halo, where the PISN does not expel the majority of the gas.  2000
+\Ms~of stars form in the expanding SN remnant shell, promptly
+enriching the halo shortly after the PISN, shown in
+Fig. \ref{fig:Zevo}.  Because these stars formed in the reference
+frame of the expanding shell, they escape from the halo, only
+enriching the halo to $\ztwo \sim -4.5$.  These stars never return to
+the halo and are still located in the IGM at $z=7$.
+
+\halo{8} This halo resides 4.5 kpc from Halo 0 at $z=7$ and is
+subjected to strong UV radiation that suppresses all star formation
+even after it becomes gas rich with $f_g > 0.1$ at $z \la 8$.
 

### 2011-02-22 ms.tex
Making the combination model the primary model.  Need to change all results once the simulation is finished.

@@
 
-We perform nine different simulations with the same initial
-conditions.  The fiducial model considers (a) primordial cooling with
-9 species of hydrogen, helium, and molecular hydrogen, (b) a Pop III
-IMF characteristic mass $M_{\rm char}$ = 100 \Ms, (c) Pop II and Pop
-III star formation, and (d) a critical metallicity of [Z/H] = --4.  We
+We perform ten different simulations with the same initial conditions.
+The baseline model considers (a) primordial cooling with 9 species of
+hydrogen, helium, and molecular hydrogen, (b) a Pop III IMF
+characteristic mass $M_{\rm char}$ = 100 \Ms, (c) Pop II and Pop III
+star formation, and (d) a critical metallicity of [Z/H] = --4.  We
 vary this model with the following changes:
@@
 \begin{enumerate}
-\item Additional radiative cooling from metal species.  We calculate a
+\item Additional radiative cooling from metal lines.  We calculate a
   cooling curve with CLOUDY \citep{CLOUDY} and use the method of
@@
   resolve the necessary scales for Pop III star formation.
+\item Combination of metal cooling (model i), increased metal yields
+  (model iii), a LW background (model v).  This provides the best
+  physical scenario for the high-$z$ universe, and we consider it as
+  our \textit{primary model}.
 \end{enumerate}
@@
 Here we present the gaseous and stellar evolution of the high-redshift
-dwarf galaxies that form in our simulations.  To illustrate its global
+dwarf galaxies that form in our \textit{primary physical model} with
+metal-line radiative cooling, Pop II metal yields that agree with MW
+data, and a LW radiation background.  To illustrate its global
 properties, we show the density-weighted projections of gas density,

### 2011-03-03 ms.tex
Changing the SFH plots to have the time axis as time instead of stellar age.

@@
 inhomogenous metal enrichment and the transition to Pop II star
-formation, and here we give a brief overview of its development.
+formation, and here we give an overview of its development.
 Considering only Pop III star formation, \citeauthor{Yoshida04}
@@
   \caption{\label{fig:SFH} The scatter plots show the Pop II star
-    formation history as a function of stellar age $t_\star$ with
-    respect to metallicity for the 10 most massive halos.  Halo 8 is
-    not shown because it contains no stars.  Each circle represents a
-    star particle, whose area is proportional to its mass.  The open
-    circles in the upper right represent $M = 10^3$, $10^4$, and
-    $10^5$ \Ms.  The dashed lines in the Halo 0 panel guide the eye to
-    two stellar populations that were formed in two satellite halos,
-    merging at $z=7.5$.  The upper histogram shows the star formation
-    rate with each bar representing 5 Myr.  The right histogram
-    depicts the Pop II metallicity distribution function.}
+    formation history as a function of time with respect to
+    metallicity for the 10 most massive halos.  Halo 8 is not shown
+    because it contains no stars.  Each circle represents a star
+    particle, whose area is proportional to its mass.  The open
+    circles in the upper right represent $M = 10^3$ and $10^4$ \Ms.
+    The dashed lines in the Halo 0 panel guide the eye to two stellar
+    populations that were formed in two satellite halos, merging at
+    $z=7.5$.  The upper histogram shows the star formation rate with
+    each bar representing 5 Myr.  The right histogram depicts the Pop
+    II metallicity distribution function.}
 \end{figure*}
@@
 population.  The SFHs of the 10 most massive haloes are shown in
-Fig. \ref{fig:SFH} in the plane of stellar age $t_\star$ and
-metallicity as scatter plots with each point representing a star
-particle and its size proportional to its mass.  Collapsing the data
-along the time and metallicity axes gives the metallicity distribution
-function (MDF) and star formation rate, respectively, also shown in
-the Figure.
+Fig. \ref{fig:SFH} in the plane of formation time and metallicity as
+scatter plots with each point representing a star particle and its
+size proportional to its mass.  Collapsing the data along the time and
+metallicity axes gives the metallicity distribution function (MDF) and
+star formation rate, respectively, also shown in the Figure.
 
@@
 lifetime $t_{\rm MS} \propto M^{-5/2}$, the maximum stellar mass in
-such a system is dependent only on its age, $M_{\rm up} = (t_\star /
-10\;\mathrm{Gyr})^{-2/5}$.  Then combining another scaling law $L
-\propto M^{7/2}$ and the Salpeter IMF $\psi(M) \propto M^{-\alpha}$,
+such a system is dependent only on its age $t_\star$, so $M_{\rm up} =
+(t_\star / 10\;\mathrm{Gyr})^{-2/5}$.  Then combining another scaling
+law $L \propto M^{7/2}$ and the Salpeter IMF $\psi(M) \propto
+M^{-\alpha}$,
 %
@@
 
+\halo{0} \textbf{Early time metal-rich stars.}
+
 \halo{3} Fig. \ref{fig:Zevo} shows that metal enrichment from Pop II
@@
 feedback creates a bipolar outflow, perpendicular to the disc, that
-enriches the surrounding IGM but not the halo itself.
+enriches the surrounding IGM but not the halo itself.  \textbf{Metal
+  poor stars at late times from minor merger.}
 

### 2011-03-13 ms.tex
Removing no H2 cooling run (leave it for a separate paper).  Removing halo mass function.

@@
 
-We perform ten different simulations with the same initial conditions.
+We perform nine different simulations with the same initial conditions.
 The baseline model considers (a) primordial cooling with 9 species of
@@
   their pair-instability and Type II SNe.
-\item Pop II star formation only and no molecular hydrogen cooling.
-  This model provides a good comparison to larger scale simulations
-  where it is not computationally feasible to consider \hh~cooling or
-  resolve the necessary scales for Pop III star formation.
+\item Combination of metal cooling (model i) and a LW background
+  (model v).  This provides the best physical scenario for the
+  high-$z$ universe, and we consider it as our \textit{primary model}.
 \item Combination of metal cooling (model i), increased metal yields
-  (model iii), a LW background (model v).  This provides the best
-  physical scenario for the high-$z$ universe, and we consider it as
-  our \textit{primary model}.
+  (model iii), a LW background (model v).  We explain in
+  \S\ref{sec:models} why we do not consider this as our primary model.
 \end{enumerate}
@@
 
-\begin{figure}
-  \plotone{mass_fn.eps}
-  \caption{\label{fig:mass_fn} Halo DM mass function of the simulated
-    haloes (points) where the error bars are Poisson noise and the
-    solid line is the analytic halo mass function of
-    \citet{Warren06}.}
-\end{figure}
+% \begin{figure}
+%   \plotone{mass_fn.eps}
+%   \caption{\label{fig:mass_fn} Halo DM mass function of the simulated
+%     haloes (points) where the error bars are Poisson noise and the
+%     solid line is the analytic halo mass function of
+%     \citet{Warren06}.}
+% \end{figure}
 
@@
 Pop II star formation, enriching their host halo and surrounding IGM.
-In Fig. \ref{fig:mass_fn}, we show the halo mass function, agreeing
-well with the analytic halo mass function of \citet{Warren06}.  We
-identify the haloes with a friends-of-friends (FOF) algorithm
-\citep{Davis85}.  The excess of low-mass haloes below $M_{\rm DM} = 2
-\times 10^6 \Ms$ is most likely associated with the biased region in
-the lower-right region in the projections.  Furthermore, the
-uncertainities in different analytic halo mass functions
-\citep[see][for a comparison]{Reed07} and halo identification are
-comparable than these differences.  Our fidicual model contains 38
-galaxies with a total of 3640 Pop II star clusters and captures the
-formation of 333 Pop III stars.
+Our primary model contains ?? galaxies with a total of ???? Pop II
+star clusters and captures the formation of ??? Pop III stars.
+
+% In Fig. \ref{fig:mass_fn}, we show the halo mass function, agreeing
+% well with the analytic halo mass function of \citet{Warren06}.  We
+% identify the haloes with a friends-of-friends (FOF) algorithm
+% \citep{Davis85}.  The excess of low-mass haloes below $M_{\rm DM} = 2
+% \times 10^6 \Ms$ is most likely associated with the biased region in
+% the lower-right region in the projections.  Furthermore, the
+% uncertainities in different analytic halo mass functions
+% \citep[see][for a comparison]{Reed07} and halo identification are
+% comparable than these differences.
 
@@
 \begin{figure*}
-  \plottwo{z7-mosaic0.eps}{z7-mosaic1.eps}
-  \caption{\label{fig:z7-mosaic} Density-weighted projections of
+  %\plottwo{z82-mosaic0.eps}{z82-mosaic1.eps}
+  \vspace{150pt}
+  \caption{\label{fig:z82-mosaic} Density-weighted projections of
     density (left), temperature (center), and metallicity (right) of
-    the 10 most massive haloes at $z=7$.  The field of view is 5 proper
-    kpc, and the circles have a radius of $r_{200}$.  The composite
-    metallicity images are constructed in the same fashion as
-    Fig. \ref{fig:evo-mosaic}.}
-\end{figure*}
-
-\begin{figure*}
-  \plottwo{z8-mosaic0.eps}{z8-mosaic1.eps}
-  \caption{\label{fig:z8-mosaic} Same as Fig. \ref{fig:z7-mosaic} but
-    at $z=8$, showing the progenitors of the 10 most massive haloes at
-    $z=7$.}
+    the 10 most massive haloes at $z=8.2$ in our primary model.  The
+    field of view is 5 proper kpc, and the circles have a radius of
+    $r_{200}$.  The composite metallicity images are constructed in
+    the same fashion as Fig. \ref{fig:evo-mosaic}.}
 \end{figure*}
@@
   \plottwo{z10-mosaic0.eps}{z10-mosaic1.eps}
-  \caption{\label{fig:z10-mosaic} Same as Fig. \ref{fig:z8-mosaic} at
-    $z=10$.}
+  \caption{\label{fig:z10-mosaic} Same as Fig. \ref{fig:z82-mosaic}
+    but at $z=10$, showing the progenitors of the 10 most massive
+    haloes at $z=8.2$.}
 \end{figure*}
+
+% \begin{figure*}
+%   \plottwo{z10-mosaic0.eps}{z10-mosaic1.eps}
+%   \caption{\label{fig:z10-mosaic} Same as Fig. \ref{fig:z8-mosaic} at
+%     $z=10$.}
+% \end{figure*}
 
@@
 projections of gas density, temperature, and composite Pop II+III
-metallicity at redshifts 7, 8, and 10 in
-Fig. \ref{fig:z7-mosaic}--\ref{fig:z10-mosaic}, respectively.  One
-common feature of all of the halos represented in these Figures is
-that they are embedded in a preheated IGM with the exception of Halo 7
-at $z=10$.  Prior radiative feedback in either the host or nearby
-halos created \hii~regions that encompass these halos.  For
-\hii~regions without sustained star formation, these so-called relic
-\hii~regions recombine and radiatively cool down to $T = 10^3$ K.
-Within the virial radius, one can see that our simulations capture the
-multi-phase ISM.  In the density projections, the effects of
-photo-evaporation and cloud crushing are clearly seen, which are
-caused by the stellar radiative and mechanical feedback, respectively.
-The filaments adjacent to the halos are photo-heated to $T = 1-3
-\times 10^4$ K, and then their gas escapes into the IGM no longer
-being pressure equilibrium with the gravitational potential of the
-filament, i.e. Jeans smoothing.  Furthermore, neighboring halos are
-photo-evaporated \citep[see][for the level of halo
-  photo-evaporation]{Wise08_Reion}, resulting in the suppression of
-gas-rich satellite haloes.  A good illustration of photo-evaporation
-in progress is the cometary structure in the bottom-center of the
-density projection of Halo 4 at $z=7$.
+metallicity at redshifts 8.2 and 10 in Fig. \ref{fig:z82-mosaic} and
+\ref{fig:z10-mosaic}, respectively.  One common feature of all of the
+halos represented in these Figures is that they are embedded in a
+preheated IGM with the exception of Halo 7 at $z=10$.  Prior radiative
+feedback in either the host or nearby halos created \hii~regions that
+encompass these halos.  For \hii~regions without sustained star
+formation, these so-called relic \hii~regions recombine and
+radiatively cool down to $T = 10^3$ K.  Within the virial radius, one
+can see that our simulations capture the multi-phase ISM.  In the
+density projections, the effects of photo-evaporation and cloud
+crushing are clearly seen, which are caused by the stellar radiative
+and mechanical feedback, respectively.  The filaments adjacent to the
+halos are photo-heated to $T = 1-3 \times 10^4$ K, and then their gas
+escapes into the IGM no longer being pressure equilibrium with the
+gravitational potential of the filament, i.e. Jeans smoothing.
+Furthermore, neighboring halos are photo-evaporated \citep[see][for
+the level of halo photo-evaporation]{Wise08_Reion}, resulting in the
+suppression of gas-rich satellite haloes.  A good illustration of
+photo-evaporation in progress is the cometary structure in the
+bottom-center of the density projection of Halo 4 at $z=7$.
 
@@
 
-\section{Differences between Physical Models}
+\section{Variations between Physical Models}
 \label{sec:models}
 
+\subsection{Reference Model}
+
 \subsection{Metal cooling}
@@
 \subsection{Neglecting Pop III star formation}
-
-\subsection{Neglecting Pop III star formation and \hh~formation}
 

### 2011-05-20 ms.tex
Merged.

@@
 detail our star formation and feedback algorithms.  We run a total of
-eight different simulations, varying physical parameters.  In the
-following description, we quote the parameters used in our fidicual
+ten different simulations, varying physical parameters.  In the
+following description, we quote the parameters used in our reference
 model and describe their variations later in Sec. \ref{sec:config}.
@@
 level of $l = 12$, resulting in a maximal comoving resolution of 1 pc.
-We stop the simulation at $z=7$ to avoid any large-scale modes with $r
-\sim L_{\rm box}/2$ entering the non-linear growth regime.  At the
-final redshift, this simulation has $1.4 \times 10^8$ computational
-cells and required 250,000 CPU hours, using 512 cores.
+We stop the simulation at $z=7$ or when the volume reaches an ionized
+fraction of 0.9.  The first stopping point prevents any large-scale
+modes with $r \sim L_{\rm box}/2$ from entering the non-linear growth
+regime.  At the final redshift, the baseline simulation has $1.4
+\times 10^8$ computational cells and required 250,000 CPU hours, using
+512 cores.
 
@@
 
-We perform nine different simulations with the same initial conditions.
-The baseline model considers (a) primordial cooling with 9 species of
+We perform ten different simulations with the same initial conditions.
+The reference model considers (a) primordial cooling with 9 species of
 hydrogen, helium, and molecular hydrogen, (b) a Pop III IMF

### 2011-06-22 ApJ/ms.tex

--- 2010-11-08 ms.tex
@@
 
-\title{The Birth of a Galaxy: Primoridal Metal Enrichment and
+\title{The Birth of a Galaxy: Primordial Metal Enrichment and
   Population II Stellar Populations}
@@
 \bibliography{ms}
-
 \end{document}

### 2011-06-23 ApJ/ms.tex
Started to incorporate more intro and methods to the expanded ApJ edition.

@@
 
-\title{The Birth of a Galaxy: Primordial Metal Enrichment and
-  Population II Stellar Populations}
+\title{The Birth of a Galaxy: Primordial Metal Enrichment and Stellar
+  Populations}
 
@@
 
-The transition from Pop III to Pop II star formation (SF) is solely
-dependent on the propagation of metals from the SNe remnants into
-future sites of SF.  Their flows are complex because of the
-interactions between the SN blastwave, cosmological accretion and halo
-mergers, and nearby stellar feedback.  In minihalos ($M \sim
-10^6~\Ms$), radiation from a massive Pop III star can drive a 30
-\kms~shock, which is 10 times greater than the escape velocity of the
-halo, and leaves behind a warm ($3 \times 10^4$ K) and diffuse (0.5
-\cubecm) medium \citep{Kitayama04, Whalen04, Abel07}.  This aids in the
-expansion of the blastwave because it delays the transition to the
+Pop III stars primarily form in dark matter halos with $M \sim 10^6
+\Ms$.  Their stellar radiation ionizes and heats an \ion{H}{2} region
+with a radius 1--3 kpc.  The overpressurized \ion{H}{2} region drives
+a 30 \kms~shock that is 10 times greater than the escape velocity of
+the halo, leaving behind a warm ($3 \times 10^4$ K) and diffuse (0.5
+\cubecm) medium \citep{Kitayama04, Whalen04, Abel07}.  This aids in
+the expansion of the blastwave because it delays the transition to the
 Sedov-Taylor and snowplow phases.  In PISNe, approximately half of the
@@
 
+The transition from Pop III to Pop II star formation (SF) is solely
+dependent on the propagation of metals from the SNe remnants into
+future sites of SF.  Their flows are complex because of the
+interactions between the SN blastwave, cosmological accretion and halo
+mergers, and nearby stellar feedback.  Spurred by the notion of a
+critical metallicity, this transition has been extensively studied
+with (i) volume-averaged semi-analytic models \citep{Scannapieco03,
+  Yoshida04, Furlanetto05_Reion}, (ii) models using hierarchical
+merger trees \citep{Tumlinson06, Tumlinson10, Salvadori07, Komiya10},
+(iii) post-processing of cosmological simulations with blastwave
+models \citep{Karlsson08, Trenti09, Trenti10}, and (iv) direct
+numerical simulations with stellar feedback \citep{Tornatore07,
+  Ricotti08, Maio10_Pop32, Maio10_Enrich}.
+
 Numerical simulations are useful to detangle and study these
-complexities and the transition from Pop III to II stars.  In this
-Letter, we present a simulation that includes both types of SF, and
-their radiative and mechanical feedback.  The methods used here
-incorporate and link together recent results from metal-enriched and
-metal-free star formation, the critical metallicity, and
-pair-instability supernovae.  This is the first time it has been
-possible to link the formation and feedback of the first stars to
-protogalaxies, resolving the important scales and including the most
-important physical effects.
+complexities and the transition from Pop III to II stars.  Here, we
+present a simulation that includes both types of SF, and their
+radiative and mechanical feedback.  The methods used here incorporate
+and link together recent results from metal-enriched and metal-free
+star formation, the critical metallicity, and pair-instability
+supernovae.  This is the first time it has been possible to link the
+formation and feedback of the first stars to protogalaxies, resolving
+the important scales and including the most important physical
+effects.
 
@@
 We use the adaptive mesh refinement (AMR) code
-enzo~v2.0\footnote{\texttt{enzo.googlecode.com, changeset
-    b86d8ba026d6}} \citep{OShea2004}, which has been modified to use a
-HLLC Riemann solver \citep{Toro94_HLLC} for additional stability in
-strong shocks.  To resolve minihalos with at least 100 dark matter
-(DM) particles and follow the formation of the first generation of
-dwarf galaxies, we use a simulation box of 1 Mpc that has a resolution
-of $256^3$.  This gives us a DM mass resolution of 1840 \Ms.  We
-refine the grid on baryon overdensities of $3 \times 2^{-0.2l}$, where
-$l$ is the AMR level, resulting in a super-Lagrangian behavior.  We
-also refine on a DM overdensity of $3 \times 2^l$ and always resolve
-the local Jeans length by at least 4 cells, avoiding artificial
-fragmentation during gaseous collapses \citep{Truelove97}.  This
-simulation has $1.4 \times 10^8$ computational elements and a maximal
-spatial resolution of 0.1 pc.  We initialize the simulation with
-\textsl{grafic} \citep{Bertschinger01} at $z = 130$ and use the
-cosmological parameters from the 7-year WMAP data \citep{WMAP7}:
-$\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h
-= 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$ with the variables having
-their usual definitions.  We stop the simulation at $z=7$.
-
-We use a non-equilibrium chemistry solver with 9 species of hydrogen,
-helium, and molecular hydrogen \citep{Abel97}.  We spatially
+\textsc{enzo~v2.0}\footnote{\texttt{enzo.googlecode.com, changeset
+    b86d8ba026d6}} \citep{OShea2004}.  It uses an $N$-body adaptive
+particle-mesh solver \citep{Efstathiou85} to follow the dark matter
+(DM) dynamics.  It solves the hydrodynamical equation using the
+second-order accurate piecewise parabolic method \citep{Woodward84,
+  Bryan95}, while a Riemann solver ensures accurate shock capturing
+with minimal viscosity.  We use the recently added HLLC Riemann solver
+\citep{Toro94_HLLC} for additional stability in strong shocks and
+rarefaction waves.  We use the nine-species (\ion{H}{1}, \ion{H}{2},
+\ion{He}{1}, \ion{He}{2}, \ion{He}{3}, e$^-$, \hh, \hh$^+$, H$^-$)
+non-equilibrium chemistry model in \enzo~\citep{Abel97, Anninos97} and
+the \hh~cooling rates from \citet{Glover08_Rates}.  We spatially
 distinguish metal enrichment from Pop II and Pop III stars.  We will
 follow-up this study with one that considers radiative cooling from
-metal-enriched gas, using the method of \citet{2008MNRAS.385.1443S}.
+metal-enriched gas, using the method of \citet{2008MNRAS.385.1443S}
+that is already implemented in \enzo.
 
-% We peform two simulations with the same initial conditions.  They
-% differ only in that one considers primordial cooling, and the other
-% considers additional cooling in metal-enriched gas.  For primordial
-% cooling, we use a non-equilbrium chemistry solver with 9 species of
-% hydrogen, helium, and molecular hydrogen.  For metal cooling, we use a
-% cooling curve that is calculated from CLOUDY \citep{CLOUDY} and using
-% the method of \citep{2008MNRAS.385.1443S}.  It is tabulated based on
-% density, temperature, electron fraction, and metallicity.
+To resolve minihalos with at least 100 dark matter (DM) particles and
+follow the formation of the first generation of dwarf galaxies, we use
+a simulation box of 1 Mpc that has a resolution of $256^3$.  This
+gives us a DM mass resolution of 1840 \Ms.  We refine the grid on
+baryon overdensities of $3 \times 2^{-0.2l}$, where $l$ is the AMR
+level, resulting in a super-Lagrangian behavior \citep[also
+  see][]{OShea08}.  We also refine on a DM overdensity of $3 \times
+2^l$ and always resolve the local Jeans length by at least 4 cells,
+avoiding artificial fragmentation during gaseous collapses
+\citep{Truelove97}.  If any of these critera are met in a single cell,
+it is flagged for further spatial refinement.
+
+We initialize the simulation with \textsc{grafic}
+\citep{Bertschinger01} at $z = 130$ and use the cosmological
+parameters from the 7-year WMAP $\Lambda$CDM+SZ+LENS best fit
+\citep{WMAP7}: $\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b
+= 0.0449$, $h = 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$ with the
+variables having their usual definitions.  We use a maximum refinement
+level of $l = 12$, resulting in a maximal comoving resolution of 1 pc.
+We stop the simulation at $z=7$ to prevent any large-scale modes with
+$r \sim L_{\rm box}/2$ from entering the non-linear growth regime.  At
+the final redshift, the baseline simulation has $1.4 \times 10^8$
+computational cells and required 250,000 CPU hours, using 512 cores.
 
 \subsection{Star formation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+%\epsscale{1.15}
+\plotone{f2}
+%\epsscale{1}
+\caption{\label{fig:projections} Density-weighted projections of gas
+  density (top), temperature (middle), and metallicity (bottom) at
+  $z=7$.  The left column shows the entire simulation volume, where
+  the center and right columns focus on the intense and quiet halos,
+  which are marked by left and right arrows in the upper-left panel.
+  The metallicity projections are a composite picture of metals
+  originating from Pop III (red) and Pop II (blue) stars with magenta
+  indicating a mixture of the two.}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-We treat Pop II SF with the same prescription as \citet{Wise09}, which
-is a modified version of the \citet{Cen92} method but accounts for the
-fact that the molecular clouds are resolved.  The critical overdensity
-is the same as the Pop III SF model.  In each star-forming region,
-seven percent of the cold gas ($T < 10^3$ K) is removed from the grid
-and deposited into the star particle that lives for 20 Myr, the
-maximum lifetime of an OB star.  These stars generate the majority of
-the ionizing radiation and SNe feedback in stellar clusters, thus we
-ignore lower mass stars.
+We treat Pop II star formation with the same prescription as
+\citet{Wise09}, which is similar to the Pop III prescription but
+without the \hh~fraction floor that is removed because the
+metal-enriched gas can efficiently cool even in the presence of a
+strong UV radiation field \citep[e.g.][]{Safranek10}.  This method is
+effectively a modified version of the \citet{Cen92} method but
+accounts for the fact that the molecular clouds are resolved.  In the
+simulation, we define the molecular cloud as a sphere, centered on the
+most dense cell, with a dynamical time $t_{\rm dyn} = 3$ Myr
+(corresponding to an average density $\bar{\rho}_{\rm MC} \simeq
+1000\mu \cubecm$) and a radius $R_{\rm MC}$, where $\mu$ is the mean
+molecular weight.  In this sphere, a fraction $c_\star = 0.07 f_{\rm
+  cold}$ of the cold gas ($T < 10^3$ K) is converted into a star
+particle with mass $m_\star = c_\star (4\pi/3) \bar{\rho}_{\rm MC}
+R_{\rm MC}^3$.  We then replace the sphere with a uniform density
+$\rho_{\rm MC} = (1 - c_\star) / (Gt_{\rm dyn}^2)$ and temperature $T
+= 10^4$ K, which approximates the initial stages of an \ion{H}{2}
+region.  Similar to the Pop III treatment, we merge any newly created
+particles within a radius $R_{\rm merge}$.  We set the minimum mass of
+a star particle to $m_{\rm \star, min} = 1000 \Ms$.  If the initial
+mass does not exceed $m_{\rm \star, min}$, the star particle does not
+provide any feedback and continues to accrete until it reaches $m_{\rm
+  \star, min}$.  The star particles live for 20 Myr, the maximum
+lifetime of an OB star.  These stars generate the majority of the
+ionizing radiation and SNe feedback in stellar clusters, thus we
+ignore any feedback from lower mass stars.
 
 \subsection{Stellar feedback}
-
-\begin{figure*}
-%\epsscale{1.15}
-\plotone{f2}
-%\epsscale{1}
-\caption{\label{fig:projections} Density-weighted projections of gas
-  density (top), temperature (middle), and metallicity (bottom) at
-  $z=7$.  The left column shows the entire simulation volume, where
-  the center and right columns focus on the intense and quiet halos,
-  which are marked by left and right arrows in the upper-left panel.
-  The metallicity projections are a composite picture of metals
-  originating from Pop III (red) and Pop II (blue) stars with magenta
-  indicating a mixture of the two.}
-\end{figure*}
 
@@
 to the hydrodynamics.  We model the \hh~dissociating radiation with an
-optically-thin, inverse square profile, centered on all stars.  These
-stars die as pair-instability SNe (PISNe) if they are in the mass
-range 140--260 \Ms~\citep{Heger03}.  We use the explosion energy from
-\citet{Heger02}, where we fit the following function to their models,
-$E_{\rm PISN} = 10^{51} \times [5.0 + 1.304 (M_{\rm He} - 64)]$, where
-$M_{\rm He} = (13/24) \times (M_\star - 20) \Ms$ is the helium core
-(and equivalently the ejecta) mass and $M_\star$ is the stellar mass.
+optically-thin, inverse square profile, centered on all star
+particles.  These stars die as pair-instability SNe (PISNe) if they
+are in the mass range 140--260 \Ms~\citep{Heger03}.  We use the
+explosion energy from \citet{Heger02}, where we fit the following
+function to their models, $E_{\rm PISN} = 10^{51} \times [5.0 + 1.304
+  (M_{\rm He} - 64)]$, where $M_{\rm He} = (13/24) \times (M_\star -
+20) \Ms$ is the helium core (and equivalently the ejecta) mass and
+$M_\star$ is the stellar mass.
 
-The Pop II stars emit 6000 hydrogen ionizing photons per baryon over
-their lifetime, and we do not consider singly- and doubly-ionizing
-helium photons.  We note that low-metallicity stars generate up to a
-factor of four more ionizing photons than a solar metallicity
-population \citep{Schaerer03} and might be underestimating the
-radiative feedback.  Nonetheless this study provides an excellent
+The Pop II star particles emit 6000 hydrogen ionizing photons per
+baryon over their lifetime, and we do not consider singly- and
+doubly-ionizing helium photons.  We note that low-metallicity stars
+generate up to a factor of four more ionizing photons than a solar
+metallicity population \citep{Schaerer03} and might be underestimating
+the radiative feedback.  Nonetheless this study provides an excellent
 first insight in the transition to Pop II SF, as the metal enrichment

### 2011-07-03 ApJ/ms.tex
Adding SFR, fullbox evolution figures.  Added filtering mass to halo mass history plots.  Added some text (but not all) to describe the new additions.

@@
 
-\newcommand{\fesc}{\ifmmode{f_{\rm esc}}\else{$f_{\rm esc}$}\fi}
-\newcommand{\fescs}{\ifmmode{f_{\rm esc}^\star}\else{$f_{\rm esc}^\star$}\fi}
-\newcommand{\kms}{\ifmmode{{\rm km~s^{-1}}}\else{km s$^{-1}$}\fi}
-\newcommand{\cubecm}{\ifmmode{{\rm cm^{-3}}}\else{cm$^{-3}$}\fi}
-\newcommand{\lsim}{\lower0.3em\hbox{$\,\buildrel <\over\sim\,$}}
-\newcommand{\gsim}{\lower0.3em\hbox{$\,\buildrel >\over\sim\,$}}
-\newcommand{\li}{\noindent$\bullet$\quad}
-\newcommand{\flux}{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$}
-\newcommand{\emis}{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$}
-\newcommand{\sfr}{M$_\odot$ yr$^{-1}$ Mpc$^{-3}$}
-\newcommand{\hst}{{\it HST}}
-\newcommand{\enzo}{{\sl Enzo}}
-\newcommand{\Ms}{\ifmmode{M_\odot}\else{$M_\odot$}\fi}
-\newcommand{\mmin}{M$_{min}$}
-\newcommand{\hh}{H$_2$}
-\newcommand{\Ol}{$\Omega_\Lambda$}
-\newcommand{\Om}{$\Omega_M$}
-\newcommand{\Ob}{$\Omega_b$}
-\newcommand{\theat}{$t_{\rm{heat}}$}
-\newcommand{\tcool}{$t_{\rm{cool}}$}
-\newcommand{\rcool}{$r_{\rm{cool}}$}
-\newcommand{\tcross}{$t_{\rm{cross}}$}
-\newcommand{\tdyn}{$t_{\rm{dyn}}$}
-\newcommand{\tkh}{$t_{\rm{KH}}$}
-\newcommand{\tH}{$t_{\rm{H}}$}
-\newcommand{\tvir}{\ifmmode{T_{\rm{vir}}}\else{$T_{\rm{vir}}$}\fi}
-\newcommand{\mvir}{\ifmmode{M_{\rm{vir}}}\else{$M_{\rm{vir}}$}\fi}
-\newcommand{\rvir}{\ifmmode{r_{\rm{vir}}}\else{$r_{\rm{vir}}$}\fi}
-\newcommand{\rr}{$r_{200}$}
-\newcommand{\lya}{Ly$\alpha$}
-\newcommand{\jj}{\ifmmode{J_{21}}\else{$J_{21}$}\fi}
-\newcommand{\flw}{\ifmmode{F_{LW}}\else{$F_{LW}$}\fi}
-\newcommand{\kph}{\ifmmode{k_{\rm ph}}\else{$k_{\rm ph}$}\fi}
-\newcommand{\tv}{$\langle T \rangle_{\rm v}$}
-\newcommand{\tm}{$\langle T \rangle_{\rm m}$}
-\newcommand{\msun}{{\rm\,M_\odot}} 
-\newcommand{\lsun}{{\rm\,L_\odot}}
-\newcommand{\zsun}{{\rm\,Z_\odot}}
-\newcommand{\etal}{et al.\ }
-\newcommand\tento[1]{$10^{#1}$}
-\newcommand\step[1]{\textit{Step #1}.---}
+\input macros.tex
 
@@
 
-\subsection{Star formation}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{figure}
-%\epsscale{1.15}
+\epsscale{1.15}
 \plotone{f1}
-%\epsscale{1}
+\epsscale{1}
 \caption{\label{fig:massfn} \textit{Top}: Halo mass function of the
@@
   \citet{Warren06}.  \textit{Bottom}: Total Pop II luminosities of
-  halos with constant mass-to-light ratios overplotted.}
+  halos versus dark matter halo mass with constant mass-to-light
+  ratios overplotted.}
 \end{figure}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{figure*}
-%\epsscale{1.15}
-\plotone{f2}
-%\epsscale{1}
-\caption{\label{fig:projections} Density-weighted projections of gas
-  density (top), temperature (middle), and metallicity (bottom) at
-  $z=7$.  The left column shows the entire simulation volume, where
-  the center and right columns focus on the intense and quiet halos,
-  which are marked by left and right arrows in the upper-left panel.
-  The metallicity projections are a composite picture of metals
-  originating from Pop III (red) and Pop II (blue) stars with magenta
-  indicating a mixture of the two.}
+\epsscale{1.15}
+\plotone{bmosaic}
+\epsscale{1}
+  \caption{\label{fig:evo-mosaic} Evolution of the entire simulation
+    volume ($L_{\rm box} = 1$ Mpc) at redshifts 15, 12, 10, 8, and 7
+    (left to right).  Pictured here are the density-weighted
+    projections of density (top), temperature (middle), and
+    metallicity (bottom).  Note how the stellar radiative feedback
+    from low-mass galaxies reionize the majority of the volume.  The
+    metallicity projections are a composite image of metals
+    originating from Pop II (blue) and III (red) stars with magneta
+    indicdating a mixture of the two.}
 \end{figure*}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Star formation}
 
@@
 \label{eqn:imf}
-f(M)dM = M^{-1.3} \exp\left[-\left(\frac{M_{\rm
+f(\log M) dM = M^{-1.3} \exp\left[-\left(\frac{M_{\rm
       char}}{M}\right)^{1.6}\right] dM
@@
 
-\begin{figure*}
-%\epsscale{1.15}
-\plotone{f3}
-%\epsscale{1}
-\caption{\label{fig:evo} (a) Evolution of the total halo mass (top),
-  stellar mass (middle), and gas fraction (bottom) of the quiet
-  (dashed) and intense (solid) halos.  (b) Mass-weighted stellar
-  metallicities and gas metallicities enriched by Pop II and Pop III
-  SNe of the intense (top) and quiet (bottom) halos.}
-\end{figure*}
-
 \section{Results}
 \label{sec:results}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+\epsscale{1.15}
+\plotone{hmosaic}
+\epsscale{1}
+  \caption{\label{fig:halo-mosaic} Density-weighted projections of
+    density (left), temperature (center), and metallicity (right) of
+    the two selected haloes at $z=7$.  The field of view is 5 proper
+    kpc, and the circles have a radius of $r_{200}$.  The composite
+    metallicity images are constructed in the same fashion as
+    Fig. \ref{fig:evo-mosaic}.}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+\epsscale{1.15}
+\plotone{sfr}
+\epsscale{1}
+\caption{\label{fig:sfr} Cosmic star formation rates for Pop II
+  (solid) and III (dashed).  Note that the Pop III rates are nearly
+  constant from redshift 12 to 7.  Pristine haloes still survive in
+  underdense regions, supporting late-time metal-free star formation.}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-% We start with the mass accretion history and enrichment of the
-% halos.  We then compare the nature of the stellar populations in
-% these halos.
+We illustrate the evolution of the simulation from $z=15$ to $z=7$ in
+Figure \ref{fig:evo-mosaic} with density weighted projections of gas
+density, temperature, and metallicity of the entire box.  Figure
+\ref{fig:halo-mosaic} shows the same types of plots but focusing on
+the two halos of interest with a field of view of 5 proper kpc.
+Radiative and mechanical feedback create a multi-phase medium inside
+these halos, which are embedded in a warm and ionized IGM.
 
-We illustrate the state of the simulation at $z=7$ in Figure
-\ref{fig:projections} with density weighted projections of gas
-density, temperature, and metallicity, showing the entire box and
-focusing on the two halos of interest.  Radiative and mechanical
-feedback create a multi-phase medium inside these halos, which are
-embedded in a warm and ionized IGM.
+\subsection{Global star formation rate}
+
+Figure \ref{fig:sfr} shows the cosmic star formation rate (SFR) in the
+simulation for Pop II and III stars.  Metal-free stars form at a
+nearly constant rate of $5 \times 10^{-4}$ \sfr~until the end of the
+simulation.  The dissociating and ionization radiation from nearby Pop
+III stars and galaxies do not halt the formation of such stars in
+low-mass haloes but only suppress them.  We expect a uniform
+\hh~dissociating (Lyman-Werner) radiation background to further delay
+them \citep{Machacek01, Wise07, OShea08}.  Metal-enriched star
+formation begins early in the simulation at $z \sim 16$ when a PISN
+blastwave overtakes a satellite halo with $M \sim 5 \times 10^5 \Ms$,
+triggering star formation there.  It rises steadily as
+$\rho_{\rm {\star,II}} \propto \exp(-z/1.1)$ until reaching $2 \times
+10^{-2}$ \sfr~at $z=7$.  This value agrees with derived SFRs from
+$z=6-10$ galaxy luminosity functions \citep[e.g.][]{Bouwens10} and
+large-scale galaxy formation simulations \citep[e.g.][]{Schaye10}.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+\epsscale{1.15}
+\plotone{f3}
+\epsscale{1}
+\caption{\label{fig:evo} (a) Evolution of the total halo mass (top),
+  stellar mass (middle), and gas fraction (bottom) of the quiet
+  (dashed) and intense (solid) halos.  In the top panel, the filtering
+  halo mass is plotted as the thick black line (overlapping with the
+  quiet halo after $z=9$.  (b) Mass-weighted stellar metallicities and
+  gas metallicities enriched by Pop II and Pop III SNe of the intense
+  (top) and quiet (bottom) halos.}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Metallicity evolution}
@@
 well-mixed ISM \citep[cf.][]{Wise08_Gal, Greif10} are apparent in the
-metallicity projections in Figure \ref{fig:projections}.  The average
+metallicity projections in Figure \ref{fig:halo-mosaic}.  The average
 stellar metallicity is within 0.5 dex of $[\bar{Z}_2/H]$.
@@
 metallicity within 0.1 dex.
-
-\begin{figure*}
-%\epsscale{1.1}
-\plotone{f4}
-%\epsscale{1}
-\caption{\label{fig:pops} The scatter plots show the SF history of the
-  quiet (left) and intense (right) halos as a function of metallicity
-  at $z=7$.  Each circle represents a star cluster, whose area is
-  proportional to its mass.  The open circles in the upper right
-  represent $10^3$, $10^4$, and $10^5$ \Ms~star clusters.  The dashed
-  lines in the right panel guide the eye to two stellar populations
-  that were formed in two satellite halos, merging at $z=7.5$.  The
-  upper histogram shows the SFR.  The right histogram depicts the
-  stellar metallicity distribution.}
-\end{figure*}
 
@@
 %% \li Present the stellar metallicity distribution at the final time
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+\plottwo{sfh1}{sfh2}
+\caption{\label{fig:pops} The scatter plots show the SF history of the
+  quiet (left) and intense (right) halos as a function of metallicity
+  at $z=7$.  Each circle represents a star cluster, whose area is
+  proportional to its mass.  The open circles in the upper right
+  represent $10^3$, $10^4$, and $10^5$ \Ms~star clusters.  The dashed
+  lines in the right panel guide the eye to two stellar populations
+  that were formed in two satellite halos, merging at $z=7.5$.  The
+  upper histogram shows the SFR.  The right histogram depicts the
+  stellar metallicity distribution.}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-In this Letter, we focus on the birth of two galaxies prior to
-reionization with a cosmological AMR radiation hydrodynamics
-simulation.  Supernovae from Pop III stars provide the necessary heavy
-elements for the transition to a Population II stellar population,
-which we have directly simulated.  These two galaxies have a 10--15\%
-probability in surviving as present-day ``fossil'' galaxies
-\citep{Gnedin06}, otherwise they will be incorporated into galactic
-stellar halos.  A $z=8.55$ galaxy was recently spectroscopically
-confirmed that is contained in an ionized bubble with radius 0.1--0.5
-Mpc with an uncharacterized population of galaxies contributing to the
-local ionizing radiation field \citep{Lehnert10_z8.6}.  The galaxies
+We have focused on the birth of two galaxies prior to reionization
+with a cosmological AMR radiation hydrodynamics simulation.
+Supernovae from Pop III stars provide the necessary heavy elements for
+the transition to a Population II stellar population, which we have
+directly simulated.  These two galaxies have a 10--15\% probability in
+surviving as present-day ``fossil'' galaxies \citep{Gnedin06},
+otherwise they will be incorporated into galactic stellar halos.  A
+$z=8.55$ galaxy was recently spectroscopically confirmed that is
+contained in an ionized bubble with radius 0.1--0.5 Mpc with an
+uncharacterized population of galaxies contributing to the local
+ionizing radiation field \citep{Lehnert10_z8.6}.  The galaxies
 simulated here might represent this population and should be detected

### 2011-07-03 ApJ/merge_eps.py

@@ -1,0 +1,9 @@
+from pyx import *
+
+files = ["f3a.eps", "f3b.eps"]
+newfile = "f3"  # omit .eps
+
+c = canvas.canvas()
+c.insert(epsfile.epsfile(0,0,files[0]))
+c.insert(epsfile.epsfile(20.5,0,files[1]))
+c.writeEPSfile(newfile)

### 2011-07-06 ApJ/ms.tex
Adding halo enrichment figure and some text on the cosmic SFR.

@@
   Matthew J. Turk\altaffilmark{3},
-  Michael L. Norman\altaffilmark{3},
-  Tom Abel\altaffilmark{4}}
+  Michael L. Norman\altaffilmark{4},
+  Tom Abel\altaffilmark{5,6,7}}
 
@@
 \altaffiltext{2}{Hubble Fellow}
-\altaffiltext{3}{Center for Astrophysics and Space Sciences,
+\altaffiltext{3}{Department of Astronomy, Columbia University, 538
+  West 120th Street, New York, NY 10027}
+\altaffiltext{4}{Center for Astrophysics and Space Sciences,
   University of California at San Diego, La Jolla, CA 92093}
-\altaffiltext{4}{Kavli Institute for Particle Astrophysics and
+\altaffiltext{5}{Kavli Institute for Particle Astrophysics and
   Cosmology, Stanford University, Menlo Park, CA 94025}
+\altaffiltext{6}{Zentrum f\"ur Astronomie der Universit\"at, Institut
+  f\"ur Theoretische Astrophysik, Albert-Ueberle-Str. 2, 69120
+  Heidelberg, Germany}
+\altaffiltext{7}{Heidelberg Institut f\"ur Theoretische Studien,
+  Schloss-Wolfsbrunnenweg 35, 69118 Heidelberg, Germany}
+
 \email{jwise@astro.princeton.edu}
@@
 from \citet{Schaerer02}.  The radiation field is evolved with adaptive
-ray tracing \citep{Abel02_RT, Wise10} and is coupled self-consistently
-to the hydrodynamics.  We model the \hh~dissociating radiation with an
-optically-thin, inverse square profile, centered on all star
-particles.  These stars die as pair-instability SNe (PISNe) if they
-are in the mass range 140--260 \Ms~\citep{Heger03}.  We use the
-explosion energy from \citet{Heger02}, where we fit the following
+ray tracing \citep{Abel02_RT, Wise11_Moray} and is coupled
+self-consistently to the hydrodynamics.  We model the \hh~dissociating
+radiation with an optically-thin, inverse square profile, centered on
+all star particles.  These stars die as pair-instability SNe (PISNe)
+if they are in the mass range 140--260 \Ms~\citep{Heger03}.  We use
+the explosion energy from \citet{Heger02}, where we fit the following
 function to their models, $E_{\rm PISN} = 10^{51} \times [5.0 + 1.304
@@
 
-Here we present the gaseous and stellar evolution of two selected
-halos in the simulation: one that has an early mass buildup but no
-major mergers after $z=12$, and one that experiences a series of major
-mergers between $z=10$ and $z=7$.  We name the halos ``quiet'' and
-``intense'', respectively.  The entire simulation contains 38 galaxies
-with 3640 Pop II stellar clusters and captures the formation of 333
-Pop III stars.  The halo mass function and galaxy luminosities are
-plotted in Figure \ref{fig:massfn}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+\epsscale{1.15}
+\plotone{z3}
+\epsscale{1}
+\caption{\label{fig:z3} Average halo metallicity from Pop III SNe as a
+  function of total halo mass.  Inhomogenous metal enrichment causes
+  the large spread in metallicity at low masses.  At $M_{\rm halo} > 3
+  \times 10^7 \Ms$, all halos are enriched by Pop III SNe above [Z/H]
+  $>$ --4.  The y-axis error bars show the 25\% and 75\% percentile
+  values because the underlying distribution is not Gaussian.}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Here we first present the global star formation rate (SFR) and metal
+enrichment during early galaxy formation and then focus on the gaseous
+and stellar evolution of two selected halos in the simulation: one
+that has an early mass buildup but no major mergers after $z=12$, and
+one that experiences a series of major mergers between $z=10$ and
+$z=7$.  We name the halos ``quiet'' and ``intense'', respectively.
+The entire simulation contains 38 galaxies with 3640 Pop II stellar
+clusters and captures the formation of 333 Pop III stars.  The halo
+mass function and galaxy luminosities are plotted in Figure
+\ref{fig:massfn}.
 
@@
 
-Figure \ref{fig:sfr} shows the cosmic star formation rate (SFR) in the
-simulation for Pop II and III stars.  Metal-free stars form at a
-nearly constant rate of $5 \times 10^{-4}$ \sfr~until the end of the
-simulation.  The dissociating and ionization radiation from nearby Pop
-III stars and galaxies do not halt the formation of such stars in
-low-mass haloes but only suppress them.  We expect a uniform
-\hh~dissociating (Lyman-Werner) radiation background to further delay
-them \citep{Machacek01, Wise07, OShea08}.  Metal-enriched star
-formation begins early in the simulation at $z \sim 16$ when a PISN
-blastwave overtakes a satellite halo with $M \sim 5 \times 10^5 \Ms$,
-triggering star formation there.  It rises steadily as
-$\rho_{\rm {\star,II}} \propto \exp(-z/1.1)$ until reaching $2 \times
-10^{-2}$ \sfr~at $z=7$.  This value agrees with derived SFRs from
-$z=6-10$ galaxy luminosity functions \citep[e.g.][]{Bouwens10} and
-large-scale galaxy formation simulations \citep[e.g.][]{Schaye10}.
+Figure \ref{fig:sfr} shows the cosmic SFR in the simulation for Pop II
+and III stars.  Metal-free stars form at a nearly constant rate of $5
+\times 10^{-4}$ \sfr~until the end of the simulation.  The
+dissociating and ionization radiation from nearby Pop III stars and
+galaxies do not halt the formation of such stars in low-mass haloes
+but only suppress them.  We expect a uniform \hh~dissociating
+(Lyman-Werner) radiation background to further delay them
+\citep{Machacek01, Wise07, OShea08}.  Metal-enriched star formation
+begins early in the simulation at $z \sim 16$ when a PISN blastwave
+overtakes a satellite halo with $M \sim 5 \times 10^5 \Ms$, triggering
+star formation there.  After $z=12$ in our simulation, it rises
+steadily as $\rho_{\rm {\star,II}} \propto \exp(-z/1.1)$.  Star
+formation commences gradually in the smallest galaxies because of
+lowered gas fractions, causing a much steeper time dependency than
+$\exp(-z/3)$ relation found in \citet{Hernquist03}.  Note that they
+also acknowledged a steeper relation should exist at early times.  At
+redshift 7, it reaches $2 \times 10^{-2}$ \sfr.  This value agrees
+with derived SFRs from $z=6-10$ galaxy luminosity functions
+\citep[e.g.][]{Bouwens10} and large-scale galaxy formation simulations
+\citep[e.g.][]{Schaye10}.
+
+\subsection{Pre-enrichment from Population III stars}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+\epsscale{1.15}
+\plotone{f3}
+\epsscale{1}
+\caption{\label{fig:evo} (a) Evolution of the total halo mass (top),
+  stellar mass (middle), and gas fraction (bottom) of the quiet
+  (dashed) and intense (solid) halos.  In the top panel, the filtering
+  halo mass is plotted as the thick black line (overlapping with the
+  quiet halo after $z=9$.  (b) Mass-weighted stellar metallicities and
+  gas metallicities enriched by Pop II and Pop III SNe of the intense
+  (top) and quiet (bottom) halos.}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Both halos start forming Pop II stars when $M = 10^7 \Ms$.  This is
-consistent with the filtering mass $M_f$ of high-redshift halos when
-it accretes mainly from a pre-heated IGM \citep{gnedin98, gnedin00,
-  Wise08_Gal}.  Afterwards these halos can cool efficiently through
-\hh~cooling, sustaining constant and sometimes bursting SF.  The
-latter characteristics are equated with the definition of a galaxy.
-The quiet halo forms $10^5 \Ms$ of stars by $z=9$.  This initial
-starburst photo-evaporates the majority of its molecular clouds, in
-addition to heating and ionizing the surrounding IGM out to a radius
-of 10--15 kpc at $z=9$.  These respectively reduce the in-situ and
-external cold gas supply that could feed future SF.
+consistent with the filtering mass $M_f$, which is plotted as a thick
+line in Figure \ref{fig:evo}a, of high-redshift halos when it accretes
+mainly from a pre-heated IGM \citep{gnedin98, gnedin00, Wise08_Gal}.
+Afterwards these halos can cool efficiently through \hh~cooling,
+sustaining constant and sometimes bursting SF.  The latter
+characteristics are equated with the definition of a galaxy.  The
+quiet halo forms $10^5 \Ms$ of stars by $z=9$.  This initial starburst
+photo-evaporates the majority of its molecular clouds, in addition to
+heating and ionizing the surrounding IGM out to a radius of 10--15 kpc
+at $z=9$.  These respectively reduce the in-situ and external cold gas
+supply that could feed future SF.
 
@@
 with the ample supply of gas during this period.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-\epsscale{1.15}
-\plotone{f3}
-\epsscale{1}
-\caption{\label{fig:evo} (a) Evolution of the total halo mass (top),
-  stellar mass (middle), and gas fraction (bottom) of the quiet
-  (dashed) and intense (solid) halos.  In the top panel, the filtering
-  halo mass is plotted as the thick black line (overlapping with the
-  quiet halo after $z=9$.  (b) Mass-weighted stellar metallicities and
-  gas metallicities enriched by Pop II and Pop III SNe of the intense
-  (top) and quiet (bottom) halos.}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-J.~H.~W. is supported by NASA through Hubble Fellowship grant
-\#120-6370 awarded by the Space Telescope Science Institute, which is
-operated by the Association of Universities for Research in Astronomy,
-Inc., for NASA, under contract NAS 5-26555.  M.~J.~T. and
-M.~L.~N. acknowledge partial support from NASA ATFP grant NNX08AH26G.
-Computational resources were provided by NASA/NCCS award SMD-09-1439.
 J.~H.~W. thanks Renyue Cen, Amina Helmi, Marco Spaans, and Eline
-Tolstoy for enlightening discussions.  The majority of the analysis
-and plots were done with \texttt{yt} \citep{yt_full_paper}.
+Tolstoy for enlightening discussions.  J.~H.~W. is supported by NASA
+through Hubble Fellowship grant \#120-6370 awarded by the Space
+Telescope Science Institute, which is operated by the Association of
+Universities for Research in Astronomy, Inc., for NASA, under contract
+NAS 5-26555.  M.~J.~T. and M.~L.~N. acknowledge partial support from
+NASA ATFP grant NNX08AH26G.  Computational resources were provided by
+NASA/NCCS award SMD-09-1439.  TA acknowledges financial support from
+the {\em Baden-W\"{u}rttemberg-Stiftung} under grant P-LS-SPII/18, the
+Heidelberg Institut f\"ur Theoretische Studien. This work was
+partially supported by NASA ATFP grant NNX08AH26G and NSF
+AST-0807312. This research has made use of NASA’s Astrophysics Data
+System Bibliographic Services.  The majority of the analysis and plots
+were done with \texttt{yt} \citep{yt_full_paper}.
 

### 2011-07-25 ApJ/ms.tex
Some more additions and changes to added content.

@@
 
-\begin{figure}
-\epsscale{1.15}
-\plotone{f1}
-\epsscale{1}
-\caption{\label{fig:massfn} \textit{Top}: Halo mass function of the
-  simulation compared with the analytical fit (solid) of
-  \citet{Warren06}.  \textit{Bottom}: Total Pop II luminosities of
-  halos versus dark matter halo mass with constant mass-to-light
-  ratios overplotted.}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{figure*}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-\epsscale{1.15}
-\plotone{z3}
-\epsscale{1}
-\caption{\label{fig:z3} Average halo metallicity from Pop III SNe as a
-  function of total halo mass.  Inhomogenous metal enrichment causes
-  the large spread in metallicity at low masses.  At $M_{\rm halo} > 3
-  \times 10^7 \Ms$, all halos are enriched by Pop III SNe above [Z/H]
-  $>$ --4.  The y-axis error bars show the 25\% and 75\% percentile
-  values because the underlying distribution is not Gaussian.}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Here we first present the global star formation rate (SFR) and metal
-enrichment during early galaxy formation and then focus on the gaseous
-and stellar evolution of two selected halos in the simulation: one
-that has an early mass buildup but no major mergers after $z=12$, and
-one that experiences a series of major mergers between $z=10$ and
-$z=7$.  We name the halos ``quiet'' and ``intense'', respectively.
-The entire simulation contains 38 galaxies with 3640 Pop II stellar
-clusters and captures the formation of 333 Pop III stars.  The halo
-mass function and galaxy luminosities are plotted in Figure
-\ref{fig:massfn}.
+Here we first present the global star formation rate (SFR) during
+early galaxy formation and then focus on the gaseous and stellar
+evolution of two selected halos in the simulation: one that has an
+early mass buildup but no major mergers after $z=12$, and one that
+experiences a series of major mergers between $z=10$ and $z=7$.  We
+name the halos ``quiet'' and ``intense'', respectively.  The entire
+simulation contains 38 galaxies with 3640 Pop II stellar clusters and
+captures the formation of 333 Pop III stars.
 
@@
 
-\subsection{Pre-enrichment from Population III stars}
+\subsection{Mass evolution}
+\label{sec:halo}
+
+%\li Describe the evolution of the baryon fraction and metallicity from
+%PISN and Type II SNe metals in the two halos.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Mass evolution}
-\label{sec:halo}
-
-%\li Describe the evolution of the baryon fraction and metallicity from
-%PISN and Type II SNe metals in the two halos.
 
@@
 metallicity within 0.1 dex.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+\epsscale{1.15}
+\plotone{z3}
+\epsscale{1}
+\caption{\label{fig:z3} Average halo metallicity from Pop III SNe as a
+  function of total halo mass.  Inhomogenous metal enrichment causes
+  the large spread in metallicity at low masses.  At $M_{\rm halo} > 3
+  \times 10^7 \Ms$, all halos are enriched by Pop III SNe above [Z/H]
+  $>$ --4.  The y-axis error bars show the 25\% and 75\% percentile
+  values because the underlying distribution is not Gaussian.}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To further demonstrate the metallicity floor in high-redshift dwarf
+galaxies, we show the average metallicity from Pop III SNe \zthree~in
+all haloes as a function of halo mass at $z =$ 7, 8, 9, and 10 in
+Fig. \ref{fig:z3}, and it is strongly dependent on halo mass.  The
+\zthree~error bars mark the 25\% and 75\% percentiles of the
+distribution at $M = M_{\rm halo}$ because the underlying distribution
+is not necessarily Gaussian at all halo masses.  Above $3 \times 10^7
+\Ms$, all haloes enriched to $\zthree \ga -4$ with little time
+evolution, further illustrating the metallicity floor.  Below this
+halo mass, the distribution is roughly bimodal composed of pristine
+and metal-enriched halos.
 
@@
 
+\subsection{Mass-to-light ratios}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+\epsscale{1.15}
+\plotone{f1}
+\epsscale{1}
+\caption{\label{fig:massfn} Total Pop II luminosities of halos versus
+  total halo mass with constant mass-to-light ratios overplotted.}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Mass-to-light ratios are crucial in interpreting observations when
+connecting the galaxy to its DM halo, and ultimately to models of
+galaxy formation.  For this paper, we use a simple model to calculate
+the total stellar luminosity of each galaxy.  In a later paper, we
+will follow up with more sophisicated models to determine more
+accurate observables.  Stars in each particle are treated an
+instantaneous burst.  Using the empirical law of main sequence
+lifetime $t_{\rm MS} \propto M^{-5/2}$, the maximum stellar mass in
+such a system is dependent only on its age $t_\star$, so $M_{\rm up} =
+(t_\star / 10\;\mathrm{Gyr})^{-2/5}$.  Then combining another scaling
+law $L \propto M^{7/2}$ and the Salpeter IMF $\psi(M) \propto
+M^{-\alpha}$,
+%
+\begin{eqnarray}
+  \label{eqn:lum}
+  L/M_\odot &=& \int_{M_{\rm lo}}^{M_{\rm up}} \psi(M) L(M) dM
+  \nonumber\\ &\simeq& M_{\rm up}^{9/2-\alpha} (9/2 - \alpha)^{-1},
+\end{eqnarray}
+where we set $M_{\rm lo} \equiv 0$ because it is negligible in the
+luminosity.  Then the galaxy luminosity is the sum of all star
+particle luminosities, which we plot in Fig. \ref{fig:massfn} with
+respect to halo mass, along with the DM halo mass function.
+
+Recall that the most massive halo ($M_{\rm tot} = 10^9 \Ms$) is
+undergoing a starburst at $z=7$, translating into a relatively high
+$M/L = 6$.  The lower mass galaxies show a spread in M/L over two
+orders of magnitude, similar to the Sloan Digital Sky Survey (SDSS)
+observations of local dSph galaxies \citep[e.g.][]{Strigari08}.
+
 \section{Discussion and Conclusions}
@@
 on the same order \citep{Wolfe05_Review}, and metal enrichment from Pop
-III SNe provides a possible explanation.
+III SNe provides a possible explanation \citep{Kobayashi11}.
 

### 2011-07-27 ApJ/ms.tex
Minor changes.  Fixed the hypernova discussion.

@@
 in the Milky Way halo and nearby dwarf spheroidal (dSph) galaxies,
-both with a metallicity floor of [Z/H] = --4 \citep{Beers05,
-  Tafelmeyer10, Frebel10_Obs}.
+both with a metallicity floor of [Z/H]\footnote{We use the
+  conventional notation, [Z/H] $\equiv \log(Z/H) -
+  \log(Z_\odot/H_\odot)$.} = --4 \citep{Beers05, Tafelmeyer10,
+  Frebel10_Obs}.
 
@@
 We use the adaptive mesh refinement (AMR) code
-\textsc{enzo~v2.0}\footnote{\texttt{enzo.googlecode.com, changeset
+enzo~v2.0\footnote{\texttt{enzo.googlecode.com, changeset
     b86d8ba026d6}} \citep{OShea2004}.  It uses an $N$-body adaptive
@@
 
-We initialize the simulation with \textsc{grafic}
-\citep{Bertschinger01} at $z = 130$ and use the cosmological
-parameters from the 7-year WMAP $\Lambda$CDM+SZ+LENS best fit
-\citep{WMAP7}: $\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b
-= 0.0449$, $h = 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$ with the
-variables having their usual definitions.  We use a maximum refinement
-level of $l = 12$, resulting in a maximal comoving resolution of 1 pc.
-We stop the simulation at $z=7$ to prevent any large-scale modes with
-$r \sim L_{\rm box}/2$ from entering the non-linear growth regime.  At
-the final redshift, the baseline simulation has $1.4 \times 10^8$
-computational cells and required 250,000 CPU hours, using 512 cores.
+We initialize the simulation with grafic \citep{Bertschinger01} at $z
+= 130$ and use the cosmological parameters from the 7-year WMAP
+$\Lambda$CDM+SZ+LENS best fit \citep{WMAP7}: $\Omega_M = 0.266$,
+$\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 =
+0.81$, and $n = 0.963$ with the variables having their usual
+definitions.  We use a maximum refinement level of $l = 12$, resulting
+in a maximal comoving resolution of 1 pc.  We stop the simulation at
+$z=7$ to prevent any large-scale modes with $r \sim L_{\rm box}/2$
+from entering the non-linear growth regime.  At the final redshift,
+the simulation has $1.4 \times 10^8$ computational cells and required
+250,000 CPU hours, using 512 cores.
 
@@
 Simulations have shown that the characteristic mass of Pop III stars
-$M_{\rm char} \sim 100~\Ms$.  They form in molecular clouds that
-coexist with the dark matter halo center with limited fragmentation
-occurring during their collapse; however \citet{2009Sci...325..601T}
-and \citet{Stacy10_Binary} have recently shown that Pop III binaries
-may form in a fraction of such halos.
+$M_{\rm char} \sim 100~\Ms$ \citep{ABN02, Bromm02_P3, OShea07a}.  They
+form in molecular clouds that coexist with the dark matter halo center
+with limited fragmentation occurring during their collapse; however
+\citet{2009Sci...325..601T} and \citet{Stacy10_Binary} have recently
+shown that Pop III binaries may form in a fraction of such halos.
 
@@
 
-For Pop III stars, we use the same SF model as \citet{Wise08_Gal} where
-each star particle represents a single star, forming at an overdensity
-of $5 \times 10^5$.  Instead of using a fixed stellar mass, we randomly
-sampled from an IMF with a functional form of
+For Pop III stars, we use the same SF model as \citet{Wise08_Gal}
+where each star particle represents a single star, forming at an
+overdensity of $5 \times 10^5$ ($\sim 10^3\; \cubecm$ at $z=10$).  If
+multiple cells meet the star particle formation criteria within 1 pc,
+we form one Pop III star particle with the center of mass of these
+flagged cells to ensure that massive star is created per metal-free
+molecular cloud.  Instead of using a fixed stellar mass like in our
+previous work, we randomly sampled from an IMF with a functional form
+of
 %
@@
 hypernovae \citep{Tumlinson07_IMF}, then this metallicity floor should
-be lowered by a factor of $\sim 10$ because (1) the metal ejecta is
-lowered by a factor of $\sim 50$ and (2) the mixing mass is
-approximately decreased by a factor of $(E_{\rm hyp}/E_{\rm
-  PISN})^{3/5}$ in the Sedov-Taylor solution, where $(E_{\rm
-  hyp}/E_{\rm PISN}) \sim 0.1$ is the ratio of explosion energies of a
-hypernova and PISN.  In the case where this metallicity floor is less
-than the critical metallicity, then the next instance of SF will
-further enrich the ISM, solidifying the transition to Pop II SF.  We
-conclude that it only takes one, at most two, SNe from Pop III stars
-in the halo progenitors to complete the transition to Population II
-\citep{Frebel10}.  The question of whether the critical metallicity is
+be lowered by a factor of $\sim 10$ because the metal ejecta from a 40
+\Ms~hypernova is 8.6 \Ms~\citep{Nomoto06}, compared to 85 \Ms~of
+metals produced by a 180 \Ms~PISN \citep{Heger02}.  Both explosions
+have approximately $3 \times 10^{52}$ erg.  Therefore the blastwaves
+from these two explosions should expand to equal radii before stalling
+in the IGM.  We note that stronger metal-line cooling in the PISN case
+may cause the blastwave to stall at a marginally smaller radius.
+
+In the case where this metallicity floor is less than the critical
+metallicity, then the next SN will further enrich the ISM, solidifying
+the transition to Pop II SF.  We conclude that it only takes one, at
+most two, SNe from Pop III stars in the halo progenitors to complete
+the transition to Population II \citep{Frebel10}.  However, this does
+not prohibit more than two instances of Pop III star formation in halo
+from happening because the stars can end in a direct collapse to a BH
+with little or no metal ejecta, keeping the surrounding environment
+pristine.  The question of whether the critical metallicity is
 \tento{-6} or \tento{-3.5} $Z_\odot$ is most applicable to nearby

### 2011-08-04 ApJ/ms.tex
Adding more text and units to colorbar labels.

@@
 
+We first describe the simulation setup and numerical methods behind
+our work in \S\ref{sec:setup}.  Then in \S\ref{sec:results} we present
+the evolution of two selected high-redshift dwarf galaxies, focusing
+on their metallicities and stellar populations.  Last we discuss
+possible dependencies of our results on the Pop III initial mass
+function and conclude in \S\ref{sec:discuss}.
+
 \section{Method}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\input{table1.tex}
 
@@
 Radiative and mechanical feedback create a multi-phase medium inside
-these halos, which are embedded in a warm and ionized IGM.
+these halos, which are embedded in a warm and ionized IGM.  At the
+final redshift, the volume and mass ionized fraction are 0.76 and
+0.72, respectively, which are consistent with large-scale reionization
+simulations \citep{Zahn11}.  PISNe enrich 0.106 and 0.027 of the mass
+and volume, respectively, above $10^{-3} \zsun$, and 0.034 and 0.0024
+of the mass and volume are enriched by Type II SNe above the same
+threshold.  Table \ref{tab:enrich} gives additional enriched fractions
+with different metallicity cuts.
 
@@
 but only suppress them.  We expect a uniform \hh~dissociating
-(Lyman-Werner) radiation background to further delay them
-\citep{Machacek01, Wise07, OShea08}.  Metal-enriched star formation
-begins early in the simulation at $z \sim 16$ when a PISN blastwave
-overtakes a satellite halo with $M \sim 5 \times 10^5 \Ms$, triggering
-star formation there.  After $z=12$ in our simulation, it rises
-steadily as $\rho_{\rm {\star,II}} \propto \exp(-z/1.1)$.  Star
-formation commences gradually in the smallest galaxies because of
-lowered gas fractions, causing a much steeper time dependency than
-$\exp(-z/3)$ relation found in \citet{Hernquist03}.  Note that they
-also acknowledged a steeper relation should exist at early times.  At
+radiation background to further delay them \citep{Machacek01, Wise07,
+  OShea08}.
+
+The cosmic Pop II SFR is best fit with an exponential $\exp(-z/1.1)$.
+Metal-enriched star formation begins early in the simulation at $z
+\sim 16$ when a PISN blastwave overtakes a satellite halo with $M \sim
+5 \times 10^5 \Ms$, triggering star formation there.  At $z>10$, these
+enriched minihalos cause the Pop II SFR to be higher than this
+relation.  Only after $z \sim 10$ does the SFR follows this
+exponential, which is a steeper time dependency than the $\exp(-z/3)$
+relation found in \citet{Hernquist03}.  Note that they also
+acknowledged that this behavior should occur at early times.  At
 redshift 7, it reaches $2 \times 10^{-2}$ \sfr.  This value agrees
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+\plottwo{sfh1}{sfh2}
+\caption{\label{fig:pops} The scatter plots show the SF history of the
+  quiet (left) and intense (right) halos as a function of metallicity
+  at $z=7$.  Each circle represents a star cluster, whose area is
+  proportional to its mass.  The open circles in the upper right
+  represent $10^3$, $10^4$, and $10^5$ \Ms~star clusters.  The dashed
+  lines in the right panel guide the eye to two stellar populations
+  that were formed in two satellite halos, merging at $z=7.5$.  The
+  upper histogram shows the SFR.  The right histogram depicts the
+  stellar metallicity distribution.}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The most massive progenitor of the quiet halo interestingly never
@@
 %% \li Present the stellar metallicity distribution at the final time
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-\plottwo{sfh1}{sfh2}
-\caption{\label{fig:pops} The scatter plots show the SF history of the
-  quiet (left) and intense (right) halos as a function of metallicity
-  at $z=7$.  Each circle represents a star cluster, whose area is
-  proportional to its mass.  The open circles in the upper right
-  represent $10^3$, $10^4$, and $10^5$ \Ms~star clusters.  The dashed
-  lines in the right panel guide the eye to two stellar populations
-  that were formed in two satellite halos, merging at $z=7.5$.  The
-  upper histogram shows the SFR.  The right histogram depicts the
-  stellar metallicity distribution.}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \section{Discussion and Conclusions}
+\label{sec:discuss}
 
@@
 
-J.~H.~W. thanks Renyue Cen, Amina Helmi, Marco Spaans, and Eline
-Tolstoy for enlightening discussions.  J.~H.~W. is supported by NASA
-through Hubble Fellowship grant \#120-6370 awarded by the Space
-Telescope Science Institute, which is operated by the Association of
-Universities for Research in Astronomy, Inc., for NASA, under contract
-NAS 5-26555.  M.~J.~T. and M.~L.~N. acknowledge partial support from
-NASA ATFP grant NNX08AH26G.  Computational resources were provided by
-NASA/NCCS award SMD-09-1439.  TA acknowledges financial support from
-the {\em Baden-W\"{u}rttemberg-Stiftung} under grant P-LS-SPII/18, the
+JHW thanks Renyue Cen, Amina Helmi, Marco Spaans, and Eline Tolstoy
+for enlightening discussions.  JHW is supported by NASA through Hubble
+Fellowship grant \#120-6370 awarded by the Space Telescope Science
+Institute, which is operated by the Association of Universities for
+Research in Astronomy, Inc., for NASA, under contract NAS 5-26555.
+MJT and MLN acknowledge partial support from NASA ATFP grant
+NNX08AH26G.  Computational resources were provided by NASA/NCCS award
+SMD-09-1439.  TA acknowledges financial support from the {\em
+  Baden-W\"{u}rttemberg-Stiftung} under grant P-LS-SPII/18, the
 Heidelberg Institut f\"ur Theoretische Studien. This work was

### 2011-08-04 ApJ/table1.tex
Adding more text and units to colorbar labels.

\begin{deluxetable*}{ccccccc}
%\tablecolumns{7}
\tabletypesize{}
\tablewidth{0pc}
\tablecaption{Enrichment Fractions\label{tab:enrich}}

\tablehead{\colhead{Source} & \colhead{Weighting} & 
  \multicolumn{5}{c}{Metallicity Cut (in units of [Z/H])} \\
%%%%%%%%%%
  \cline{3-7} \\
%%%%%%%%%%
  \colhead{} & \colhead{} & 
  \colhead{-6} & \colhead{-5} & \colhead{-4} & \colhead{-3} & \colhead{-2}
}
\startdata
Pop III & Volume & 0.0384 & 0.0331 & 0.0268 & 0.0188 & 0.00836 \\
Pop III & Mass & 0.144 & 0.125 & 0.102 & 0.0650 & 0.0124 \\
Pop II & Volume & 0.00560 & 0.00397 & 0.00236 & 0.00102 & 0.000266 \\
Pop II & Mass & 0.0525 & 0.0438 & 0.0344 & 0.0251 & 0.0174
\enddata
\end{deluxetable*}

### 2011-08-05 ApJ/table1.tex
Reworked enrichment fraction table.

@@
-\begin{deluxetable*}{ccccccc}
+\begin{deluxetable}{ccccc}
 %\tablecolumns{7}
 \tabletypesize{}
-\tablewidth{0pc}
+\tablewidth{\columnwidth}
 \tablecaption{Enrichment Fractions\label{tab:enrich}}
 
-\tablehead{\colhead{Source} & \colhead{Weighting} & 
-  \multicolumn{5}{c}{Metallicity Cut (in units of [Z/H])} \\
-%%%%%%%%%%
-  \cline{3-7} \\
-%%%%%%%%%%
-  \colhead{} & \colhead{} & 
-  \colhead{-6} & \colhead{-5} & \colhead{-4} & \colhead{-3} & \colhead{-2}
+\tablehead{\colhead{[Z/H]} & 
+  \colhead{$f_v$(Pop III)} & \colhead{$f_m$(Pop III)} & 
+  \colhead{$f_v$(Pop II)} & \colhead{$f_m$(Pop II)}
 }
 \startdata
-Pop III & Volume & 0.0384 & 0.0331 & 0.0268 & 0.0188 & 0.00836 \\
-Pop III & Mass & 0.144 & 0.125 & 0.102 & 0.0650 & 0.0124 \\
-Pop II & Volume & 0.00560 & 0.00397 & 0.00236 & 0.00102 & 0.000266 \\
-Pop II & Mass & 0.0525 & 0.0438 & 0.0344 & 0.0251 & 0.0174
+-6 & 3.84(-2) & 1.44(-1) & 5.60(-2) & 5.25(-2) \\
+-5 & 3.31(-2) & 1.25(-1) & 3.97(-2) & 4.38(-2) \\
+-4 & 2.68(-2) & 1.02(-1) & 2.36(-2) & 3.44(-2) \\
+-3 & 1.88(-2) & 6.50(-2) & 1.02(-2) & 2.51(-2) \\
+-2 & 8.36(-3) & 1.24(-2) & 2.66(-3) & 1.74(-2)
 \enddata
-\end{deluxetable*}
+
+\tablecomments{$f_v$ and $f_m$ are volume filling and mass-weighted
+  fractions, respectively, above several different metallicity cuts.
+  Values are listed in scientific notation with the exponents in
+  parentheses.}
+
+\end{deluxetable}

### 2011-08-05 ApJ/ms.tex
Reworked enrichment fraction table.
Final changes before proofreading.  Renaming figures into f[1-9].eps convention.

@@
 \epsscale{1.15}
-\plotone{bmosaic}
+\plotone{f1}
 \epsscale{1}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\input{table1.tex}
 
@@
 
-We use mass-dependent luminosities and lifetimes of the Pop III stars
-from \citet{Schaerer02}.  The radiation field is evolved with adaptive
-ray tracing \citep{Abel02_RT, Wise11_Moray} and is coupled
-self-consistently to the hydrodynamics.  We model the \hh~dissociating
-radiation with an optically-thin, inverse square profile, centered on
-all star particles.  These stars die as pair-instability SNe (PISNe)
-if they are in the mass range 140--260 \Ms~\citep{Heger03}.  We use
-the explosion energy from \citet{Heger02}, where we fit the following
-function to their models, $E_{\rm PISN} = 10^{51} \times [5.0 + 1.304
-  (M_{\rm He} - 64)]$, where $M_{\rm He} = (13/24) \times (M_\star -
-20) \Ms$ is the helium core (and equivalently the ejecta) mass and
-$M_\star$ is the stellar mass.
+The radiation field is evolved with adaptive ray tracing
+\citep{Abel02_RT, Wise11_Moray} that is based on the HEALPix framework
+\citep{HEALPix} and is coupled self-consistently to the hydrodynamics.
+Each star particle is a point source of hydrogen ionizing radiation
+with the ionizing luminosity equally split between 48 initial rays
+(HEALPix level 2).  We use a mono-chromatic spectrum for the radiation
+with the energy $E_{\rm ph}$ equaling the luminosity-weighted photon
+energy of the spectrum.  For a cosmological simulation that focuses on
+galaxies, this does not significantly affect the overall galactic
+dynamics \citep[see Sec. 6.3 in][]{Wise11_Moray}.  We do not consider helium
+singly- and doubly-ionizing radiation.  As the rays propagate from the
+source or into a high resolution AMR grid, they are adaptively split
+into 4 child rays, increasing the angular resolution of the solution,
+when the solid angle of the ray $\theta = 4\pi/(12 \times 4^{L})$ is
+larger than 1/3 of the cell area, where $L$ is the HEALPix level.  We
+model the \hh~dissociating radiation with an optically-thin, inverse
+square profile, centered on all star particles.  In haloes with $M
+\ga 10^8 \Ms$, the \hh~column density may become large enough to
+self-shield itself from LW radiation \citep{Wise08_Gal}.  Thus we may
+be underestimating the SFRs in our work.
 
-The Pop II star particles emit 6000 hydrogen ionizing photons per
-baryon over their lifetime, and we do not consider singly- and
-doubly-ionizing helium photons.  We note that low-metallicity stars
-generate up to a factor of four more ionizing photons than a solar
-metallicity population \citep{Schaerer03} and might be underestimating
-the radiative feedback.  Nonetheless this study provides an excellent
-first insight in the transition to Pop II SF, as the metal enrichment
-is the key ingredient here.  For SN feedback, these stars generate
-$6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$ after living for 4 Myr,
-which is injected into spheres with a radius of 10 pc.  If the
-resolution of the grid is less than 10/3 pc, we deposit the energy
-into a $3^3$ cube surrounding the star particle.
+We use mass-dependent hydrogen ionizing and LW photon luminosites and
+lifetimes of the Pop III stars from \citet{Schaerer02}.  We use a
+mass-independent photon energy $E_{\rm ph} = 29.6$ eV, appropriate for
+the near-constant $10^5$ K surface temperatures of Pop III stars.
+They die as Type II SNe if $11 \le M_\star/\Ms \le 40$
+\Ms~\citep{Woosley95} and as PISNe if they are in the mass range
+140--260 \Ms~\citep{Heger03}, where $M_\star$ is the stellar mass.
+For normal Type II SNe between 11--20 \Ms, we use an explosion energy
+of \tento{51}~erg and a linear fit to the metal ejecta mass calculated
+in \citet{Nomoto06},
+%
+\begin{equation}
+  \label{eqn:typeii}
+  M_{\rm Z}/\Ms = 0.1077 + 0.3383 \times (M_\star/\Ms - 11).
+\end{equation}
+%
+We model the SNe of stars with $20 \le M_\star/\Ms \le 40$ as
+hypernova with the energies and ejecta masses also taken from
+\citeauthor{Nomoto06}, linearly interpolating their results to
+$M_\star$.  For PISNe, we use the explosion energy from
+\citet{Heger02}, where we fit the following function to their models,
+%
+\begin{equation}
+  \label{eqn:pisn}
+  E_{\rm PISN} = 10^{51} \times [5.0 + 1.304 (M_{\rm He}/\Ms - 64)] \; \mathrm{erg},
+\end{equation}
+%
+where $M_{\rm He} = (13/24) \times (M_\star - 20) \Ms$ is the helium
+core (and equivalently the metal ejecta) mass and $M_\star$ is the
+stellar mass.  The blastwave is modeled by injecting the explosion
+energy and ejecta mass into a sphere of 10 pc, smoothed at its surface
+to improve numerical stability \citep{Wise08_Gal}.  Because we resolve
+the blastwave relatively well with several cells across at its
+initialization, the thermal energy is converted into kinetic energy
+and agrees with the Sedov-Taylor solution \citep[e.g.][]{Greif07}.
+
+The Pop II stars emit 6000 hydrogen ionizing photons per baryon over
+their lifetime and $E_{\rm ph} = 21.6$ eV, appropriate for a [Z/H] =
+$-1.3$ population.  We note that lower-metallicity stars generate up
+to 60\% more ionizing photons and might be underestimating the
+radiative feedback \citep{Schaerer03}.  Nonetheless this study
+provides an excellent first insight in the transition to Pop II SF, as
+the metal enrichment is the key ingredient here.  For SN feedback,
+these stars generate $6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$
+after living for 4 Myr, which is injected into spheres with a radius
+of 10 pc, using the same technique as the Pop III SNe.  However if the
+resolution of the grid is less than 10/3 pc, we distribute the energy
+into a $3^3$ cube surrounding the star particle.  In the same region,
+star particles also return ejected material with mass
+%
+\begin{equation}
+  \label{eqn:SNmass}
+  \Delta m_{\rm ej} = \frac{0.25 \; \Delta t \; M_\star} 
+         {t_0 - 4\;\mathrm{Myr}}
+\end{equation}
+back to the grid at every timestep on the finest AMR level.  Here
+$t_0$ = 20 Myr is the lifetime of the star particle.  This ejected gas
+has solar metallicity $Z = 0.02$, resulting in a total metal yield $y
+= 0.005$.  In addition to numerical stability, energy distribution
+across several cells instead of a single cell has been shown to match
+cosmic SFRs better in galaxy simulations at lower redshifts
+\citep{Smith10}.
 
@@
 \label{sec:results}
+
+\input{table1.tex}
 
@@
 \epsscale{1.15}
-\plotone{hmosaic}
+\plotone{f2}
 \epsscale{1}
@@
 \epsscale{1.15}
-\plotone{sfr}
+\plotone{f3}
 \epsscale{1}
@@
 \epsscale{1.15}
-\plotone{f3}
+\plotone{f4}
 \epsscale{1}
@@
 \epsscale{1.15}
-\plotone{z3}
+\plotone{f5}
 \epsscale{1}
@@
 \begin{figure*}
-\plottwo{sfh1}{sfh2}
+\plottwo{f6a}{f6b}
 \caption{\label{fig:pops} The scatter plots show the SF history of the
@@
 \epsscale{1.15}
-\plotone{f1}
+\plotone{f7}
 \epsscale{1}
 \caption{\label{fig:massfn} Total Pop II luminosities of halos versus
-  total halo mass with constant mass-to-light ratios overplotted.}
+  total halo mass with constant mass-to-light ratios overplotted at
+  redshift 7.  The halos with $M \gsim 10^8 \Ms$ form stars
+  efficiently because they can cool through atomic line cooling,
+  whereas the lower mass galaxies rely on molecular hydrogen cooling
+  only.  The low M/L ratios and spread across two orders of magnitude
+  are similar to ones observed in nearby ultra faint dwarf galaxies.}
 \end{figure}
@@
 undergoing a starburst at $z=7$, translating into a relatively high
-$M/L = 6$.  The lower mass galaxies show a spread in M/L over two
-orders of magnitude, similar to the Sloan Digital Sky Survey (SDSS)
-observations of local dSph galaxies \citep[e.g.][]{Strigari08}.
+$M/L = 6$.  The lower mass galaxies show a spread in M/L between 30
+and 3000, similar to the Sloan Digital Sky Survey (SDSS) observations
+of local ultra faint dwarf (uFd) galaxies \citep[e.g.][]{Strigari08}.
+This is suggestive that these low-mass ($M_{\rm tot} \lsim 10^8 \Ms$)
+galaxies that cannot cool through hydrogen line cooling are the
+progenitors of uFd galaxies \citep{Bovill11a, Bovill11b}.  In this
+scenario, all of the star formation occurs before reionization and
+was subsequently terminated by UV heating from external sources.
 
@@
 
-% We also find that the merger history plays an important role in
-% supplying gas into halos after its first epoch of SF.  Mergers of
-% halos below the filtering mass are inefficient in providing gas
-% whereas the opposite is true for merging halos above the filtering
-% mass.  Halos do not necessarily need $\tvir \ge 10^4$ K to form
-% significant stellar populations; however SFRs dramatically increase,
-% and thus metal enrichment, when this threshold is reached.  Halos
-% with mostly gas-poor mergers or a quiet merger history result in a
-% monotonic increase in metallicity with time.  SFHs become more
-% complex with multiple metallicity-age tracks if the halo experiences
-% mergers with other halos that have an established stellar
-% population.  Furthermore SF that is triggered by blastwaves
-% interacting with molecular clouds can have metallicities up to a
-% factor of 10 higher than the main starburst.  Starbursts at $\tvir =
-% 10^4$ K can enrich the host halo enough to create a bimodal
-% metallicity distribution, where the metal-poor component is created
-% before the burst.  Note that mergers of stellar populations can also
-% create a similar bimodal distribution, which are observed in dSphs
-% \cite{Battaglia10}.
+We also find that the merger history plays an important role in
+supplying gas into halos after its first epoch of SF.  Mergers of
+halos below the filtering mass are inefficient in providing gas
+whereas the opposite is true for merging halos above the filtering
+mass.  Halos do not necessarily need $\tvir \ge 10^4$ K to form
+significant stellar populations; however SFRs dramatically increase,
+and thus metal enrichment, when this threshold is reached.  Halos with
+mostly gas-poor mergers or a queiscent merger history result in a
+monotonic increase in metallicity with time.  SFHs become more complex
+with multiple metallicity-age tracks if the halo experiences mergers
+with other halos that have an established stellar population.
+Furthermore SF that is triggered by blastwaves interacting with
+molecular clouds can have metallicities up to a factor of 10 higher
+than the main starburst.  Starbursts at $\tvir = 10^4$ K can enrich
+the host halo enough to create a bimodal metallicity distribution,
+where the metal-poor component is created before the burst.  Note that
+mergers of stellar populations can also create a similar bimodal
+distribution, which are observed in dSphs \cite{Battaglia10}.
 
@@
 first galaxies and the role of metal-free stars in the early universe.
-There exists a wealth of information in this simulation, and we plan
-to follow up this preliminary report with more detailed analysis of
-the metal enrichment of the IGM, global SF rates, and observational
+We plan to follow up this work by focusing on observational
 connections with high-redshift galaxies and Local Group dwarf galaxies
-in the near future.
+in the near future that can better constrain the physical models and
+assumptions, such as the critical metallicity, radiation backgrounds,
+and IMFs, used in \textit{ab initio} dwarf galaxy simulations.
 

### 2011-08-26 ApJ/ms.tex
Changing affilation to GT.

@@
 
-\author{John H. Wise\altaffilmark{1,2}, 
-  Matthew J. Turk\altaffilmark{3},
-  Michael L. Norman\altaffilmark{4},
-  Tom Abel\altaffilmark{5,6,7}}
+\author{John H. Wise\altaffilmark{1}, 
+  Matthew J. Turk\altaffilmark{2},
+  Michael L. Norman\altaffilmark{3},
+  Tom Abel\altaffilmark{4,5,6}}
 
-\altaffiltext{1}{Department of Astrophysical Sciences, Princeton
-  University, Peyton Hall, Ivy Lane, Princeton, NJ 08544}
-\altaffiltext{2}{Hubble Fellow}
-\altaffiltext{3}{Department of Astronomy, Columbia University, 538
+\altaffiltext{1}{Center for Relativistic Astrophysics, School of
+  Physics, Georgia Institute of Technology, 837 State Street, Atlanta,
+  GA 30332}
+\altaffiltext{2}{Department of Astronomy, Columbia University, 538
   West 120th Street, New York, NY 10027}
-\altaffiltext{4}{Center for Astrophysics and Space Sciences,
+\altaffiltext{3}{Center for Astrophysics and Space Sciences,
   University of California at San Diego, La Jolla, CA 92093}
-\altaffiltext{5}{Kavli Institute for Particle Astrophysics and
+\altaffiltext{4}{Kavli Institute for Particle Astrophysics and
   Cosmology, Stanford University, Menlo Park, CA 94025}
-\altaffiltext{6}{Zentrum f\"ur Astronomie der Universit\"at, Institut
+\altaffiltext{5}{Zentrum f\"ur Astronomie der Universit\"at, Institut
   f\"ur Theoretische Astrophysik, Albert-Ueberle-Str. 2, 69120
   Heidelberg, Germany}
-\altaffiltext{7}{Heidelberg Institut f\"ur Theoretische Studien,
+\altaffiltext{6}{Heidelberg Institut f\"ur Theoretische Studien,
   Schloss-Wolfsbrunnenweg 35, 69118 Heidelberg, Germany}
 
-\email{jwise@astro.princeton.edu}
+\email{jwise@physics.gatech.edu}
 
@@
 JHW thanks Renyue Cen, Amina Helmi, Marco Spaans, and Eline Tolstoy
-for enlightening discussions.  JHW is supported by NASA through Hubble
-Fellowship grant \#120-6370 awarded by the Space Telescope Science
-Institute, which is operated by the Association of Universities for
-Research in Astronomy, Inc., for NASA, under contract NAS 5-26555.
-MJT and MLN acknowledge partial support from NASA ATFP grant
-NNX08AH26G.  Computational resources were provided by NASA/NCCS award
-SMD-09-1439.  TA acknowledges financial support from the {\em
+for enlightening discussions.  JHW is partially supported by NASA
+through Hubble Fellowship grant \#120-6370 awarded by the Space
+Telescope Science Institute, which is operated by the Association of
+Universities for Research in Astronomy, Inc., for NASA, under contract
+NAS 5-26555.  MJT and MLN acknowledge partial support from NASA ATFP
+grant NNX08AH26G.  Computational resources were provided by NASA/NCCS
+award SMD-09-1439.  TA acknowledges financial support from the {\em
   Baden-W\"{u}rttemberg-Stiftung} under grant P-LS-SPII/18, the

### 2011-08-26 ApJ/ms.tex
Minor corrections after a proofreading.

@@
 both with a metallicity floor of [Z/H]\footnote{We use the
-  conventional notation, [Z/H] $\equiv \log(Z/H) -
-  \log(Z_\odot/H_\odot)$.} = --4 \citep{Beers05, Tafelmeyer10,
+  conventional notation, [Z/H] $\equiv$ log(Z/H) -
+  log(Z$_\odot$/H$_\odot$).} = --4 \citep{Beers05, Tafelmeyer10,
   Frebel10_Obs}.
@@
 future sites of SF.  Their flows are complex because of the
-interactions between the SN blastwave, cosmological accretion and halo
+interactions between the SN blastwave, cosmological accretion, halo
 mergers, and nearby stellar feedback.  Spurred by the notion of a
@@
 We use the adaptive mesh refinement (AMR) code
-enzo~v2.0\footnote{\texttt{enzo.googlecode.com, changeset
+\enzo~v2.0\footnote{\texttt{enzo.googlecode.com, changeset
     b86d8ba026d6}} \citep{OShea2004}.  It uses an $N$-body adaptive
@@
 level, resulting in a super-Lagrangian behavior \citep[also
-  see][]{OShea08}.  We also refine on a DM overdensity of $3 \times
-2^l$ and always resolve the local Jeans length by at least 4 cells,
-avoiding artificial fragmentation during gaseous collapses
-\citep{Truelove97}.  If any of these critera are met in a single cell,
-it is flagged for further spatial refinement.
+  see][]{OShea08}.  We also refine on a DM overdensity of three and
+always resolve the local Jeans length by at least 4 cells, avoiding
+artificial fragmentation during gaseous collapses \citep{Truelove97}.
+If any of these critera are met in a single cell, it is flagged for
+further spatial refinement.
 
@@
 molecular cloud.  Instead of using a fixed stellar mass like in our
-previous work, we randomly sampled from an IMF with a functional form
+previous work, we randomly sample from an IMF with a functional form
 of
@@
 region.  Similar to the Pop III treatment, we merge any newly created
-particles within a radius $R_{\rm merge}$.  We set the minimum mass of
-a star particle to $m_{\rm \star, min} = 1000 \Ms$.  If the initial
-mass does not exceed $m_{\rm \star, min}$, the star particle does not
-provide any feedback and continues to accrete until it reaches $m_{\rm
-  \star, min}$.  The star particles live for 20 Myr, the maximum
-lifetime of an OB star.  These stars generate the majority of the
-ionizing radiation and SNe feedback in stellar clusters, thus we
-ignore any feedback from lower mass stars.
+particles within a radius of 10 pc.  We set the minimum mass of a star
+particle to $m_{\rm \star, min} = 1000 \Ms$.  If the initial mass does
+not exceed $m_{\rm \star, min}$, the star particle does not provide
+any feedback and continues to accrete until it reaches $m_{\rm \star,
+  min}$.  The star particles live for 20 Myr, the maximum lifetime of
+an OB star.  These stars generate the majority of the ionizing
+radiation and SNe feedback in stellar clusters, thus we ignore any
+feedback from lower mass stars.
 
@@
 after living for 4 Myr, which is injected into spheres with a radius
-of 10 pc, using the same technique as the Pop III SNe.  However if the
-resolution of the grid is less than 10/3 pc, we distribute the energy
-into a $3^3$ cube surrounding the star particle.  In the same region,
-star particles also return ejected material with mass
+of 10 pc.  However if the resolution of the grid is less than 10/3 pc,
+we distribute the energy into a $3^3$ cube surrounding the star
+particle.  In the same region, star particles also return ejected
+material with mass
 %
@@
 exponential, which is a steeper time dependency than the $\exp(-z/3)$
-relation found in \citet{Hernquist03}.  Note that they also
-acknowledged that this behavior should occur at early times.  At
-redshift 7, it reaches $2 \times 10^{-2}$ \sfr.  This value agrees
-with derived SFRs from $z=6-10$ galaxy luminosity functions
-\citep[e.g.][]{Bouwens10} and large-scale galaxy formation simulations
-\citep[e.g.][]{Schaye10}.
+relation found in \citet{Hernquist03}, who also acknowledged that this
+behavior should occur at early times.  At redshift 7, it reaches $2
+\times 10^{-2}$ \sfr.  This value agrees with derived SFRs from
+$z=6-10$ galaxy luminosity functions \citep[e.g.][]{Bouwens10} and
+large-scale galaxy formation simulations \citep[e.g.][]{Schaye10}.
 
@@
 \end{eqnarray}
-where we set $M_{\rm lo} \equiv 0$ because it is negligible in the
-luminosity.  Then the galaxy luminosity is the sum of all star
-particle luminosities, which we plot in Fig. \ref{fig:massfn} with
-respect to halo mass, along with the DM halo mass function.
+where we set $M_{\rm lo} \equiv 0$ because the total luminosity of
+low-mass stars is negligible.  Then the galaxy luminosity is the sum
+of all star particle luminosities, which we plot in
+Fig. \ref{fig:massfn} with respect to halo mass, along with the DM
+halo mass function.
 

### 2011-08-26 ApJ/ms.tex
Updated preprint references.

@@
   conventional notation, [Z/H] $\equiv$ log(Z/H) -
-  log(Z$_\odot$/H$_\odot$).} = --4 \citep{Beers05, Tafelmeyer10,
-  Frebel10_Obs}.
+  log(Z$_\odot$/H$_\odot$).} = --4 \citep{Beers05, Frebel10_Obs,
+  Tafelmeyer10}.
 
@@
 numerical simulations with stellar feedback \citep{Tornatore07,
-  Ricotti08, Maio10_Pop32, Maio10_Enrich}.
+  Ricotti08, Maio10_Pop32, Maio11_Enrich}.
 
@@
 cosmic SFRs better in galaxy simulations at lower redshifts
-\citep{Smith10}.
+\citep{Smith11}.
 
@@
 \times 10^{-2}$ \sfr.  This value agrees with derived SFRs from
-$z=6-10$ galaxy luminosity functions \citep[e.g.][]{Bouwens10} and
+$z=6-10$ galaxy luminosity functions \citep[e.g.][]{Bouwens11} and
 large-scale galaxy formation simulations \citep[e.g.][]{Schaye10}.
@@
 -3$ in both systems, consistent with observations of metal-poor stars
-in the halo and dSphs \citep{Beers05, Battaglia10}.
+in the halo and dSphs \citep{Beers05, Battaglia11}.
 
@@
 mergers of stellar populations can also create a similar bimodal
-distribution, which are observed in dSphs \cite{Battaglia10}.
+distribution, which are observed in dSphs \cite{Battaglia11}.
 

### 2011-09-08 ApJ/ms.tex
Incorporated changes from Mike's comments and corrections.

@@
   refinement radiation hydrodynamics simulations that follows the
-  transition from Population III to II star formation.  We model
-  stellar radiative feedback with adaptive ray tracing.  A top-heavy
-  initial mass function for the Population III stars is considered,
-  resulting in a plausible distribution of pair-instability supernovae
-  and associated metal enrichment.  We find that the gas fraction
-  recovers from 5 percent to nearly the cosmic fraction in halos with
-  merger histories rich in halos above $10^7 \Ms$.  A single
-  pair-instability supernova is sufficient to enrich the host halo to
-  a metallicity floor of $10^{-3} Z_\odot$ and to transition to
-  Population II star formation.  This provides a natural explanation
-  for the observed floor on damped Lyman alpha (DLA) systems
-  metallicities reported in the literature, which is of this order.
-  We find that stellar metallicities do not necessarily trace stellar
-  ages, as mergers of halos with established stellar populations can
-  create superpositions of $t-Z$ evolutionary tracks.  A bimodal
-  metallicity distribution is created after a starburst occurs when
-  the halo can cool efficiently through atomic line cooling.
+  transition from Population III to II star formation.  The maximum
+  spatial resolution of 1 comoving parsec is an order of magnitude
+  improvement over previous dwarf galaxy simulations, allowing for
+  individual molecular clouds to be well-resolved and their stellar
+  associations to be studied in detail.  We model stellar radiative
+  feedback with adaptive ray tracing.  A top-heavy initial mass
+  function for the Population III stars is considered, resulting in a
+  plausible distribution of pair-instability supernovae and associated
+  metal enrichment.  We find that the gas fraction recovers from 5
+  percent to nearly the cosmic fraction in halos with merger histories
+  rich in halos above $10^7 \Ms$.  A single pair-instability supernova
+  is sufficient to enrich the host halo to a metallicity floor of
+  $10^{-3} Z_\odot$ and to transition to Population II star formation.
+  This provides a natural explanation for the observed floor on damped
+  Lyman alpha (DLA) systems metallicities reported in the literature,
+  which is of this order.  We find that stellar metallicities do not
+  necessarily trace stellar ages, as mergers of halos with established
+  stellar populations can create superpositions of $t-Z$ evolutionary
+  tracks.  A bimodal metallicity distribution is created after a
+  starburst occurs when the halo can cool efficiently through atomic
+  line cooling.
 
@@
 Jeans mass.  An intermediate characteristic mass of $\sim10~\Ms$ can
-be occur if the gas cooling is suppressed to the cosmic microwave
+occur if the gas cooling is suppressed to the cosmic microwave
 background (CMB) temperature \citep{Larson98, Tumlinson07_IMF,
@@
 
-Numerical simulations are useful to detangle and study these
-complexities and the transition from Pop III to II stars.  Here, we
-present a simulation that includes both types of SF, and their
-radiative and mechanical feedback.  The methods used here incorporate
-and link together recent results from metal-enriched and metal-free
-star formation, the critical metallicity, and pair-instability
-supernovae.  This is the first time it has been possible to link the
-formation and feedback of the first stars to protogalaxies, resolving
-the important scales and including the most important physical
-effects.
+Over the past decade, these works have refined the general picture of
+inhomogenous metal enrichment and the transition to Pop II star
+formation, and here we give an overview of its development.
+Considering only Pop III star formation, \citeauthor{Yoshida04}
+calculated that Pop III stars can raise the mean metallicity to $-4.5
+\lsim$ [Z/H] $\lsim -3.5$ by redshift 15 in the upper limit where all
+metal-free stars have $M = 200 \Ms$ and produce PISNe.  Considering
+both Pop III and II star formation, \citeauthor{Scannapieco03} found
+that the transition between the two modes is a gradual process where
+both modes are coeval, confirmed by most of the later works.  Because
+the host galaxies have small masses and are subject to negative
+radiative feedback through photo-heating and photo-dissociation, the
+minimum halo mass gradually increases with the radiation background
+intensity, which \citeauthor{Furlanetto05_Reion} found to delay metal
+enrichment and place it closer to the epoch of reionization.
+\citeauthor{Trenti09} noted that underdense regions of the universe
+are still pristine at $z=6$ with Pop III stars still forming at these
+late epochs.  This group later expanded on these results to find that
+Pop II SFR becomes dominant at $z>25$ in the buildup of a Milky Way
+(MW) like halo.  Furthermore they stress the importance of a
+photo-dissociating radiation background that reduces enrichment by
+PISNe and increases the importance of metal-rich galactic outflows,
+where only $10^{-4} - 10^{-2}$ of PISN ejecta ends up in extremely
+metal poor (EMP) stars with $M > 0.9 \Ms$.
+
+The Pop III IMF should play an important role in abundance patterns in
+EMP stars in the MW halo and the physics of reionization.  Using these
+data as constraints, \citeauthor{Tumlinson06} found that Pop III IMFs
+with log-normal distributions with mean masses between 8 and 42
+\Ms~best fit the data.  Furthermore he concludes that EMP stars with
+[Z/H] $<$ --3 have between 1 and 10 metal-free SN progenitors and
+the Pop III SFR is less than 1\% of the total SFR at $z=6$.
+\citeauthor{Karlsson08} use observational data of EMP stars with
+their model to constrain the mass fraction of Pop III stars that
+die with a PISN is less than 40 per cent.  They also conclude that
+stars enriched primarily by PISNe have [Ca/H] $\gsim$ --2.6, which
+could have been missed by some EMP surveys.
+
+These works have clearly shown that many processes play a key role in
+the transition from Pop III to II stars, but how does their interplay
+affect the formation of the first galaxies?  Will metal-free pockets
+of gas still exist in dwarf galaxies that are already forming
+metal-enriched stars?  How do the metal-enriched ejecta propagate into
+future sites of star formation?  Numerical simulations are powerful
+tools to detangle and study these complexities.  To answer such
+questions, we have carried out a simulation that includes both types
+of SF, and their radiative and mechanical feedback.  The methods used
+here incorporate and link together recent results from metal-enriched
+and metal-free star formation, the critical metallicity, and
+pair-instability supernovae.  This is the first time it has been
+possible to correlate the formation and feedback of the first stars to
+protogalaxies, resolving individual molecular clouds and minihalos
+down to $10^5 \Ms$ and including the most important physical effects,
+such as radiative and supernova feedback.
 
@@
 Simulations have shown that the characteristic mass of Pop III stars
-$M_{\rm char} \sim 100~\Ms$ \citep{ABN02, Bromm02_P3, OShea07a}.  They
-form in molecular clouds that coexist with the dark matter halo center
-with limited fragmentation occurring during their collapse; however
-\citet{2009Sci...325..601T} and \citet{Stacy10_Binary} have recently
-shown that Pop III binaries may form in a fraction of such halos.
+$M_{\rm char} \sim 100~\Ms$ \citep{ABN02, Bromm02_P3, OShea07a,
+  Yoshida08}.  They form in molecular clouds that coexist with the
+dark matter halo center with limited fragmentation occurring during
+their collapse; however \citet{2009Sci...325..601T} and
+\citet{Stacy10_Binary} have recently shown that Pop III binaries may
+form in a fraction of such halos.
 
@@
 Salpeter IMF but is exponentially cutoff below that mass
-\citep{Chabrier03, Clark09}.  For reproducibility, we record the number
-of times the random number generator (Mersenne twister;
+\citep{Chabrier03, Clark09}.  For reproducibility, we record the
+number of times the random number generator (Mersenne twister;
 \citet{MTwister}) has been called for use when restarting the
-simulations.
+simulations.  The Pop III IMF is highly uncertain.  In
+Sec. \ref{sec:discuss}, we discuss possible dependencies of our
+results to changes in the IMF.
 
@@
 particles within a radius of 10 pc.  We set the minimum mass of a star
-particle to $m_{\rm \star, min} = 1000 \Ms$.  If the initial mass does
-not exceed $m_{\rm \star, min}$, the star particle does not provide
-any feedback and continues to accrete until it reaches $m_{\rm \star,
-  min}$.  The star particles live for 20 Myr, the maximum lifetime of
-an OB star.  These stars generate the majority of the ionizing
-radiation and SNe feedback in stellar clusters, thus we ignore any
-feedback from lower mass stars.
+particle to $m_{\rm \star, min} = 1000 \Ms$.  Unlike Pop III star
+particles that represent individual stars, Pop II star particles
+represent a star cluster of some total mass and an assumed normal IMF.
+If the initial mass does not exceed $m_{\rm \star, min}$, the star
+particle does not provide any feedback and continues to accrete until
+it reaches $m_{\rm \star, min}$.  The star particles live for 20 Myr,
+the maximum lifetime of an OB star.  These stars generate the majority
+of the ionizing radiation and SNe feedback in stellar clusters, thus
+we ignore any feedback from lower mass stars.
 
@@
 \citep{HEALPix} and is coupled self-consistently to the hydrodynamics.
-Each star particle is a point source of hydrogen ionizing radiation
-with the ionizing luminosity equally split between 48 initial rays
-(HEALPix level 2).  We use a mono-chromatic spectrum for the radiation
-with the energy $E_{\rm ph}$ equaling the luminosity-weighted photon
-energy of the spectrum.  For a cosmological simulation that focuses on
-galaxies, this does not significantly affect the overall galactic
-dynamics \citep[see Sec. 6.3 in][]{Wise11_Moray}.  We do not consider helium
-singly- and doubly-ionizing radiation.  As the rays propagate from the
-source or into a high resolution AMR grid, they are adaptively split
-into 4 child rays, increasing the angular resolution of the solution,
-when the solid angle of the ray $\theta = 4\pi/(12 \times 4^{L})$ is
-larger than 1/3 of the cell area, where $L$ is the HEALPix level.  We
-model the \hh~dissociating radiation with an optically-thin, inverse
-square profile, centered on all star particles.  In haloes with $M
-\ga 10^8 \Ms$, the \hh~column density may become large enough to
-self-shield itself from LW radiation \citep{Wise08_Gal}.  Thus we may
-be underestimating the SFRs in our work.
+In this work, we only consider energy coupling to the gas; we defer an
+investigation of the effects of radiation momentum coupling to a
+subsequent paper.  Each star particle is a point source of hydrogen
+ionizing radiation with the ionizing luminosity equally split between
+48 initial rays (HEALPix level 2).  We use a mono-chromatic spectrum
+for the radiation with the energy $E_{\rm ph}$ equaling the
+luminosity-weighted photon energy of the spectrum.  For a cosmological
+simulation that focuses on galaxies, this does not significantly
+affect the overall galactic dynamics \citep[see Sec. 6.3
+  in][]{Wise11_Moray}.  We do not consider helium singly- and
+doubly-ionizing radiation.  As the rays propagate from the source or
+into a high resolution AMR grid, they are adaptively split into 4
+child rays, increasing the angular resolution of the solution, when
+the solid angle of the ray $\theta = 4\pi/(12 \times 4^{L})$ is larger
+than 1/3 of the cell area, where $L$ is the HEALPix level.  We model
+the \hh~dissociating radiation with an optically-thin, inverse square
+profile, centered on all Pop II and III star particles.  In halos
+with $M \ga 10^8 \Ms$, the \hh~column density may become large enough
+to self-shield itself from LW radiation \citep{Wise08_Gal}.  Thus we
+may be underestimating the SFRs in our work.
 
@@
 core (and equivalently the metal ejecta) mass and $M_\star$ is the
-stellar mass.  The blastwave is modeled by injecting the explosion
-energy and ejecta mass into a sphere of 10 pc, smoothed at its surface
-to improve numerical stability \citep{Wise08_Gal}.  Because we resolve
-the blastwave relatively well with several cells across at its
+stellar mass.  If the stellar mass is outside of these ranges, then an
+inert, collisionless black hole (BH) particle is created.
+
+The blastwave is modeled by injecting the explosion energy and ejecta
+mass into a sphere of 10 pc, smoothed at its surface to improve
+numerical stability \citep{Wise08_Gal}.  Because we resolve the
+blastwave relatively well with several cells across at its
 initialization, the thermal energy is converted into kinetic energy
@@
     density (left), temperature (center), and metallicity (right) of
-    the two selected haloes at $z=7$.  The field of view is 5 proper
+    the two selected halos at $z=7$.  The field of view is 5 proper
     kpc, and the circles have a radius of $r_{200}$.  The composite
@@
   (solid) and III (dashed).  Note that the Pop III rates are nearly
-  constant from redshift 12 to 7.  Pristine haloes still survive in
+  constant from redshift 12 to 7.  Pristine halos still survive in
   underdense regions, supporting late-time metal-free star formation.}
@@
 0.72, respectively, which are consistent with large-scale reionization
-simulations \citep{Zahn11}.  PISNe enrich 0.106 and 0.027 of the mass
-and volume, respectively, above $10^{-3} \zsun$, and 0.034 and 0.0024
-of the mass and volume are enriched by Type II SNe above the same
-threshold.  Table \ref{tab:enrich} gives additional enriched fractions
-with different metallicity cuts.
+simulations \citep{Zahn11}.  PISNe enrich 0.065 and 0.019 of the mass
+and volume, respectively, above $10^{-3} \zsun$, and 0.025 and 0.0010
+of the mass and volume are enriched by Type II SNe from Pop II stars
+above the same threshold.  With $M_{\rm char} = 100 \Ms$, a negligible
+fraction of Pop III stars die as Type II SNe; thus, all metals
+originating from Pop III stars are produced in PISNe.  Table
+\ref{tab:enrich} gives additional enriched fractions with different
+metallicity cuts.
 
@@
 and III stars.  Metal-free stars form at a nearly constant rate of $5
-\times 10^{-4}$ \sfr~until the end of the simulation.  The
+\times 10^{-5}$ \sfr~until the end of the simulation.  The
 dissociating and ionization radiation from nearby Pop III stars and
-galaxies do not halt the formation of such stars in low-mass haloes
+galaxies do not halt the formation of such stars in low-mass halos
 but only suppress them.  We expect a uniform \hh~dissociating
@@
 galaxies, we show the average metallicity from Pop III SNe \zthree~in
-all haloes as a function of halo mass at $z =$ 7, 8, 9, and 10 in
+all halos as a function of halo mass at $z =$ 7, 8, 9, and 10 in
 Fig. \ref{fig:z3}, and it is strongly dependent on halo mass.  The
@@
 is not necessarily Gaussian at all halo masses.  Above $3 \times 10^7
-\Ms$, all haloes enriched to $\zthree \ga -4$ with little time
+\Ms$, all halos enriched to $\zthree \ga -4$ with little time
 evolution, further illustrating the metallicity floor.  Below this
@@
 progenitors of the intense halo host a total of 56 Pop III stars with
-21 producing PISNe.  The first forms in a $6 \times 10^5 \Ms$ halo at
-$z=19$.  Pop III stars form on a regular interval in the halo's
-progenitors until $z=9$ when most of these halos enter the metal-rich
-bubble surrounding the intense halo.
+21 producing PISNe and the other 35 producing intermediate-mass BHs.
+The first forms in a $6 \times 10^5 \Ms$ halo at $z=19$.  Pop III
+stars form on a regular interval in the halo's progenitors until $z=9$
+when most of these halos enter the metal-rich bubble surrounding the
+intense halo.
 
@@
 will follow up with more sophisicated models to determine more
-accurate observables.  Stars in each particle are treated an
+accurate observables.  Stars in each particle are treated as an
 instantaneous burst.  Using the empirical law of main sequence
@@
 We have focused on the birth of two galaxies prior to reionization
-with a cosmological AMR radiation hydrodynamics simulation.
-Supernovae from Pop III stars provide the necessary heavy elements for
-the transition to a Population II stellar population, which we have
-directly simulated.  These two galaxies have a 10--15\% probability in
+with a cosmological AMR radiation hydrodynamics simulation with
+unprecedented spatial (1 pc comoving) and mass resolution (1800 \Ms).
+With this resolution, we are able to follow the Pop III star formation
+and radiative and chemical feedback effects in hundreds of minihalos
+that contribute to the formation of a protogalaxy.  Supernovae from
+Pop III stars provide the necessary heavy elements for the transition
+to a Population II stellar population, which we have directly
+simulated.  These two galaxies have a 10--15\% probability in
 surviving as present-day ``fossil'' galaxies \citep{Gnedin06},
@@
 given $M_{\rm char} = 100~\Ms$.  DLA systems have a metallicity floor
-on the same order \citep{Wolfe05_Review}, and metal enrichment from Pop
-III SNe provides a possible explanation \citep{Kobayashi11}.
+on the same order \citep{Wolfe05_Review, Penprase10}, and metal
+enrichment from Pop III SNe provides a possible explanation
+\citep{Kobayashi11}.  Ours is the first simulation with sufficient
+physics and resolution to support this claim.
 
@@
 
+Because our simulation only samples 1 comoving Mpc$^3$, it misses the
+more rare density fluctuations and is biased toward late galaxy
+formation \citep{Barkana04}.  In such rare galaxies, the physical
+scenario described by this work is largely unchanged but is shifted to
+higher redshifts.  Thus our results can be generalized to any epoch
+prior to cosmic reionization.  However, two possible consequences in
+very high ($z \gsim 20$) redshift galaxy formation are 1) an
+intermediate mass IMF \citep{Larson98, Tumlinson07_IMF,
+  2009ApJ...691..441S}, resulting from the CMB temperature floor,
+could be more prevelant, and 2) streaming gas velocities arising from
+the recombination epoch \citep{Tselia10} could suppress star formation
+in halos below $10^6 \Ms$ \citep{Tselia10_Minihalo, Greif11_Delay}.
+
 We have shown that it is possible to simulate the formation of a
@@
 Heidelberg Institut f\"ur Theoretische Studien. This work was
-partially supported by NASA ATFP grant NNX08AH26G and NSF
-AST-0807312. This research has made use of NASA’s Astrophysics Data
-System Bibliographic Services.  The majority of the analysis and plots
-were done with \texttt{yt} \citep{yt_full_paper}.
+partially supported by NASA ATFP grant NNX08AH26G, NSF AST-0807312,
+and NSF AST-1109243. This research has made use of NASA’s Astrophysics
+Data System Bibliographic Services.  The majority of the analysis and
+plots were done with \texttt{yt} \citep{yt_full_paper}.
 

### 2011-09-13 ApJ/ms.tex
Fixing typo.
Changes from Matt's comments

@@
 late epochs.  This group later expanded on these results to find that
-Pop II SFR becomes dominant at $z>25$ in the buildup of a Milky Way
+Pop II SFR becomes dominant at $z<25$ in the buildup of a Milky Way
 (MW) like halo.  Furthermore they stress the importance of a
@@
     b86d8ba026d6}} \citep{OShea2004}.  It uses an $N$-body adaptive
-particle-mesh solver \citep{Efstathiou85} to follow the dark matter
-(DM) dynamics.  It solves the hydrodynamical equation using the
-second-order accurate piecewise parabolic method \citep{Woodward84,
-  Bryan95}, while a Riemann solver ensures accurate shock capturing
-with minimal viscosity.  We use the recently added HLLC Riemann solver
-\citep{Toro94_HLLC} for additional stability in strong shocks and
-rarefaction waves.  We use the nine-species (\ion{H}{1}, \ion{H}{2},
-\ion{He}{1}, \ion{He}{2}, \ion{He}{3}, e$^-$, \hh, \hh$^+$, H$^-$)
-non-equilibrium chemistry model in \enzo~\citep{Abel97, Anninos97} and
-the \hh~cooling rates from \citet{Glover08_Rates}.  We spatially
-distinguish metal enrichment from Pop II and Pop III stars.  We will
-follow-up this study with one that considers radiative cooling from
-metal-enriched gas, using the method of \citet{2008MNRAS.385.1443S}
-that is already implemented in \enzo.
+particle-mesh solver \citep{Efstathiou85, Couchman91, BryanNorman1997}
+to follow the dark matter (DM) dynamics.  It solves the hydrodynamical
+equation using the second-order accurate piecewise parabolic method
+\citep{Woodward84, Bryan95}, while a Riemann solver ensures accurate
+shock capturing with minimal viscosity.  We use the recently added
+HLLC Riemann solver \citep{Toro94_HLLC} for additional stability in
+strong shocks and rarefaction waves.  We use the nine-species
+(\ion{H}{1}, \ion{H}{2}, \ion{He}{1}, \ion{He}{2}, \ion{He}{3}, e$^-$,
+\hh, \hh$^+$, H$^-$) non-equilibrium chemistry model in
+\enzo~\citep{Abel97, Anninos97} and the \hh~cooling rates from
+\citet{Glover08_Rates}.  We spatially distinguish metal enrichment
+from Pop II and Pop III stars.  We will follow-up this study with one
+that considers radiative cooling from metal-enriched gas, using the
+method of \citet{2008MNRAS.385.1443S} that is already implemented in
+\enzo.
 
@@
 definitions.  We use a maximum refinement level of $l = 12$, resulting
-in a maximal comoving resolution of 1 pc.  We stop the simulation at
-$z=7$ to prevent any large-scale modes with $r \sim L_{\rm box}/2$
-from entering the non-linear growth regime.  At the final redshift,
-the simulation has $1.4 \times 10^8$ computational cells and required
-250,000 CPU hours, using 512 cores.
+in a maximal comoving resolution of 1 pc.  The adaptive particle-mesh
+solver has a force resolution of two cell widths of a given AMR grid.
+We stop the simulation at $z=7$ to prevent any large-scale modes with
+$r \sim L_{\rm box}/2$ from entering the non-linear growth regime.  At
+the final redshift, the simulation has $1.4 \times 10^8$ computational
+cells and required 250,000 CPU hours, using 512 cores.
 
@@
 their collapse; however \citet{2009Sci...325..601T} and
-\citet{Stacy10_Binary} have recently shown that Pop III binaries may
-form in a fraction of such halos.
+\citet{Stacy10_Binary} have shown that Pop III binaries may form in a
+fraction of such halos.  There have been some recent hints that the
+accretion disk around the first protostar may fragment and produce
+clustered Pop III star formation \citep{Clark11_Frag,
+  Greif11_P3Cluster}.  The final stellar masses in the aforementioned
+calculations are still highly uncertain with a limited number of
+samples.  Nevertheless, they all point toward an IMF with a larger
+characteristic mass than present-day star formation.
 
@@
 \citet{MTwister}) has been called for use when restarting the
-simulations.  The Pop III IMF is highly uncertain.  In
-Sec. \ref{sec:discuss}, we discuss possible dependencies of our
-results to changes in the IMF.
+simulations.  We stress that the Pop III IMF is still highly
+uncertain.  In Sec. \ref{sec:discuss}, we discuss possible
+dependencies of our results to changes in the IMF.
 
@@
 effectively a modified version of the \citet{Cen92} method but
-accounts for the fact that the molecular clouds are resolved.  In the
-simulation, we define the molecular cloud as a sphere, centered on the
-most dense cell, with a dynamical time $t_{\rm dyn} = 3$ Myr
-(corresponding to an average density $\bar{\rho}_{\rm MC} \simeq
-1000\mu \cubecm$) and a radius $R_{\rm MC}$, where $\mu$ is the mean
-molecular weight.  In this sphere, a fraction $c_\star = 0.07 f_{\rm
-  cold}$ of the cold gas ($T < 10^3$ K) is converted into a star
-particle with mass $m_\star = c_\star (4\pi/3) \bar{\rho}_{\rm MC}
-R_{\rm MC}^3$.  We then replace the sphere with a uniform density
-$\rho_{\rm MC} = (1 - c_\star) / (Gt_{\rm dyn}^2)$ and temperature $T
-= 10^4$ K, which approximates the initial stages of an \ion{H}{2}
-region.  Similar to the Pop III treatment, we merge any newly created
-particles within a radius of 10 pc.  We set the minimum mass of a star
-particle to $m_{\rm \star, min} = 1000 \Ms$.  Unlike Pop III star
-particles that represent individual stars, Pop II star particles
-represent a star cluster of some total mass and an assumed normal IMF.
-If the initial mass does not exceed $m_{\rm \star, min}$, the star
-particle does not provide any feedback and continues to accrete until
-it reaches $m_{\rm \star, min}$.  The star particles live for 20 Myr,
-the maximum lifetime of an OB star.  These stars generate the majority
-of the ionizing radiation and SNe feedback in stellar clusters, thus
-we ignore any feedback from lower mass stars.
+accounts for the fact that the molecular clouds are resolved.  Unlike
+Pop III star particles that represent individual stars, Pop II star
+particles represent a star cluster of some total mass and an assumed
+normal IMF.  In the simulation, we define the molecular cloud as a
+sphere, centered on the most dense cell, with a dynamical time $t_{\rm
+  dyn} = 3$ Myr (corresponding to an average density $\bar{\rho}_{\rm
+  MC} \simeq 1000\mu \cubecm$) and a radius $R_{\rm MC}$, where $\mu$
+is the mean molecular weight.  In this sphere, a fraction $c_\star =
+0.07 f_{\rm cold}$ of the cold gas ($T < 10^3$ K) is converted into a
+star particle with mass $m_\star = c_\star (4\pi/3) \bar{\rho}_{\rm
+  MC} R_{\rm MC}^3$.  We then replace the sphere with a uniform
+density $\rho_{\rm MC} = (1 - c_\star) / (Gt_{\rm dyn}^2)$ and
+temperature $T = 10^4$ K, which approximates the initial stages of an
+\ion{H}{2} region.  Similar to the Pop III treatment, we merge any
+newly created particles within a radius of 10 pc.  The new star
+particle acquires the center of mass of the merged particles.  During
+the merging, the gas is unaltered besides the initial gas accretion
+from the grid to the star particles.  We set the minimum mass of a
+star particle to $m_{\rm \star, min} = 1000 \Ms$.  If the initial mass
+does not exceed $m_{\rm \star, min}$, the star particle does not
+provide any feedback and continues to accrete until it reaches $m_{\rm
+  \star, min}$.  The star particles live for 20 Myr, the maximum
+lifetime of an OB star.  These stars generate the majority of the
+ionizing radiation and SNe feedback in stellar clusters, thus we
+ignore any feedback from lower mass stars.
 
@@
 the \hh~dissociating radiation with an optically-thin, inverse square
-profile, centered on all Pop II and III star particles.  In halos
-with $M \ga 10^8 \Ms$, the \hh~column density may become large enough
-to self-shield itself from LW radiation \citep{Wise08_Gal}.  Thus we
-may be underestimating the SFRs in our work.
+profile, centered on all Pop II and III star particles.  In principle,
+self-shielding effects can be included by utilizing our ray tracing
+framework or other approximate methods that calculate the \hh~column
+density using the local Sobolev length \citep{Wolcott11} or only
+integrating along Cartesian axes or random lines of sight
+\citep{Yoshida03, Yoshida07_HII, Glover07}.  In halos with $M \ga 10^8
+\Ms$, the \hh~column density may become large enough to self-shield
+itself from LW radiation \citep{Wise08_Gal}.  Thus we may be
+underestimating the SFRs in our work.
 

### 2011-09-28 ApJ/ms.tex
One more proofreading after the changes from Mike's and Matt's feedback.

@@
   protostellar collapse is driven by molecular hydrogen cooling in the
-  gas-phase, leading to a massive characteristic mass $\sim 100~\Ms$
-  and suppressed fragmentation.  Population II stars with lower
-  characteristic masses form when the star-forming gas reaches a
-  critical metallicity of $10^{-6} - 10^{-3.5}~Z_\odot$, depending on
-  whether dust cooling is important.  We present adaptive mesh
-  refinement radiation hydrodynamics simulations that follows the
-  transition from Population III to II star formation.  The maximum
-  spatial resolution of 1 comoving parsec is an order of magnitude
-  improvement over previous dwarf galaxy simulations, allowing for
-  individual molecular clouds to be well-resolved and their stellar
-  associations to be studied in detail.  We model stellar radiative
-  feedback with adaptive ray tracing.  A top-heavy initial mass
-  function for the Population III stars is considered, resulting in a
-  plausible distribution of pair-instability supernovae and associated
-  metal enrichment.  We find that the gas fraction recovers from 5
-  percent to nearly the cosmic fraction in halos with merger histories
-  rich in halos above $10^7 \Ms$.  A single pair-instability supernova
-  is sufficient to enrich the host halo to a metallicity floor of
-  $10^{-3} Z_\odot$ and to transition to Population II star formation.
-  This provides a natural explanation for the observed floor on damped
-  Lyman alpha (DLA) systems metallicities reported in the literature,
-  which is of this order.  We find that stellar metallicities do not
-  necessarily trace stellar ages, as mergers of halos with established
-  stellar populations can create superpositions of $t-Z$ evolutionary
-  tracks.  A bimodal metallicity distribution is created after a
-  starburst occurs when the halo can cool efficiently through atomic
-  line cooling.
+  gas-phase, leading to massive characteristic masses.  Population II
+  stars with lower characteristic masses form when the star-forming
+  gas reaches a critical metallicity of $10^{-6} - 10^{-3.5}~Z_\odot$,
+  depending on whether dust cooling is important.  We present an
+  adaptive mesh refinement radiation hydrodynamics simulation that
+  follows the transition from Population III to II star formation.
+  The maximum spatial resolution of 1 comoving parsec is an order of
+  magnitude improvement over previous dwarf galaxy simulations,
+  allowing for individual molecular clouds to be well-resolved and
+  their stellar associations to be studied in detail.  We model
+  stellar radiative feedback with adaptive ray tracing.  A top-heavy
+  initial mass function for the Population III stars is considered,
+  resulting in a plausible distribution of pair-instability supernovae
+  and associated metal enrichment.  We find that the gas fraction
+  recovers from 5 percent to nearly the cosmic fraction in halos with
+  merger histories rich in halos above $10^7 \Ms$.  A single
+  pair-instability supernova is sufficient to enrich the host halo to
+  a metallicity floor of $10^{-3} Z_\odot$ and to transition to
+  Population II star formation.  This provides a natural explanation
+  for the observed floor on damped Lyman alpha (DLA) systems
+  metallicities reported in the literature, which is of this order.
+  We find that stellar metallicities do not necessarily trace stellar
+  ages, as mergers of halos with established stellar populations can
+  create superpositions of $t-Z$ evolutionary tracks.  A bimodal
+  metallicity distribution is created after a starburst occurs when
+  the halo can cool efficiently through atomic line cooling.
 
@@
 \Ms$.  Their stellar radiation ionizes and heats an \ion{H}{2} region
-with a radius 1--3 kpc.  The overpressurized \ion{H}{2} region drives
+with a radius 1--3 kpc.  The over-pressurized \ion{H}{2} region drives
 a 30 \kms~shock that is 10 times greater than the escape velocity of
@@
 metals stay in the IGM with a metal bubble size of a few kpc
-\citep{Wise08_Gal, Greif10}.  The blastwave may induce SF in nearby
-halos through the compression of the gas \citep{Ferrara98}, and
-timescales for metal mixing into the dense gas are many dynamical
-times \citep{Cen08} for shock velocities $\lsim100~\kms$.
+\citep{Wise08_Gal, Greif10}.  The blastwave may induce star formation
+(SF) in nearby halos through the compression of the gas
+\citep{Ferrara98}, and timescales for metal mixing into the dense gas
+are many dynamical times \citep{Cen08} for shock velocities
+$\lsim100~\kms$.
 
-The transition from Pop III to Pop II star formation (SF) is solely
-dependent on the propagation of metals from the SNe remnants into
-future sites of SF.  Their flows are complex because of the
-interactions between the SN blastwave, cosmological accretion, halo
-mergers, and nearby stellar feedback.  Spurred by the notion of a
-critical metallicity, this transition has been extensively studied
-with (i) volume-averaged semi-analytic models \citep{Scannapieco03,
-  Yoshida04, Furlanetto05_Reion}, (ii) models using hierarchical
-merger trees \citep{Tumlinson06, Tumlinson10, Salvadori07, Komiya10},
-(iii) post-processing of cosmological simulations with blastwave
-models \citep{Karlsson08, Trenti09, Trenti10}, and (iv) direct
-numerical simulations with stellar feedback \citep{Tornatore07,
-  Ricotti08, Maio10_Pop32, Maio11_Enrich}.
+The transition from Pop III to Pop II SF is solely dependent on the
+propagation of metals from the SNe remnants into future sites of SF.
+Their flows are complex because of the interactions between the SN
+blastwave, cosmological accretion, halo mergers, and nearby stellar
+feedback.  Spurred by the notion of a critical metallicity, this
+transition has been extensively studied with (i) volume-averaged
+semi-analytic models \citep{Scannapieco03, Yoshida04,
+  Furlanetto05_Reion}, (ii) models using hierarchical merger trees
+\citep{Tumlinson06, Tumlinson10, Salvadori07, Komiya10}, (iii)
+post-processing of cosmological simulations with blastwave models
+\citep{Karlsson08, Trenti09, Trenti10}, and (iv) direct numerical
+simulations with stellar feedback \citep{Tornatore07, Ricotti08,
+  Maio10_Pop32, Maio11_Enrich}.
 
 Over the past decade, these works have refined the general picture of
-inhomogenous metal enrichment and the transition to Pop II star
+inhomogeneous metal enrichment and the transition to Pop II star
 formation, and here we give an overview of its development.
@@
 questions, we have carried out a simulation that includes both types
-of SF, and their radiative and mechanical feedback.  The methods used
+of SF and their radiative and mechanical feedback.  The methods used
 here incorporate and link together recent results from metal-enriched
@@
 artificial fragmentation during gaseous collapses \citep{Truelove97}.
-If any of these critera are met in a single cell, it is flagged for
+If any of these criteria are met in a single cell, it is flagged for
 further spatial refinement.
@@
     metallicity projections are a composite image of metals
-    originating from Pop II (blue) and III (red) stars with magneta
-    indicdating a mixture of the two.}
+    originating from Pop II (blue) and III (red) stars with magenta
+    indicating a mixture of the two.}
 \end{figure*}
@@
 temperature $T = 10^4$ K, which approximates the initial stages of an
-\ion{H}{2} region.  Similar to the Pop III treatment, we merge any
-newly created particles within a radius of 10 pc.  The new star
-particle acquires the center of mass of the merged particles.  During
-the merging, the gas is unaltered besides the initial gas accretion
-from the grid to the star particles.  We set the minimum mass of a
-star particle to $m_{\rm \star, min} = 1000 \Ms$.  If the initial mass
-does not exceed $m_{\rm \star, min}$, the star particle does not
-provide any feedback and continues to accrete until it reaches $m_{\rm
-  \star, min}$.  The star particles live for 20 Myr, the maximum
-lifetime of an OB star.  These stars generate the majority of the
-ionizing radiation and SNe feedback in stellar clusters, thus we
-ignore any feedback from lower mass stars.
+\ion{H}{2} region.  Our choice of $c_\star$ agrees with the theory
+proposed in \citet{Krumholz05} that are supported by observations.
+Observations of star-forming regions show that the dynamical time is
+approximately 700 kyr and that SF is extended over several dynamical
+times \citep[e.g.][]{Tan06}, which motivates our choice of $t_{\rm
+  dyn}$ of our definition of molecular clouds in our SF prescription.
+
+Similar to the Pop III treatment, we merge any newly created particles
+within a radius of 10 pc.  The new star particle acquires the center
+of mass of the merged particles.  During the merging, the gas is
+unaltered besides the initial gas accretion from the grid to the star
+particles.  We set the minimum mass of a star particle to $m_{\rm
+  \star, min} = 1000 \Ms$.  If the initial mass does not exceed
+$m_{\rm \star, min}$, the star particle does not provide any feedback
+and continues to accrete until it reaches $m_{\rm \star, min}$.  The
+star particles live for 20 Myr, the maximum lifetime of an OB star.
+These stars generate the majority of the ionizing radiation and SNe
+feedback in stellar clusters, thus we ignore any feedback from lower
+mass stars.
 
@@
 
-We use mass-dependent hydrogen ionizing and LW photon luminosites and
+We use mass-dependent hydrogen ionizing and LW photon luminosities and
 lifetimes of the Pop III stars from \citet{Schaerer02}.  We use a
@@
 halo undergoes a series of major mergers at $z > 12$, growing by a
-factor of 30 to $2.5 \times 10^7 \Ms$ within 150 Myr.  Afterwards it
-only grows by a factor of 3 by $z=7$ mainly through smooth accretion
-from the filaments and IGM.  It is the most massive halo in the
-simulation between redshifts 13 and 10.  At the same time, the intense
-halo has a mass $M = 3 \times 10^6 \Ms$, but it is contained in a
-biased region on a comoving scale of 50 kpc with $\sim25$ halos with
-$M \sim 10^6 \Ms$.  After $z=10$, these halos hierarchically merge to
-form a $10^9 \Ms$ halo at $z=7$ with two major mergers at redshifts 10
-and 7.9, seen in the rapid increases in total mass in Figure
-\ref{fig:evo}a.  The merger history of the two halos are not atypical
-as dark matter halos can experience both quiescent and vigorous mass
-accretion rates.
+factor of 30 to $2.5 \times 10^7 \Ms$ within 150 Myr.  Subsequently,
+it only grows by a factor of 3 by $z=7$ mainly through smooth
+accretion from the filaments and IGM.  It is the most massive halo in
+the simulation between redshifts 13 and 10.  At the same time, the
+intense halo has a mass $M = 3 \times 10^6 \Ms$, but it is contained
+in a biased region on a comoving scale of 50 kpc with $\sim25$ halos
+with $M \sim 10^6 \Ms$.  After $z=10$, these halos hierarchically
+merge to form a $10^9 \Ms$ halo at $z=7$ with two major mergers at
+redshifts 10 and 7.9, seen in the rapid increases in total mass in
+Figure \ref{fig:evo}a.  The merger history of the two halos are not
+atypical as dark matter halos can experience both quiescent and
+vigorous mass accretion rates.
 
@@
 between --1 and --2 and dominate the average stellar metallicity at $z
-> 8$.  Afterwards the metallicity increases by a factor of 30 to
+> 8$.  The metallicity later increases by a factor of 30 to
 $[\bar{Z}_2/H] = -1.5$ through self-enrichment from a starburst.
@@
 \caption{\label{fig:z3} Average halo metallicity from Pop III SNe as a
-  function of total halo mass.  Inhomogenous metal enrichment causes
+  function of total halo mass.  Inhomogeneous metal enrichment causes
   the large spread in metallicity at low masses.  At $M_{\rm halo} > 3
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+\plottwo{f6a}{f6b}
+\caption{\label{fig:pops} The scatter plots show the SF history of the
+  quiet (left) and intense (right) halos as a function of metallicity
+  at $z=7$.  Each circle represents a star cluster, whose area is
+  proportional to its mass.  The open circles in the upper right
+  represent $10^3$, $10^4$, and $10^5$ \Ms~star clusters.  The dashed
+  lines in the right panel guide the eye to two stellar populations
+  that were formed in two satellite halos, merging at $z=7.5$.  The
+  upper histogram shows the SFR.  The right histogram depicts the
+  stellar metallicity distribution.}
+\end{figure*}
 
@@
 \label{sec:pop}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-\plottwo{f6a}{f6b}
-\caption{\label{fig:pops} The scatter plots show the SF history of the
-  quiet (left) and intense (right) halos as a function of metallicity
-  at $z=7$.  Each circle represents a star cluster, whose area is
-  proportional to its mass.  The open circles in the upper right
-  represent $10^3$, $10^4$, and $10^5$ \Ms~star clusters.  The dashed
-  lines in the right panel guide the eye to two stellar populations
-  that were formed in two satellite halos, merging at $z=7.5$.  The
-  upper histogram shows the SFR.  The right histogram depicts the
-  stellar metallicity distribution.}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 sizable stellar components merge into the halo at $z \sim 8$, and
-their stellar populations are still discernible in the metallicity-age
-plot.  Stars with [Z/H] $<$ --3 compose 1.8 percent of the total
-stellar mass.
+their stellar populations, which are traced by dashed lines in Figure
+\ref{fig:pops}, are still discernible in the metallicity-age plot.
+Stars with [Z/H] $<$ --3 compose 1.8 percent of the total stellar
+mass.
 
@@
 the total stellar luminosity of each galaxy.  In a later paper, we
-will follow up with more sophisicated models to determine more
+will follow up with more sophisticated models to determine more
 accurate observables.  Stars in each particle are treated as an
@@
 and thus metal enrichment, when this threshold is reached.  Halos with
-mostly gas-poor mergers or a queiscent merger history result in a
+mostly gas-poor mergers or a quiescent merger history result in a
 monotonic increase in metallicity with time.  SFHs become more complex
@@
 mergers of stellar populations can also create a similar bimodal
-distribution, which are observed in dSphs \cite{Battaglia11}.
+distribution, which are observed in dSphs \citep{Battaglia11}.
 
@@
   2009ApJ...691..441S}, resulting from the CMB temperature floor,
-could be more prevelant, and 2) streaming gas velocities arising from
+could be more prevalent, and 2) streaming gas velocities arising from
 the recombination epoch \citep{Tselia10} could suppress star formation

### 2011-10-27 ApJ/ms_2c.tex
Adding referee report and emulateapj version.

--- 2011-09-28 ApJ/ms.tex
@@
-\documentclass[apjl]{emulateapj}
+\documentclass[apj]{emulateapj}
 %\documentclass[12pt,preprint]{aastex}
@@
 
-  Population III stars first form in dark matter halos with masses
-  around $10^6 \Ms$.  By definition, they are metal-free, and their
+By definition, Population III stars are metal-free, and their
 protostellar collapse is driven by molecular hydrogen cooling in the
-  gas-phase, leading to massive characteristic masses.  Population II
-  stars with lower characteristic masses form when the star-forming
-  gas reaches a critical metallicity of $10^{-6} - 10^{-3.5}~Z_\odot$,
-  depending on whether dust cooling is important.  We present an
-  adaptive mesh refinement radiation hydrodynamics simulation that
-  follows the transition from Population III to II star formation.
-  The maximum spatial resolution of 1 comoving parsec is an order of
-  magnitude improvement over previous dwarf galaxy simulations,
-  allowing for individual molecular clouds to be well-resolved and
-  their stellar associations to be studied in detail.  We model
-  stellar radiative feedback with adaptive ray tracing.  A top-heavy
-  initial mass function for the Population III stars is considered,
-  resulting in a plausible distribution of pair-instability supernovae
-  and associated metal enrichment.  We find that the gas fraction
-  recovers from 5 percent to nearly the cosmic fraction in halos with
-  merger histories rich in halos above $10^7 \Ms$.  A single
-  pair-instability supernova is sufficient to enrich the host halo to
-  a metallicity floor of $10^{-3} Z_\odot$ and to transition to
-  Population II star formation.  This provides a natural explanation
-  for the observed floor on damped Lyman alpha (DLA) systems
-  metallicities reported in the literature, which is of this order.
-  We find that stellar metallicities do not necessarily trace stellar
-  ages, as mergers of halos with established stellar populations can
-  create superpositions of $t-Z$ evolutionary tracks.  A bimodal
-  metallicity distribution is created after a starburst occurs when
-  the halo can cool efficiently through atomic line cooling.
+gas-phase, leading to large characteristic masses.  Population II
+stars with lower characteristic masses form when the star-forming gas
+reaches a critical metallicity of $10^{-6} - 10^{-3.5}~Z_\odot$.  We
+present an adaptive mesh refinement radiation hydrodynamics simulation
+that follows the transition from Population III to II star formation.
+The maximum spatial resolution of 1 comoving parsec allows for
+individual molecular clouds to be well-resolved and their stellar
+associations to be studied in detail.  We model stellar radiative
+feedback with adaptive ray tracing.  A top-heavy initial mass function
+for the Population III stars is considered, resulting in a plausible
+distribution of pair-instability supernovae and associated metal
+enrichment.  We find that the gas fraction recovers from 5 percent to
+nearly the cosmic fraction in halos with   merger histories rich in
+halos above $10^7 \Ms$.  A single pair-instability supernova is
+sufficient to enrich the host halo to a metallicity floor of $10^{-3}
+Z_\odot$ and to transition to Population II star formation.  This
+provides a natural explanation for the observed floor on damped Lyman
+alpha (DLA) systems metallicities reported in the literature, which is
+of this order.  We find that stellar metallicities do not necessarily
+trace stellar ages, as mergers of halos with established stellar
+populations can create superpositions of $t-Z$ evolutionary tracks.  A
+bimodal metallicity distribution is created after a starburst occurs
+when the halo can cool efficiently through atomic line cooling.
+
+%% Original abstract.  Over the word limit by ~30 words.
+  %% Population III stars first form in dark matter halos with masses
+  %% around $10^6 \Ms$.  By definition, they are metal-free, and their
+  %% protostellar collapse is driven by molecular hydrogen cooling in the
+  %% gas-phase, leading to massive characteristic masses.  Population II
+  %% stars with lower characteristic masses form when the star-forming
+  %% gas reaches a critical metallicity of $10^{-6} - 10^{-3.5}~Z_\odot$,
+  %% depending on whether dust cooling is important.  We present an
+  %% adaptive mesh refinement radiation hydrodynamics simulation that
+  %% follows the transition from Population III to II star formation.
+  %% The maximum spatial resolution of 1 comoving parsec is an order of
+  %% magnitude improvement over previous dwarf galaxy simulations,
+  %% allowing for individual molecular clouds to be well-resolved and
+  %% their stellar associations to be studied in detail.  We model
+  %% stellar radiative feedback with adaptive ray tracing.  A top-heavy
+  %% initial mass function for the Population III stars is considered,
+  %% resulting in a plausible distribution of pair-instability supernovae
+  %% and associated metal enrichment.  We find that the gas fraction
+  %% recovers from 5 percent to nearly the cosmic fraction in halos with
+  %% merger histories rich in halos above $10^7 \Ms$.  A single
+  %% pair-instability supernova is sufficient to enrich the host halo to
+  %% a metallicity floor of $10^{-3} Z_\odot$ and to transition to
+  %% Population II star formation.  This provides a natural explanation
+  %% for the observed floor on damped Lyman alpha (DLA) systems
+  %% metallicities reported in the literature, which is of this order.
+  %% We find that stellar metallicities do not necessarily trace stellar
+  %% ages, as mergers of halos with established stellar populations can
+  %% create superpositions of $t-Z$ evolutionary tracks.  A bimodal
+  %% metallicity distribution is created after a starburst occurs when
+  %% the halo can cool efficiently through atomic line cooling.
 
@@
 %\clearpage
-%\input biblio.tex
-\bibliography{ms}
+\begin{thebibliography}{101}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Abel} {et~al.}(1997){Abel}, {Anninos}, {Zhang}, \&
+  {Norman}}]{Abel97}
+{Abel}, T., {Anninos}, P., {Zhang}, Y., \& {Norman}, M.~L. 1997, New Astronomy,
+  2, 181
+
+\bibitem[{{Abel} {et~al.}(2002){Abel}, {Bryan}, \& {Norman}}]{ABN02}
+{Abel}, T., {Bryan}, G.~L., \& {Norman}, M.~L. 2002, Science, 295, 93
+
+\bibitem[{{Abel} \& {Wandelt}(2002)}]{Abel02_RT}
+{Abel}, T., \& {Wandelt}, B.~D. 2002, \mnras, 330, L53
+
+\bibitem[{{Abel} {et~al.}(2007){Abel}, {Wise}, \& {Bryan}}]{Abel07}
+{Abel}, T., {Wise}, J.~H., \& {Bryan}, G.~L. 2007, \apjl, 659, L87
+
+\bibitem[{{Anninos} {et~al.}(1997){Anninos}, {Zhang}, {Abel}, \&
+  {Norman}}]{Anninos97}
+{Anninos}, P., {Zhang}, Y., {Abel}, T., \& {Norman}, M.~L. 1997, New Astronomy,
+  2, 209
+
+\bibitem[{{Barkana} \& {Loeb}(2004)}]{Barkana04}
+{Barkana}, R., \& {Loeb}, A. 2004, \apj, 609, 474
+
+\bibitem[{{Battaglia} {et~al.}(2011){Battaglia}, {Tolstoy}, {Helmi}, {Irwin},
+  {Parisi}, {Hill}, \& {Jablonka}}]{Battaglia11}
+{Battaglia}, G., {Tolstoy}, E., {Helmi}, A., {Irwin}, M., {Parisi}, P., {Hill},
+  V., \& {Jablonka}, P. 2011, \mnras, 411, 1013
+
+\bibitem[{{Beers} \& {Christlieb}(2005)}]{Beers05}
+{Beers}, T.~C., \& {Christlieb}, N. 2005, \araa, 43, 531
+
+\bibitem[{{Bertschinger}(2001)}]{Bertschinger01}
+{Bertschinger}, E. 2001, \apjs, 137, 1
+
+\bibitem[{{Bouwens} {et~al.}(2011){Bouwens}, {Illingworth}, {Oesch},
+  {Labb{\'e}}, {Trenti}, {van Dokkum}, {Franx}, {Stiavelli}, {Carollo},
+  {Magee}, \& {Gonzalez}}]{Bouwens11}
+{Bouwens}, R.~J., {Illingworth}, G.~D., {Oesch}, P.~A., {Labb{\'e}}, I.,
+  {Trenti}, M., {van Dokkum}, P., {Franx}, M., {Stiavelli}, M., {Carollo},
+  C.~M., {Magee}, D., \& {Gonzalez}, V. 2011, \apj, 737, 90
+
+\bibitem[{{Bovill} \& {Ricotti}(2010{\natexlab{a}})}]{Bovill11a}
+{Bovill}, M.~S., \& {Ricotti}, M. 2010{\natexlab{a}}, ArXiv e-prints
+  (1010.2231)
+
+\bibitem[{{Bovill} \& {Ricotti}(2010{\natexlab{b}})}]{Bovill11b}
+---. 2010{\natexlab{b}}, ArXiv e-prints (1010.2233)
+
+\bibitem[{{Bromm} {et~al.}(2002){Bromm}, {Coppi}, \& {Larson}}]{Bromm02_P3}
+{Bromm}, V., {Coppi}, P.~S., \& {Larson}, R.~B. 2002, \apj, 564, 23
+
+\bibitem[{{Bromm} {et~al.}(2001){Bromm}, {Ferrara}, {Coppi}, \&
+  {Larson}}]{Bromm01}
+{Bromm}, V., {Ferrara}, A., {Coppi}, P.~S., \& {Larson}, R.~B. 2001, \mnras,
+  328, 969
+
+\bibitem[{{Bryan} \& {Norman}(1997)}]{BryanNorman1997}
+{Bryan}, G.~L., \& {Norman}, M.~L. 1997, ArXiv Astrophysics e-prints
+
+\bibitem[{{Bryan} {et~al.}(1995){Bryan}, {Norman}, {Stone}, {Cen}, \&
+  {Ostriker}}]{Bryan95}
+{Bryan}, G.~L., {Norman}, M.~L., {Stone}, J.~M., {Cen}, R., \& {Ostriker},
+  J.~P. 1995, Computer Physics Communications, 89, 149
+
+\bibitem[{{Cen} \& {Ostriker}(1992)}]{Cen92}
+{Cen}, R., \& {Ostriker}, J.~P. 1992, \apjl, 399, L113
+
+\bibitem[{{Cen} \& {Riquelme}(2008)}]{Cen08}
+{Cen}, R., \& {Riquelme}, M.~A. 2008, \apj, 674, 644
+
+\bibitem[{{Chabrier}(2003)}]{Chabrier03}
+{Chabrier}, G. 2003, \pasp, 115, 763
+
+\bibitem[{{Clark} {et~al.}(2009){Clark}, {Glover}, {Bonnell}, \&
+  {Klessen}}]{Clark09}
+{Clark}, P.~C., {Glover}, S.~C.~O., {Bonnell}, I.~A., \& {Klessen}, R.~S. 2009,
+  ArXiv e-prints (0904.3302)
+
+\bibitem[{{Clark} {et~al.}(2008){Clark}, {Glover}, \& {Klessen}}]{clark08}
+{Clark}, P.~C., {Glover}, S.~C.~O., \& {Klessen}, R.~S. 2008, \apj, 672, 757
+
+\bibitem[{{Clark} {et~al.}(2011){Clark}, {Glover}, {Smith}, {Greif}, {Klessen},
+  \& {Bromm}}]{Clark11_Frag}
+{Clark}, P.~C., {Glover}, S.~C.~O., {Smith}, R.~J., {Greif}, T.~H., {Klessen},
+  R.~S., \& {Bromm}, V. 2011, Science, 331, 1040
+
+\bibitem[{{Couchman}(1991)}]{Couchman91}
+{Couchman}, H.~M.~P. 1991, \apjl, 368, L23
+
+\bibitem[{{Efstathiou} {et~al.}(1985){Efstathiou}, {Davis}, {White}, \&
+  {Frenk}}]{Efstathiou85}
+{Efstathiou}, G., {Davis}, M., {White}, S.~D.~M., \& {Frenk}, C.~S. 1985,
+  \apjs, 57, 241
+
+\bibitem[{{Ferrara}(1998)}]{Ferrara98}
+{Ferrara}, A. 1998, \apjl, 499, L17+
+
+\bibitem[{{Frebel} \& {Bromm}(2010)}]{Frebel10}
+{Frebel}, A., \& {Bromm}, V. 2010, ArXiv e-prints (1010.1261)
+
+\bibitem[{{Frebel} {et~al.}(2010){Frebel}, {Kirby}, \& {Simon}}]{Frebel10_Obs}
+{Frebel}, A., {Kirby}, E.~N., \& {Simon}, J.~D. 2010, \nat, 464, 72
+
+\bibitem[{{Furlanetto} \& {Loeb}(2005)}]{Furlanetto05_Reion}
+{Furlanetto}, S.~R., \& {Loeb}, A. 2005, \apj, 634, 1
+
+\bibitem[{{Glover} \& {Abel}(2008)}]{Glover08_Rates}
+{Glover}, S.~C.~O., \& {Abel}, T. 2008, \mnras, 388, 1627
+
+\bibitem[{{Glover} \& {Mac Low}(2007)}]{Glover07}
+{Glover}, S.~C.~O., \& {Mac Low}, M.-M. 2007, \apjs, 169, 239
+
+\bibitem[{{Gnedin}(2000)}]{gnedin00}
+{Gnedin}, N.~Y. 2000, \apj, 542, 535
+
+\bibitem[{{Gnedin} \& {Hui}(1998)}]{gnedin98}
+{Gnedin}, N.~Y., \& {Hui}, L. 1998, \mnras, 296, 44
+
+\bibitem[{{Gnedin} \& {Kravtsov}(2006)}]{Gnedin06}
+{Gnedin}, N.~Y., \& {Kravtsov}, A.~V. 2006, \apj, 645, 1054
+
+\bibitem[{{G{\'o}rski} {et~al.}(2005){G{\'o}rski}, {Hivon}, {Banday},
+  {Wandelt}, {Hansen}, {Reinecke}, \& {Bartelmann}}]{HEALPix}
+{G{\'o}rski}, K.~M., {Hivon}, E., {Banday}, A.~J., {Wandelt}, B.~D., {Hansen},
+  F.~K., {Reinecke}, M., \& {Bartelmann}, M. 2005, \apj, 622, 759
+
+\bibitem[{{Greif} {et~al.}(2010){Greif}, {Glover}, {Bromm}, \&
+  {Klessen}}]{Greif10}
+{Greif}, T.~H., {Glover}, S.~C.~O., {Bromm}, V., \& {Klessen}, R.~S. 2010,
+  \apj, 716, 510
+
+\bibitem[{{Greif} {et~al.}(2007){Greif}, {Johnson}, {Bromm}, \&
+  {Klessen}}]{Greif07}
+{Greif}, T.~H., {Johnson}, J.~L., {Bromm}, V., \& {Klessen}, R.~S. 2007, \apj,
+  670, 1
+
+\bibitem[{{Greif} {et~al.}(2011{\natexlab{a}}){Greif}, {Springel}, {White},
+  {Glover}, {Clark}, {Smith}, {Klessen}, \& {Bromm}}]{Greif11_P3Cluster}
+{Greif}, T.~H., {Springel}, V., {White}, S.~D.~M., {Glover}, S.~C.~O., {Clark},
+  P.~C., {Smith}, R.~J., {Klessen}, R.~S., \& {Bromm}, V. 2011{\natexlab{a}},
+  \apj, 737, 75
+
+\bibitem[{{Greif} {et~al.}(2011{\natexlab{b}}){Greif}, {White}, {Klessen}, \&
+  {Springel}}]{Greif11_Delay}
+{Greif}, T.~H., {White}, S.~D.~M., {Klessen}, R.~S., \& {Springel}, V.
+  2011{\natexlab{b}}, \apj, 736, 147
+
+\bibitem[{{Heger} {et~al.}(2003){Heger}, {Fryer}, {Woosley}, {Langer}, \&
+  {Hartmann}}]{Heger03}
+{Heger}, A., {Fryer}, C.~L., {Woosley}, S.~E., {Langer}, N., \& {Hartmann},
+  D.~H. 2003, \apj, 591, 288
+
+\bibitem[{{Heger} \& {Woosley}(2002{\natexlab{a}})}]{2002ApJ...567..532H}
+{Heger}, A., \& {Woosley}, S.~E. 2002{\natexlab{a}}, \apj, 567, 532
+
+\bibitem[{{Heger} \& {Woosley}(2002{\natexlab{b}})}]{Heger02}
+---. 2002{\natexlab{b}}, \apj, 567, 532
+
+\bibitem[{{Hernquist} \& {Springel}(2003)}]{Hernquist03}
+{Hernquist}, L., \& {Springel}, V. 2003, \mnras, 341, 1253
+
+\bibitem[{{Karlsson} {et~al.}(2008){Karlsson}, {Johnson}, \&
+  {Bromm}}]{Karlsson08}
+{Karlsson}, T., {Johnson}, J.~L., \& {Bromm}, V. 2008, \apj, 679, 6
+
+\bibitem[{{Kitayama} {et~al.}(2004){Kitayama}, {Yoshida}, {Susa}, \&
+  {Umemura}}]{Kitayama04}
+{Kitayama}, T., {Yoshida}, N., {Susa}, H., \& {Umemura}, M. 2004, \apj, 613,
+  631
+
+\bibitem[{{Kobayashi} {et~al.}(2011){Kobayashi}, {Tominaga}, \&
+  {Nomoto}}]{Kobayashi11}
+{Kobayashi}, C., {Tominaga}, N., \& {Nomoto}, K. 2011, \apjl, 730, L14+
+
+\bibitem[{{Komatsu} {et~al.}(2011)}]{WMAP7}
+{Komatsu}, E., {et~al.} 2011, \apjs, 192, 18
+
+\bibitem[{{Komiya} {et~al.}(2010){Komiya}, {Habe}, {Suda}, \&
+  {Fujimoto}}]{Komiya10}
+{Komiya}, Y., {Habe}, A., {Suda}, T., \& {Fujimoto}, M.~Y. 2010, \apj, 717, 542
+
+\bibitem[{{Krumholz} \& {McKee}(2005)}]{Krumholz05}
+{Krumholz}, M.~R., \& {McKee}, C.~F. 2005, \apj, 630, 250
+
+\bibitem[{{Larson}(1998)}]{Larson98}
+{Larson}, R.~B. 1998, \mnras, 301, 569
+
+\bibitem[{{Lehnert} {et~al.}(2010){Lehnert}, {Nesvadba}, {Cuby}, {Swinbank},
+  {Morris}, {Cl{\'e}ment}, {Evans}, {Bremer}, \& {Basa}}]{Lehnert10_z8.6}
+{Lehnert}, M.~D., {Nesvadba}, N.~P.~H., {Cuby}, J., {Swinbank}, A.~M.,
+  {Morris}, S., {Cl{\'e}ment}, B., {Evans}, C.~J., {Bremer}, M.~N., \& {Basa},
+  S. 2010, \nat, 467, 940
+
+\bibitem[{{Machacek} {et~al.}(2001){Machacek}, {Bryan}, \& {Abel}}]{Machacek01}
+{Machacek}, M.~E., {Bryan}, G.~L., \& {Abel}, T. 2001, \apj, 548, 509
+
+\bibitem[{{Maio} {et~al.}(2010){Maio}, {Ciardi}, {Dolag}, {Tornatore}, \&
+  {Khochfar}}]{Maio10_Pop32}
+{Maio}, U., {Ciardi}, B., {Dolag}, K., {Tornatore}, L., \& {Khochfar}, S. 2010,
+  \mnras, 407, 1003
+
+\bibitem[{{Maio} {et~al.}(2011){Maio}, {Khochfar}, {Johnson}, \&
+  {Ciardi}}]{Maio11_Enrich}
+{Maio}, U., {Khochfar}, S., {Johnson}, J.~L., \& {Ciardi}, B. 2011, \mnras,
+  414, 1145
+
+\bibitem[{Matsumoto \& Nishimura(1998)}]{MTwister}
+Matsumoto, M., \& Nishimura, T. 1998, ACM Trans. Model. Comput. Simul., 8, 3
+
+\bibitem[{{Nomoto} {et~al.}(2006){Nomoto}, {Tominaga}, {Umeda}, {Kobayashi}, \&
+  {Maeda}}]{Nomoto06}
+{Nomoto}, K., {Tominaga}, N., {Umeda}, H., {Kobayashi}, C., \& {Maeda}, K.
+  2006, Nuclear Physics A, 777, 424
+
+\bibitem[{{Omukai} {et~al.}(2005){Omukai}, {Tsuribe}, {Schneider}, \&
+  {Ferrara}}]{Omukai05}
+{Omukai}, K., {Tsuribe}, T., {Schneider}, R., \& {Ferrara}, A. 2005, \apj, 626,
+  627
+
+\bibitem[{{O'Shea} {et~al.}(2004){O'Shea}, {Bryan}, {Bordner}, {Norman},
+  {Abel}, {Harkness}, \& {Kritsuk}}]{OShea2004}
+{O'Shea}, B.~W., {Bryan}, G., {Bordner}, J., {Norman}, M.~L., {Abel}, T.,
+  {Harkness}, R., \& {Kritsuk}, A. 2004, ArXiv Astrophysics e-prints
+  (astro-ph/0403044)
+
+\bibitem[{{O'Shea} \& {Norman}(2007)}]{OShea07a}
+{O'Shea}, B.~W., \& {Norman}, M.~L. 2007, \apj, 654, 66
+
+\bibitem[{{O'Shea} \& {Norman}(2008)}]{OShea08}
+---. 2008, \apj, 673, 14
+
+\bibitem[{{Penprase} {et~al.}(2010){Penprase}, {Prochaska}, {Sargent},
+  {Toro-Martinez}, \& {Beeler}}]{Penprase10}
+{Penprase}, B.~E., {Prochaska}, J.~X., {Sargent}, W.~L.~W., {Toro-Martinez},
+  I., \& {Beeler}, D.~J. 2010, \apj, 721, 1
+
+\bibitem[{{Ricotti} {et~al.}(2008){Ricotti}, {Gnedin}, \& {Shull}}]{Ricotti08}
+{Ricotti}, M., {Gnedin}, N.~Y., \& {Shull}, J.~M. 2008, \apj, 685, 21
+
+\bibitem[{{Safranek-Shrader} {et~al.}(2010){Safranek-Shrader}, {Bromm}, \&
+  {Milosavljevi{\'c}}}]{Safranek10}
+{Safranek-Shrader}, C., {Bromm}, V., \& {Milosavljevi{\'c}}, M. 2010, \apj,
+  723, 1568
+
+\bibitem[{{Salvadori} {et~al.}(2007){Salvadori}, {Schneider}, \&
+  {Ferrara}}]{Salvadori07}
+{Salvadori}, S., {Schneider}, R., \& {Ferrara}, A. 2007, \mnras, 381, 647
+
+\bibitem[{{Scannapieco} {et~al.}(2003){Scannapieco}, {Schneider}, \&
+  {Ferrara}}]{Scannapieco03}
+{Scannapieco}, E., {Schneider}, R., \& {Ferrara}, A. 2003, \apj, 589, 35
+
+\bibitem[{{Schaerer}(2002)}]{Schaerer02}
+{Schaerer}, D. 2002, \aap, 382, 28
+
+\bibitem[{{Schaerer}(2003)}]{Schaerer03}
+---. 2003, \aap, 397, 527
+
+\bibitem[{{Schaye} {et~al.}(2010){Schaye}, {Dalla Vecchia}, {Booth}, {Wiersma},
+  {Theuns}, {Haas}, {Bertone}, {Duffy}, {McCarthy}, \& {van de
+  Voort}}]{Schaye10}
+{Schaye}, J., {Dalla Vecchia}, C., {Booth}, C.~M., {Wiersma}, R.~P.~C.,
+  {Theuns}, T., {Haas}, M.~R., {Bertone}, S., {Duffy}, A.~R., {McCarthy},
+  I.~G., \& {van de Voort}, F. 2010, \mnras, 402, 1536
+
+\bibitem[{{Schneider} {et~al.}(2006){Schneider}, {Omukai}, {Inoue}, \&
+  {Ferrara}}]{Schneider06_Frag}
+{Schneider}, R., {Omukai}, K., {Inoue}, A.~K., \& {Ferrara}, A. 2006, \mnras,
+  369, 1437
+
+\bibitem[{{Smith} {et~al.}(2008){Smith}, {Sigurdsson}, \&
+  {Abel}}]{2008MNRAS.385.1443S}
+{Smith}, B., {Sigurdsson}, S., \& {Abel}, T. 2008, \mnras, 385, 1443
+
+\bibitem[{{Smith} {et~al.}(2011){Smith}, {Hallman}, {Shull}, \&
+  {O'Shea}}]{Smith11}
+{Smith}, B.~D., {Hallman}, E.~J., {Shull}, J.~M., \& {O'Shea}, B.~W. 2011,
+  \apj, 731, 6
+
+\bibitem[{{Smith} {et~al.}(2009){Smith}, {Turk}, {Sigurdsson}, {O'Shea}, \&
+  {Norman}}]{2009ApJ...691..441S}
+{Smith}, B.~D., {Turk}, M.~J., {Sigurdsson}, S., {O'Shea}, B.~W., \& {Norman},
+  M.~L. 2009, \apj, 691, 441
+
+\bibitem[{{Stacy} {et~al.}(2010){Stacy}, {Greif}, \& {Bromm}}]{Stacy10_Binary}
+{Stacy}, A., {Greif}, T.~H., \& {Bromm}, V. 2010, \mnras, 403, 45
+
+\bibitem[{{Strigari} {et~al.}(2008){Strigari}, {Bullock}, {Kaplinghat},
+  {Simon}, {Geha}, {Willman}, \& {Walker}}]{Strigari08}
+{Strigari}, L.~E., {Bullock}, J.~S., {Kaplinghat}, M., {Simon}, J.~D., {Geha},
+  M., {Willman}, B., \& {Walker}, M.~G. 2008, \nat, 454, 1096
+
+\bibitem[{{Tafelmeyer} {et~al.}(2010){Tafelmeyer}, {Jablonka}, {Hill},
+  {Shetrone}, {Tolstoy}, {Irwin}, {Battaglia}, {Helmi}, {Starkenburg}, {Venn},
+  {Abel}, {Francois}, {Kaufer}, {North}, {Primas}, \&
+  {Szeifert}}]{Tafelmeyer10}
+{Tafelmeyer}, M., {Jablonka}, P., {Hill}, V., {Shetrone}, M., {Tolstoy}, E.,
+  {Irwin}, M.~J., {Battaglia}, G., {Helmi}, A., {Starkenburg}, E., {Venn},
+  K.~A., {Abel}, T., {Francois}, P., {Kaufer}, A., {North}, P., {Primas}, F.,
+  \& {Szeifert}, T. 2010, \aap, 524, A58+
+
+\bibitem[{{Tan} {et~al.}(2006){Tan}, {Krumholz}, \& {McKee}}]{Tan06}
+{Tan}, J.~C., {Krumholz}, M.~R., \& {McKee}, C.~F. 2006, \apjl, 641, L121
+
+\bibitem[{{Tornatore} {et~al.}(2007){Tornatore}, {Ferrara}, \&
+  {Schneider}}]{Tornatore07}
+{Tornatore}, L., {Ferrara}, A., \& {Schneider}, R. 2007, \mnras, 382, 945
+
+\bibitem[{Toro {et~al.}(1994)Toro, Spruce, \& Speares}]{Toro94_HLLC}
+Toro, E.~F., Spruce, M., \& Speares, W. 1994, Shock Waves, 4, 25,
+  10.1007/BF01414629
+
+\bibitem[{{Trenti} \& {Shull}(2010)}]{Trenti10}
+{Trenti}, M., \& {Shull}, J.~M. 2010, \apj, 712, 435
+
+\bibitem[{{Trenti} {et~al.}(2009){Trenti}, {Stiavelli}, \& {Shull}}]{Trenti09}
+{Trenti}, M., {Stiavelli}, M., \& {Shull}, J.~M. 2009, \apj, 700, 1672
+
+\bibitem[{{Truelove} {et~al.}(1997){Truelove}, {Klein}, {McKee}, {Holliman},
+  {Howell}, \& {Greenough}}]{Truelove97}
+{Truelove}, J.~K., {Klein}, R.~I., {McKee}, C.~F., {Holliman}, II, J.~H.,
+  {Howell}, L.~H., \& {Greenough}, J.~A. 1997, \apjl, 489, L179+
+
+\bibitem[{{Tseliakhovich} {et~al.}(2010){Tseliakhovich}, {Barkana}, \&
+  {Hirata}}]{Tselia10_Minihalo}
+{Tseliakhovich}, D., {Barkana}, R., \& {Hirata}, C. 2010, ArXiv e-prints
+
+\bibitem[{{Tseliakhovich} \& {Hirata}(2010)}]{Tselia10}
+{Tseliakhovich}, D., \& {Hirata}, C. 2010, \prd, 82, 083520
+
+\bibitem[{{Tumlinson}(2006)}]{Tumlinson06}
+{Tumlinson}, J. 2006, \apj, 641, 1
+
+\bibitem[{{Tumlinson}(2007)}]{Tumlinson07_IMF}
+---. 2007, \apjl, 664, L63
+
+\bibitem[{{Tumlinson}(2010)}]{Tumlinson10}
+---. 2010, \apj, 708, 1398
+
+\bibitem[{{Turk} {et~al.}(2009){Turk}, {Abel}, \&
+  {O'Shea}}]{2009Sci...325..601T}
+{Turk}, M.~J., {Abel}, T., \& {O'Shea}, B. 2009, Science, 325, 601
+
+\bibitem[{{Turk} {et~al.}(2011){Turk}, {Smith}, {Oishi}, {Skory}, {Skillman},
+  {Abel}, \& {Norman}}]{yt_full_paper}
+{Turk}, M.~J., {Smith}, B.~D., {Oishi}, J.~S., {Skory}, S., {Skillman}, S.~W.,
+  {Abel}, T., \& {Norman}, M.~L. 2011, \apjs, 192, 9
+
+\bibitem[{{Whalen} {et~al.}(2004){Whalen}, {Abel}, \& {Norman}}]{Whalen04}
+{Whalen}, D., {Abel}, T., \& {Norman}, M.~L. 2004, \apj, 610, 14
+
+\bibitem[{{Wise} \& {Abel}(2007)}]{Wise07}
+{Wise}, J.~H., \& {Abel}, T. 2007, \apj, 665, 899
+
+\bibitem[{{Wise} \& {Abel}(2008)}]{Wise08_Gal}
+---. 2008, \apj, 685, 40
+
+\bibitem[{{Wise} \& {Abel}(2011)}]{Wise11_Moray}
+---. 2011, \mnras, 414, 3458
+
+\bibitem[{{Wise} \& {Cen}(2009)}]{Wise09}
+{Wise}, J.~H., \& {Cen}, R. 2009, \apj, 693, 984
+
+\bibitem[{{Wolcott-Green} {et~al.}(2011){Wolcott-Green}, {Haiman}, \&
+  {Bryan}}]{Wolcott11}
+{Wolcott-Green}, J., {Haiman}, Z., \& {Bryan}, G.~L. 2011, ArXiv e-prints
+
+\bibitem[{{Wolfe} {et~al.}(2005){Wolfe}, {Gawiser}, \&
+  {Prochaska}}]{Wolfe05_Review}
+{Wolfe}, A.~M., {Gawiser}, E., \& {Prochaska}, J.~X. 2005, \araa, 43, 861
+
+\bibitem[{{Woodward} \& {Colella}(1984)}]{Woodward84}
+{Woodward}, P., \& {Colella}, P. 1984, Journal of Computational Physics, 54,
+  115
+
+\bibitem[{{Woosley} \& {Weaver}(1995)}]{Woosley95}
+{Woosley}, S.~E., \& {Weaver}, T.~A. 1995, \apjs, 101, 181
+
+\bibitem[{{Yoshida} {et~al.}(2003){Yoshida}, {Abel}, {Hernquist}, \&
+  {Sugiyama}}]{Yoshida03}
+{Yoshida}, N., {Abel}, T., {Hernquist}, L., \& {Sugiyama}, N. 2003, \apj, 592,
+  645
+
+\bibitem[{{Yoshida} {et~al.}(2004){Yoshida}, {Bromm}, \&
+  {Hernquist}}]{Yoshida04}
+{Yoshida}, N., {Bromm}, V., \& {Hernquist}, L. 2004, \apj, 605, 579
+
+\bibitem[{{Yoshida} {et~al.}(2007){Yoshida}, {Oh}, {Kitayama}, \&
+  {Hernquist}}]{Yoshida07_HII}
+{Yoshida}, N., {Oh}, S.~P., {Kitayama}, T., \& {Hernquist}, L. 2007, \apj, 663,
+  687
+
+\bibitem[{{Yoshida} {et~al.}(2008){Yoshida}, {Omukai}, \&
+  {Hernquist}}]{Yoshida08}
+{Yoshida}, N., {Omukai}, K., \& {Hernquist}, L. 2008, Science, 321, 669
+
+\bibitem[{{Zahn} {et~al.}(2011){Zahn}, {Mesinger}, {McQuinn}, {Trac}, {Cen}, \&
+  {Hernquist}}]{Zahn11}
+{Zahn}, O., {Mesinger}, A., {McQuinn}, M., {Trac}, H., {Cen}, R., \&
+  {Hernquist}, L.~E. 2011, \mnras, 414, 727
+
+\end{thebibliography}
+
 \end{document}

### 2011-10-29 ApJ/ms.tex
Addressing two of the referee's points.

@@
-\documentclass[apjl]{emulateapj}
-%\documentclass[12pt,preprint]{aastex}
+%\documentclass[apj]{emulateapj}
+\documentclass[12pt,preprint]{aastex}
 
@@
     metallicity projections are a composite image of metals
-    originating from Pop II (blue) and III (red) stars with magenta
+    originating from Pop II (red) and III (blue) stars with magenta
     indicating a mixture of the two.}

### 2011-11-01 ApJ/ms.tex
Cleaning up star formation and feedback sections to be more clear.

--- 2011-09-28 ApJ/ms.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-\epsscale{1.15}
-\plotone{f1}
-\epsscale{1}
-  \caption{\label{fig:evo-mosaic} Evolution of the entire simulation
-    volume ($L_{\rm box} = 1$ Mpc) at redshifts 15, 12, 10, 8, and 7
-    (left to right).  Pictured here are the density-weighted
-    projections of density (top), temperature (middle), and
-    metallicity (bottom).  Note how the stellar radiative feedback
-    from low-mass galaxies reionize the majority of the volume.  The
-    metallicity projections are a composite image of metals
-    originating from Pop II (blue) and III (red) stars with magenta
-    indicating a mixture of the two.}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Star formation}
@@
 Pop III.2 stars and intermediate mass stars from CMB-limited cooling.
+
+\subsubsection{Population III star formation}
 
@@
 For Pop III stars, we use the same SF model as \citet{Wise08_Gal}
-where each star particle represents a single star, forming at an
-overdensity of $5 \times 10^5$ ($\sim 10^3\; \cubecm$ at $z=10$).  If
-multiple cells meet the star particle formation criteria within 1 pc,
-we form one Pop III star particle with the center of mass of these
-flagged cells to ensure that massive star is created per metal-free
-molecular cloud.  Instead of using a fixed stellar mass like in our
-previous work, we randomly sample from an IMF with a functional form
-of
+where each star particle represents a single star.  In this model, a
+star particle forms when a cell has all of the following criteria:
+%
+\begin{enumerate}
+\item an overdensity of $5 \times 10^5$ ($\sim 10^3\; \cubecm$ at
+  $z=10$),
+\item a converging gas flow ($\nabla \cdot \mathbf{v}_{\rm gas} < 0$),
+  and
+\item a molecular hydrogen fraction $f_{\rm H2} > 5 \times 10^{-4}$.
+\end{enumerate}
+%
+These physical conditions are typical of collapsing metal-free
+molecular clouds $\sim 10$ Myr before the birth of a Pop III
+main-sequence star \citep{ABN02, OShea07a}.  This prescription is
+similar to the \citet{Cen92} method but removes the Jeans unstable
+($M_{\rm gas} > M_J$) and cooling timescale ($t_{\rm cool} < t_{\rm
+  dyn}$) requirements.  We do not consider the former criterion
+because it is not applicable to simulations that resolve the Jeans
+length at all times.  The molecular hydrogen fraction requirement
+effectively constrains star formation to cooling molecular clouds,
+where the \hh~formation rate is significantly larger than the
+dissociation rate from a Lyman-Werner radiation field.
+
+If multiple cells meet the star particle formation criteria within 1
+pc, we form one Pop III star particle with the center of mass of these
+flagged cells to ensure that one massive star is created per
+metal-free molecular cloud.  Instead of using a fixed stellar mass
+like in our previous work, we randomly sample from an IMF with a
+functional form of
 %
@@
 \end{equation}
+%
 to determine the stellar mass.  Above $M_{\rm char}$, it behaves as a
@@
 dependencies of our results to changes in the IMF.
+
+After the star particle forms and its mass is randomly sampled from
+the IMF, an equal amount of gas is removed from the computational grid
+in a sphere that contains twice the stellar mass and is centered on
+the star particle.  The star particle acquires the mass-weighted
+velocity of the gas contained in this sphere.
 
@@
 
+\subsubsection{Population II star formation}
+
 We treat Pop II star formation with the same prescription as
 \citet{Wise09}, which is similar to the Pop III prescription but
-without the \hh~fraction floor that is removed because the
-metal-enriched gas can efficiently cool even in the presence of a
-strong UV radiation field \citep[e.g.][]{Safranek10}.  This method is
-effectively a modified version of the \citet{Cen92} method but
-accounts for the fact that the molecular clouds are resolved.  Unlike
-Pop III star particles that represent individual stars, Pop II star
-particles represent a star cluster of some total mass and an assumed
-normal IMF.  In the simulation, we define the molecular cloud as a
-sphere, centered on the most dense cell, with a dynamical time $t_{\rm
-  dyn} = 3$ Myr (corresponding to an average density $\bar{\rho}_{\rm
-  MC} \simeq 1000\mu \cubecm$) and a radius $R_{\rm MC}$, where $\mu$
-is the mean molecular weight.  In this sphere, a fraction $c_\star =
-0.07 f_{\rm cold}$ of the cold gas ($T < 10^3$ K) is converted into a
+without the minimum \hh~fraction requirement.  This is removed because
+the metal-enriched gas can efficiently cool even in the presence of a
+strong UV radiation field \citep[e.g.][]{Safranek10}.  To ensure the
+volume is cooling, we restrict star formation to gas with temperatures
+$T < 1000$ K.  Unlike Pop III star particles that represent individual
+stars, Pop II star particles represent a star cluster of some total
+mass and an assumed normal IMF.
+
+Once a cell meets these criteria, the prescription searches outward
+with increasing radius for the boundary of the molecular cloud,
+centered on the most dense cell.  Here, we define a molecular cloud as
+a sphere with a dynamical time $t_{\rm dyn} = 3$ Myr (corresponding to
+an average density $\bar{\rho}_{\rm MC} \simeq 1000\mu\; \cubecm$) and
+a radius $R_{\rm MC}$, where $\mu$ is the mean molecular weight.  Once
+the sphere radius is found, a fraction $c_\star = 0.07 f_{\rm cold}$
+of the cold gas ($T < 10^3$ K) inside the sphere is converted into a
 star particle with mass $m_\star = c_\star (4\pi/3) \bar{\rho}_{\rm
-  MC} R_{\rm MC}^3$.  We then replace the sphere with a uniform
-density $\rho_{\rm MC} = (1 - c_\star) / (Gt_{\rm dyn}^2)$ and
+  MC} R_{\rm MC}^3$.  This treatment of cold gas accretion is similar
+to a star formation model with a multi-phase subgrid model
+\citep{Springel03b} but is employed in a simulation that can resolve
+the multi-phase interstellar stellar medium (ISM).
+
+After the star particle is created, we replace the sphere with a
+uniform density $\rho_{\rm MC} = (1 - c_\star) / (Gt_{\rm dyn}^2)$ and
 temperature $T = 10^4$ K, which approximates the initial stages of an
@@
 $m_{\rm \star, min}$, the star particle does not provide any feedback
-and continues to accrete until it reaches $m_{\rm \star, min}$.  The
-star particles live for 20 Myr, the maximum lifetime of an OB star.
-These stars generate the majority of the ionizing radiation and SNe
-feedback in stellar clusters, thus we ignore any feedback from lower
-mass stars.
+and continues to accrete until it reaches $m_{\rm \star, min}$.
 
@@
 
+\subsubsection{Population III stellar feedback}
+
 We use mass-dependent hydrogen ionizing and LW photon luminosities and
@@
   \label{eqn:pisn}
-  E_{\rm PISN} = 10^{51} \times [5.0 + 1.304 (M_{\rm He}/\Ms - 64)] \; \mathrm{erg},
+  E_{\rm PISN} = 10^{51} \times [5.0 + 1.304 (M_{\rm He}/\Ms - 64)] \;
+  \mathrm{erg},
 \end{equation}
@@
 stellar mass.  If the stellar mass is outside of these ranges, then an
-inert, collisionless black hole (BH) particle is created.
+inert, collisionless black hole (BH) particle is created.  The
+blastwave is modeled by injecting the explosion energy and ejecta mass
+into a sphere of 10 pc, smoothed at its surface to improve numerical
+stability \citep{Wise08_Gal}.  Because we resolve the blastwave
+relatively well with several cells across at its initialization, the
+thermal energy is converted into kinetic energy and agrees with the
+Sedov-Taylor solution \citep[e.g.][]{Greif07}.
 
-The blastwave is modeled by injecting the explosion energy and ejecta
-mass into a sphere of 10 pc, smoothed at its surface to improve
-numerical stability \citep{Wise08_Gal}.  Because we resolve the
-blastwave relatively well with several cells across at its
-initialization, the thermal energy is converted into kinetic energy
-and agrees with the Sedov-Taylor solution \citep[e.g.][]{Greif07}.
+\subsubsection{Population II star formation}
 
@@
 provides an excellent first insight in the transition to Pop II SF, as
-the metal enrichment is the key ingredient here.  For SN feedback,
-these stars generate $6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$
-after living for 4 Myr, which is injected into spheres with a radius
-of 10 pc.  However if the resolution of the grid is less than 10/3 pc,
-we distribute the energy into a $3^3$ cube surrounding the star
-particle.  In the same region, star particles also return ejected
-material with mass
+the metal enrichment is the key ingredient here.  The star particles
+live for 20 Myr, the maximum lifetime of an OB star.  These stars
+generate the majority of the ionizing radiation and SNe feedback in
+stellar clusters, thus we ignore any feedback from lower mass stars.
+
+For SN feedback, these stars generate $6.8 \times 10^{48}$ erg
+s$^{-1}$ $\Ms^{-1}$ after living for 4 Myr, which is injected into
+spheres with a radius of 10 pc.  However if the resolution of the grid
+is less than 10/3 pc, we distribute the energy into a $3^3$ cube
+surrounding the star particle.  In the same region, star particles
+also return ejected material with mass
 %
@@
 
-\input{table1.tex}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+%\epsscale{1.15}
+\plotone{f1}
+\epsscale{1}
+  \caption{\label{fig:evo-mosaic} Evolution of the entire simulation
+    volume ($L_{\rm box} = 1$ Mpc) at redshifts 15, 12, 10, 8, and 7
+    (left to right).  Pictured here are the density-weighted
+    projections of density (top), temperature (middle), and
+    metallicity (bottom).  Note how the stellar radiative feedback
+    from low-mass galaxies reionize the majority of the volume.  The
+    metallicity projections are a composite image of metals
+    originating from Pop II (red) and III (blue) stars with magenta
+    indicating a mixture of the two.}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{figure}
-\epsscale{1.15}
+%\epsscale{1.15}
 \plotone{f2}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-\epsscale{1.15}
-\plotone{f3}
-\epsscale{1}
-\caption{\label{fig:sfr} Cosmic star formation rates for Pop II
-  (solid) and III (dashed).  Note that the Pop III rates are nearly
-  constant from redshift 12 to 7.  Pristine halos still survive in
-  underdense regions, supporting late-time metal-free star formation.}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{table1.tex}
 
@@
 \subsection{Global star formation rate}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+%\epsscale{1.15}
+\plotone{f3}
+\epsscale{1}
+\caption{\label{fig:sfr} Cosmic star formation rates for Pop II
+  (solid) and III (dashed).  Note that the Pop III rates are nearly
+  constant from redshift 12 to 7.  Pristine halos still survive in
+  underdense regions, supporting late-time metal-free star formation.}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{figure*}
-\epsscale{1.15}
+\epsscale{1}
 \plotone{f4}
@@
 \begin{figure}
-\epsscale{1.15}
+\epsscale{1}
 \plotone{f5}
@@
 \begin{figure}
-\epsscale{1.15}
+\epsscale{1}
 \plotone{f7}
@@
 %\clearpage
-%\input biblio.tex
 \bibliography{ms}
+
 \end{document}

### 2011-11-01 ApJ/ms.tex
Addressing two more points.

@@
 \plottwo{f6a}{f6b}
-\caption{\label{fig:pops} The scatter plots show the SF history of the
-  quiet (left) and intense (right) halos as a function of metallicity
-  at $z=7$.  Each circle represents a star cluster, whose area is
-  proportional to its mass.  The open circles in the upper right
-  represent $10^3$, $10^4$, and $10^5$ \Ms~star clusters.  The dashed
-  lines in the right panel guide the eye to two stellar populations
-  that were formed in two satellite halos, merging at $z=7.5$.  The
-  upper histogram shows the SFR.  The right histogram depicts the
-  stellar metallicity distribution.}
+\caption{\label{fig:pops} The scatter plots show the metal-enriched
+  (Pop II) star formation history of the intense (left) and quiet
+  (right) halos as a function of total metallicity, i.e. the sum of
+  metal ejecta from both Pop II and Pop III SNe, at $z=7$.  Each
+  circle represents a star cluster, whose area is proportional to its
+  mass.  The open circles in the upper right represent $10^3$ and
+  $10^4$ \Ms~star clusters.  The upper histogram shows the SFR.  The
+  right histogram depicts the stellar metallicity distribution.  The
+  intense halo shows a large spread in metallicity at $z>10$ because
+  these stars formed in progenitor halos that were enriched by
+  different SN explosions.  At $z<10$, the majority of stellar
+  metallicities increase as the halo is self-enriched.  The spikes in
+  metallicity at $t$ = 620, 650, and 700 Myr show induced star
+  formation with enhanced metallicities in SN remnant shells.  The
+  dashed lines in the left panel guide the eye to two stellar
+  populations that were formed in two satellite halos, merging at
+  $z=7.5$.  The quiet halo evolves in relative isolation and steadily
+  increases its metallicity to [Z/H] $\sim$ --2 until there is an
+  equilibrium between \textit{in-situ} star formation and metal-poor
+  inflows from filaments.}
 \end{figure*}
@@
 enrichment from Pop III SNe provides a possible explanation
-\citep{Kobayashi11}.  Ours is the first simulation with sufficient
-physics and resolution to support this claim.
+\citep{Kobayashi11}.  Our simulation strengthens this claim of a
+metallicity floor from Pop III SNe \citep[see also][]{Tornatore07,
+  Karlsson08, Maio11_Enrich}, where our work improves on previous
+studies by resolving star-forming molecular clouds and employing more
+realistic feedback physics, in particular, radiation transport.
 

### 2011-11-02 ApJ/ms.tex
Making changes in response to the first two points in the referee report.

@@
 The first (Pop III) stars are metal-free and have a large
-characteristic mass and suppressed fragmentation in its protostellar
-collapse \citep{ABN02, Bromm02_P3, OShea07a}.  A fraction of these
-stars enrich the surrounding intergalactic medium (IGM) when they go
-supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
-supernovae (SNe) or in stars roughly between 140 \Ms~and 260 \Ms~in
-pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}.  The host
-halo and the neighboring halos are then enriched with this ejecta.
-There exists a critical metallicity that is $\sim 10^{-6} Z_\odot$ if
-dust cooling is efficient \citep{Omukai05, Schneider06_Frag, clark08}
-and $\sim 10^{-3.5} Z_\odot$ otherwise \citep{Bromm01,
-  2009ApJ...691..441S}, where the gas can cool rapidly, lowering its
-Jeans mass.  An intermediate characteristic mass of $\sim10~\Ms$ can
-occur if the gas cooling is suppressed to the cosmic microwave
-background (CMB) temperature \citep{Larson98, Tumlinson07_IMF,
-  2009ApJ...691..441S}.  The resulting Population II star cluster will
-thus have a lower characteristic stellar mass than its metal-free
-progenitors.  These first stellar clusters may be connected to stars
-in the Milky Way halo and nearby dwarf spheroidal (dSph) galaxies,
-both with a metallicity floor of [Z/H]\footnote{We use the
-  conventional notation, [Z/H] $\equiv$ log(Z/H) -
+characteristic mass.  Previously, these stars were believed to be
+massive, with universally suppressed fragmentation \citep{ABN02,
+Bromm02_P3, OShea07a}.  Recently, several studies have suggested that
+while fragmentation at times prior to the formation of the first
+protostar may occur at scales of $1000-2000~\mathrm{AU}$, such
+fragmentation is likely to result in high-mass, low-multiplicity
+groups \citep{2009Sci...325..601T, Stacy10_Binary}.  Subsequent
+studies have suggested that at later times, subsequent to the
+formation of the first protostar, additional fragmentation may proceed
+\citep{Greif11_P3Cluster, Clark11_Frag}.  A fraction of high-mass,
+metal-free stars enrich the surrounding intergalactic medium (IGM)
+when they go supernova, which can happen in stars $\lsim 40~\Ms$ in
+Type II supernovae (SNe) or in stars roughly between 140 \Ms~and 260
+\Ms~in pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}.
+The host halo and the neighboring halos are then enriched with this
+ejecta.  There exists a critical metallicity that is $\sim 10^{-6}
+Z_\odot$ if dust cooling is efficient \citep{Omukai05,
+Schneider06_Frag, clark08} and $\sim 10^{-3.5} Z_\odot$ otherwise
+\citep{Bromm01, 2009ApJ...691..441S}, where the gas can cool rapidly,
+lowering its Jeans mass.  An intermediate characteristic mass of
+$\sim10~\Ms$ can occur if the gas cooling is suppressed to the cosmic
+microwave background (CMB) temperature \citep{Larson98,
+Tumlinson07_IMF, 2009ApJ...691..441S}.  The resulting Population II
+star cluster will thus have a lower characteristic stellar mass than
+its metal-free progenitors.  These first stellar clusters may be
+connected to stars in the Milky Way halo and nearby dwarf spheroidal
+(dSph) galaxies, both with a metallicity floor of [Z/H]\footnote{We
+use the conventional notation, [Z/H] $\equiv$ log(Z/H) -
 log(Z$_\odot$/H$_\odot$).} = --4 \citep{Beers05, Frebel10_Obs,
@@
 
-Simulations have shown that the characteristic mass of Pop III stars
-$M_{\rm char} \sim 100~\Ms$ \citep{ABN02, Bromm02_P3, OShea07a,
-  Yoshida08}.  They form in molecular clouds that coexist with the
-dark matter halo center with limited fragmentation occurring during
-their collapse; however \citet{2009Sci...325..601T} and
-\citet{Stacy10_Binary} have shown that Pop III binaries may form in a
-fraction of such halos.  There have been some recent hints that the
-accretion disk around the first protostar may fragment and produce
-clustered Pop III star formation \citep{Clark11_Frag,
-  Greif11_P3Cluster}.  The final stellar masses in the aforementioned
-calculations are still highly uncertain with a limited number of
-samples.  Nevertheless, they all point toward an IMF with a larger
-characteristic mass than present-day star formation.
+Simulations following the full accretion history of Pop III stars,
+from their formation inside cosmological minihalos through
+transitioning onto the main sequence, are not currently possible.
+However, under the assumption of spherical accretion, reasonable
+estimates of the mass ranges for Pop III stars can be made by
+extrapolating forward in time the instantaneous accretion rate at the
+time of formation of the first protostellar core and comparing the
+timescales for accretion against the Kelvin-Helmholtz time.  Several
+studies, conducting this extrapolation, have shown that the
+characteristic mass of Pop III stars $M_{\rm char} \sim 100~\Ms$
+\citep{ABN02, Bromm02_P3, OShea07a, Yoshida08}.  They form in
+molecular clouds that coexist with the dark matter halo center with
+limited fragmentation occurring during their collapse; however
+\citet{2009Sci...325..601T} and \citet{Stacy10_Binary} have shown that
+Pop III binaries may form in a fraction of such halos.  There have
+been some recent hints that the accretion disk around the first
+protostar may fragment and produce clustered Pop III star formation
+\citep{Clark11_Frag, Greif11_P3Cluster}.  The final stellar masses in
+the aforementioned calculations are still highly uncertain with a
+limited number of samples.  Nevertheless, they all point toward an IMF
+with a larger characteristic mass than present-day star formation.
 

### 2011-11-18 ApJ/ms.tex
Adding OCI fellowship.
Addressing the final point in the referee report by rewriting a couple of paragraphs in the discussion and summary.  Updating preprint references.

@@
 of local ultra faint dwarf (uFd) galaxies \citep[e.g.][]{Strigari08}.
-This is suggestive that these low-mass ($M_{\rm tot} \lsim 10^8 \Ms$)
-galaxies that cannot cool through hydrogen line cooling are the
-progenitors of uFd galaxies \citep{Bovill11a, Bovill11b}.  In this
-scenario, all of the star formation occurs before reionization and
-was subsequently terminated by UV heating from external sources.
+It has been suggested that these low-mass ($M_{\rm tot} \lsim 10^8
+\Ms$) galaxies that cannot cool through hydrogen line cooling are the
+progenitors of uFd galaxies \citep{Bovill11a, Bovill11b}, where all of
+the star formation occurs before reionization and was subsequently
+terminated by UV heating from external sources.  These galaxies have
+stellar masses ranging from 210 \Ms~(SDSS J1058+2843) to $3.2 \times
+10^5$ \Ms~(Dra) with most between $10^3$ and $10^4$
+\Ms. \citep{Martin08_uFd}.  Because the total stellar population would
+be sampled, on average, by several star particles, we cannot make
+robust conclusions about the nature of uFd galaxies.
 
@@
 We have focused on the birth of two galaxies prior to reionization
-with a cosmological AMR radiation hydrodynamics simulation with
-unprecedented spatial (1 pc comoving) and mass resolution (1800 \Ms).
-With this resolution, we are able to follow the Pop III star formation
-and radiative and chemical feedback effects in hundreds of minihalos
-that contribute to the formation of a protogalaxy.  Supernovae from
-Pop III stars provide the necessary heavy elements for the transition
-to a Population II stellar population, which we have directly
-simulated.  These two galaxies have a 10--15\% probability in
-surviving as present-day ``fossil'' galaxies \citep{Gnedin06},
-otherwise they will be incorporated into galactic stellar halos.  A
-$z=8.55$ galaxy was recently spectroscopically confirmed that is
-contained in an ionized bubble with radius 0.1--0.5 Mpc with an
-uncharacterized population of galaxies contributing to the local
-ionizing radiation field \citep{Lehnert10_z8.6}.  The galaxies
-simulated here might represent this population and should be detected
-with the upcoming \textit{James Webb Space Telescope}.
+with a cosmological AMR radiation hydrodynamics simulation with very
+high spatial (1 pc comoving) and mass resolution (1800 \Ms).  With
+this resolution, we are able to follow the Pop III star formation and
+radiative and chemical feedback effects in hundreds of minihalos that
+contribute to the formation of a protogalaxy.  Supernovae from Pop III
+stars provide the necessary heavy elements for the transition to a
+Population II stellar population, which we have directly simulated.
+The galaxies simulated here represent a population of uncharacterized
+high-redshift dwarf galaxies, which should be detected with the
+upcoming \textit{James Webb Space Telescope}, that should contribute a
+significant fraction of the ionizing photons during reionization.
+Recently, a $z=8.6$ spectroscopically confirmed galaxy was found to
+reside in an \ion{H}{2} region that extends beyond 1 Mpc.  However,
+using the SFRs and \lya~continuum as estimators, this galaxy produces
+enough ionizing radiation to create an \ion{H}{2} region between $\sim
+0.1(f_{\rm esc}/0.1)^{1/3}$ Mpc and $0.5(f_{\rm esc}/0.1)^{1/3}$ Mpc,
+where $f_{\rm esc}$ is the fraction of ionizing radiation escaping
+into the IGM \citep{Lehnert10_z8.6}.  This discrepancy could be caused
+by undetected satellite dwarf galaxies, such ones presented here, that
+contribute to local radiation field, or an ionizing radiation escape
+fraction near unity \citep{Wise09, Razoumov10, Paardekooper11,
+  Yajima11}.
 
@@
 
-In the case where this metallicity floor is less than the critical
-metallicity, then the next SN will further enrich the ISM, solidifying
-the transition to Pop II SF.  We conclude that it only takes one, at
-most two, SNe from Pop III stars in the halo progenitors to complete
-the transition to Population II \citep{Frebel10}.  However, this does
-not prohibit more than two instances of Pop III star formation in halo
-from happening because the stars can end in a direct collapse to a BH
-with little or no metal ejecta, keeping the surrounding environment
-pristine.  The question of whether the critical metallicity is
-\tento{-6} or \tento{-3.5} $Z_\odot$ is most applicable to nearby
-halos where the heavy elements mix slowly into dense cores as the
-blastwave overtakes it.  Less than two percent of stars have [Z/H] $<
--3$ in both systems, consistent with observations of metal-poor stars
-in the halo and dSphs \citep{Beers05, Battaglia11}.
+Building upon this idea of a lower metallicity floor, consider a
+pre-galactic halo that has hosted a Pop III star, producing a SN.  The
+majority of the gas is ejected into the IGM and re-accretes after
+$\sim 10-50$ Myr \citep{Johnson07, Wise08_Gal}.  What happens if the
+metallicity is not greater than the critical metallicity?  Massive Pop
+III stars would form again in this halo; however, enriching the
+surrounding IGM with Pop III SNe and ejecting material becomes more
+difficult in halos with $M \gsim 10^7 \Ms$ \citep{Whalen08_SN}.  Thus
+it is more likely for these subsequent Pop III stars to retain more of
+its gas during star formation episodes and self-enrich its host halo
+and less of the IGM.  This would accelerate the transition from Pop
+III to II in more massive halos.
+
+Using our result of the metallicity floor, we conclude that it only
+takes one, at most two, SNe from Pop III stars in the halo progenitors
+to complete the transition to Population II \citep{Frebel10}.
+However, this does not prohibit more than two instances of Pop III
+star formation in halo from happening because the stars can produce
+BHs with little or no metal ejecta, keeping the surrounding
+environment pristine.  Although we find that Pop III SNe create a
+floor of $10^{-4} - 10^{-3} \zsun$, gas with $Z/\zsun < 10^{-4}$ can
+still exists in nearby halos, where the metal-rich SN ejecta mix
+slowly into dense cores as the blastwave overtakes it \citep{Cen08}.
+These environments may be the host of true extremely metal-poor star
+formation, such as the recently discovered halo star with all detected
+metals below $10^{-4.2} \zsun$ \citep{Caffau11}.
 
@@
 JHW thanks Renyue Cen, Amina Helmi, Marco Spaans, and Eline Tolstoy
-for enlightening discussions.  JHW is partially supported by NASA
-through Hubble Fellowship grant \#120-6370 awarded by the Space
-Telescope Science Institute, which is operated by the Association of
+for enlightening discussions.  We thank an anonymous referee for
+helpful suggestions.  JHW is partially supported by NASA through
+Hubble Fellowship grant \#120-6370 awarded by the Space Telescope
+Science Institute, which is operated by the Association of
 Universities for Research in Astronomy, Inc., for NASA, under contract
 NAS 5-26555.  MJT and MLN acknowledge partial support from NASA ATFP
-grant NNX08AH26G.  Computational resources were provided by NASA/NCCS
-award SMD-09-1439.  TA acknowledges financial support from the {\em
-  Baden-W\"{u}rttemberg-Stiftung} under grant P-LS-SPII/18, the
-Heidelberg Institut f\"ur Theoretische Studien. This work was
-partially supported by NASA ATFP grant NNX08AH26G, NSF AST-0807312,
-and NSF AST-1109243. This research has made use of NASA’s Astrophysics
-Data System Bibliographic Services.  The majority of the analysis and
-plots were done with \texttt{yt} \citep{yt_full_paper}.
+grant NNX08AH26G.  MJT~acknowledges support by the NSF CI TraCS
+fellowship award OCI-1048505.  Computational resources were provided
+by NASA/NCCS award SMD-09-1439.  TA acknowledges financial support
+from the {\em Baden-W\"{u}rttemberg-Stiftung} under grant
+P-LS-SPII/18, the Heidelberg Institut f\"ur Theoretische Studien. This
+work was partially supported by NASA ATFP grant NNX08AH26G, NSF
+AST-0807312, and NSF AST-1109243. This research has made use of NASA’s
+Astrophysics Data System Bibliographic Services.  The majority of the
+analysis and plots were done with \texttt{yt} \citep{yt_full_paper}.
 

### 2011-11-29 ApJ/ms.tex
Minor corrections in finish proofreading.

@@
 difficult in halos with $M \gsim 10^7 \Ms$ \citep{Whalen08_SN}.  Thus
-it is more likely for these subsequent Pop III stars to retain more of
-its gas during star formation episodes and self-enrich its host halo
-and less of the IGM.  This would accelerate the transition from Pop
-III to II in more massive halos.
-
-Using our result of the metallicity floor, we conclude that it only
-takes one, at most two, SNe from Pop III stars in the halo progenitors
-to complete the transition to Population II \citep{Frebel10}.
-However, this does not prohibit more than two instances of Pop III
-star formation in halo from happening because the stars can produce
-BHs with little or no metal ejecta, keeping the surrounding
-environment pristine.  Although we find that Pop III SNe create a
-floor of $10^{-4} - 10^{-3} \zsun$, gas with $Z/\zsun < 10^{-4}$ can
-still exists in nearby halos, where the metal-rich SN ejecta mix
-slowly into dense cores as the blastwave overtakes it \citep{Cen08}.
-These environments may be the host of true extremely metal-poor star
-formation, such as the recently discovered halo star with all detected
-metals below $10^{-4.2} \zsun$ \citep{Caffau11}.
+it is more likely for these halos to retain more of its gas during
+star formation episodes and self-enrich its host halo and less of the
+IGM.  This would accelerate the transition from Pop III to II in more
+massive halos.
+
+We conclude that it only takes one, at most two, SNe from Pop III
+stars in the halo progenitors to complete the transition to Population
+II \citep{Frebel10}.  However, this does not prohibit more than two
+instances of Pop III star formation in halo from happening because the
+stars can produce BHs with little or no metal ejecta, keeping the
+surrounding environment pristine.  Even though we find that Pop III
+SNe create a floor of $\sim 10^{-3} \zsun$, gas with lower
+metallicities can still exists in nearby halos, where the metal-rich
+SN ejecta will mix slowly into dense cores as the blastwave overtakes
+them \citep{Cen08}.  These environments may be the host of true
+extremely metal-poor star formation, such as the recently discovered
+halo star with all detected metals below $10^{-4.2} \zsun$
+\citep{Caffau11}.
 

### 2011-11-29 ApJ/ms.tex
Putting bibliography directly into ms.tex for IoP PDF creation.

@@
 %\clearpage
-\bibliography{ms}
+%\bibliography{ms}
+\begin{thebibliography}{108}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Abel} {et~al.}(1997){Abel}, {Anninos}, {Zhang}, \&
+  {Norman}}]{Abel97}
+{Abel}, T., {Anninos}, P., {Zhang}, Y., \& {Norman}, M.~L. 1997, New Astronomy,
+  2, 181
+
+\bibitem[{{Abel} {et~al.}(2002){Abel}, {Bryan}, \& {Norman}}]{ABN02}
+{Abel}, T., {Bryan}, G.~L., \& {Norman}, M.~L. 2002, Science, 295, 93
+
+\bibitem[{{Abel} \& {Wandelt}(2002)}]{Abel02_RT}
+{Abel}, T., \& {Wandelt}, B.~D. 2002, \mnras, 330, L53
+
+\bibitem[{{Abel} {et~al.}(2007){Abel}, {Wise}, \& {Bryan}}]{Abel07}
+{Abel}, T., {Wise}, J.~H., \& {Bryan}, G.~L. 2007, \apjl, 659, L87
+
+\bibitem[{{Anninos} {et~al.}(1997){Anninos}, {Zhang}, {Abel}, \&
+  {Norman}}]{Anninos97}
+{Anninos}, P., {Zhang}, Y., {Abel}, T., \& {Norman}, M.~L. 1997, New Astronomy,
+  2, 209
+
+\bibitem[{{Barkana} \& {Loeb}(2004)}]{Barkana04}
+{Barkana}, R., \& {Loeb}, A. 2004, \apj, 609, 474
+
+\bibitem[{{Battaglia} {et~al.}(2011){Battaglia}, {Tolstoy}, {Helmi}, {Irwin},
+  {Parisi}, {Hill}, \& {Jablonka}}]{Battaglia11}
+{Battaglia}, G., {Tolstoy}, E., {Helmi}, A., {Irwin}, M., {Parisi}, P., {Hill},
+  V., \& {Jablonka}, P. 2011, \mnras, 411, 1013
+
+\bibitem[{{Beers} \& {Christlieb}(2005)}]{Beers05}
+{Beers}, T.~C., \& {Christlieb}, N. 2005, \araa, 43, 531
+
+\bibitem[{{Bertschinger}(2001)}]{Bertschinger01}
+{Bertschinger}, E. 2001, \apjs, 137, 1
+
+\bibitem[{{Bouwens} {et~al.}(2011){Bouwens}, {Illingworth}, {Oesch},
+  {Labb{\'e}}, {Trenti}, {van Dokkum}, {Franx}, {Stiavelli}, {Carollo},
+  {Magee}, \& {Gonzalez}}]{Bouwens11}
+{Bouwens}, R.~J., {Illingworth}, G.~D., {Oesch}, P.~A., {Labb{\'e}}, I.,
+  {Trenti}, M., {van Dokkum}, P., {Franx}, M., {Stiavelli}, M., {Carollo},
+  C.~M., {Magee}, D., \& {Gonzalez}, V. 2011, \apj, 737, 90
+
+\bibitem[{{Bovill} \& {Ricotti}(2011{\natexlab{a}})}]{Bovill11a}
+{Bovill}, M.~S., \& {Ricotti}, M. 2011{\natexlab{a}}, \apj, 741, 17
+
+\bibitem[{{Bovill} \& {Ricotti}(2011{\natexlab{b}})}]{Bovill11b}
+---. 2011{\natexlab{b}}, \apj, 741, 18
+
+\bibitem[{{Bromm} {et~al.}(2002){Bromm}, {Coppi}, \& {Larson}}]{Bromm02_P3}
+{Bromm}, V., {Coppi}, P.~S., \& {Larson}, R.~B. 2002, \apj, 564, 23
+
+\bibitem[{{Bromm} {et~al.}(2001){Bromm}, {Ferrara}, {Coppi}, \&
+  {Larson}}]{Bromm01}
+{Bromm}, V., {Ferrara}, A., {Coppi}, P.~S., \& {Larson}, R.~B. 2001, \mnras,
+  328, 969
+
+\bibitem[{{Bryan} \& {Norman}(1997)}]{BryanNorman1997}
+{Bryan}, G.~L., \& {Norman}, M.~L. 1997, ArXiv Astrophysics e-prints
+
+\bibitem[{{Bryan} {et~al.}(1995){Bryan}, {Norman}, {Stone}, {Cen}, \&
+  {Ostriker}}]{Bryan95}
+{Bryan}, G.~L., {Norman}, M.~L., {Stone}, J.~M., {Cen}, R., \& {Ostriker},
+  J.~P. 1995, Computer Physics Communications, 89, 149
+
+\bibitem[{{Caffau} {et~al.}(2011){Caffau}, {Bonifacio}, {Fran{\c c}ois},
+  {Sbordone}, {Monaco}, {Spite}, {Spite}, {Ludwig}, {Cayrel}, {Zaggia},
+  {Hammer}, {Randich}, {Molaro}, \& {Hill}}]{Caffau11}
+{Caffau}, E., {Bonifacio}, P., {Fran{\c c}ois}, P., {Sbordone}, L., {Monaco},
+  L., {Spite}, M., {Spite}, F., {Ludwig}, H.-G., {Cayrel}, R., {Zaggia}, S.,
+  {Hammer}, F., {Randich}, S., {Molaro}, P., \& {Hill}, V. 2011, \nat, 477, 67
+
+\bibitem[{{Cen} \& {Ostriker}(1992)}]{Cen92}
+{Cen}, R., \& {Ostriker}, J.~P. 1992, \apjl, 399, L113
+
+\bibitem[{{Cen} \& {Riquelme}(2008)}]{Cen08}
+{Cen}, R., \& {Riquelme}, M.~A. 2008, \apj, 674, 644
+
+\bibitem[{{Chabrier}(2003)}]{Chabrier03}
+{Chabrier}, G. 2003, \pasp, 115, 763
+
+\bibitem[{{Clark} {et~al.}(2009){Clark}, {Glover}, {Bonnell}, \&
+  {Klessen}}]{Clark09}
+{Clark}, P.~C., {Glover}, S.~C.~O., {Bonnell}, I.~A., \& {Klessen}, R.~S. 2009,
+  ArXiv e-prints (0904.3302)
+
+\bibitem[{{Clark} {et~al.}(2008){Clark}, {Glover}, \& {Klessen}}]{clark08}
+{Clark}, P.~C., {Glover}, S.~C.~O., \& {Klessen}, R.~S. 2008, \apj, 672, 757
+
+\bibitem[{{Clark} {et~al.}(2011){Clark}, {Glover}, {Smith}, {Greif}, {Klessen},
+  \& {Bromm}}]{Clark11_Frag}
+{Clark}, P.~C., {Glover}, S.~C.~O., {Smith}, R.~J., {Greif}, T.~H., {Klessen},
+  R.~S., \& {Bromm}, V. 2011, Science, 331, 1040
+
+\bibitem[{{Couchman}(1991)}]{Couchman91}
+{Couchman}, H.~M.~P. 1991, \apjl, 368, L23
+
+\bibitem[{{Efstathiou} {et~al.}(1985){Efstathiou}, {Davis}, {White}, \&
+  {Frenk}}]{Efstathiou85}
+{Efstathiou}, G., {Davis}, M., {White}, S.~D.~M., \& {Frenk}, C.~S. 1985,
+  \apjs, 57, 241
+
+\bibitem[{{Ferrara}(1998)}]{Ferrara98}
+{Ferrara}, A. 1998, \apjl, 499, L17+
+
+\bibitem[{{Frebel} \& {Bromm}(2010)}]{Frebel10}
+{Frebel}, A., \& {Bromm}, V. 2010, ArXiv e-prints (1010.1261)
+
+\bibitem[{{Frebel} {et~al.}(2010){Frebel}, {Kirby}, \& {Simon}}]{Frebel10_Obs}
+{Frebel}, A., {Kirby}, E.~N., \& {Simon}, J.~D. 2010, \nat, 464, 72
+
+\bibitem[{{Furlanetto} \& {Loeb}(2005)}]{Furlanetto05_Reion}
+{Furlanetto}, S.~R., \& {Loeb}, A. 2005, \apj, 634, 1
+
+\bibitem[{{Glover} \& {Abel}(2008)}]{Glover08_Rates}
+{Glover}, S.~C.~O., \& {Abel}, T. 2008, \mnras, 388, 1627
+
+\bibitem[{{Glover} \& {Mac Low}(2007)}]{Glover07}
+{Glover}, S.~C.~O., \& {Mac Low}, M.-M. 2007, \apjs, 169, 239
+
+\bibitem[{{Gnedin}(2000)}]{gnedin00}
+{Gnedin}, N.~Y. 2000, \apj, 542, 535
+
+\bibitem[{{Gnedin} \& {Hui}(1998)}]{gnedin98}
+{Gnedin}, N.~Y., \& {Hui}, L. 1998, \mnras, 296, 44
+
+\bibitem[{{G{\'o}rski} {et~al.}(2005){G{\'o}rski}, {Hivon}, {Banday},
+  {Wandelt}, {Hansen}, {Reinecke}, \& {Bartelmann}}]{HEALPix}
+{G{\'o}rski}, K.~M., {Hivon}, E., {Banday}, A.~J., {Wandelt}, B.~D., {Hansen},
+  F.~K., {Reinecke}, M., \& {Bartelmann}, M. 2005, \apj, 622, 759
+
+\bibitem[{{Greif} {et~al.}(2010){Greif}, {Glover}, {Bromm}, \&
+  {Klessen}}]{Greif10}
+{Greif}, T.~H., {Glover}, S.~C.~O., {Bromm}, V., \& {Klessen}, R.~S. 2010,
+  \apj, 716, 510
+
+\bibitem[{{Greif} {et~al.}(2007){Greif}, {Johnson}, {Bromm}, \&
+  {Klessen}}]{Greif07}
+{Greif}, T.~H., {Johnson}, J.~L., {Bromm}, V., \& {Klessen}, R.~S. 2007, \apj,
+  670, 1
+
+\bibitem[{{Greif} {et~al.}(2011{\natexlab{a}}){Greif}, {Springel}, {White},
+  {Glover}, {Clark}, {Smith}, {Klessen}, \& {Bromm}}]{Greif11_P3Cluster}
+{Greif}, T.~H., {Springel}, V., {White}, S.~D.~M., {Glover}, S.~C.~O., {Clark},
+  P.~C., {Smith}, R.~J., {Klessen}, R.~S., \& {Bromm}, V. 2011{\natexlab{a}},
+  \apj, 737, 75
+
+\bibitem[{{Greif} {et~al.}(2011{\natexlab{b}}){Greif}, {White}, {Klessen}, \&
+  {Springel}}]{Greif11_Delay}
+{Greif}, T.~H., {White}, S.~D.~M., {Klessen}, R.~S., \& {Springel}, V.
+  2011{\natexlab{b}}, \apj, 736, 147
+
+\bibitem[{{Heger} {et~al.}(2003){Heger}, {Fryer}, {Woosley}, {Langer}, \&
+  {Hartmann}}]{Heger03}
+{Heger}, A., {Fryer}, C.~L., {Woosley}, S.~E., {Langer}, N., \& {Hartmann},
+  D.~H. 2003, \apj, 591, 288
+
+\bibitem[{{Heger} \& {Woosley}(2002{\natexlab{a}})}]{2002ApJ...567..532H}
+{Heger}, A., \& {Woosley}, S.~E. 2002{\natexlab{a}}, \apj, 567, 532
+
+\bibitem[{{Heger} \& {Woosley}(2002{\natexlab{b}})}]{Heger02}
+---. 2002{\natexlab{b}}, \apj, 567, 532
+
+\bibitem[{{Hernquist} \& {Springel}(2003)}]{Hernquist03}
+{Hernquist}, L., \& {Springel}, V. 2003, \mnras, 341, 1253
+
+\bibitem[{{Johnson} {et~al.}(2007){Johnson}, {Greif}, \& {Bromm}}]{Johnson07}
+{Johnson}, J.~L., {Greif}, T.~H., \& {Bromm}, V. 2007, \apj, 665, 85
+
+\bibitem[{{Karlsson} {et~al.}(2008){Karlsson}, {Johnson}, \&
+  {Bromm}}]{Karlsson08}
+{Karlsson}, T., {Johnson}, J.~L., \& {Bromm}, V. 2008, \apj, 679, 6
+
+\bibitem[{{Kitayama} {et~al.}(2004){Kitayama}, {Yoshida}, {Susa}, \&
+  {Umemura}}]{Kitayama04}
+{Kitayama}, T., {Yoshida}, N., {Susa}, H., \& {Umemura}, M. 2004, \apj, 613,
+  631
+
+\bibitem[{{Kobayashi} {et~al.}(2011){Kobayashi}, {Tominaga}, \&
+  {Nomoto}}]{Kobayashi11}
+{Kobayashi}, C., {Tominaga}, N., \& {Nomoto}, K. 2011, \apjl, 730, L14+
+
+\bibitem[{{Komatsu} {et~al.}(2011)}]{WMAP7}
+{Komatsu}, E., {et~al.} 2011, \apjs, 192, 18
+
+\bibitem[{{Komiya} {et~al.}(2010){Komiya}, {Habe}, {Suda}, \&
+  {Fujimoto}}]{Komiya10}
+{Komiya}, Y., {Habe}, A., {Suda}, T., \& {Fujimoto}, M.~Y. 2010, \apj, 717, 542
+
+\bibitem[{{Krumholz} \& {McKee}(2005)}]{Krumholz05}
+{Krumholz}, M.~R., \& {McKee}, C.~F. 2005, \apj, 630, 250
+
+\bibitem[{{Larson}(1998)}]{Larson98}
+{Larson}, R.~B. 1998, \mnras, 301, 569
+
+\bibitem[{{Lehnert} {et~al.}(2010){Lehnert}, {Nesvadba}, {Cuby}, {Swinbank},
+  {Morris}, {Cl{\'e}ment}, {Evans}, {Bremer}, \& {Basa}}]{Lehnert10_z8.6}
+{Lehnert}, M.~D., {Nesvadba}, N.~P.~H., {Cuby}, J., {Swinbank}, A.~M.,
+  {Morris}, S., {Cl{\'e}ment}, B., {Evans}, C.~J., {Bremer}, M.~N., \& {Basa},
+  S. 2010, \nat, 467, 940
+
+\bibitem[{{Machacek} {et~al.}(2001){Machacek}, {Bryan}, \& {Abel}}]{Machacek01}
+{Machacek}, M.~E., {Bryan}, G.~L., \& {Abel}, T. 2001, \apj, 548, 509
+
+\bibitem[{{Maio} {et~al.}(2010){Maio}, {Ciardi}, {Dolag}, {Tornatore}, \&
+  {Khochfar}}]{Maio10_Pop32}
+{Maio}, U., {Ciardi}, B., {Dolag}, K., {Tornatore}, L., \& {Khochfar}, S. 2010,
+  \mnras, 407, 1003
+
+\bibitem[{{Maio} {et~al.}(2011){Maio}, {Khochfar}, {Johnson}, \&
+  {Ciardi}}]{Maio11_Enrich}
+{Maio}, U., {Khochfar}, S., {Johnson}, J.~L., \& {Ciardi}, B. 2011, \mnras,
+  414, 1145
+
+\bibitem[{{Martin} {et~al.}(2008){Martin}, {de Jong}, \& {Rix}}]{Martin08_uFd}
+{Martin}, N.~F., {de Jong}, J.~T.~A., \& {Rix}, H.-W. 2008, \apj, 684, 1075
+
+\bibitem[{Matsumoto \& Nishimura(1998)}]{MTwister}
+Matsumoto, M., \& Nishimura, T. 1998, ACM Trans. Model. Comput. Simul., 8, 3
+
+\bibitem[{{Nomoto} {et~al.}(2006){Nomoto}, {Tominaga}, {Umeda}, {Kobayashi}, \&
+  {Maeda}}]{Nomoto06}
+{Nomoto}, K., {Tominaga}, N., {Umeda}, H., {Kobayashi}, C., \& {Maeda}, K.
+  2006, Nuclear Physics A, 777, 424
+
+\bibitem[{{Omukai} {et~al.}(2005){Omukai}, {Tsuribe}, {Schneider}, \&
+  {Ferrara}}]{Omukai05}
+{Omukai}, K., {Tsuribe}, T., {Schneider}, R., \& {Ferrara}, A. 2005, \apj, 626,
+  627
+
+\bibitem[{{O'Shea} {et~al.}(2004){O'Shea}, {Bryan}, {Bordner}, {Norman},
+  {Abel}, {Harkness}, \& {Kritsuk}}]{OShea2004}
+{O'Shea}, B.~W., {Bryan}, G., {Bordner}, J., {Norman}, M.~L., {Abel}, T.,
+  {Harkness}, R., \& {Kritsuk}, A. 2004, ArXiv Astrophysics e-prints
+  (astro-ph/0403044)
+
+\bibitem[{{O'Shea} \& {Norman}(2007)}]{OShea07a}
+{O'Shea}, B.~W., \& {Norman}, M.~L. 2007, \apj, 654, 66
+
+\bibitem[{{O'Shea} \& {Norman}(2008)}]{OShea08}
+---. 2008, \apj, 673, 14
+
+\bibitem[{{Paardekooper} {et~al.}(2011){Paardekooper}, {Pelupessy}, {Altay}, \&
+  {Kruip}}]{Paardekooper11}
+{Paardekooper}, J.-P., {Pelupessy}, F.~I., {Altay}, G., \& {Kruip}, C.~J.~H.
+  2011, \aap, 530, A87
+
+\bibitem[{{Penprase} {et~al.}(2010){Penprase}, {Prochaska}, {Sargent},
+  {Toro-Martinez}, \& {Beeler}}]{Penprase10}
+{Penprase}, B.~E., {Prochaska}, J.~X., {Sargent}, W.~L.~W., {Toro-Martinez},
+  I., \& {Beeler}, D.~J. 2010, \apj, 721, 1
+
+\bibitem[{{Razoumov} \& {Sommer-Larsen}(2010)}]{Razoumov10}
+{Razoumov}, A.~O., \& {Sommer-Larsen}, J. 2010, \apj, 710, 1239
+
+\bibitem[{{Ricotti} {et~al.}(2008){Ricotti}, {Gnedin}, \& {Shull}}]{Ricotti08}
+{Ricotti}, M., {Gnedin}, N.~Y., \& {Shull}, J.~M. 2008, \apj, 685, 21
+
+\bibitem[{{Safranek-Shrader} {et~al.}(2010){Safranek-Shrader}, {Bromm}, \&
+  {Milosavljevi{\'c}}}]{Safranek10}
+{Safranek-Shrader}, C., {Bromm}, V., \& {Milosavljevi{\'c}}, M. 2010, \apj,
+  723, 1568
+
+\bibitem[{{Salvadori} {et~al.}(2007){Salvadori}, {Schneider}, \&
+  {Ferrara}}]{Salvadori07}
+{Salvadori}, S., {Schneider}, R., \& {Ferrara}, A. 2007, \mnras, 381, 647
+
+\bibitem[{{Scannapieco} {et~al.}(2003){Scannapieco}, {Schneider}, \&
+  {Ferrara}}]{Scannapieco03}
+{Scannapieco}, E., {Schneider}, R., \& {Ferrara}, A. 2003, \apj, 589, 35
+
+\bibitem[{{Schaerer}(2002)}]{Schaerer02}
+{Schaerer}, D. 2002, \aap, 382, 28
+
+\bibitem[{{Schaerer}(2003)}]{Schaerer03}
+---. 2003, \aap, 397, 527
+
+\bibitem[{{Schaye} {et~al.}(2010){Schaye}, {Dalla Vecchia}, {Booth}, {Wiersma},
+  {Theuns}, {Haas}, {Bertone}, {Duffy}, {McCarthy}, \& {van de
+  Voort}}]{Schaye10}
+{Schaye}, J., {Dalla Vecchia}, C., {Booth}, C.~M., {Wiersma}, R.~P.~C.,
+  {Theuns}, T., {Haas}, M.~R., {Bertone}, S., {Duffy}, A.~R., {McCarthy},
+  I.~G., \& {van de Voort}, F. 2010, \mnras, 402, 1536
+
+\bibitem[{{Schneider} {et~al.}(2006){Schneider}, {Omukai}, {Inoue}, \&
+  {Ferrara}}]{Schneider06_Frag}
+{Schneider}, R., {Omukai}, K., {Inoue}, A.~K., \& {Ferrara}, A. 2006, \mnras,
+  369, 1437
+
+\bibitem[{{Smith} {et~al.}(2008){Smith}, {Sigurdsson}, \&
+  {Abel}}]{2008MNRAS.385.1443S}
+{Smith}, B., {Sigurdsson}, S., \& {Abel}, T. 2008, \mnras, 385, 1443
+
+\bibitem[{{Smith} {et~al.}(2011){Smith}, {Hallman}, {Shull}, \&
+  {O'Shea}}]{Smith11}
+{Smith}, B.~D., {Hallman}, E.~J., {Shull}, J.~M., \& {O'Shea}, B.~W. 2011,
+  \apj, 731, 6
+
+\bibitem[{{Smith} {et~al.}(2009){Smith}, {Turk}, {Sigurdsson}, {O'Shea}, \&
+  {Norman}}]{2009ApJ...691..441S}
+{Smith}, B.~D., {Turk}, M.~J., {Sigurdsson}, S., {O'Shea}, B.~W., \& {Norman},
+  M.~L. 2009, \apj, 691, 441
+
+\bibitem[{{Springel} \& {Hernquist}(2003)}]{Springel03b}
+{Springel}, V., \& {Hernquist}, L. 2003, \mnras, 339, 289
+
+\bibitem[{{Stacy} {et~al.}(2010){Stacy}, {Greif}, \& {Bromm}}]{Stacy10_Binary}
+{Stacy}, A., {Greif}, T.~H., \& {Bromm}, V. 2010, \mnras, 403, 45
+
+\bibitem[{{Strigari} {et~al.}(2008){Strigari}, {Bullock}, {Kaplinghat},
+  {Simon}, {Geha}, {Willman}, \& {Walker}}]{Strigari08}
+{Strigari}, L.~E., {Bullock}, J.~S., {Kaplinghat}, M., {Simon}, J.~D., {Geha},
+  M., {Willman}, B., \& {Walker}, M.~G. 2008, \nat, 454, 1096
+
+\bibitem[{{Tafelmeyer} {et~al.}(2010){Tafelmeyer}, {Jablonka}, {Hill},
+  {Shetrone}, {Tolstoy}, {Irwin}, {Battaglia}, {Helmi}, {Starkenburg}, {Venn},
+  {Abel}, {Francois}, {Kaufer}, {North}, {Primas}, \&
+  {Szeifert}}]{Tafelmeyer10}
+{Tafelmeyer}, M., {Jablonka}, P., {Hill}, V., {Shetrone}, M., {Tolstoy}, E.,
+  {Irwin}, M.~J., {Battaglia}, G., {Helmi}, A., {Starkenburg}, E., {Venn},
+  K.~A., {Abel}, T., {Francois}, P., {Kaufer}, A., {North}, P., {Primas}, F.,
+  \& {Szeifert}, T. 2010, \aap, 524, A58+
+
+\bibitem[{{Tan} {et~al.}(2006){Tan}, {Krumholz}, \& {McKee}}]{Tan06}
+{Tan}, J.~C., {Krumholz}, M.~R., \& {McKee}, C.~F. 2006, \apjl, 641, L121
+
+\bibitem[{{Tornatore} {et~al.}(2007){Tornatore}, {Ferrara}, \&
+  {Schneider}}]{Tornatore07}
+{Tornatore}, L., {Ferrara}, A., \& {Schneider}, R. 2007, \mnras, 382, 945
+
+\bibitem[{Toro {et~al.}(1994)Toro, Spruce, \& Speares}]{Toro94_HLLC}
+Toro, E.~F., Spruce, M., \& Speares, W. 1994, Shock Waves, 4, 25,
+  10.1007/BF01414629
+
+\bibitem[{{Trenti} \& {Shull}(2010)}]{Trenti10}
+{Trenti}, M., \& {Shull}, J.~M. 2010, \apj, 712, 435
+
+\bibitem[{{Trenti} {et~al.}(2009){Trenti}, {Stiavelli}, \& {Shull}}]{Trenti09}
+{Trenti}, M., {Stiavelli}, M., \& {Shull}, J.~M. 2009, \apj, 700, 1672
+
+\bibitem[{{Truelove} {et~al.}(1997){Truelove}, {Klein}, {McKee}, {Holliman},
+  {Howell}, \& {Greenough}}]{Truelove97}
+{Truelove}, J.~K., {Klein}, R.~I., {McKee}, C.~F., {Holliman}, II, J.~H.,
+  {Howell}, L.~H., \& {Greenough}, J.~A. 1997, \apjl, 489, L179+
+
+\bibitem[{{Tseliakhovich} {et~al.}(2011){Tseliakhovich}, {Barkana}, \&
+  {Hirata}}]{Tselia10_Minihalo}
+{Tseliakhovich}, D., {Barkana}, R., \& {Hirata}, C.~M. 2011, \mnras, 1501
+
+\bibitem[{{Tseliakhovich} \& {Hirata}(2010)}]{Tselia10}
+{Tseliakhovich}, D., \& {Hirata}, C. 2010, \prd, 82, 083520
+
+\bibitem[{{Tumlinson}(2006)}]{Tumlinson06}
+{Tumlinson}, J. 2006, \apj, 641, 1
+
+\bibitem[{{Tumlinson}(2007)}]{Tumlinson07_IMF}
+---. 2007, \apjl, 664, L63
+
+\bibitem[{{Tumlinson}(2010)}]{Tumlinson10}
+---. 2010, \apj, 708, 1398
+
+\bibitem[{{Turk} {et~al.}(2009){Turk}, {Abel}, \&
+  {O'Shea}}]{2009Sci...325..601T}
+{Turk}, M.~J., {Abel}, T., \& {O'Shea}, B. 2009, Science, 325, 601
+
+\bibitem[{{Turk} {et~al.}(2011){Turk}, {Smith}, {Oishi}, {Skory}, {Skillman},
+  {Abel}, \& {Norman}}]{yt_full_paper}
+{Turk}, M.~J., {Smith}, B.~D., {Oishi}, J.~S., {Skory}, S., {Skillman}, S.~W.,
+  {Abel}, T., \& {Norman}, M.~L. 2011, \apjs, 192, 9
+
+\bibitem[{{Whalen} {et~al.}(2004){Whalen}, {Abel}, \& {Norman}}]{Whalen04}
+{Whalen}, D., {Abel}, T., \& {Norman}, M.~L. 2004, \apj, 610, 14
+
+\bibitem[{{Whalen} {et~al.}(2008){Whalen}, {van Veelen}, {O'Shea}, \&
+  {Norman}}]{Whalen08_SN}
+{Whalen}, D., {van Veelen}, B., {O'Shea}, B.~W., \& {Norman}, M.~L. 2008, \apj,
+  682, 49
+
+\bibitem[{{Wise} \& {Abel}(2007)}]{Wise07}
+{Wise}, J.~H., \& {Abel}, T. 2007, \apj, 665, 899
+
+\bibitem[{{Wise} \& {Abel}(2008)}]{Wise08_Gal}
+---. 2008, \apj, 685, 40
+
+\bibitem[{{Wise} \& {Abel}(2011)}]{Wise11_Moray}
+---. 2011, \mnras, 414, 3458
+
+\bibitem[{{Wise} \& {Cen}(2009)}]{Wise09}
+{Wise}, J.~H., \& {Cen}, R. 2009, \apj, 693, 984
+
+\bibitem[{{Wolcott-Green} {et~al.}(2011){Wolcott-Green}, {Haiman}, \&
+  {Bryan}}]{Wolcott11}
+{Wolcott-Green}, J., {Haiman}, Z., \& {Bryan}, G.~L. 2011, \mnras, 1673
+
+\bibitem[{{Wolfe} {et~al.}(2005){Wolfe}, {Gawiser}, \&
+  {Prochaska}}]{Wolfe05_Review}
+{Wolfe}, A.~M., {Gawiser}, E., \& {Prochaska}, J.~X. 2005, \araa, 43, 861
+
+\bibitem[{{Woodward} \& {Colella}(1984)}]{Woodward84}
+{Woodward}, P., \& {Colella}, P. 1984, Journal of Computational Physics, 54,
+  115
+
+\bibitem[{{Woosley} \& {Weaver}(1995)}]{Woosley95}
+{Woosley}, S.~E., \& {Weaver}, T.~A. 1995, \apjs, 101, 181
+
+\bibitem[{{Yajima} {et~al.}(2011){Yajima}, {Choi}, \& {Nagamine}}]{Yajima11}
+{Yajima}, H., {Choi}, J.-H., \& {Nagamine}, K. 2011, \mnras, 412, 411
+
+\bibitem[{{Yoshida} {et~al.}(2003){Yoshida}, {Abel}, {Hernquist}, \&
+  {Sugiyama}}]{Yoshida03}
+{Yoshida}, N., {Abel}, T., {Hernquist}, L., \& {Sugiyama}, N. 2003, \apj, 592,
+  645
+
+\bibitem[{{Yoshida} {et~al.}(2004){Yoshida}, {Bromm}, \&
+  {Hernquist}}]{Yoshida04}
+{Yoshida}, N., {Bromm}, V., \& {Hernquist}, L. 2004, \apj, 605, 579
+
+\bibitem[{{Yoshida} {et~al.}(2007){Yoshida}, {Oh}, {Kitayama}, \&
+  {Hernquist}}]{Yoshida07_HII}
+{Yoshida}, N., {Oh}, S.~P., {Kitayama}, T., \& {Hernquist}, L. 2007, \apj, 663,
+  687
+
+\bibitem[{{Yoshida} {et~al.}(2008){Yoshida}, {Omukai}, \&
+  {Hernquist}}]{Yoshida08}
+{Yoshida}, N., {Omukai}, K., \& {Hernquist}, L. 2008, Science, 321, 669
+
+\bibitem[{{Zahn} {et~al.}(2011){Zahn}, {Mesinger}, {McQuinn}, {Trac}, {Cen}, \&
+  {Hernquist}}]{Zahn11}
+{Zahn}, O., {Mesinger}, A., {McQuinn}, M., {Trac}, H., {Cen}, R., \&
+  {Hernquist}, L.~E. 2011, \mnras, 414, 727
+
+\end{thebibliography}
 

### 2011-11-30 ApJ/ms_2c.tex
Updating emulateapj version with the accepted version.

@@
 
-Simulations have shown that the characteristic mass of Pop III stars
-$M_{\rm char} \sim 100~\Ms$ \citep{ABN02, Bromm02_P3, OShea07a,
-  Yoshida08}.  They form in molecular clouds that coexist with the
-dark matter halo center with limited fragmentation occurring during
-their collapse; however \citet{2009Sci...325..601T} and
-\citet{Stacy10_Binary} have shown that Pop III binaries may form in a
-fraction of such halos.  There have been some recent hints that the
-accretion disk around the first protostar may fragment and produce
-clustered Pop III star formation \citep{Clark11_Frag,
-  Greif11_P3Cluster}.  The final stellar masses in the aforementioned
-calculations are still highly uncertain with a limited number of
-samples.  Nevertheless, they all point toward an IMF with a larger
-characteristic mass than present-day star formation.
+\subsubsection{Population III star formation}
+
+Simulations following the full accretion history of Pop III stars,
+from their formation inside cosmological minihalos through
+transitioning onto the main sequence, are not currently possible.
+However, under the assumption of spherical accretion, reasonable
+estimates of the mass ranges for Pop III stars can be made by
+extrapolating forward in time the instantaneous accretion rate at the
+time of formation of the first protostellar core and comparing the
+timescales for accretion against the Kelvin-Helmholtz time.  Several
+studies, conducting this extrapolation, have shown that the
+characteristic mass of Pop III stars $M_{\rm char} \sim 100~\Ms$
+\citep{ABN02, Bromm02_P3, OShea07a, Yoshida08}.  They form in
+molecular clouds that coexist with the dark matter halo center with
+limited fragmentation occurring during their collapse; however
+\citet{2009Sci...325..601T} and \citet{Stacy10_Binary} have shown that
+Pop III binaries may form in a fraction of such halos.  There have
+been some recent hints that the accretion disk around the first
+protostar may fragment and produce clustered Pop III star formation
+\citep{Clark11_Frag, Greif11_P3Cluster}.  The final stellar masses in
+the aforementioned calculations are still highly uncertain with a
+limited number of samples.  Nevertheless, they all point toward an IMF
+with a larger characteristic mass than present-day star formation.
 
@@
 
+After the star particle forms and its mass is randomly sampled from
+the IMF, an equal amount of gas is removed from the computational grid
+in a sphere that contains twice the stellar mass and is centered on
+the star particle.  The star particle acquires the mass-weighted
+velocity of the gas contained in this sphere.
+
 %%% FOR THE COMPARISON BETWEEN RUNS WITH AND WITHOUT METAL COOLING %%%
@@
 stellar mass.  If the stellar mass is outside of these ranges, then an
-inert, collisionless black hole (BH) particle is created.
-
-The blastwave is modeled by injecting the explosion energy and ejecta
-mass into a sphere of 10 pc, smoothed at its surface to improve
-numerical stability \citep{Wise08_Gal}.  Because we resolve the
-blastwave relatively well with several cells across at its
-initialization, the thermal energy is converted into kinetic energy
-and agrees with the Sedov-Taylor solution \citep[e.g.][]{Greif07}.
+inert, collisionless black hole (BH) particle is created.  The
+blastwave is modeled by injecting the explosion energy and ejecta mass
+into a sphere of 10 pc, smoothed at its surface to improve numerical
+stability \citep{Wise08_Gal}.  Because we resolve the blastwave
+relatively well with several cells across at its initialization, the
+thermal energy is converted into kinetic energy and agrees with the
+Sedov-Taylor solution \citep[e.g.][]{Greif07}.
+
+\subsubsection{Population II star formation}
 
@@
 
-\input{table1.tex}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+\epsscale{1.15}
+\plotone{f1}
+\epsscale{1}
+  \caption{\label{fig:evo-mosaic} Evolution of the entire simulation
+    volume ($L_{\rm box} = 1$ Mpc) at redshifts 15, 12, 10, 8, and 7
+    (left to right).  Pictured here are the density-weighted
+    projections of density (top), temperature (middle), and
+    metallicity (bottom).  Note how the stellar radiative feedback
+    from low-mass galaxies reionize the majority of the volume.  The
+    metallicity projections are a composite image of metals
+    originating from Pop II (red) and III (blue) stars with magenta
+    indicating a mixture of the two.}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+\epsscale{1.15}
+\plotone{f3}
+\epsscale{1}
+\caption{\label{fig:sfr} Cosmic star formation rates for Pop II
+  (solid) and III (dashed).  Note that the Pop III rates are nearly
+  constant from redshift 12 to 7.  Pristine halos still survive in
+  underdense regions, supporting late-time metal-free star formation.}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Figure \ref{fig:sfr} shows the cosmic SFR in the simulation for Pop II
@@
 
-In the case where this metallicity floor is less than the critical
-metallicity, then the next SN will further enrich the ISM, solidifying
-the transition to Pop II SF.  We conclude that it only takes one, at
-most two, SNe from Pop III stars in the halo progenitors to complete
-the transition to Population II \citep{Frebel10}.  However, this does
-not prohibit more than two instances of Pop III star formation in halo
-from happening because the stars can end in a direct collapse to a BH
-with little or no metal ejecta, keeping the surrounding environment
-pristine.  The question of whether the critical metallicity is
-\tento{-6} or \tento{-3.5} $Z_\odot$ is most applicable to nearby
-halos where the heavy elements mix slowly into dense cores as the
-blastwave overtakes it.  Less than two percent of stars have [Z/H] $<
--3$ in both systems, consistent with observations of metal-poor stars
-in the halo and dSphs \citep{Beers05, Battaglia11}.
+Building upon this idea of a lower metallicity floor, consider a
+pre-galactic halo that has hosted a Pop III star, producing a SN.  The
+majority of the gas is ejected into the IGM and re-accretes after
+$\sim 10-50$ Myr \citep{Johnson07, Wise08_Gal}.  What happens if the
+metallicity is not greater than the critical metallicity?  Massive Pop
+III stars would form again in this halo; however, enriching the
+surrounding IGM with Pop III SNe and ejecting material becomes more
+difficult in halos with $M \gsim 10^7 \Ms$ \citep{Whalen08_SN}.  Thus
+it is more likely for these halos to retain more of its gas during
+star formation episodes and self-enrich its host halo and less of the
+IGM.  This would accelerate the transition from Pop III to II in more
+massive halos.
+
+We conclude that it only takes one, at most two, SNe from Pop III
+stars in the halo progenitors to complete the transition to Population
+II \citep{Frebel10}.  However, this does not prohibit more than two
+instances of Pop III star formation in halo from happening because the
+stars can produce BHs with little or no metal ejecta, keeping the
+surrounding environment pristine.  Even though we find that Pop III
+SNe create a floor of $\sim 10^{-3} \zsun$, gas with lower
+metallicities can still exists in nearby halos, where the metal-rich
+SN ejecta will mix slowly into dense cores as the blastwave overtakes
+them \citep{Cen08}.  These environments may be the host of true
+extremely metal-poor star formation, such as the recently discovered
+halo star with all detected metals below $10^{-4.2} \zsun$
+\citep{Caffau11}.
 
@@
 JHW thanks Renyue Cen, Amina Helmi, Marco Spaans, and Eline Tolstoy
-for enlightening discussions.  JHW is partially supported by NASA
-through Hubble Fellowship grant \#120-6370 awarded by the Space
-Telescope Science Institute, which is operated by the Association of
+for enlightening discussions.  We thank an anonymous referee for
+helpful suggestions.  JHW is partially supported by NASA through
+Hubble Fellowship grant \#120-6370 awarded by the Space Telescope
+Science Institute, which is operated by the Association of
 Universities for Research in Astronomy, Inc., for NASA, under contract
 NAS 5-26555.  MJT and MLN acknowledge partial support from NASA ATFP
-grant NNX08AH26G.  Computational resources were provided by NASA/NCCS
-award SMD-09-1439.  TA acknowledges financial support from the {\em
-  Baden-W\"{u}rttemberg-Stiftung} under grant P-LS-SPII/18, the
-Heidelberg Institut f\"ur Theoretische Studien. This work was
-partially supported by NASA ATFP grant NNX08AH26G, NSF AST-0807312,
-and NSF AST-1109243. This research has made use of NASA’s Astrophysics
-Data System Bibliographic Services.  The majority of the analysis and
-plots were done with \texttt{yt} \citep{yt_full_paper}.
+grant NNX08AH26G.  MJT~acknowledges support by the NSF CI TraCS
+fellowship award OCI-1048505.  Computational resources were provided
+by NASA/NCCS award SMD-09-1439.  TA acknowledges financial support
+from the {\em Baden-W\"{u}rttemberg-Stiftung} under grant
+P-LS-SPII/18, the Heidelberg Institut f\"ur Theoretische Studien. This
+work was partially supported by NASA ATFP grant NNX08AH26G, NSF
+AST-0807312, and NSF AST-1109243. This research has made use of NASA’s
+Astrophysics Data System Bibliographic Services.  The majority of the
+analysis and plots were done with \texttt{yt} \citep{yt_full_paper}.
 
 %\clearpage
-\begin{thebibliography}{101}
+%\bibliography{ms}
+\begin{thebibliography}{108}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
@@
 
-\bibitem[{{Bovill} \& {Ricotti}(2010{\natexlab{a}})}]{Bovill11a}
-{Bovill}, M.~S., \& {Ricotti}, M. 2010{\natexlab{a}}, ArXiv e-prints
-  (1010.2231)
-
-\bibitem[{{Bovill} \& {Ricotti}(2010{\natexlab{b}})}]{Bovill11b}
----. 2010{\natexlab{b}}, ArXiv e-prints (1010.2233)
+\bibitem[{{Bovill} \& {Ricotti}(2011{\natexlab{a}})}]{Bovill11a}
+{Bovill}, M.~S., \& {Ricotti}, M. 2011{\natexlab{a}}, \apj, 741, 17
+
+\bibitem[{{Bovill} \& {Ricotti}(2011{\natexlab{b}})}]{Bovill11b}
+---. 2011{\natexlab{b}}, \apj, 741, 18
 
@@
 
+\bibitem[{{Caffau} {et~al.}(2011){Caffau}, {Bonifacio}, {Fran{\c c}ois},
+  {Sbordone}, {Monaco}, {Spite}, {Spite}, {Ludwig}, {Cayrel}, {Zaggia},
+  {Hammer}, {Randich}, {Molaro}, \& {Hill}}]{Caffau11}
+{Caffau}, E., {Bonifacio}, P., {Fran{\c c}ois}, P., {Sbordone}, L., {Monaco},
+  L., {Spite}, M., {Spite}, F., {Ludwig}, H.-G., {Cayrel}, R., {Zaggia}, S.,
+  {Hammer}, F., {Randich}, S., {Molaro}, P., \& {Hill}, V. 2011, \nat, 477, 67
+
 \bibitem[{{Cen} \& {Ostriker}(1992)}]{Cen92}
@@
 {Gnedin}, N.~Y., \& {Hui}, L. 1998, \mnras, 296, 44
-
-\bibitem[{{Gnedin} \& {Kravtsov}(2006)}]{Gnedin06}
-{Gnedin}, N.~Y., \& {Kravtsov}, A.~V. 2006, \apj, 645, 1054
 
@@
 
+\bibitem[{{Johnson} {et~al.}(2007){Johnson}, {Greif}, \& {Bromm}}]{Johnson07}
+{Johnson}, J.~L., {Greif}, T.~H., \& {Bromm}, V. 2007, \apj, 665, 85
+
 \bibitem[{{Karlsson} {et~al.}(2008){Karlsson}, {Johnson}, \&
@@
 
+\bibitem[{{Martin} {et~al.}(2008){Martin}, {de Jong}, \& {Rix}}]{Martin08_uFd}
+{Martin}, N.~F., {de Jong}, J.~T.~A., \& {Rix}, H.-W. 2008, \apj, 684, 1075
+
 \bibitem[{Matsumoto \& Nishimura(1998)}]{MTwister}
@@
 
+\bibitem[{{Paardekooper} {et~al.}(2011){Paardekooper}, {Pelupessy}, {Altay}, \&
+  {Kruip}}]{Paardekooper11}
+{Paardekooper}, J.-P., {Pelupessy}, F.~I., {Altay}, G., \& {Kruip}, C.~J.~H.
+  2011, \aap, 530, A87
+
 \bibitem[{{Penprase} {et~al.}(2010){Penprase}, {Prochaska}, {Sargent},
@@
   I., \& {Beeler}, D.~J. 2010, \apj, 721, 1
+
+\bibitem[{{Razoumov} \& {Sommer-Larsen}(2010)}]{Razoumov10}
+{Razoumov}, A.~O., \& {Sommer-Larsen}, J. 2010, \apj, 710, 1239
 
@@
   M.~L. 2009, \apj, 691, 441
+
+\bibitem[{{Springel} \& {Hernquist}(2003)}]{Springel03b}
+{Springel}, V., \& {Hernquist}, L. 2003, \mnras, 339, 289
 
@@
 
-\bibitem[{{Tseliakhovich} {et~al.}(2010){Tseliakhovich}, {Barkana}, \&
+\bibitem[{{Tseliakhovich} {et~al.}(2011){Tseliakhovich}, {Barkana}, \&
   {Hirata}}]{Tselia10_Minihalo}
-{Tseliakhovich}, D., {Barkana}, R., \& {Hirata}, C. 2010, ArXiv e-prints
+{Tseliakhovich}, D., {Barkana}, R., \& {Hirata}, C.~M. 2011, \mnras, 1501
 
@@
 
+\bibitem[{{Whalen} {et~al.}(2008){Whalen}, {van Veelen}, {O'Shea}, \&
+  {Norman}}]{Whalen08_SN}
+{Whalen}, D., {van Veelen}, B., {O'Shea}, B.~W., \& {Norman}, M.~L. 2008, \apj,
+  682, 49
+
 \bibitem[{{Wise} \& {Abel}(2007)}]{Wise07}
@@
   {Bryan}}]{Wolcott11}
-{Wolcott-Green}, J., {Haiman}, Z., \& {Bryan}, G.~L. 2011, ArXiv e-prints
+{Wolcott-Green}, J., {Haiman}, Z., \& {Bryan}, G.~L. 2011, \mnras, 1673
 
@@
 {Woosley}, S.~E., \& {Weaver}, T.~A. 1995, \apjs, 101, 181
+
+\bibitem[{{Yajima} {et~al.}(2011){Yajima}, {Choi}, \& {Nagamine}}]{Yajima11}
+{Yajima}, H., {Choi}, J.-H., \& {Nagamine}, K. 2011, \mnras, 412, 411
 
